### 2015-04-15 paper/ms.tex
paper template

%Document Class
\documentclass{latex/emulateapj}
\usepackage{multirow,color,wrapfig,ulem}

%Packages and Commands
\include{latex/packages_commands}

\begin{document}

\title{Titulo}
\shorttitle{shorttitle}

\shortauthors{shortauthors}

\author{author1, author2 \& author3} 
\affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
No. 18A-10, Edificio Ip, Bogot\'a, Colombia}

\email{email1}
\email{email2}
\email{email3}

\keywords{keywords....}

\begin{abstract}

Abstract...

\end{abstract}

\section{Introduction}
\label{sec:intro}

Introduction... \\

\section{Theoretical Background}
\label{sec:theo}

Theoretical background...\\

\section{Results}
\label{sec:results}

Results...\\

\section{Discussion}
\label{sec:discussion}

Discussion...\\

\section{Conclusions}
\label{sec:conclusions}

Conclusions...\\

\section*{Acknowledgments}

Acknowledgments...\\

\bibliographystyle{latex/apj}
\bibliography{references}

\newpage

### 2015-04-16 code/mc.py
threads added

@@ -114,14 +114,14 @@ def lnprob(param, x_d, y_d):
 #Running emcee
 
 ndim = 5
-nwalkers = 20
+nwalkers = 10
 nsteps = 100
 
 first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0]
 
 pos = [first_guess+ 1e-3*random.randn(ndim) for i in range(nwalkers)]
 
-sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data))
+sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data), threads=8)
 
 print("Running MCMC...")
 sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())

### 2015-04-16 code/mc_no_mplt.py

@@ -96,14 +96,14 @@ def lnprob(param, x_d, y_d):
 #Running emcee
 
 ndim = 5
-nwalkers = 20
+nwalkers = 10
 nsteps = 100
 
 first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0]
 
 pos = [first_guess+ 1e-3*random.randn(ndim) for i in range(nwalkers)]
 
-sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data))
+sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data), threads=8)
 
 print("Running MCMC...")
 sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())

### 2015-04-16 code/mc_no_mplt.py
first try with 10 steps

@@ -97,7 +97,7 @@ def lnprob(param, x_d, y_d):
 
 ndim = 5
 nwalkers = 10
-nsteps = 100
+nsteps = 10
 
 first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0]
 

### 2015-04-17 code/mc.py
two different scripts, one does the mcmc, the other plots

@@ -1,10 +1,6 @@
 from numpy import *
-import matplotlib
-matplotlib.use('Agg') 
-from matplotlib.pyplot import *
 from scipy.interpolate import interp1d
 import emcee
-import triangle
 import os
 
 #Constants
@@ -34,7 +30,7 @@ def model(logtau, vmax, theta, logT, voff, x_d, y_d):
 
     os.system( ('./analytic_solution.x %f %f %f > "./model.dat"')%(10.0**logtau, vmax, theta) )
 
-    mod = loadtxt('./model.dat')
+    mod = genfromtxt('./model.dat', skip_footer=1)
 
     x_m_i = mod[:,0]
     y_m_i = mod[:,1]
@@ -65,20 +61,6 @@ logT_0 = 4
 voff_0 = -11
 
 x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, voff_0, x_data, y_data)
-
-#Plot data and first guess
-
-fig = figure(figsize=(12,6))
-
-scatter(x_data, y_data, c='c', alpha=0.6, label='$\mathrm{LARS 02}$')
-plot(x_data, y_data, c='c', alpha=0.6)
-plot(x_0, y_0, c='b', alpha=0.6, label='$\mathrm{Rotation\ model}$', lw=2)
-
-xlabel('$\mathrm{Velocity (km/s)}$', fontsize=20)
-ylabel('$\mathrm{Intensity (Arbitrary Units)}$', fontsize=20)
-legend(loc='best', fontsize=20)
-
-savefig('./first_guess.png')
 
 #emcee functions
 
@@ -115,7 +97,7 @@ def lnprob(param, x_d, y_d):
 
 ndim = 5
 nwalkers = 10
-nsteps = 100
+nsteps = 10
 
 first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0]
 
@@ -128,56 +110,13 @@ sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())
 print("Done!")
 
 
-# Walkers plot
+# Saving results
 
-clf()
+samples_fc = sampler.flatchain
 
-fig, axes = subplots(5, 1, sharex=True, figsize=(12, 13))
-
-axes[0].plot(sampler.chain[:, :, 0].T, color="k", alpha=0.4)
-axes[0].yaxis.set_major_locator(MaxNLocator(5))
-axes[0].axhline(logtau_0, color="#888888", lw=2)
[…]

### 2015-04-17 code/plots.py

@@ -1,0 +1,120 @@
+from numpy import *
+from matplotlib.pyplot import *
+from scipy.interpolate import interp1d
+import triangle
+import os
+
+#Info
+nwalkers = 10
+nsteps = 100
+nparameters = 5
+
+z = 0.029836
+c = 299792.458
+
+#Best parameters
+logtau_b = 5
+vmax_b = 50
+theta_b = 45
+logT_b = 4
+voff_b = -11
+
+#Functions
+def model_to_data_interp(x_m, y_m, x_d):
+
+    f = interp1d(x_m, y_m, kind="linear")
+    x_m_new = x_d
+    y_m_new = f(x_d)
+
+    return x_m_new, y_m_new
+
+def normalization(y_d, y_m):
+
+    obs_int = sum(y_d)
+    teo_int = sum(y_m)
+    y_m = y_m*obs_int/teo_int
+
+    return y_m
+
+def model(logtau, vmax, theta, logT, voff, x_d, y_d):
+
+    os.system( ('./analytic_solution.x %f %f %f > "./model.dat"')%(10.0**logtau, vmax, theta) )
+
+    mod = genfromtxt('./model.dat', skip_footer=1)
+
+    x_m_i = mod[:,0]
+    y_m_i = mod[:,1]
+
+    v_th = 12.85*sqrt((10.0**logT)/(10.0**4.0))
+    x_m_i = x_m_i*v_th + voff
+
+    x_m, y_m = model_to_data_interp(x_m_i, y_m_i, x_d)
+
+    y_m = normalization(y_d, y_m)
+
+    return x_m, y_m
+
+#Data
+lars = loadtxt('./LARS02.txt')
+samples = loadtxt('./sampler_flatchain.dat', delimiter=',')
+
+x_data = lars[:-17,0] - c*z
+y_data = lars[:-17,1]
+
+x_model, y_model = model(logtau_b, vmax_b, theta_b, logT_b, voff_b, x_data, y_data)
+
+#Plot fit and original
+fig = figure(figsize=(12,6))
+
+scatter(x_data, y_data, c='c', alpha=0.6, label='$\mathrm{LARS 02}$')
+plot(x_data, y_data, c='c', alpha=0.6)
+plot(x_model, y_model, c='b', alpha=0.6, label='$\mathrm{Rotation\ model}$', lw=2)
+
+xlabel('$\mathrm{Velocity (km/s)}$', fontsize=20)
[…]

### 2015-04-17 code/mc_no_mplt.py
Delete mc_no_mplt.py

@@ -1,124 +1,0 @@
-from numpy import *
-from scipy.interpolate import interp1d
-import emcee
-import os
-
-#Constants
-
-z = 0.029836
-c = 299792.458
-
-#Functions
-
-def model_to_data_interp(x_m, y_m, x_d):
-
-    f = interp1d(x_m, y_m, kind="linear")
-    x_m_new = x_d
-    y_m_new = f(x_d)
-
-    return x_m_new, y_m_new
-
-def normalization(y_d, y_m):
-
-    obs_int = sum(y_d)
-    teo_int = sum(y_m)
-    y_m = y_m*obs_int/teo_int
-
-    return y_m
-
-def model(logtau, vmax, theta, logT, voff, x_d, y_d):
-
-    os.system( ('./analytic_solution.x %f %f %f > "./model.dat"')%(10.0**logtau, vmax, theta) )
-
-    mod = loadtxt('./model.dat')
-
-    x_m_i = mod[:,0]
-    y_m_i = mod[:,1]
-
-    v_th = 12.85*sqrt((10.0**logT)/(10.0**4.0))
-    x_m_i = x_m_i*v_th + voff
-
-    x_m, y_m = model_to_data_interp(x_m_i, y_m_i, x_d)
-
-    y_m = normalization(y_d, y_m)
-
-    return x_m, y_m
-
-
-#Observed data
-
-lars = loadtxt('./LARS02.txt')
-
-x_data = lars[:-17,0] - c*z
-y_data = lars[:-17,1]
-
-#First guess
-
-logtau_0 = 5
-vmax_0 = 50
-theta_0 = 45
-logT_0 = 4
-voff_0 = -11
-
-x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, voff_0, x_data, y_data)
-
-#emcee functions
-
-def lnprior(param):
-
-    logtau, vmax, theta, logT, voff = param
-
-    if 4 < logtau < 6 and 0 < vmax < 100 and 0 < theta < 90 and 4 < logT < 4.5 and -20 < voff < 20:
-        return 0.0
-
-    return -inf
-
-
-def lnlike(param, x_d, y_d):
-
-    logtau, vmax, theta, logT, voff = param
-
-    x_m, y_m = model(logtau, vmax, theta, logT, voff, x_d, y_d)
-
-    chi_squared = (1.0/2.0)*sum((y_d-y_m)**2)
-
-    return -chi_squared
-
-
-def lnprob(param, x_d, y_d):
-
[…]

### 2015-04-17 paper/ms.tex
basic format and text

@@
-%Document Class
-\documentclass{latex/emulateapj}
+\documentclass{emulateapj}
+\submitted{{\it Submitted for publication in ApJ Letters}}
 \usepackage{multirow,color,wrapfig,ulem}
-
-%Packages and Commands
-\include{latex/packages_commands}
-
+\usepackage {graphicx}
+\usepackage{graphics}
+\usepackage[dvips]{epsfig}
+\newcommand{\avg}[1]{\langle{#1}\rangle}  
+\newcommand{\nscatt}{\langle N_{\rm  scatt}\rangle}
+\newcommand{\ly}{{\ifmmode{{\rm Ly}\alpha~}\else{Ly$\alpha$~}\fi}}
+\newcommand{\hMpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}   
+\newcommand{\hGpc}{{\ifmmode{h^{-1}{\rm Gpc}}\else{$h^{-1}$Gpc }\fi}}   
+\newcommand{\hmpc}{{\ifmmode{h^{-1}{\rm Mpc}}\else{$h^{-1}$Mpc }\fi}}  
+\newcommand{\hkpc}{{\ifmmode{h^{-1}{\rm kpc}}\else{$h^{-1}$kpc }\fi}}  
+\newcommand{\hMsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
+\newcommand{\hmsun}{{\ifmmode{h^{-1}{\rm
+        {M_{\odot}}}}\else{$h^{-1}{\rm{M_{\odot}}}$}\fi}}   
+\newcommand{\Msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\msun}{{\ifmmode{{\rm {M_{\odot}}}}\else{${\rm{M_{\odot}}}$}\fi}}  
+\newcommand{\lya}{{Lyman $\alpha$~}}
+\newcommand{\clara}{{\texttt{CLARA}}~}
+\newcommand{\rand}{{\ifmmode{{\mathcal{R}}}\else{${\mathcal{R}}$ }\fi}}  
+\newcommand{\hs}{{\hspace{1mm}}}  
+\newcommand{\kms}{{\ifmmode{{\mathrm{\,km\ s}^{-1}}}\else{\,km~s$^{-1}$}\fi}}
+% definition to produce a "less than or similar to" symbol
+\def\lsim{~\rlap{$<$}{\lower 1.0ex\hbox{$\sim$}}}
+% definition to produce a "greater than or similar to" symbol
+\def\gsim{~\rlap{$>$}{\lower 1.0ex\hbox{$\sim$}}}
+%@arxiver{fig3.pdf,fig11a.pdf, fig11b.pdf} 
 \begin{document}
 
-\title{Titulo}
-\shorttitle{shorttitle}
+\title{First estimate of a galaxy rotational velocity from
+  its observed Lyman-$\alpha$ line} 
+\shorttitle{Rotational velocity from the Lyman $\alpha$ line}
 
-\shortauthors{shortauthors}
+\shortauthors{Remolina-Gutierrez, Garavito-Camargo, Forero-Romero}
 
-\author{author1, author2 \& author3} 
+\author{ Maria C. Remolina-Gutierrez, Juan N. Garavito-Camargo, Jaime
+  E. Forero-Romero}  
 \affil{Departamento de F\'{i}sica, Universidad de los Andes, Cra. 1
 No. 18A-10, Edificio Ip, Bogot\'a, Colombia}
+\email{mc.remolina197@uniandes.edu.co}
+\email{jn.garavito57@uniandes.edu.co}
+\email{je.forero@uniandes.edu.co}
 
-\email{email1}
-\email{email2}
-\email{email3}
-
-\keywords{keywords....}
-
+\keywords{galaxies: high-redshift --- line: formation --- methods:
+  numerical ---  radiative transfer} 
 \begin{abstract}
-
-Abstract...
-
+First.
 \end{abstract}
@@
 Introduction... \\ 
+\cite{Garavito14}
 
@@
 \label{sec:results}
+
+\begin{figure}
+\begin{center}
+  \includegraphics[width=0.5\textwidth]{mcmc.png}
+\end{center}
+\caption{
+    \label{fig:mcmc_result}}  
+\end{figure}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.7\textwidth]{parameters.png}
+\end{center}
+\caption{
+    \label{fig:mcmc_triangle}}  
+\end{figure*}
 
@@
 
-\bibliographystyle{latex/apj}
+\bibliographystyle{apj}
 \bibliography{references}
 
-\newpage
+\end{document}

### 2015-04-18 code/mc.py
test with likelihood

@@ -52,16 +52,6 @@ lars = loadtxt('./LARS02.txt')
 x_data = lars[:-17,0] - c*z
 y_data = lars[:-17,1]
 
-#First guess
-
-logtau_0 = 5
-vmax_0 = 50
-theta_0 = 45
-logT_0 = 4
-voff_0 = -11
-
-x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, voff_0, x_data, y_data)
-
 #emcee functions
 
 def lnprior(param):
@@ -93,13 +83,27 @@ def lnprob(param, x_d, y_d):
 
     return lp + lnlike(param, x_d, y_d)
 
+
+#First guess
+
+logtau_0 = 5
+vmax_0 = 50
+theta_0 = 45
+logT_0 = 4
+voff_0 = -11
+
+x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, voff_0, x_data, y_data)
+
+lnlikelihood_0 = lnlike([logtau_0, vmax_0, theta_0, logT_0, voff_0], x_0, y_0)
+
+first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0, lnlikelihood_0]
+
+
 #Running emcee
 
-ndim = 5
-nwalkers = 10
-nsteps = 10
-
-first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0]
+ndim = 6
+nwalkers = 12
+nsteps = 2
 
 pos = [first_guess+ 1e-3*random.randn(ndim) for i in range(nwalkers)]
 

### 2015-04-20 code/mc.py
fixing interpolation mistake

@@ -13,10 +13,31 @@ c = 299792.458
 def model_to_data_interp(x_m, y_m, x_d):
 
     f = interp1d(x_m, y_m, kind="linear")
-    x_m_new = x_d
-    y_m_new = f(x_d)
 
-    return x_m_new, y_m_new
+    try:
+        x_m_new = x_d
+        y_m_new = f(x_d)
+
+        return x_m_new, y_m_new
+
+    except ValueError:
+
+        n = len(x_d)
+
+        x_m_new = x_d
+        y_m_new = zeros(n)
+
+        for i in range(n):
+
+            x_d_i = x_d[i]
+
+            if(x_d_i >= x_m[0] and x_d_i <= x_m[-1]):
+                y_m_new[i] = f(x_d_i)
+            else:
+                y_m_new[i] = 0.0
+
+        return x_m_new, y_m_new
+
 
 def normalization(y_d, y_m):
 
@@ -66,6 +87,8 @@ def lnprior(param):
 
 def lnlike(param, x_d, y_d):
 
+    print(param)
+
     logtau, vmax, theta, logT, voff = param
 
     x_m, y_m = model(logtau, vmax, theta, logT, voff, x_d, y_d)
@@ -94,7 +117,7 @@ voff_0 = -11
 
 x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, voff_0, x_data, y_data)
 
-lnlikelihood_0 = lnlike([logtau_0, vmax_0, theta_0, logT_0, voff_0], x_0, y_0)
+lnlikelihood_0 = lnlike(array([logtau_0, vmax_0, theta_0, logT_0, voff_0]), x_0, y_0)
 
 first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0, lnlikelihood_0]
 

### 2015-04-20 code/mc.py
didnt erase some things

@@ -87,8 +87,6 @@ def lnprior(param):
 
 def lnlike(param, x_d, y_d):
 
-    print(param)
-
     logtau, vmax, theta, logT, voff = param
 
     x_m, y_m = model(logtau, vmax, theta, logT, voff, x_d, y_d)
@@ -117,16 +115,14 @@ voff_0 = -11
 
 x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, voff_0, x_data, y_data)
 
-lnlikelihood_0 = lnlike(array([logtau_0, vmax_0, theta_0, logT_0, voff_0]), x_0, y_0)
-
-first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0, lnlikelihood_0]
+first_guess = [logtau_0, vmax_0, theta_0, logT_0, voff_0]
 
 
 #Running emcee
 
-ndim = 6
-nwalkers = 12
-nsteps = 2
+ndim = 5
+nwalkers = 10
+nsteps = 2000
 
 pos = [first_guess+ 1e-3*random.randn(ndim) for i in range(nwalkers)]
 

### 2015-04-25 paper/ms.tex

@@
 
-Theoretical background...\\
+\cite{Garavito14} presented an analytical expresion that approximates
+the results for the Lyman-$\alpha$ line morphology for a spherical galaxy
+rotating as a solid body.
+
+Ths input parameters of the analytical solution are the optical depth
+$\tau_{H}$, the rotational velocity at the sphere's surface $V_{\rm
+  max}$ and the angle of view measured from the equatorial plane
+(which is perpendicular to the rotational axis) $\theta$. 
+A $\texttt{C}$ source code implementation is available in the public
+repository associated to this paper.
+
+The main result \cite{Garavito14} is that rotation does have a
+noticeable impact on the \ly line morphology.
+This impact is two fold. 
+First, the rotation axis breaks the spherical symmetry, introducing a
+dependence of the line shape with viewing angle.
+Second, for increasing rotational velocities and viewing angles off
+the rotational axis, the intensity at the line's centers increases;
+for sufficiently high rotational velocities the line becomes single peaked.
 

### 2015-04-27 code/histograms.py
plots

@@ -1,0 +1,83 @@
+from numpy import *
+from matplotlib.pyplot import *
+from scipy.interpolate import interp1d
+import triangle
+import os
+
+#Info
+nwalkers = 10
+nsteps = 2000
+nparameters = 5
+
+z = 0.029836
+c = 299792.458
+
+#Data
+samples = loadtxt('./sampler_flatchain.dat', delimiter=',')
+
+logtaus = samples[:,0]
+vmaxs = samples[:,1]
+thetas = samples[:,2]
+logTs = samples[:,3]
+voffs = samples[:,4]
+
+#Histograms
+labels=[r"$\log{\tau}$", "$v_{max}$", r"$\theta$", "$\log{T}$", "$\Delta v_{off}$"]
+
+#logtau
+fig = figure()
+
+n,b,p = hist(logtaus, bins=100, histtype='step')
+logtau_b = b[argmax(n)]
+vlines(logtau_b, 0, 400)
+xlabel(labels[0])
+ylabel('$\mathrm{N}$')
+
+savefig('./histograms_logtau.png')
+
+#vmax
+fig = figure()
+
+n,b,p = hist(vmaxs, bins=100, histtype='step')
+vmax_b = b[argmax(n)]
+vlines(vmax_b, 0, 700)
+xlabel(labels[1])
+ylabel('$\mathrm{N}$')
+
+savefig('./histograms_vmax.png')
+
+#theta
+fig = figure()
+
+n,b,p = hist(thetas, bins=100, histtype='step')
+theta_b = b[argmax(n)]
+vlines(theta_b, 0, 1200)
+xlabel(labels[2])
+ylabel('$\mathrm{N}$')
+
+savefig('./histograms_theta.png')
+
+#logT
+fig = figure()
+
+n,b,p = hist(logTs, bins=100, histtype='step')
+logT_b = b[argmax(n)]
+vlines(logT_b, 0, 450)
+xlabel(labels[3])
+ylabel('$\mathrm{N}$')
+
+savefig('./histograms_logT.png')
+
+#voff
+fig = figure()
+
+n,b,p = hist(voffs, bins=100, histtype='step')
+voff_b = b[argmax(n)]
+vlines(voff_b, 0, 800)
+xlabel(labels[4])
+ylabel('$\mathrm{N}$')
+
+savefig('./histograms_voff.png')
+
+#Best parameters
[…]

### 2015-04-27 code/plots.py

@@ -6,18 +6,30 @@ import os
 
 #Info
 nwalkers = 10
-nsteps = 100
+nsteps = 2000
 nparameters = 5
 
 z = 0.029836
 c = 299792.458
 
+#Data
+lars = loadtxt('./LARS02.txt')
+samples = loadtxt('./sampler_flatchain.dat', delimiter=',')
+
+x_data = lars[:-17,0] - c*z
+y_data = lars[:-17,1]
+
 #Best parameters
-logtau_b = 5
-vmax_b = 50
-theta_b = 45
-logT_b = 4
-voff_b = -11
+
+f_best = open('./best_parameters.dat')
+best = f_best.readline().split(',')
+f_best.close()
+
+logtau_b = float(best[0])
+vmax_b = float(best[1])
+theta_b = float(best[2])
+logT_b = float(best[3])
+voff_b = float(best[4].split(r'\n')[0])
 
 #Functions
 def model_to_data_interp(x_m, y_m, x_d):
@@ -54,17 +66,11 @@ def model(logtau, vmax, theta, logT, voff, x_d, y_d):
 
     return x_m, y_m
 
-#Data
-lars = loadtxt('./LARS02.txt')
-samples = loadtxt('./sampler_flatchain.dat', delimiter=',')
-
-x_data = lars[:-17,0] - c*z
-y_data = lars[:-17,1]
-
-x_model, y_model = model(logtau_b, vmax_b, theta_b, logT_b, voff_b, x_data, y_data)
 
 #Plot fit and original
 fig = figure(figsize=(12,6))
+
+x_model, y_model = model(logtau_b, vmax_b, theta_b, logT_b, voff_b, x_data, y_data)
 
 scatter(x_data, y_data, c='c', alpha=0.6, label='$\mathrm{LARS 02}$')
 plot(x_data, y_data, c='c', alpha=0.6)
@@ -75,6 +81,7 @@ ylabel('$\mathrm{Intensity (Arbitrary Units)}$', fontsize=20)
 legend(loc='best', fontsize=20)
 
 savefig('./mcmc.png')
+
 
 # Walkers plot
 clf()

### 2015-04-29 paper/letter.tex
abstract

\documentclass{article}
\title{Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha
  line emission}
\author{MCRG, JNGC, JEFR}
\begin{document}
\maketitle
\begin{abstract}
The Lyman-alpha emission line is a strong indicator of star formation.
Observations of this line are central to construct samples of the most
distant star forming galaxies, which in turn are useful for studies in
cosmology and galaxy evolution.  
The intepretation of Ly-$\alpha$ observations has to go together with
computational models for the radiative transfer of Lyman-alpha photons.
Recent theoretical work suggested that galaxy rotation should have a
measurable impact on the shape of the Lyman-alpha line. 
Here we show that galaxy rotation can be measured from the Lyman-alpha
line profile. 
We found that lyman-alpha observations of a dwarf galaxy (Tol 1214-277) in
the local universe, which had previously evaded theoretical 
interpretation, are naturally explained by rotational effects.
We constrain the rotational velocity, viewing angle and total
neutral hydrogen mass from the Lyman-alpha observations.
These alues in agreement with other observational constraints.
Our results present a new observational method by which the rotational
velocity of a dwarf galaxy can be estimated. 
Considering the expected similarities between the local and the most
distant dwarf galaxies, we anticipate that the Lyman-alpha line could be
used to constraint the kinematic state of the highest redshift
galaxies to be detected with next generation infrared spectroscopic
facilities such as the James Webb Space Telescope.

\end{abstract}

\end{document}

### 2015-04-29 paper/ms.tex
new plots + best parameters

@@
 \usepackage[dvips]{epsfig}
+\usepackage{float}
 \newcommand{\avg}[1]{\langle{#1}\rangle}  
@@
 
-\section{Theoretical Background}
+\subsection{Theoretical Background}
 \label{sec:theo}
@@
 
+An approximated analytic solution was derived for a spherical galaxy with 
+central \lya sources.
+
+\begin{equation}
+J(x,b,\phi,i)=\frac{\sqrt{\pi}}{\sqrt{24}a\tau_0}\Bigg{(}\frac{(x-x_{\rm
+    b})^2}{1+{\rm cosh}\Big{[}\sqrt{\frac{2\pi^3}{27}}\frac{|(x
+      -x_{\rm b})^3|}{a\tau_0}\Big{]}}\Bigg{)},
+\end{equation}
+
+\begin{equation}
+J(x,i) \approx 2\pi \int_0^Rdb \hs b
+\int_0^{2\pi}d\phi \hs J(x,b,\phi,i)
+\end{equation}
+
+\subsection{Low redshift observations}
+
+The \ly emission line is a powerfull tool to study the properties 
+of the high redshift Universe. Important intrinsic properties of this
+galaxy population, such as the redshift, luminosity functions, 
+equivalent width and the kinematic state are derived from the 
+\ly line. With the aim to study in more detail the impact of this 
+properties on the \ly line several surveys have observe nearby
+galaxies whose properties are known from . We are particularly
+interested in study the kinematic state of the galaxys using 
+the \ly line. The \citep{LARS} survey have observed 14 nearby galaxies
+with strong \ly emission using the HST telescope and the .
+
+The LARS survey have observed galaxies with different properties, 
+the spectra of all this galaxies and their properties are described 
+in detail in \citep{LARS2} \citep{LARS3, LARS4}.
+
 \section{Results}
@@
 
-\begin{figure}
+$$\tau_{H} = 69663.485 $$
+$$V_{\rm max} = 49.961\kms $$
+$$\theta = 44.495^\circ $$
+$$T = 9962.731 \rm K$$
+$$\Delta V_{off} = -9.722 \kms$$
+
+\begin{figure}[H]
 \begin{center}
@@
 
-\begin{figure*}
+\begin{figure}[H]
 \begin{center}
-  \includegraphics[width=0.7\textwidth]{parameters.png}
+  \includegraphics[width=0.5\textwidth]{parameters.png}
 \end{center}
@@
     \label{fig:mcmc_triangle}}  
-\end{figure*}
+\end{figure}
 

### 2015-04-29 paper/letter.tex
orden de figura y parrafos

@@
 \begin{abstract}
-The Lyman-alpha emission line is a strong indicator of star formation.
+{\bf The Lyman-alpha emission line is a strong indicator of star formation.
 Observations of this line are central to construct samples of the most
@@
 measurable impact on the shape of the Lyman-alpha line. 
-Here we show that galaxy rotation can be measured from the Lyman-alpha
-line profile. 
-We found that lyman-alpha observations of a dwarf galaxy (Tol 1214-277) in
-the local universe, which had previously evaded theoretical 
+Here we report that lyman-alpha observations of a dwarf galaxy (Tol
+1214-277) in the local universe, which had previously evaded theoretical 
 interpretation, are naturally explained by rotational effects.
@@
 neutral hydrogen mass from the Lyman-alpha observations.
-These alues in agreement with other observational constraints.
+These values are in agreement with other observational constraints.
 Our results present a new observational method by which the rotational
@@
 galaxies to be detected with next generation infrared spectroscopic
-facilities such as the James Webb Space Telescope.
+facilities such as the James Webb Space Telescope.}
 
@@
 
+1. General paragraph about the Lyman alpha line.
+
+2. General paragraph about modelling the Lyman alpha
+line. Outflows.
+
+3. Rotation and the expected features.
+
+4. The charachteristics of the dwarf galaxy of interest.
+
+5. The results of the fit.
+
+Figure 1. Observed line + fit.
+
+6. Comparison of these results against other observational data.
+
+7. Implications for outflow+rotation in existing samples.
+
+8. Implications for very high-z dwarf galaxies.
+
 \end{document}

### 2015-05-09 code/plots.py
new plots

@@ -16,8 +16,8 @@ c = 299792.458
 tol = loadtxt('./tol.txt')
 samples = loadtxt('./sampler_flatchain.dat', delimiter=',')
 
-x_data = tol[:-17,0]
-y_data = tol[:-17,1]
+x_data = tol[:,0]
+y_data = tol[:,1]
 
 #Best parameters
 
@@ -35,10 +35,30 @@ voff_b = float(best[4].split(r'\n')[0])
 def model_to_data_interp(x_m, y_m, x_d):
 
     f = interp1d(x_m, y_m, kind="linear")
-    x_m_new = x_d
-    y_m_new = f(x_d)
 
-    return x_m_new, y_m_new
+    try:
+        x_m_new = x_d
+        y_m_new = f(x_d)
+
+        return x_m_new, y_m_new
+
+    except ValueError:
+
+        n = len(x_d)
+
+        x_m_new = x_d
+        y_m_new = zeros(n)
+
+        for i in range(n):
+
+            x_d_i = x_d[i]
+
+            if(x_d_i >= x_m[0] and x_d_i <= x_m[-1]):
+                y_m_new[i] = f(x_d_i)
+            else:
+                y_m_new[i] = 0.0
+
+        return x_m_new, y_m_new
 
 def normalization(y_d, y_m):
 

### 2015-05-09 paper/letter.tex
esta fuente es rara
updated style

@@
-\documentclass{article}
-\title{Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha
+\documentclass[a4paper, 12pt]{article}
+\usepackage{subfig}
+\usepackage{float}
+\usepackage{wrapfig}
+\usepackage{graphicx}
+\usepackage{amsmath}
+\usepackage{amssymb}
+\usepackage{booktabs}
+\usepackage[top=3.5cm, bottom=2.5cm, left=3.5cm, right=3.5cm]{geometry}
+
+%----------------------New commands -------------------
+\newcommand{\hb}{H$\beta$}
+\newcommand{\ha}{H$\alpha$}
+\newcommand{\oiii}{[OIII]}
+\newcommand{\oii}{[OII]}
+\newcommand{\nii}{[NII]}
+\newcommand{\esca}{erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$}
+\newcommand{\esc}{erg cm$^{-2}$ s$^{-1}$}
+\newcommand{\es}{erg s$^{-1}$}
+\newcommand{\esa}{erg s$^{-1}$}
+\newcommand{\kms}{km s$^{-1}$}
+\def\simgt{\lower.5ex\hbox{\gtsima}}
+\def\simlt{\lower.5ex\hbox{\ltsima}}
+%------------------------------------------------------
+
+\begin{document}
+\pagestyle{empty}
+\noindent
+\textbf{Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha
   line emission}
-\author{MCRG, JNGC, JEFR}
-\begin{document}
-\maketitle
-\begin{abstract}
-{\bf The Lyman-alpha emission line is a strong indicator of star formation.
+\\
+\\
+JEFR$^{1}$, MCRG$^1$, JNGC$^1$,
+\\
+\\
+\scriptsize
+{$^1$ Universided de los Andes
+\\
+$^2$ a
+\normalsize
+\\
+\\
+\textbf{The Lyman-alpha emission line is a strong indicator of star formation.
 Observations of this line are central to construct samples of the most
@@
 measurable impact on the shape of the Lyman-alpha line. 
-Here we report that lyman-alpha observations of a dwarf galaxy (Tol
+Here we report that lyman-alpha observations of a dwarf compact galaxy (Tol
 1214-277) in the local universe, which had previously evaded theoretical 
@@
 neutral hydrogen mass from the Lyman-alpha observations.
-These values are in agreement with other observational constraints.
+These values are in broad agreement with other observational
+constraints, although  they raise questions about the rather atypical nature
+of such source.
 Our results present a new observational method by which the rotational
@@
 facilities such as the James Webb Space Telescope.}
-
-\end{abstract}
 

### 2015-06-22 paper/letter.tex
update
removed subtitles
paragraph on total M_HI mass

@@
 
+%\section{Introduction}
+
 1. General paragraph about the Lyman alpha line.
@@
 
+%\section{TOL1214-277}
+
 4. The charachteristics of the dwarf galaxy of interest.
+
+TOL1214-277 Blue Compact Dwarf Galaxy
+
+Star forming galaxy, no old stars.
+
+%\section{Results}
 
@@
 
-6. Comparison of these results against other observational data.
+%6. Comparison of these results against other observational data.
+
+We estimate the total neutral hydrogen mass to be $M\approx
+m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
+the optical depth and $n$ is the number density of neutral Hydrogen
+atoms. For this system we estimate that for average values of
+$n=1\times 10^3$ the total hydrogen mass is $M\times
+10^{14}$M$_{\odot}$. However, blind HI surveys have put an upper limit
+in the neutral hydrogen mass of ???
 

### 2015-07-08 paper/letter.tex
update

@@
 
-TOL1214-277 Blue Compact Dwarf Galaxy
+TOL1214-277 was first observed by ... it is a compact 
+dwarf galaxy and does not have old stars.
 
-Star forming galaxy, no old stars.
+The Ly$\alpha$ emission line was first observed in the TOL1214-277 
+galaxy by \citep{Thuan97}. It has two main important features which 
+make this a very uncommun LAE. First it shown a symmetric profile 
+which is , Second the Ly$\alpha$ line is not shifted with respect to 
+the H$\beta$ line.  Blue compact Dwarf Galaxy
 

### 2015-09-22 paper/letter.tex
new plot

@@
 computational models for the radiative transfer of Lyman-alpha photons.
-Recent theoretical work suggested that galaxy rotation should have a
+Recent theoretical work suggests that galaxy rotation has a
 measurable impact on the shape of the Lyman-alpha line. 
-Here we report that lyman-alpha observations of a dwarf compact galaxy (Tol
+Here we report that lyman-alpha observations of a dwarf compact galaxy (TOL
 1214-277) in the local universe, which had previously evaded theoretical 
@@
 These values are in broad agreement with other observational
-constraints, although  they raise questions about the rather atypical nature
-of such source.
-Our results present a new observational method by which the rotational
-velocity of a dwarf galaxy can be estimated. 
+constraints, although  they point towards a rather atypical physical
+nature for the source.  
+Our results present a new observational method to estimate the rotational
+velocity of dwarf galaxies.
 Considering the expected similarities between the local and the most
 distant dwarf galaxies, we anticipate that the Lyman-alpha line could be
-used to constraint the kinematic state of the highest redshift
-galaxies to be detected with next generation infrared spectroscopic
-facilities such as the James Webb Space Telescope.}
+used to constraint the rotational state of the neutral gas in the
+highest redshift galaxies to be detected with next generation infrared
+spectroscopic facilities such as the James Webb Space Telescope.}
 

### 2015-09-22 paper/letter.tex
simple paragraph describing rotation results

@@
 %----------------------New commands -------------------
+
+\newcommand{\tol}{TOL1214-277}
 \newcommand{\hb}{H$\beta$}
@@
 \noindent
-\textbf{Measurement of a dwarf galaxy rotational velocity from its Lyman-alpha
-  line emission}
+\textbf{Measurement of a dwarf galaxy rotational velocity from its
+  Lyman-alpha line emission} 
 \\
@@
 3. Rotation and the expected features.
+It has been shown that rotation also imprints an effect on the
+Lyman-alpha morphology. 
+The most important consequence of rotation is that spherical 
+symmetry is broken.
+The line morphology now depends on the viewing angle respect to the
+rotation axis.  
+For a line sight perpendicular to the rotation axis the intensity and
+the line center and the line width increase with rotational velocity. 
+When the rotational velocity is close to the half-line width of the
+static line, the line becomes single peaked as it is observed in
+\tol, a unique feature that other theoretical models find
+impossible to reproduce.
 

### 2015-09-22 paper/letter.tex
adding best parameters

@@
 rotation axis.  
-For a line sight perpendicular to the rotation axis the intensity and
+For a line of sight perpendicular to the rotation axis the intensity and
 the line center and the line width increase with rotational velocity. 
@@
 
-TOL1214-277 was first observed by ... it is a compact 
+\tol was first observed by ... it is a compact 
 dwarf galaxy and does not have old stars.
@@
 
-Figure 1. Observed line + fit.
+Figure 1. shows the observational data for \tol with the overplot from
+our best fit model. The parameters for the best fit are
+$v_{max}=300$kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
+viewing angle $\theta<30$ degrees.
+
+Observed line + fit.
 
@@
 m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
-the optical depth and $n$ is the number density of neutral Hydrogen
-atoms. For this system we estimate that for average values of
-$n=1\times 10^3$ the total hydrogen mass is $M\times
-10^{14}$M$_{\odot}$. However, blind HI surveys have put an upper limit
-in the neutral hydrogen mass of ???
+the optical depth, $\sigma$ is the cross section at the line's center
+and $n$ is the number density of neutral Hydrogen atoms. For this
+system we estimate that for average values of $n=1\times 10^3$ the
+total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. However, blind HI
+surveys have put an upper limit in the neutral hydrogen mass of ???
 

### 2015-09-23 paper/letter.tex
small changes

@@
 \newcommand{\tol}{TOL1214-277}
+\newcommand{\lya}{Ly$\alpha$}
 \newcommand{\hb}{H$\beta$}
@@
 Figure 1. shows the observational data for \tol with the overplot from
-our best fit model. The parameters for the best fit are
-$v_{max}=300$kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
+our best fit model from the full radiative transfer simulation. 
+The parameters for the best fit are
+$v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
 viewing angle $\theta<30$ degrees.
@@
 
-We estimate the total neutral hydrogen mass to be $M\approx
-m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a Hydrogen's atom, $\tau$ is
-the optical depth, $\sigma$ is the cross section at the line's center
-and $n$ is the number density of neutral Hydrogen atoms. For this
-system we estimate that for average values of $n=1\times 10^3$ the
-total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. However, blind HI
+Assuming spherical symmetry and a homogeneous gas distribution we
+estimate the total neutral hydrogen mass to be on the order of
+$M\approx m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a
+Hydrogen's atom, $\tau$  the optical depth, $\sigma$ is the cross
+section at the line's center and $n$ is the number density of neutral
+Hydrogen atoms. 
+For this system we estimate that for average values of $n=1\times
+10^3$ the total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. 
+However, blind HI
 surveys have put an upper limit in the neutral hydrogen mass of ???

### 2016-01-27 paper/letter.tex
new title, basic info about TOL

@@
-\documentclass[a4paper, 12pt]{article}
+\documentclass[a4paper, usenatbib, 12pt]{article}
 \usepackage{subfig}
@@
 \usepackage{booktabs}
+\usepackage{cite}
 \usepackage[top=3.5cm, bottom=2.5cm, left=3.5cm, right=3.5cm]{geometry}
@@
 \newcommand{\kms}{km s$^{-1}$}
+\newcommand{\apj}{ApJ}  
+\newcommand{\jcap}{JCAP}  
+\newcommand{\apjs}{ApJS}  
+\newcommand{\apjl}{ApJL}  
+\newcommand{\aj}{AJ}  
+\newcommand{\mnras}{MNRAS}  
+\newcommand{\mnrassub}{MNRAS accepted}  
+\newcommand{\aap}{A\&A}  
+\newcommand{\aaps}{A\&AS}  
+\newcommand{\araa}{ARA\&A}  
+\newcommand{\nat}{Nature}  
+\newcommand{\physrep}{PhR}
+\newcommand{\pasp}{PASP}    
+\newcommand{\pasj}{PASJ}    
 \def\simgt{\lower.5ex\hbox{\gtsima}}
@@
 \noindent
-\textbf{Measurement of a dwarf galaxy rotational velocity from its
-  Lyman-alpha line emission} 
+\textbf{Lyman-alpha emission reveals an unusual fast rotating dwarf galaxy}  
 \\
 \\
-JEFR$^{1}$, MCRG$^1$, JNGC$^1$,
+JEFR$^{1}$, MCRG$^1$, JNGC$^2$,
 \\
@@
 \\
-$^2$ a
+$^2$ Arizona
 \normalsize
@@
 computational models for the radiative transfer of Lyman-alpha photons.
-Recent theoretical work suggests that galaxy rotation has a
-measurable impact on the shape of the Lyman-alpha line. 
+Recent theoretical work suggests that galaxy rotation has a measurable
+impact on the shape of the Lyman-alpha line.  
 Here we report that lyman-alpha observations of a dwarf compact galaxy (TOL
@@
 The Ly$\alpha$ emission line was first observed in the TOL1214-277 
-galaxy by \citep{Thuan97}. It has two main important features which 
+galaxy by \cite{Thuan97}. It has two main important features which 
 make this a very uncommun LAE. First it shown a symmetric profile 
@@
 %6. Comparison of these results against other observational data.
-
 Assuming spherical symmetry and a homogeneous gas distribution we
@@
 
-8. Implications for very high-z dwarf galaxies.
+%8. Implications for very high-z dwarf galaxies.
+
+%=====
+
+\bibliography{references}{}
+\bibliographystyle{plain}
+
+\newpage
+\begin{table}
+\begin{center}
+
+\begin{tabular}{lc}
+$\alpha$(2000)$^{a}$ & 12\ 17\ 17.1\\
+$\delta$(2000)$^{b}$ & -28\ 02\ 32\\
+$l$, $b$ (deg) & 294, 34\\
+$m_V$ & 17.5\\
+$v$(km s$^{-1}$) & 7795
+\end{tabular}
+\end{center}
+
+\caption{Observational characteristics of TOL1214-277 \cite{Thuan97}\\
+$^{a}$ Units of right ascension are hours, minutes and
+  seconds.\\ $^{b}$ Units of declination are degrees, arcminutes and arcseconds.}
+\end{table}
 

### 2016-01-27 paper/letter.tex
TOL description, new references

@@
 impact on the shape of the Lyman-alpha line.  
-Here we report that lyman-alpha observations of a dwarf compact galaxy (TOL
+Here we report that lyman-alpha observations of a blue dwarf compact galaxy (TOL
 1214-277) in the local universe, which had previously evaded theoretical 
@@
 \begin{tabular}{lc}
-$\alpha$(2000)$^{a}$ & 12\ 17\ 17.1\\
-$\delta$(2000)$^{b}$ & -28\ 02\ 32\\
+$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
+$\delta$(2000)$^{b}$ & -28d02m32s\\
 $l$, $b$ (deg) & 294, 34\\
@@
 
+The metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
+spectroscopy. The observed flux for the Lyman alpha line is $\sim
+8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$ \cite{Thuan97}
+and a Equivalent Width of $70$\AA.
+
+Interpretation by \citep{masshesse}.
+
 \end{document}

### 2016-02-01 paper/letter.tex
estimados de masa HI y masa dinamica

@@
 
-Interpretation by \citep{masshesse}.
+Interpretation by \cite{mashesse03}.
 
+For an homogeneous sphere the HI optical depth can be written
+as $\tau = \sigma_0 n s$, where $\sigma_0$ is the optical depth at the
+line's center, $n$ is the number density and $s$ is the sistem's
+size. 
+This can be rewritten in terms of the gas' temperature $T$ and column
+density $N_{H}$as $\tau = 3.31 \times 10^{-14} (10^{4}\mathrm{K}/T)^{1/2}
+(N_{H}/\mathrm{atoms\ cm}^{-2})$.
+
+This allows us to approximate the total hydrogen mass as
+\begin{equation}
+M_{H} = m_{H}  N_{H} D^{2} = 226\times \tau  \left(\frac{T}{10^4
+  \mathrm{K}}\right)^{1/2}\left(\frac{D}{\mathrm{kpc}}\right)^2M_{\odot}
+\end{equation}
+
+On the other hand, we have an estimate for the dynamical mass from the
+galaxy size $D$ and its rotational velocity $V$:
+
+\begin{equation}
+M_{T} = \frac{V^{2}D}{G} = 4.32\times10^{5}
+\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
+\end{equation}
 \end{document}

### 2016-02-01 paper/letter.tex
observational limits on HI mass

@@
 
+The receeding velocity is $7785\pm 50$km s$^{-1}$, which translates
+into a distance of $106.6$ Mpc (Hubble constant 73 Mpc km$^{-1}$
+s$^{1}$)
 The metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
@@
 8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$ \cite{Thuan97}
-and a Equivalent Width of $70$\AA.
+and a Equivalent Width of $70$\AA, with the emission comming from a
+region with approximate diameter ?. There is an upper limit for the
+integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
+upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
+\cite{pustilnikmartin07}.
 
@@
 \begin{equation}
-M_{T} = \frac{V^{2}D}{G} = 4.32\times10^{5}
+M_{T} = \frac{V^{2}D}{G} = 2.16\times10^{5}
 \left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}

### 2016-02-01 paper/letter.tex
conclusiones interesantes

@@
 \end{document}
+
+%% interpretation
+From the optical depth of $10^7$ and the non-detection in the HI line,
+we have an upper limit for the size where the Lya emission comes of
+$D<0.34$kpc. From this limit and the rotational velocity of $300$ km/s
+we have in turn an upper limit for the dynamical mass of $6.6\times
+10^{9}$ Msun, which is $\sim 25$ times larger than the $HI$ mass.

### 2016-02-01 paper/letter.tex
nueva referencia (size in optical)

@@
 and a Equivalent Width of $70$\AA, with the emission comming from a
-region with approximate diameter ?. There is an upper limit for the
+region with approximate diameter ?? \cite{Fricke01}. There is an upper limit for the
 integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a

### 2016-02-03 paper/simple.py
calculos simples para el paper

@@ -1,0 +1,16 @@
+tau = 1E7
+v_rot = 300 # km/s
+sigma_0 = 5.898E-14 #cm-2
+n_values = [1,1E-3]
+kpc_in_cm = 3.08E21
+
+for n in n_values:
+    D = 2.0 * tau / (sigma_0 * n) # in cm
+    M_D = 2.16E5 * (v_rot)**2 * (D/kpc_in_cm)
+    print("n= {} cm^-3 D={} kpc".format(n,D/kpc_in_cm, M_D/1E10)) 
+
+
+D_kpc = [0.11, 0.34] # rango in kpc
+for D in D_kpc:
+    M_D = 2.16E5 * (v_rot)**2 * (D)
+    print("M = {} 1E9 Msun".format(M_D/1E9)) 

### 2016-02-03 paper/letter.tex
nuevos limits en D y M_D

--- 2016-02-01 paper/letter.tex
@@
 \noindent
-\textbf{Lyman-alpha emission reveals an unusual fast rotating dwarf galaxy}  
+\textbf{Lyman-alpha emission reveals an unusual fastly rotating
+  compact dwarf galaxy}  
 \\
@@
 \scriptsize
-{$^1$ Universided de los Andes
+{$^1$ Universidad de los Andes
 \\
@@
 \\
-\textbf{The Lyman-alpha emission line is a strong indicator of star formation.
-Observations of this line are central to construct samples of the most
-distant star forming galaxies, which in turn are useful for studies in
-cosmology and galaxy evolution.  
-The intepretation of Ly-$\alpha$ observations has to go together with
-computational models for the radiative transfer of Lyman-alpha photons.
-Recent theoretical work suggests that galaxy rotation has a measurable
-impact on the shape of the Lyman-alpha line.  
-Here we report that lyman-alpha observations of a blue dwarf compact galaxy (TOL
-1214-277) in the local universe, which had previously evaded theoretical 
-interpretation, are naturally explained by rotational effects.
-We constrain the rotational velocity, viewing angle and total
-neutral hydrogen mass from the Lyman-alpha observations.
-These values are in broad agreement with other observational
-constraints, although  they point towards a rather atypical physical
-nature for the source.  
-Our results present a new observational method to estimate the rotational
-velocity of dwarf galaxies.
-Considering the expected similarities between the local and the most
-distant dwarf galaxies, we anticipate that the Lyman-alpha line could be
+\textbf{
+Compact dwarf galaxies (CDGs) are puzzling systems. 
+They form large quantities of stars in spite of their lack of
+heavy chemical elements which are present in other nearby galaxies. 
+The conditions in their interstellar medium resemble the expected
+pristine environment of the first galaxies. 
+Until these early galaxy generations are observationally
+detected, CDGs are the best present day population to test our ideas
+on primordial galaxy formation and evolution. 
+Here we report on one of such CDGs, Tololo 1214-277, which presents
+features in its Lyman$\alpha$ emission thad had evaded theoretical
+interpretation so far. 
+We show that these special features can be naturally explained by
+rotational effects.  
+We use the Lyman$\alpha$ observations available for Tololo 1214-277 to
+constrain the rotational velocity and total neutral hydrogen optical
+depth.  
+We find that the neutral hydrogen region in Tololo 1214-277 should
+have a rotational velocity of $V_{r}=300$ km s$^{-1}$ and an optical
+depth of $\tau=10^7$.  Considering previous
+observational upper limits on  the total neutral hydrogen mass and
+expected number density, we find that the diameter for the Ly$\alpha$
+emission region is in the range of $110$ pc $<D<$ $340$
+pc. Correspondingly the total dynamical mass in that region is between
+$2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
+We anticipate that the Lyman-alpha line could be
 used to constraint the rotational state of the neutral gas in the
@@
 The metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
-spectroscopy. The observed flux for the Lyman alpha line is $\sim
-8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$ \cite{Thuan97}
-and a Equivalent Width of $70$\AA, with the emission comming from a
-region with approximate diameter ?. There is an upper limit for the
+spectroscopy.
+
+The observed flux for the Lyman alpha line is $\sim
+8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \cite{Thuan97}
+and a Equivalent Width of $70$\AA and its H$\beta$ flux is 
+$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ cm${-2}$
+\cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
+4.9$\pm$0.1. 
+Comparing this ratio with the theoretical expectation from case B
+recombination of $23.3$ \cite{Hummer1987} one can estimate an escape
+fraction of $20$\% for Ly$\alpha$ radiation.
+
+The optical emission  comes from a   region with approximate diameter
+?? \cite{Fricke01}.
+
+Interpretation by \cite{mashesse03}.
+
+There is an upper limit for the  
 integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
@@
 \cite{pustilnikmartin07}. 
+From the optical depth of $10^7$ and the non-detection in the HI line,
+we have an upper limit for the size where the Lya emission comes of
+$D<0.34$kpc.
 
-Interpretation by \cite{mashesse03}.
+ For an homogeneous sphere the HI optical depth from its can be
+ written as $\tau = \sigma_0 n D/2$, where $\sigma_0=5.898\times
+10^{-14}$cm$^{-2}$ is the Lyman$\alpha$  optical depth at the 
+line's center, $n$ is the number density and $D$ is the sphere's
+diameter. 
+From this we can impose additional constrains on $D$ from the tipical
+values of the Hydrogen number density and our constrain on
+$\tau=10^{7}$.  Using a range of $1<n/\mathrm{atoms/cm}^{-3} <
+10^{-3}$. This gives us a range of $0.11 < D/\mathrm{kpc}<100$. 
+Together from the total HI mass we have thus that the HI region should
+have a diameter of $0.11 < D/\mathrm{kpc}<0.34$.
 
-For an homogeneous sphere the HI optical depth can be written
-as $\tau = \sigma_0 n s$, where $\sigma_0$ is the optical depth at the
-line's center, $n$ is the number density and $s$ is the sistem's
-size. 
 This can be rewritten in terms of the gas' temperature $T$ and column
@@
 \end{equation}
+
+From this limit and the rotational velocity of $300$ km/s and the
+limit in the size $D$ we have limits of for the dynamical mass of
+$2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
+
+which is at least $7$ to $25$ times larger than the H$I$ mass.
+
 \end{document}
+
+%% interpretation

### 2016-02-04 paper/letter.tex
nuevo abstract

@@
 
-\newcommand{\tol}{TOL1214-277}
+\newcommand{\tol}{Tololo 1214-277}
 \newcommand{\lya}{Ly$\alpha$}
@@
 \textbf{
-Compact dwarf galaxies (CDGs) are puzzling systems. 
-They form large quantities of stars in spite of their lack of
-heavy chemical elements which are present in other nearby galaxies. 
-The conditions in their interstellar medium resemble the expected
-pristine environment of the first galaxies. 
+Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected pristine
+conditions of the first galaxies.  
 Until these early galaxy generations are observationally
-detected, CDGs are the best present day population to test our ideas
-on primordial galaxy formation and evolution. 
-Here we report on one of such CDGs, Tololo 1214-277, which presents
-features in its Lyman$\alpha$ emission thad had evaded theoretical
+detected, CDGs are the best systems to test our ideas on primordial
+galaxy formation and evolution.  
+Here we report on one of such CDGs, \tol, which presents
+features in its Lyman-$\alpha$ emission thad had evaded theoretical
 interpretation so far. 
-We show that these special features can be naturally explained by
-rotational effects.  
-We use the Lyman$\alpha$ observations available for Tololo 1214-277 to
-constrain the rotational velocity and total neutral hydrogen optical
-depth.  
-We find that the neutral hydrogen region in Tololo 1214-277 should
-have a rotational velocity of $V_{r}=300$ km s$^{-1}$ and an optical
-depth of $\tau=10^7$.  Considering previous
-observational upper limits on  the total neutral hydrogen mass and
-expected number density, we find that the diameter for the Ly$\alpha$
-emission region is in the range of $110$ pc $<D<$ $340$
-pc. Correspondingly the total dynamical mass in that region is between
-$2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
-We anticipate that the Lyman-alpha line could be
-used to constraint the rotational state of the neutral gas in the
-highest redshift galaxies to be detected with next generation infrared
-spectroscopic facilities such as the James Webb Space Telescope.}
+We show that these special features, a symmetric triple peaked
+emission line, are naturally explained by gas rotation.  
+We find that the Lyman-$\alpha$ emission region in \tol\ should
+have a rotational velocity of $V_{r}=300$ km s$^{-1}$ and a neutral
+Hydrogen column density of $\log N_{HI}=20.5$ atoms cm$^{-2}$.  
+Considering other observational information we find that
+the diameter for that region should be in the range of
+$110$ pc $<D<$ $340$ pc and its total dynamical mass 
+should be between $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times
+10^{9}$M$_{\odot}$. 
+This dynamical mass is at least $16\pm 9$ times
+larger than the neutral mass hydrogen.
+We argue that a possibility to explain the excess in
+dynamical mass is the presence of a super-massive black hole. }
 

### 2016-02-08 paper/letter.tex
nueva estructura de parrafos

@@
 have a rotational velocity of $V_{r}=300$ km s$^{-1}$ and a neutral
-Hydrogen column density of $\log N_{HI}=20.5$ atoms cm$^{-2}$.  
-Considering other observational information we find that
+Hydrogen column density of $\log N_{HI} / \mathrm{atoms\ cm}^{-2} =
+  20.5$.   
+Using archival observational information we find that
 the diameter for that region should be in the range of
@@
 
-1. General paragraph about the Lyman alpha line.
+1. [General paragraph about the first galaxies and CDGs]
 
-2. General paragraph about modelling the Lyman alpha
-line. Outflows.
+2. [General paragrph about the expected Lyman-alpha emission]. Almost
+fifty years ago \cite{PartridgePeebles} it was realized that young
+galaxies should have a strong Lyman-$\alpha$ line emission. 
+This theoretical prediciotn was only confirmed XX year later. 
+Currently, Lyman Alpha Emitting galaxies are commonly measure in
+surveys.
 
-3. Rotation and the expected features.
+3. [The link betwween high-z galaxies and lyman alpha, LARS]
+
+4. [Observations require interpretation, common features and
+  models]. The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
+will follow a difussion-like process before escaping the galaxy or
+being absorbed by dust. This makes it hard to interpret Lyman-alpha
+line observations as the reulting profile is sensitive to the
+dynamical, chemical and thermal conditions in the interstellar
+medium. State-of-the-art models
+
+5. [Rotation and the expected features.]
 It has been shown that rotation also imprints an effect on the
@@
 rotation axis.  
-For a line of sight perpendicular to the rotation axis the intensity and
-the line center and the line width increase with rotational velocity. 
+For a line of sight perpendicular to the rotation axis the intensity
+and the line center and the line width increase with rotational
+velocity.  
 When the rotational velocity is close to the half-line width of the
@@
 
-%\section{TOL1214-277}
-
-4. The charachteristics of the dwarf galaxy of interest.
+6. [The charachteristics of the dwarf galaxy of interest as a puzzling
+system]
 
@@
 
-The Ly$\alpha$ emission line was first observed in the TOL1214-277 
+The Ly$\alpha$ emission line was first observed in the \tol
 galaxy by \cite{Thuan97}. It has two main important features which 
@@
 
-	%\section{Results}
-
-5. The results of the fit.
+7. [The results of the fit + Physical picture using other results]
 
@@
 
-Observed line + fit.
+Figura Observed line + fit.
 
-%6. Comparison of these results against other observational data.
+%6. Comparison of these results against other observational 
 Assuming spherical symmetry and a homogeneous gas distribution we
@@
 
-7. Implications for outflow+rotation in existing samples.
+8. [Possible interpretation of this results]
 
-%8. Implications for very high-z dwarf galaxies.
+9. [Implications for outflow+rotation in existing samples.]
+
+10. [Future outlook]
 
@@
 \newpage
+
+\section*{\tol\ characteristics}
+
 \begin{table}
 \begin{center}
-
 \begin{tabular}{lc}
@@
 
-\caption{Observational characteristics of TOL1214-277 \cite{Thuan97}\\
-$^{a}$ Units of right ascension are hours, minutes and
-  seconds.\\ $^{b}$ Units of declination are degrees, arcminutes and arcseconds.}
+\caption{Observational characteristics of TOL1214-277
+  \cite{Thuan97}\\} 
 \end{table}
@@
 ?? \cite{Fricke01}.
+
+\section*{MCMC constraints}
+
+\section*{Physical Interpretation}
 

### 2016-02-10 paper/letter.tex
paragraph on LARS

@@
 
-2. [General paragrph about the expected Lyman-alpha emission]. Almost
-fifty years ago \cite{PartridgePeebles} it was realized that young
-galaxies should have a strong Lyman-$\alpha$ line emission. 
-This theoretical prediciotn was only confirmed XX year later. 
+2. [General paragrph about the expected Lyman-alpha emission,
+  LARS]. Almost fifty years ago \cite{PartridgePeebles} it was
+realized that young galaxies could be detected through a stron
+Lyman-$\alpha$ line emission.  This theoretical prediction was only
+confirmed XX year later. 
 Currently, Lyman Alpha Emitting galaxies are commonly measure in
 surveys. 
+The presence of this line provides confirmation of the distance of a
+galaxy and also provides clues about the stellar population powering
+the emission.
 
-3. [The link betwween high-z galaxies and lyman alpha, LARS]
+Lyman alpha emission is not exclusive of high redshift galaxies. It
+does, require a low dust content to avoid complete extinction and an
+source of ionizing radiation.  This has motivated the creation of
+local Universe surveys to perform a detailed study of the Lyman-alpha
+emission \cite{LARS}. A nearby simple permits the study of other
+indicators that might be more difficult to obtain for distant galaxies
+such as morphology, dust attenuation, neutral hydrogen contents and
+ionization state.
 
-4. [Observations require interpretation, common features and
+3. [Observations require interpretation, common features and
   models]. The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
@@
 dynamical, chemical and thermal conditions in the interstellar
-medium. State-of-the-art models
+medium. State-of-the-art models use mon
 
-5. [Rotation and the expected features.]
+4. [Rotation and the expected features.]
 It has been shown that rotation also imprints an effect on the
@@
 
-6. [The charachteristics of the dwarf galaxy of interest as a puzzling
+5. [The charachteristics of the dwarf galaxy of interest as a puzzling
 system]
@@
 
-7. [The results of the fit + Physical picture using other results]
+6. [The results of the fit + Physical picture using other results]
 
@@
 
-8. [Possible interpretation of this results]
+7. [Possible interpretation of this results]
 
-9. [Implications for outflow+rotation in existing samples.]
+8. [Implications for outflow+rotation in existing samples.]
 
-10. [Future outlook]
+9. [Future outlook]
 

### 2016-02-10 paper/letter.tex
rotation+outflow appendix

@@
 
+\section*{Joint Effect of Rotation and Outflow}
+
+The almost complete absence of outflows is a central requirement for
+reproducing the lyman alpha line in \tol. In this section we present
+some results on the exploration of the presence of outflows join with
+the bulk rotation. We defer a detailed exploration of this effects for
+another publication.
+
+Figure XX shows the results of four different models. a) pure rotation
+($V_{\rm rot}=100$ km s$^{-1}$), b) pure outflow ($V_{\rm out}=100$ km
+s$^{-1}$), c) mixed outflow with rotation ($V_{\rm rot}=100$ km s$^{-1}$)($V_{\rm rot}=25$ km s$^{-1}$).
+
 \end{document}

### 2016-02-11 paper/letter.tex
affiliations
first plot, one paragraph, minor reference edit

@@
 \usepackage{cite}
-\usepackage[top=3.5cm, bottom=2.5cm, left=3.5cm, right=3.5cm]{geometry}
+\usepackage[icelandic,spanish,english]{babel}
+\usepackage[T1]{fontenc}
+\usepackage[utf8]{inputenc}
+\usepackage[top=3.5cm, bottom=2.5cm, left=3.5cm,right=3.5cm]{geometry}
 
@@
 \noindent
-\textbf{Lyman-alpha emission reveals an unusual fastly rotating
-  compact dwarf galaxy}  
+\textbf{Þú ert jörðin}
 \\
 \\
-JEFR$^{1}$, MCRG$^1$, JNGC$^2$,
+JEFR$^{1}$, MCRG$^1$, JNGC$^2$, MD$^3$
 \\
@@
 \scriptsize
-{$^1$ Universidad de los Andes
+{$^1$ Bogota
 \\
-$^2$ Arizona
+$^2$ Tucson
+\\
+$^3$ Oslo
 \normalsize
@@
 \textbf{
-Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected pristine
-conditions of the first galaxies.  
+Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected pristine conditions of the first galaxies.  
 Until these early galaxy generations are observationally
@@
 dynamical, chemical and thermal conditions in the interstellar
-medium. State-of-the-art models use mon
+medium. State-of-the-art models use mon.
 
@@
 
-Figure 1. shows the observational data for \tol with the overplot from
+Figure 1. shows the observational data for \tol
+
+with the overplot from
 our best fit model from the full radiative transfer simulation. 
@@
 
-Figura Observed line + fit.
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{tolfit.png}
+\caption{Nice fit}
+\end{center}
+\end{figure}
 
@@
 
-8. [Implications for outflow+rotation in existing samples.]
+8. [Implications for outflow+rotation in existing samples.] Why are
+not more examples of triple peaked emission? 
+The ubiuquity of galaxy outflows overimposed to the rotation
+transforms the line into the common double or single peaked
+observations.
 
 9. [Future outlook]
-
-%=====
 
@@
 
-The receeding velocity is $7785\pm 50$km s$^{-1}$, which translates
+\tol receeding velocity is $7785\pm 50$km s$^{-1}$, which translates
 into a distance of $106.6$ Mpc (Hubble constant 73 Mpc km$^{-1}$
 s$^{1}$)
-The metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
+Its metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
 spectroscopy.

### 2016-02-12 paper/letter.tex
first full draft of the main body of the paper

@@
 
-%\section{Introduction}
+The first generation of galaxies point to our cosmic corigins. Their
+initial conditions and characteristiscs are the first page on the
+evolution of galaxies such as the milky way that evolve to the present
+time. In the standard big bang cosmology the only elemets that were
+created in the nucleosynthesis where Hydrogen, Helium and
+Lithium. Heavier elemets must hve been created in the internal
+processes of stellar evolution. Therefore the first generation of
+galaxies shoudl be metal free and rich in hydrogen. We haven detected
+these galaxies yet. The best obsrevational proxy we have for them are
+dwarf star forming galaxies with a low metallicity content. Compact
+dwarf galaxies (CDGs) are the best observational example.
 
-1. [General paragraph about the first galaxies and CDGs]
-
-2. [General paragrph about the expected Lyman-alpha emission,
-  LARS]. Almost fifty years ago \cite{PartridgePeebles} it was
-realized that young galaxies could be detected through a stron
-Lyman-$\alpha$ line emission.  This theoretical prediction was only
-confirmed XX year later. 
-Currently, Lyman Alpha Emitting galaxies are commonly measure in
-surveys. 
+How can we develop a strategy to look for the first galaxies How can we recognize a first galaxy when we see one? 
+Almost fifty years ago \cite{PartridgePeebles} realized that young
+galaxies could be detected through a strong Lyman-$\alpha$ line
+emission.  This theoretical prediction was only confirmed XX year
+later.  Currently, Lyman Alpha Emitting galaxies are commonly measure
+in surveys. 
 The presence of this line provides confirmation of the distance of a
@@
 
-Lyman alpha emission is not exclusive of high redshift galaxies. It
-does, require a low dust content to avoid complete extinction and an
-source of ionizing radiation.  This has motivated the creation of
+Lyman alpha emission, as suggested in the first paragraph, is not
+exclusive of high redshift galaxies. Any galaxy with low metallicity
+and dust content and ongoing star formation should present this line.  This has motivated the creation of
 local Universe surveys to perform a detailed study of the Lyman-alpha
@@
 
-3. [Observations require interpretation, common features and
-  models]. The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
+The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
 will follow a difussion-like process before escaping the galaxy or
@@
 
-4. [Rotation and the expected features.]
 It has been shown that rotation also imprints an effect on the
@@
 
-5. [The charachteristics of the dwarf galaxy of interest as a puzzling
-system]
-
-\tol was first observed by ... it is a compact 
-dwarf galaxy and does not have old stars.
-
 The Ly$\alpha$ emission line was first observed in the \tol
 galaxy by \cite{Thuan97}. It has two main important features which 
-make this a very uncommun LAE. First it shown a symmetric profile 
-which is , Second the Ly$\alpha$ line is not shifted with respect to 
-the H$\beta$ line.  Blue compact Dwarf Galaxy
+make this a very uncommun LAE. First it has symmetric profile 
+without any systemic displacement from the expected
+line-center. Second it shows a triple peak, while the most common
+observational feature corresponds either to a single or asymetric
+double peak. 
+This profile has escaped a clear theoretical understading based on
+models that consider galaxies as spherical gas distributions with an
+outflow. 
+We have attempted an interpretation of the lya spectrum in \tol\ wihas
+a central feature the bulk gas rotation without any outflow. This
+model provides a complete explanation of \tol's puzzling feature.
 
-6. [The results of the fit + Physical picture using other results]
-
-Figure 1. shows the observational data for \tol
-
-with the overplot from
-our best fit model from the full radiative transfer simulation. 
-The parameters for the best fit are
-$v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K and a
-viewing angle $\theta<30$ degrees.
+Dots in Figure 1. represebt the observational data for \tol with the
+overplot from our best fit model from the full radiative transfer
+simulation.   The parameters for the best fit are
+$v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K.
+The optical depth and temperature can be translated into a column
+density of $N_{HI}$. Our model is also able to constrain the angle
+between the rotation axis and the observational line-of-sight to $\theta=65^{\circ}\pm$.
+To constrain the model uncertainties we perform a Markov Chain Monte
+Carlo calculation using an approximate analytical solution for the
+lya spectrum in the bulk rotation case.
 
@@
 
-%6. Comparison of these results against other observational 
-Assuming spherical symmetry and a homogeneous gas distribution we
-estimate the total neutral hydrogen mass to be on the order of
-$M\approx m_H\tau^3\sigma^{-3}n^{-2}$, where $m_H$ is the mass a
-Hydrogen's atom, $\tau$  the optical depth, $\sigma$ is the cross
-section at the line's center and $n$ is the number density of neutral
-Hydrogen atoms. 
-For this system we estimate that for average values of $n=1\times
-10^3$ the total hydrogen mass is $M\times 10^{14}$M$_{\odot}$. 
-However, blind HI
-surveys have put an upper limit in the neutral hydrogen mass of ???
+Radio surveys have put an upper limit to the neutral hydrogen mass in
+\tol of $M<2.65\times 10^{8}$ M$_{\odot}$. Together with our velocity
+and column density results, under the assumption of spherical
+symmetry, we can constrain the total dynamical mass of the HI region
+to be in the range $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times
+10^{9}$M$_{\odot}$ and the diameter of HI region should
+have a diameter of $0.11 < D/\mathrm{kpc}<0.34$. This makes the
+dynamical mass  at least $7$ to $25$ times larger than the H$I$ mass.
 
-7. [Possible interpretation of this results]
+We consider three possibilities to contribute to this high
+dynamical mass: stars, dark matter and a supermassive black
+hole. The stellar mass can be constrained by measurements of the
+stellar continuum, this can only represent $xx$M$_{\odot}$ of the total
+contribution . Considering a standard variations for the dark matter
+halo, it can only constributio to $xx$ M$_{\odot}$ in the region of
+interest. A super massive black hole remains an open
+possibility. Recent observations of ultra-compact dwarf galaxies
+\cite{Seth2014} have confirmed the presence of super-massive black
+holes containing $15\%$ of the total objects mass, suggesting that
+there is a large population of undetected black holes.
 
-8. [Implications for outflow+rotation in existing samples.] Why are
-not more examples of triple peaked emission? 
+A future observational test of this possibility in \tol\ would require
+integral field unit measurements spatially resolving its spatial
+extent. 
+\tol\ spans a region of $\approx 4$ arcminutes. 
+An instrument such as the Multi Unit Spectroscopic Explorer with its
+nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
+in wide-field mode could provide a detailed mapping of different
+ionization lines and infer a kinematic map.
+
+Why are not more examples of triple peaked emission in observed
+Lyman-alpha emitting gaalaxies?  
 The ubiuquity of galaxy outflows overimposed to the rotation
@@
 observations.  
+Therefore, the absence of HI outflows in \tol\ is another special
+feature that permitted a symmetric triple peaked lya line to emerge.
 
-9. [Future outlook]
+The implications of our finding for the study of lyman-alpha
+emitters, including the first generation of galaxies are
+manifold. First of all, it provides support to including rotation as a
+feature to interpret observed spectra. Secondly, it provides a
+motivation to explore under what conditions rotation dominated
+dynamics are expected in comparison with outflow dominated
+dynamics. Finally, if the hypothesis of a supermassive black hole in
+\tol\ proves to be consistend with future observational kinematic
+maps, it would provide a new information to test and probe theories on
+the coevolution of galaxies and black holes.
 
@@
 $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
-
 which is at least $7$ to $25$ times larger than the H$I$ mass.

### 2016-02-12 paper/letter.tex
new reference

@@
 dynamical, chemical and thermal conditions in the interstellar
-medium. State-of-the-art models use mon.
+medium. State-of-the-art models use montecarlo radiative transfer
+simulations to interpret lya line profiles. Only in very few symmetric
+cases analytical solutions are available.
 
-It has been shown that rotation also imprints an effect on the
-Lyman-alpha morphology. 
+Recent models computational models \cite{GaravitoCamargo2014} have
+shown that rotation also imprints an effect on the Lyman-alpha
+morphology.  
 The most important consequence of rotation is that spherical 

### 2016-02-15 paper/letter.tex
editando

@@
 
-The first generation of galaxies point to our cosmic corigins. Their
-initial conditions and characteristiscs are the first page on the
-evolution of galaxies such as the milky way that evolve to the present
-time. In the standard big bang cosmology the only elemets that were
-created in the nucleosynthesis where Hydrogen, Helium and
-Lithium. Heavier elemets must hve been created in the internal
-processes of stellar evolution. Therefore the first generation of
-galaxies shoudl be metal free and rich in hydrogen. We haven detected
-these galaxies yet. The best obsrevational proxy we have for them are
-dwarf star forming galaxies with a low metallicity content. Compact
-dwarf galaxies (CDGs) are the best observational example.
+The first generation of galaxies trace our cosmic origins. 
+Their characteristiscs are the first step on the evolution of galaxies
+such as the Milky Way.
+In the standard Big Bang cosmology the only elements that were
+created in the nucleosynthesis process were Hydrogen, Helium and
+Lithium. 
+Heavier elemets must have been created in stellar evolution process. 
+Therefore the first generation of
+galaxies should be metal free and rich in Hydrogen. 
+This kind of primordial galaxies have not been detected yet. 
+However, dwarf star forming galaxies with a low metallicity content
+are close template to understand the early galaxy evolution process.
 
-How can we develop a strategy to look for the first galaxies How can we recognize a first galaxy when we see one? 
-Almost fifty years ago \cite{PartridgePeebles} realized that young
-galaxies could be detected through a strong Lyman-$\alpha$ line
-emission.  This theoretical prediction was only confirmed XX year
-later.  Currently, Lyman Alpha Emitting galaxies are commonly measure
+Almost fifty years ago \cite{PartridgePeebles} it was realized that
+young galaxies could be detected through a strong Lyman-$\alpha$ line
+emission.  
+This theoretical prediction was only confirmed thirty year later,  not
+on first generation galaxies but on distant relatively young systems. 
+Currently, Lyman Alpha Emitting (LAE) galaxies are commonly targetted
 in surveys. 
-The presence of this line provides confirmation of the distance of a
-galaxy and also provides clues about the stellar population powering
-the emission.
+The presence of the Ly-$\alpha$ emission line provides confirmation of
+the distance of a galaxy and also provides clues about the stellar
+population powering the emission.
 
-Lyman alpha emission, as suggested in the first paragraph, is not
-exclusive of high redshift galaxies. Any galaxy with low metallicity
-and dust content and ongoing star formation should present this line.  This has motivated the creation of
-local Universe surveys to perform a detailed study of the Lyman-alpha
-emission \cite{LARS}. A nearby simple permits the study of other
-indicators that might be more difficult to obtain for distant galaxies
-such as morphology, dust attenuation, neutral hydrogen contents and
-ionization state.
+Ly-$\alpha$ emission is not exclusive of distant galaxies. 
+Any galaxy with low dust content and ongoing star formation has the
+right conditions to show this line.  
+There are, for instance,  local Universe surveys that target
+Ly-$\alpha$ emission in nearby dwarf star forming galaxies. 
+\cite{LARS}. 
+A nearby LAE sample allow for the study of other indicators that
+might be more difficult to obtain for distant galaxies such as
+morphology, dust attenuation, neutral hydrogen contents and ionization
+state.
 
-The Lyman-$\alpha$ line is resonant. A yman-$\alpha$ photon
-will follow a difussion-like process before escaping the galaxy or
-being absorbed by dust. This makes it hard to interpret Lyman-alpha
-line observations as the reulting profile is sensitive to the
-dynamical, chemical and thermal conditions in the interstellar
-medium. State-of-the-art models use montecarlo radiative transfer
-simulations to interpret lya line profiles. Only in very few symmetric
-cases analytical solutions are available.
+However, the physical interpratation of Ly-$\alpha$ observations is
+not straightforward. 
+This is due to the resonant nature of the Ly-$\alpha$ line. 
+A Ly-$\alpha$ photon followw a difussion-like process before escaping
+the galaxy or being absorbed by dust. 
+The reulting line profile becomes sensitive to the dynamical, chemical
+and thermal conditions in the interstellar medium. 
+Only in very few cases of high symmetry there are analytical solutions
+available. 
+Interpretation of observations require state-of-the-art models use
+montecarlo radiative transfer simulations.
 
@@
 
-The Ly$\alpha$ emission line was first observed in the \tol
-galaxy by \cite{Thuan97}. It has two main important features which 
-make this a very uncommun LAE. First it has symmetric profile 
-without any systemic displacement from the expected
-line-center. Second it shows a triple peak, while the most common
-observational feature corresponds either to a single or asymetric
-double peak. 
-This profile has escaped a clear theoretical understading based on
-models that consider galaxies as spherical gas distributions with an
-outflow. 
-We have attempted an interpretation of the lya spectrum in \tol\ wihas
-a central feature the bulk gas rotation without any outflow. This
-model provides a complete explanation of \tol's puzzling feature.
+\tol is a compact star forming dwarf galaxies (CDGs) that presents a
+strong Ly-$\alpha$ emission \cite{Thuan97} with two features that had
+so far evaded a natural physical interpratation.
+First, it has symmetric profile  without any systemic displacement
+from the expected line-center. 
+Second, it shows a triple peak, while the most common observational
+feature corresponds either to a single or asymetric double peak. 
+We have attempted an interpretation of the Ly-$\alpha$ line in
+\tol\ by including the effect of gas bulk rotation.
+We find that this model provides a satisfactory explanation of \tol's
+puzzling features.
 

### 2016-02-15 paper/letter.tex
main body updated

@@
 
-Recent models computational models \cite{GaravitoCamargo2014} have
+Recent computational models \cite{GaravitoCamargo2014} have
 shown that rotation also imprints an effect on the Lyman-alpha
@@
 
-\tol is a compact star forming dwarf galaxies (CDGs) that presents a
+\tol\ is a compact star forming dwarf galaxies (CDGs) that presents a
 strong Ly-$\alpha$ emission \cite{Thuan97} with two features that had
@@
 
-Dots in Figure 1. represebt the observational data for \tol with the
+Figure 1. summarizes our findings.
+Dots represent the observational data for \tol with the
 overplot from our best fit model from the full radiative transfer
-simulation.   The parameters for the best fit are
+simulation.   
+The parameters for the best fit are
 $v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K.
 The optical depth and temperature can be translated into a column
-density of $N_{HI}$. Our model is also able to constrain the angle
+density of $\log N_{HI} / \mathrm{atoms\ cm}^{-2} =
+  20.5$.   
+Our model is also able to constrain the angle
 between the rotation axis and the observational line-of-sight to $\theta=65^{\circ}\pm$.
-To constrain the model uncertainties we perform a Markov Chain Monte
+To determine the uncertainties we perform a Markov Chain Monte
 Carlo calculation using an approximate analytical solution for the
-lya spectrum in the bulk rotation case.
+Ly-$\alpha$ spectrum including rotational effects.
 
-\begin{figure}
-\begin{center}
-\includegraphics[width=0.8\textwidth]{tolfit.png}
-\caption{Nice fit}
-\end{center}
-\end{figure}
-
-Radio surveys have put an upper limit to the neutral hydrogen mass in
-\tol of $M<2.65\times 10^{8}$ M$_{\odot}$. Together with our velocity
-and column density results, under the assumption of spherical
-symmetry, we can constrain the total dynamical mass of the HI region
-to be in the range $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times
-10^{9}$M$_{\odot}$ and the diameter of HI region should
-have a diameter of $0.11 < D/\mathrm{kpc}<0.34$. This makes the
+Radio surveys of the 21cm line have put an upper limit to the neutral
+hydrogen mass in \tol of $M<2.65\times 10^{8}$ M$_{\odot}$. 
+Together with our velocity and column density results, under the
+assumption of spherical symmetry, we can constrain the total dynamical
+mass of the HI region to be in the range $2.1\times 10^{9}$M$_{\odot}$
+$<M_D<$  $6.6\times 10^{9}$M$_{\odot}$ and the diameter of HI region
+should have a diameter of $0.11 < D/\mathrm{kpc}<0.34$. 
+This makes the
 dynamical mass  at least $7$ to $25$ times larger than the H$I$ mass.
 
-We consider three possibilities to contribute to this high
-dynamical mass: stars, dark matter and a supermassive black
-hole. The stellar mass can be constrained by measurements of the
+We consider three possibilities to explain the dynamical 
+mass: stars, dark matter and a supermassive black hole. 
+The stellar mass can be constrained by measurements of the 
 stellar continuum, this can only represent $xx$M$_{\odot}$ of the total
-contribution . Considering a standard variations for the dark matter
-halo, it can only constributio to $xx$ M$_{\odot}$ in the region of
-interest. A super massive black hole remains an open
-possibility. Recent observations of ultra-compact dwarf galaxies
+contribution. 
+Considering a standard dark matter halo, it can only constributio to
+$xx$ M$_{\odot}$ in the region of interest. 
+A super massive black hole remains an open  possibility. 
+Recent observations of ultra-compact dwarf galaxies
 \cite{Seth2014} have confirmed the presence of super-massive black
-holes containing $15\%$ of the total objects mass, suggesting that
-there is a large population of undetected black holes.
+holes containing $15\%$ of the total object mass, suggesting that
+there is a large population of undetected black holes in dwarf
+galaxies.
 
@@
 in wide-field mode could provide a detailed mapping of different
-ionization lines and infer a kinematic map.
+ionization lines to infer a kinematic map.
 
-Why are not more examples of triple peaked emission in observed
-Lyman-alpha emitting gaalaxies?  
+Why is triple peaked emission not common in  Lyman-alpha emitting
+gaalaxies?   
 The ubiuquity of galaxy outflows overimposed to the rotation
 transforms the line into the common double or single peaked
-observations.  
+line.
 Therefore, the absence of HI outflows in \tol\ is another special
@@
 
-The implications of our finding for the study of lyman-alpha
-emitters, including the first generation of galaxies are
-manifold. First of all, it provides support to including rotation as a
-feature to interpret observed spectra. Secondly, it provides a
-motivation to explore under what conditions rotation dominated
-dynamics are expected in comparison with outflow dominated
-dynamics. Finally, if the hypothesis of a supermassive black hole in
-\tol\ proves to be consistend with future observational kinematic
-maps, it would provide a new information to test and probe theories on
-the coevolution of galaxies and black holes.
+The implications of our finding for the study of LAEs, including the
+first generation of galaxies are manifold. 
+First of all, it demonstrated the importance of including rotation as
+theoretical feature to interpret observed spectra. 
+Secondly, it provides a motivation to explore under what conditions
+rotation dominated dynamics are expected in comparison with outflow
+dominated dynamics. 
+Finally, if the hypothesis of a supermassive black
+hole in \tol\ proves to be consistend with future observational
+kinematic maps, it would provide a new information to test and probe
+theories on the coevolution of galaxies and black holes in the first
+generation of galaxies.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{tolfit.png}
+\caption{{\bf Symmetric triple peaked Ly-$\alpha$ emission of \tol.}
+  Dots correspond to the observational data. The line shows the result
+of our best model from a full radiative transfer simulation. The best
+parameters correspond to a rotational velocity of $300$km s$^{-1}$,
+neutral Hydrogen optical depth of $10^{7}$ and a viewing angle of
+$65^{\circ}$ measured from the rotation axis.} 
+\end{center}
+\end{figure}
 

### 2016-02-24 paper/letter.tex
fluxes in table

@@
 $m_V$ & 17.5\\
-$v$(km s$^{-1}$) & 7795
+$v$(km s$^{-1}$) & 7795\\
+M$_V$ & -17.6\\ 
+Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
+Ly-$\alpha$ EW & $70$\AA\\
+H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
+$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
 \end{tabular}
 \end{center}
-
-\caption{Observational characteristics of TOL1214-277
+\caption{Basic observational characteristics of TOL1214-277
   \cite{Thuan97}\\} 
@@
 and a Equivalent Width of $70$\AA and its H$\beta$ flux is 
-$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ cm${-2}$
+$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
 \cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of

### 2016-02-24 paper/letter.tex
data update, M/L estimate

@@
 $m_V$ & 17.5\\
+M$_V$ & -17.6\\ 
 $v$(km s$^{-1}$) & 7795\\
-M$_V$ & -17.6\\ 
 Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
@@
 \cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
-4.9$\pm$0.1. 
+4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
+$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA
+bandwidth, which in turns translates  into a star formation rate of
+$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
+luminosity and star formation rate of $9.1\times 10^{-43}$
+$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
+The absolute magnitude in the $V$ band translates into a luminosity of
+$8.9\times 10^{8}$ L$_{\odot}$.
+% using http://tomdwelly.com/tools_fluxtolum.php
 Comparing this ratio with the theoretical expectation from case B
@@
 $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
-which is at least $7$ to $25$ times larger than the H$I$ mass.
+which is at least $7$ to $25$ times larger than the H$I$ mass. The
+mass to luminosity ratio is in turn between $2$ to $7$ times
+$L_{\odot}/M_{\odot}$ considering the total luminosity in the $V$
+band.
 

### 2016-05-18 paper/letter.tex
recompile
better format for the fit plot
minor edits

@@
 \textbf{
-Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected pristine conditions of the first galaxies.  
-Until these early galaxy generations are observationally
-detected, CDGs are the best systems to test our ideas on primordial
+  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
+  pristine conditions of the first galaxies in the Universe.    
+Before the observational detection of the first galaxies becomes
+reality, CDGs are the best systems to test our ideas on primordial
 galaxy formation and evolution.    
@@
 We show that these special features, a symmetric triple peaked
-emission line, are naturally explained by gas rotation.  
+emission line, can be explained by gas bulk rotation.  
 We find that the Lyman-$\alpha$ emission region in \tol\ should
@@
   20.5$.   
-Using archival observational information we find that
-the diameter for that region should be in the range of
-$110$ pc $<D<$ $340$ pc and its total dynamical mass 
-should be between $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times
+Using archival observational information about \tol\ we find that the
+diameter for that emission region diameter should be in the range of
+$110$ pc $<D<$ $340$ pc and its total dynamical mass   should be
+between $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times
 10^{9}$M$_{\odot}$.  
@@
 The first generation of galaxies trace our cosmic origins. 
-Their characteristiscs are the first step on the evolution of galaxies
-such as the Milky Way.
+They were the first steps in the evolution of galaxies such as the Milky
+Way. 
 In the standard Big Bang cosmology the only elements that were
@@
 Heavier elemets must have been created in stellar evolution process. 
-Therefore the first generation of
-galaxies should be metal free and rich in Hydrogen. 
+Therefore, we expect the first generation of
+galaxies to be metal free and rich in Hydrogen. 
 This kind of primordial galaxies have not been detected yet. 
 However, dwarf star forming galaxies with a low metallicity content
-are close template to understand the early galaxy evolution process.
+are seen as templates to understand the early galaxy evolution process.
 
@@
 emission.  
-This theoretical prediction was only confirmed thirty year later,  not
-on first generation galaxies but on distant relatively young systems. 
-Currently, Lyman Alpha Emitting (LAE) galaxies are commonly targetted
+This theoretical prediction was only confirmed thirty year later on
+distant relatively young, not primordial, galaxies.
+Currently Lyman Alpha Emitting (LAE) galaxies are commonly targetted
 in surveys. 
 The presence of the Ly-$\alpha$ emission line provides confirmation of
-the distance of a galaxy and also provides clues about the stellar
-population powering the emission.
+the distance of a galaxy while provides clues about the stellar
+population and inter-stellar medium conditions regulating the
+Ly-$\alpha$ emission.
 
-Ly-$\alpha$ emission is not exclusive of distant galaxies. 
+The Ly-$\alpha$ emission line is not exclusive of distant galaxies. 
 Any galaxy with low dust content and ongoing star formation has the
@@
 \cite{LARS}. 
-A nearby LAE sample allow for the study of other indicators that
-might be more difficult to obtain for distant galaxies such as
-morphology, dust attenuation, neutral hydrogen contents and ionization
-state.
+The study of nearby LAE samples has allowd the study of other
+indicators that might be more difficult to obtain for distant galaxies
+such as morphology, dust attenuation, neutral hydrogen contents and
+ionization state.
 
@@
 This is due to the resonant nature of the Ly-$\alpha$ line. 
-A Ly-$\alpha$ photon followw a difussion-like process before escaping
+A Ly-$\alpha$ photon follows a difussion-like process before escaping
 the galaxy or being absorbed by dust. 
-The reulting line profile becomes sensitive to the dynamical, chemical
+The resulting line profile becomes sensitive to the dynamical, chemical
 and thermal conditions in the interstellar medium. 
-Only in very few cases of high symmetry there are analytical solutions
-available. 
-Interpretation of observations require state-of-the-art models use
-montecarlo radiative transfer simulations.
+There are very few analytical tools available to interpret the
+Ly-$\alpha$ line.
+They are applicable only in very few cases of highly symmetrical
+conditions, which are hardly met in real astrophysical systems.
 
-Recent computational models \cite{GaravitoCamargo2014} have
-shown that rotation also imprints an effect on the Lyman-alpha
-morphology.  
-The most important consequence of rotation is that spherical 
-symmetry is broken.
-The line morphology now depends on the viewing angle respect to the
-rotation axis.  
+For these reasons the interpretation of Ly-$\alpha$ observations
+require state-of-the-art montecarlo radiative transfer simulations.   
+Recent advances in these computational models
+\cite{GaravitoCamargo2014} have shown that galaxy rotation imprints an
+effect on the Lyman-$\alpha$ line.
+The most important consequence of rotation is that even for a
+spherical gas distribution, the line morphology now depends on the
+viewing angle respect to the rotation axis.  
 For a line of sight perpendicular to the rotation axis the intensity
@@
 When the rotational velocity is close to the half-line width of the
-static line, the line becomes single peaked as it is observed in
+static line the line becomes single peaked, as it is observed in
 \tol, a unique feature that other theoretical models find
-impossible to reproduce.
+difficult to reproduce without invoking complex gas distributions.
 
@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{tolfit.png}
+\includegraphics[width=0.8\textwidth]{tolfit.pdf}
 \caption{{\bf Symmetric triple peaked Ly-$\alpha$ emission of \tol.}

### 2016-05-18 paper/letter.tex
rewriting results

@@
 
-\tol\ is a compact star forming dwarf galaxies (CDGs) that presents a
-strong Ly-$\alpha$ emission \cite{Thuan97} with two features that had
-so far evaded a natural physical interpratation.
+\tol\ is a compact star forming dwarf galaxy that presents a
+strong Ly-$\alpha$ emission \cite{Thuan97} with two important
+features. 
 First, it has symmetric profile  without any systemic displacement
 from the expected line-center. 
-Second, it shows a triple peak, while the most common observational
-feature corresponds either to a single or asymetric double peak. 
-We have attempted an interpretation of the Ly-$\alpha$ line in
-\tol\ by including the effect of gas bulk rotation.
-We find that this model provides a satisfactory explanation of \tol's
-puzzling features.
+Second, it shows a triple peaked profile. 
+Commonly, the Ly-$\alpha$ line features a single or asymetric double peak. 
+These two special features in \tol\ had evaded a natural physical
+interpratation so far.
 
+We find that a rotating spherical gas distribution provides a
+satisfactory explanation of \tol's puzzling features.  
 Figure 1. summarizes our findings.
@@
 simulation.   
-The parameters for the best fit are
-$v_{max}=300$\kms, $\tau=1\times10^7$, $T=1.5\times 10^{4}$K.
+The parameters for the best fit are a rotational velocity of
+$v_{max}=300$\kms, an optical depth $\tau=1\times10^7$ and temperature
+of $T=1.5\times 10^{4}$K.
 The optical depth and temperature can be translated into a column
@@
 Our model is also able to constrain the angle
-between the rotation axis and the observational line-of-sight to $\theta=65^{\circ}\pm$.
+between the rotation axis and the observational line-of-sight to
+$\theta=65^{\circ}\pm$. 
 To determine the uncertainties we perform a Markov Chain Monte

### 2016-05-18 paper/letter.tex
first pass

@@
 \\
-JEFR$^{1}$, MCRG$^1$, JNGC$^2$, MD$^3$
+JEFR$^{1}$, MCRG$^1$, JNGC$^2$, MG$^3$, MD$^3$
 \\
@@
 Radio surveys of the 21cm line have put an upper limit to the neutral
-hydrogen mass in \tol of $M<2.65\times 10^{8}$ M$_{\odot}$. 
-Together with our velocity and column density results, under the
-assumption of spherical symmetry, we can constrain the total dynamical
-mass of the HI region to be in the range $2.1\times 10^{9}$M$_{\odot}$
-$<M_D<$  $6.6\times 10^{9}$M$_{\odot}$ and the diameter of HI region
-should have a diameter of $0.11 < D/\mathrm{kpc}<0.34$. 
-This makes the
-dynamical mass  at least $7$ to $25$ times larger than the H$I$ mass.
+hydrogen mass in \tol\ of $M<2.65\times 10^{8}$ M$_{\odot}$. 
+Together with our velocity and column density results we constrain the
+total dynamical mass of the HI region to be in the range $2.1\times
+10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$ and the
+diameter of HI region should have a diameter of $0.11 <
+D/\mathrm{kpc}<0.34$.  
+This makes the dynamical mass  at least $7$ to $25$ times larger than
+the neutral Hydrogen mass.
 
@@
 contribution. 
-Considering a standard dark matter halo, it can only constributio to
+Considering a standard dark matter halo, it can only constribute to
 $xx$ M$_{\odot}$ in the region of interest. 
@@
 extent. 
-\tol\ spans a region of $\approx 4$ arcminutes. 
+\tol\ spans a region of $4$ arcminutes. 
 An instrument such as the Multi Unit Spectroscopic Explorer with its
@@
 gaalaxies?   
-The ubiuquity of galaxy outflows overimposed to the rotation
+The ubiquity of galaxy outflows overimposed to the rotation
 transforms the line into the common double or single peaked
@@
 first generation of galaxies are manifold. 
-First of all, it demonstrated the importance of including rotation as
+First of all, it demonstrates the importance of including rotation as
 theoretical feature to interpret observed spectra. 
 Secondly, it provides a motivation to explore under what conditions
-rotation dominated dynamics are expected in comparison with outflow
+rotation dominated dynamics dominate over outflow
 dominated dynamics. 

### 2016-05-18 paper/letter.tex
some typos corrected

@@
 Here we report on one of such CDGs, \tol, which presents
-features in its Lyman-$\alpha$ emission thad had evaded theoretical
+features in its Lyman-$\alpha$ emission that had evaded theoretical
 interpretation so far. 
@@
 Lithium. 
-Heavier elemets must have been created in stellar evolution process. 
+Heavier elements must have been created in stellar evolution process. 
 Therefore, we expect the first generation of
@@
 distant relatively young, not primordial, galaxies.
-Currently Lyman Alpha Emitting (LAE) galaxies are commonly targetted
+Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
 in surveys. 
@@
 \cite{LARS}. 
-The study of nearby LAE samples has allowd the study of other
+The study of nearby LAE samples has allowed the study of other
 indicators that might be more difficult to obtain for distant galaxies
@@
 
-However, the physical interpratation of Ly-$\alpha$ observations is
+However, the physical interpretation of Ly-$\alpha$ observations is
 not straightforward. 
 This is due to the resonant nature of the Ly-$\alpha$ line. 
-A Ly-$\alpha$ photon follows a difussion-like process before escaping
+A Ly-$\alpha$ photon follows a diffusion-like process before escaping
 the galaxy or being absorbed by dust. 
@@
 and thermal conditions in the interstellar medium. 
-There are very few analytical tools available to interpret the
+There are very few analytically tools available to interpret the
 Ly-$\alpha$ line.
@@
 For these reasons the interpretation of Ly-$\alpha$ observations
-require state-of-the-art montecarlo radiative transfer simulations.   
+require state-of-the-art Monte Carlo radiative transfer simulations.   
 Recent advances in these computational models
@@
 Second, it shows a triple peaked profile. 
-Commonly, the Ly-$\alpha$ line features a single or asymetric double peak. 
+Commonly, the Ly-$\alpha$ line features a single or asymmetric double peak. 
 These two special features in \tol\ had evaded a natural physical
-interpratation so far.
+interpretation so far.
 
@@
 To determine the uncertainties we perform a Markov Chain Monte
-Carlo calculation using an approximate analytical solution for the
+Carlo calculation using an approximate analytic solution for the
 Ly-$\alpha$ spectrum including rotational effects.
@@
 contribution. 
-Considering a standard dark matter halo, it can only constribute to
+Considering a standard dark matter halo, it can only contribute to
 $xx$ M$_{\odot}$ in the region of interest. 
@@
 Finally, if the hypothesis of a supermassive black
-hole in \tol\ proves to be consistend with future observational
+hole in \tol\ proves to be consistent with future observational
 kinematic maps, it would provide a new information to test and probe
-theories on the coevolution of galaxies and black holes in the first
+theories on the co-evolution of galaxies and black holes in the first
 generation of galaxies.
@@
 
-\tol receeding velocity is $7785\pm 50$km s$^{-1}$, which translates
+\tol receding velocity is $7785\pm 50$km s$^{-1}$, which translates
 into a distance of $106.6$ Mpc (Hubble constant 73 Mpc km$^{-1}$

### 2016-05-20 paper/letter.tex
some typos corrected
comma

@@
 Way. 
-In the standard Big Bang cosmology the only elements that were
-created in the nucleosynthesis process were Hydrogen, Helium and
+In the standard Big Bang cosmology the only chemical elements that
+were created in the nucleosynthesis process were Hydrogen, Helium and
 Lithium.  
@@
 This theoretical prediction was only confirmed thirty year later on
-distant relatively young, not primordial, galaxies.
+distant, relatively young, not primordial, galaxies.
 Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted

### 2016-05-26 paper/letter.tex
size correction

@@
 extent. 
-\tol\ spans a region of $4$ arcminutes. 
+\tol\ spans a region of $4$ arcseconds. 
 An instrument such as the Multi Unit Spectroscopic Explorer with its
 nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
-in wide-field mode could provide a detailed mapping of different
+in wide-field mode could provide a coarse mapping of different
 ionization lines to infer a kinematic map.
@@
 The optical emission  comes from a   region with approximate diameter
-?? \cite{Fricke01}.
+4 kpc \cite{Fricke01}.
 

### 2016-06-03 paper/letter.tex
new abstract

@@
 We show that these special features, a symmetric triple peaked
-emission line, can be explained by gas bulk rotation.  
-We find that the Lyman-$\alpha$ emission region in \tol\ should
-have a rotational velocity of $V_{r}=300$ km s$^{-1}$ and a neutral
-Hydrogen column density of $\log N_{HI} / \mathrm{atoms\ cm}^{-2} =
-  20.5$.   
-Using archival observational information about \tol\ we find that the
-diameter for that emission region diameter should be in the range of
-$110$ pc $<D<$ $340$ pc and its total dynamical mass   should be
-between $2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times
-10^{9}$M$_{\odot}$.  
-This dynamical mass is at least $16\pm 9$ times
+emission line, could be explained by two different models: an
+homogeneous sphere undergoing gas bulk rotation or a clumpy outflowing
+multiphase inter-stellar medium.
+Using archival observational information about \tol\ we 
+find that both models require a total dynamical mass in the range
+$2.5\times 10^{9}$M$_{\odot}$ $<M_D<$  $4.5\times 10^{9}$M$_{\odot}$.  
+This dynamical mass is at least $15\pm 5$ times
 larger than the neutral mass hydrogen.
 We argue that a possibility to explain the excess in
-dynamical mass is the presence of a super-massive black hole. }
+dynamical mass is the presence of a super-massive black hole.}
 

### 2016-06-07 code/stellar_mass.py
stellar mass

@@ -1,0 +1,9 @@
+import numpy as np
+#http://www.brera.inaf.it/utenti/marcella/masse.html
+#estimate stellar mass from non detection in 2mass
+m_l = 1.0 # mass to light ratio
+d_pc = 100E6 # distance in parsec
+Mag_sun = 3.41 # Sun magnitude in this filter
+mag_gal  = 15.0
+log_m_stellar = np.log10(m_l) + 2.0 * np.log10(d_pc) - 2.0 + 0.4 * Mag_sun - 0.4 * mag_gal
+print log_m_stellar

### 2016-06-07 paper/letter.tex
new paragraph on the multiphase model

@@
 conditions, which are hardly met in real astrophysical systems.
-
 For these reasons the interpretation of Ly-$\alpha$ observations
 require state-of-the-art Monte Carlo radiative transfer simulations.   
-Recent advances in these computational models
-\cite{GaravitoCamargo2014} have shown that galaxy rotation imprints an
-effect on the Lyman-$\alpha$ line.
-The most important consequence of rotation is that even for a
+Recent advances in these computational models have explored the
+effects that bulk rotation and a multiphase state in the interstellar
+medium should have on on the Lyman-$\alpha$ line.
+
+The most important consequence of bulk rotation is that, even for a
 spherical gas distribution, the line morphology now depends on the
@@
 difficult to reproduce without invoking complex gas distributions.
+
+In the case of a multiphase interstellar medium there are a wide variety
+of possible emerging spectra, mostly due to the increased complexity
+of a model that must take into account the behaviour of neutral hydrogen
+clumps dispersed in a tenous intraclump medium. 
+This variety includes single, double and triple peaked
+spectra. 
+A clumpy interstellar medium also facilitates the escape of Ly
+continuum and \lya\ photons.
 
@@
 
+FIXME: Add non detection in 2MASS %\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
+
 \tol receding velocity is $7785\pm 50$km s$^{-1}$, which translates

### 2016-06-09 paper/letter.tex
new multiphase info

@@
 Commonly, the Ly-$\alpha$ line features a single or asymmetric double peak. 
-These two special features in \tol\ had evaded a natural physical
+These two special features in \tol\ had evaded a physical
 interpretation so far.
+We find that rotation and a multiphase ISM can independently explain
+these two features.
 
-We find that a rotating spherical gas distribution provides a
-satisfactory explanation of \tol's puzzling features.  
 Figure 1. summarizes our findings.
@@
 overplot from our best fit model from the full radiative transfer
-simulation.   
+simulation for a rotating sphere (continous line) and a clumpy ISM
+(dashed line).
+
 The parameters for the best fit are a rotational velocity of
@@
 
-Why is triple peaked emission not common in Lyman-alpha emitting
-gaalaxies?   
-The ubiquity of galaxy outflows overimposed to the rotation
-transforms the line into the common double or single peaked
-line.
-Therefore, the absence of HI outflows in \tol\ is another special
-feature that permitted a symmetric triple peaked lya line to emerge.
+%Why is triple peaked emission not common in Lyman-alpha emitting
+%galaxies?   
+%The ubiquity of galaxy outflows overimposed to the rotation
+%transforms the line into the common double or single peaked
+%line.
+%Therefore, the absence of HI outflows in \tol\ is another special
+%feature that permitted a symmetric triple peaked lya line to emerge.
 

### 2016-06-09 paper/letter.tex
narrative

--- 2016-06-07 paper/letter.tex
@@
 Here we report on one of such CDGs, \tol, which presents
-features in its Lyman-$\alpha$ emission that had evaded theoretical
+a broad symmetric Lyman-$\alpha$ emission that had evaded theoretical
 interpretation so far. 
-We show that these special features, a symmetric triple peaked
-emission line, could be explained by two different models: an
-homogeneous sphere undergoing gas bulk rotation or a clumpy outflowing
-multiphase inter-stellar medium.
-Using archival observational information about \tol\ we 
-find that both models require a total dynamical mass in the range
-$2.5\times 10^{9}$M$_{\odot}$ $<M_D<$  $4.5\times 10^{9}$M$_{\odot}$.  
-This dynamical mass is at least $15\pm 5$ times
-larger than the neutral mass hydrogen.
-We argue that a possibility to explain the excess in
-dynamical mass is the presence of a super-massive black hole.}
+We explain these features by two different models: an
+homogeneous sphere undergoing gas bulk rotation and an interstellar
+medium composed by clumps with random motions.
+It is the first time that an observed \lya\ spectrum can be explained
+with these physical conditions.
+We  find that both models independently require high velocities that
+translate into a dynamical mass at least $10$ times larger than the
+neutral mass hydrogen in the galaxy. 
+We argue that a possibility to explain the high
+dynamical mass is the presence of a super-massive black hole.
+The implications of our findings for the study of LAEs, including the
+first generation of galaxies are manifold. 
+It demonstrates the importance of considering rotation and multiphase
+physics under the possible conditions shaping the \lya\ spectra of the
+first galaxies. 
+Aditionally, if future kinematic maps of \tol\ confirm the high
+velocities postulated in our model, it would provide new
+evidence for dwarf galaxies as hosts of supermassive black holes. 
+}
 
@@
 There are, for instance,  local Universe surveys that target
-Ly-$\alpha$ emission in nearby dwarf star forming galaxies. 
+Ly-$\alpha$ emission in nearby dwarf star forming galaxies 
 \cite{LARS}. 
@@
 When the rotational velocity is close to the half-line width of the
-static line the line becomes single peaked, as it is observed in
-\tol, a unique feature that other theoretical models find
-difficult to reproduce without invoking complex gas distributions.
+static line the line becomes single peaked and symmetric, a unique
+feature that other theoretical models find difficult to reproduce
+without introducing more complexity into the gas distribution.
 
-In the case of a multiphase interstellar medium there are a wide variety
-of possible emerging spectra, mostly due to the increased complexity
-of a model that must take into account the behaviour of neutral hydrogen
-clumps dispersed in a tenous intraclump medium. 
+This is the case of a multiphase interstellar medium.
+The model is more complex as it must take into account the behaviour
+of neutral dense hydrogen clumps dispersed in a tenous intraclump medium.  
+Corresponding to the elaborate physical conditions in the model,
+there are a wide variety of possible emerging spectra.
 This variety includes single, double and triple peaked
-spectra. 
-A clumpy interstellar medium also facilitates the escape of Ly
-continuum and \lya\ photons.
+spectra with different degrees of symmetry around the line's center.
 
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong Ly-$\alpha$ emission \cite{Thuan97} with two important
-features. 
-First, it has symmetric profile  without any systemic displacement
-from the expected line-center. 
-Second, it shows a triple peaked profile. 
-Commonly, the Ly-$\alpha$ line features a single or asymmetric double peak. 
-These two special features in \tol\ had evaded a natural physical
-interpretation so far.
+strong Ly-$\alpha$ emission \cite{Thuan97} with two puzzling 
+features: it is symmetric and single peaked.
+Commonly, the Ly-$\alpha$ line has a single or asymmetric double peak. 
+These two special features in \tol\ had evaded a physical
+interpretation so far, because bulk rotation and a multiphase ISM can
+independently explain the \lya\ line in \tol.
 
-We find that a rotating spherical gas distribution provides a
-satisfactory explanation of \tol's puzzling features.  
 Figure 1. summarizes our findings.
 Dots represent the observational data for \tol with the
-overplot from our best fit model from the full radiative transfer
-simulation.   
-The parameters for the best fit are a rotational velocity of
-$v_{max}=300$\kms, an optical depth $\tau=1\times10^7$ and temperature
-of $T=1.5\times 10^{4}$K.
-The optical depth and temperature can be translated into a column
-density of $\log N_{HI} / \mathrm{atoms\ cm}^{-2} =
-  20.5$.   
-Our model is also able to constrain the angle
-between the rotation axis and the observational line-of-sight to
-$\theta=65^{\circ}\pm$. 
-To determine the uncertainties we perform a Markov Chain Monte
-Carlo calculation using an approximate analytic solution for the
-Ly-$\alpha$ spectrum including rotational effects.
+overplot from our best fit models from the full radiative transfer
+simulations for a rotating sphere (continous line) and a clumpy ISM
+(dashed line).
+
+The best parameters in the rotation model are a rotational velocity of 
+$v_{max}=300^{+xx}_{-xx}$\kms, an optical depth $\log\tau=7^{+xx}_{-xx}$ and a temperature
+of $T=1.5^{+xx}_{-xx}\times 10^{4}$K. 
+This translates into a column density of $\log N_{HI} /
+\mathrm{atoms\ cm}^{-2} =  20.5^{+xx}_{-xx}$.  
+This model is also able to constrain the angle between the rotation
+axis and the observational line-of-sight to
+$\theta=65^{+xx}_{-xx}$$^{\circ}$.
+
+In the multiphase model the best constrained parameters are
+the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+17}_{-25}$ \kms,
+the clumps ouflowing velocity $v_{\infty, \rm{cl}}=79^{+167}_{60}$
+\kms and the fraction of the \lya emission that is comming comming from the cold clumps
+$P_{cl}=0.72^{+0.20}_{-0.32}$. 
+The muliphase model assumes that the clouds are distributed over a
+sphere of $5$kpc in radius, close to the $\approx 4$kpc physical size
+of \tol\ as determined by optical imaging.
+The assumed physical size and the velocity dispersion $\sigma_{\rm
+  cl}$ correspond to a  dynamical mass of  $3.0^{+1.5}_{-1.8}\times
+10^9$ M$_{\odot}$.
 
 Radio surveys of the 21cm line have put an upper limit to the neutral
-hydrogen mass in \tol\ of $M<2.65\times 10^{8}$ M$_{\odot}$. 
-Together with our velocity and column density results we constrain the
-total dynamical mass of the HI region to be in the range $2.1\times
-10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$ and the
-diameter of HI region should have a diameter of $0.11 <
-D/\mathrm{kpc}<0.34$.  
-This makes the dynamical mass  at least $7$ to $25$ times larger than
-the neutral Hydrogen mass.
+hydrogen mass in \tol\ of $M<2.65\times 10^{8}$ M$_{\odot}$ \cite{pustilnikmartin07}. 
+In the case of the rotation model, this information help us to constrain the
+diameter of the HI region where the \lya\ emission and transfer takes
+place. 
+We find this size to be in the range $0.11 < D/\mathrm{kpc}<0.34$, one
+order of magnitude smaller than \tol's size in the optical.   
+That size and the rotational velocity of $300$\kms put a constraint on
+the dynamical mass of $4.5^{+2.1}_{-2.4} \times 10^{9}$M$_{\odot}$.
 
-We consider three possibilities to explain the dynamical 
+This is evidence for a dynamical mass at least 11 (multiphase case) to
+17 (rotation case) times higher than the mass in neutral hydrogen.  
+There are three main possibilities to explain the dynamical 
 mass: stars, dark matter and a supermassive black hole. 
-The stellar mass can be constrained by measurements of the 
-stellar continuum, this can only represent $xx$M$_{\odot}$ of the total
-contribution. 
+The stellar mass in old stars hass been constrained by non-detections
+in the K-band to be $<XXX$M$_{\odot}$.
 Considering a standard dark matter halo, it can only contribute to
@@
 
-A future observational test of this possibility in \tol\ would require
-integral field unit measurements spatially resolving its spatial
-extent. 
-\tol\ spans a region of $4$ arcseconds. 
-An instrument such as the Multi Unit Spectroscopic Explorer with its
+A future observational test to clarify the physical nature of
+\tol\ would require integral field unit measurements spatially
+resolving its spatial extent. 
+\tol\ spans a region of $4$ arcseconds,
+an instrument such as the Multi Unit Spectroscopic Explorer with its
 nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
@@
 ionization lines to infer a kinematic map.
+Another observational test includes the measurement of the escape
+fraction of Ly continuum ionizing radiation. 
+In the rotational model this fraction should be zero, while
+the multiphase model predicts that in this case it should be around
+$0.5^{+1.0}_{-0.4}$\%.
 
-Why is triple peaked emission not common in Lyman-alpha emitting
-gaalaxies?   
-The ubiquity of galaxy outflows overimposed to the rotation
-transforms the line into the common double or single peaked
-line.
-Therefore, the absence of HI outflows in \tol\ is another special
-feature that permitted a symmetric triple peaked lya line to emerge.
+All in all, the mere existence of a strong LAE galaxy with a broad,
+symmetric line is interesting.
+It raises the question whether some high redshift LAEs have asymmetric
+lines because the blue half was truncated by the intergalactic medium.
+In this case the \lya\ radiation could emerge as a low surface
+brightness glow, which may be connected to \lya\ halos, while also
+influencing the way LAEs can be used as a probe of reionization.
 
-The implications of our finding for the study of LAEs, including the
-first generation of galaxies are manifold. 
-First of all, it demonstrates the importance of including rotation as
-theoretical feature to interpret observed spectra. 
-Secondly, it provides a motivation to explore under what conditions
-rotation dominated dynamics dominate over outflow
-dominated dynamics. 
-Finally, if the hypothesis of a supermassive black
+These findings demonstrate the importance of including rotation and multiphase
+conditions as features to model the \lya\ line in high redshift
+galaxies.
+Aditionally, if the hypothesis of a supermassive black
 hole in \tol\ proves to be consistent with future observational
-kinematic maps, it would provide a new information to test and probe
+kinematic maps, it could correspond to a so far undetected black hole
+in a dwarf galaxy, providing a new way to test and probe
 theories on the co-evolution of galaxies and black holes in the first

### 2016-06-09 paper/letter.tex
typos

@@
 first galaxies. 
-Aditionally, if future kinematic maps of \tol\ confirm the high
+Additionally, if future kinematic maps of \tol\ confirm the high
 velocities postulated in our model, it would provide new
@@
 This is the case of a multiphase interstellar medium.
-The model is more complex as it must take into account the behaviour
-of neutral dense hydrogen clumps dispersed in a tenous intraclump medium.  
+The model is more complex as it must take into account the behavior
+of neutral dense hydrogen clumps dispersed in a tenuous intraclump medium.  
 Corresponding to the elaborate physical conditions in the model,
@@
 overplot from our best fit models from the full radiative transfer
-simulations for a rotating sphere (continous line) and a clumpy ISM
+simulations for a rotating sphere (continuous line) and a clumpy ISM
 (dashed line).
@@
 the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+17}_{-25}$ \kms,
-the clumps ouflowing velocity $v_{\infty, \rm{cl}}=79^{+167}_{60}$
-\kms and the fraction of the \lya emission that is comming comming from the cold clumps
+the clumps outflowing velocity $v_{\infty, \rm{cl}}=79^{+167}_{-60}$
+\kms and the fraction of the \lya emission that is  coming
+from the cold clumps  
 $P_{cl}=0.72^{+0.20}_{-0.32}$. 
-The muliphase model assumes that the clouds are distributed over a
+The multiphase model assumes that the clouds are distributed over a
 sphere of $5$kpc in radius, close to the $\approx 4$kpc physical size
@@
 mass: stars, dark matter and a supermassive black hole. 
-The stellar mass in old stars hass been constrained by non-detections
+The stellar mass in old stars has been constrained by non-detections
 in the K-band to be $<XXX$M$_{\odot}$.
@@
 galaxies.
-Aditionally, if the hypothesis of a supermassive black
+Additionally, if the hypothesis of a supermassive black
 hole in \tol\ proves to be consistent with future observational
@@
 diameter. 
-From this we can impose additional constrains on $D$ from the tipical
+From this we can impose additional constrains on $D$ from the typical
 values of the Hydrogen number density and our constrain on
@@
 The almost complete absence of outflows is a central requirement for
-reproducing the lyman alpha line in \tol. In this section we present
+reproducing the \lya\ alpha line in \tol. In this section we present
 some results on the exploration of the presence of outflows join with

### 2016-06-16 paper/letter.tex
letter includes new plot with multiphase and rotation

@@
 \begin{center}
-\includegraphics[width=0.8\textwidth]{tolfit.pdf}
-\caption{{\bf Symmetric triple peaked Ly-$\alpha$ emission of \tol.}
-  Dots correspond to the observational data. The line shows the result
-of our best model from a full radiative transfer simulation. The best
-parameters correspond to a rotational velocity of $300$km s$^{-1}$,
-neutral Hydrogen optical depth of $10^{7}$ and a viewing angle of
-$65^{\circ}$ measured from the rotation axis.} 
+\includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
+\caption{{\bf Broadn, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
+  Dots correspond to the observational data. The line shows the results
+of our best model from a full radiative transfer simulation both for the rotation and multiphase models.}
 \end{center}

### 2016-06-16 paper/letter.tex
removed rotation + outflow

@@
 
-\section*{Joint Effect of Rotation and Outflow}
-
-The almost complete absence of outflows is a central requirement for
-reproducing the \lya\ alpha line in \tol. In this section we present
-some results on the exploration of the presence of outflows join with
-the bulk rotation. We defer a detailed exploration of this effects for
-another publication.
-
-Figure XX shows the results of four different models. a) pure rotation
-($V_{\rm rot}=100$ km s$^{-1}$), b) pure outflow ($V_{\rm out}=100$ km
-s$^{-1}$), c) mixed outflow with rotation ($V_{\rm rot}=100$ km s$^{-1}$)($V_{\rm rot}=25$ km s$^{-1}$).
-
 \end{document}
-
-%% interpretation

### 2016-06-17 paper/letter.tex
2 paragraphs for the rotation model

@@
 
+\section*{Additional Information}
+
+The rotation model used was based on the one explored by
+\cite{GaravitoCamargo2014}. Ly-$\alpha$ photons are propagated
+within a spherical and homogeneous cloud of HI gas undergoing solid
+body rotation. The sources of Ly-$\alpha$ photons are located in the
+center of the sphere of HI gas. Dust is not taking into account in our
+simulations since their effect doesn't affect the morphology of the
+Ly-$\alpha$. The radiative transfer simulations were done using
+Monte Carlo simulations with the code \cite{CLARA}.
+
+In this model rotation increases the width of the line and the flux at
+the line center. Furthermore, observers at different line of sights
+(LOS) angles with respect to the rotation axis of the galaxy will observe
+different morphologies of the line. LOS parallel to the rotation axis
+will tend to observe a double peaked line, while an observer with a LOS
+perpendicular to the rotation axis will observed a single peaked
+broader line.
+
 \end{document}

### 2016-06-19 paper/letter.tex
Added paragraphs about multiphase-model.

@@
 
+The idealized multiphase model consists of spherical, cold, dens clumps of neutral hydrogen (and dust) embedded in a hot, ionized medium.
+The clumps also have a random and an outflowing velocity component which totals the number of parameters describing the model to be $14$.
+In order to map out this large parameter space, we randomly drew $2500$ sets of parameters within a observationally realistic range (based on the considerations of \cite{Laursen2013ApJ...766..124L}) yielding a large variety of single-, double- and triple-peaked spectra.
+The full analysis of the the spectral features as well as more details on the radiative transfer are presented in \cite{Gronke2016}.
+
+\textbf{MG: I don't know how much details you want -- should we name all of the $14$ (best fit) parameters? Just delete what is unnecessary.}
+
+For the current work, we computed the $\chi^2$ for each of the $2500$ parameters yielding the best fit parameters of $(...)$.
+Here, the subscripts ${}_{\rm cl}$ and $_{\rm ICM}$ stand for the quantities filling the clumps and the medium between the clumps, respectively.
+Furthermore, we found that some parameters such as the magnitude of the random clump motion $\sigma_{\rm cl}$ improved the fit significantly whereas others did not.
+This makes sense also qualitatively as \tol\ possesses a very wide spectrum which can be achieved by subsequent scatterings off (relatively) fast moving clumps while the multi-phase nature (i.e., the existence of low-density channels) ensures the high flux at line center as observed.
+
 \end{document}

### 2016-08-03 paper/letter.tex
abstract

@@
 It is the first time that an observed \lya\ spectrum can be explained
-with these physical conditions.
+assuming these physical conditions.
 We  find that both models independently require high velocities that
@@
 dynamical mass is the presence of a super-massive black hole. 
+Ionization emission lines present in this galaxy support the idea that
+\tol\ might have harbored an an Active Galactic Nucleus  
 The implications of our findings for the study of LAEs, including the
@@
 velocities postulated in our model, it would provide new
-evidence for dwarf galaxies as hosts of supermassive black holes. 
+evidence for dwarf galaxies as hosts of active supermassive black
+holes.  
 }

### 2016-08-08 paper/letter.tex
rewritting the rotation description

@@
 
-\section*{Additional Information}
+\section*{The Rotation Model}
 
-The rotation model used was based on the one explored by
-\cite{GaravitoCamargo2014}. Ly-$\alpha$ photons are propagated
+The rotation model corresponds to the work presented in
+\cite{GaravitoCamargo2014}. 
+In that model the Ly-$\alpha$ photons are propagated 
 within a spherical and homogeneous cloud of HI gas undergoing solid
-body rotation. The sources of Ly-$\alpha$ photons are located in the
-center of the sphere of HI gas. Dust is not taking into account in our
-simulations since their effect doesn't affect the morphology of the
-Ly-$\alpha$. The radiative transfer simulations were done using
-Monte Carlo simulations with the code \cite{CLARA}.
+body rotation.
+The sphere is fully characterized by three parameters: the optical
+depth $\tau$ measured from the center to the surface, the HI
+temperature, $T$, and the velocity at the surface $V_{\rm max}$.  
+Photons are emitted at their natural frequency from the center of the
+sphere. 
+Including the effect of dust only changes the overall line
+normalization but not its shape.  
+The results we report in the main body of the paper do not include any
+dust model.
+In the current work, the radiative transfer simulations were done
+using Monte Carlo simulations with the code \texttt{CLARA}
+\cite{CLARA}.
 
+The main effects of rotation are the following.
+First, rotation breaks spherical symmetry of the
+static case, making the line's observed morphology dependent on the
+angle between the line-of-sight and the rotation axis.
+
+First, the line width increases with rotational velocity.
+Second, the intensity at the line's center alto 
 In this model rotation increases the width of the line and the flux at
-the line center. Furthermore, observers at different line of sights
+the line center. 
+Furthermore, observers at different line of sights
 (LOS) angles with respect to the rotation axis of the galaxy will observe
@@
 
-The idealized multiphase model consists of spherical, cold, dens clumps of neutral hydrogen (and dust) embedded in a hot, ionized medium.
-The clumps also have a random and an outflowing velocity component which totals the number of parameters describing the model to be $14$.
-In order to map out this large parameter space, we randomly drew $2500$ sets of parameters within a observationally realistic range (based on the considerations of \cite{Laursen2013ApJ...766..124L}) yielding a large variety of single-, double- and triple-peaked spectra.
-The full analysis of the the spectral features as well as more details on the radiative transfer are presented in \cite{Gronke2016}.
+\section*{The Multiphase Model}
+The idealized multiphase model consists of spherical, cold, dens
+clumps of neutral hydrogen (and dust) embedded in a hot, ionized
+medium. The clumps also have a random and an outflowing velocity
+component which totals the number of parameters describing the model
+to be $14$. In order to map out this large parameter space, we
+randomly drew $2500$ sets of parameters within a observationally
+realistic range (based on the considerations of
+\cite{Laursen2013ApJ...766..124L}) yielding a large variety of
+single-, double- and triple-peaked spectra. The full analysis of the
+the spectral features as well as more details on the radiative
+transfer are presented in \cite{Gronke2016}.
 
-\textbf{MG: I don't know how much details you want -- should we name all of the $14$ (best fit) parameters? Just delete what is unnecessary.}
+\textbf{MG: I don't know how much details you want -- should we name
+  all of the $14$ (best fit) parameters? Just delete what is
+  unnecessary.}
 
-For the current work, we computed the $\chi^2$ for each of the $2500$ parameters yielding the best fit parameters of $(...)$.
-Here, the subscripts ${}_{\rm cl}$ and $_{\rm ICM}$ stand for the quantities filling the clumps and the medium between the clumps, respectively.
-Furthermore, we found that some parameters such as the magnitude of the random clump motion $\sigma_{\rm cl}$ improved the fit significantly whereas others did not.
-This makes sense also qualitatively as \tol\ possesses a very wide spectrum which can be achieved by subsequent scatterings off (relatively) fast moving clumps while the multi-phase nature (i.e., the existence of low-density channels) ensures the high flux at line center as observed.
+For the current work, we computed the $\chi^2$ for each of the $2500$
+parameters yielding the best fit parameters of $(...)$. Here, the
+subscripts ${}_{\rm cl}$ and $_{\rm ICM}$ stand for the quantities
+filling the clumps and the medium between the clumps,
+respectively. Furthermore, we found that some parameters such as the
+magnitude of the random clump motion $\sigma_{\rm cl}$ improved the
+fit significantly whereas others did not. This makes sense also
+qualitatively as \tol\ possesses a very wide spectrum which can be
+achieved by subsequent scatterings off (relatively) fast moving clumps
+while the multi-phase nature (i.e., the existence of low-density
+channels) ensures the high flux at line center as observed.
 

### 2016-08-08 paper/letter.tex
+1 paragraph on the rotation model

@@
 The sphere is fully characterized by three parameters: the optical
-depth $\tau$ measured from the center to the surface, the HI
-temperature, $T$, and the velocity at the surface $V_{\rm max}$.  
+depth $\tau$ measured from the center to its surface, the HI
+temperature $T$, and the linear surface velocity $V_{\rm max}$.  
 Photons are emitted at their natural frequency from the center of the
@@
 
-The main effects of rotation are the following.
-First, rotation breaks spherical symmetry of the
-static case, making the line's observed morphology dependent on the
-angle between the line-of-sight and the rotation axis.
+The first important effect of rotation is that it breaks the spherical
+symmetry of the static case. 
+Now the line's observed morphology depends on the angle between the
+line-of-sight (LOS) and the rotation axis. 
+LOS parallel to the rotation axis tend to observed the line without
+any modification from rotation, while the perpendicular LOS will
+observe a maximal change in the line's morphology due to rotation.
 
-First, the line width increases with rotational velocity.
-Second, the intensity at the line's center alto 
-In this model rotation increases the width of the line and the flux at
-the line center. 
-Furthermore, observers at different line of sights
-(LOS) angles with respect to the rotation axis of the galaxy will observe
-different morphologies of the line. LOS parallel to the rotation axis
-will tend to observe a double peaked line, while an observer with a LOS
-perpendicular to the rotation axis will observed a single peaked
-broader line.
+The main change in the line's morphology is that it broadens and the
+intensity at the center increases. 
+For high enough rotational velocities the intensity at the peak's
+center increases so much that the line goes from double to single
+peaked, sometimes slightly triple peaked.
+This is the feature that allows this model to fit the observational
+features of \tol.
+
+There is a concise analytical description for those features.
+This description takes into account how different parts of the
+sphere's surface shift in frequency the \lya photons. 
+Different shifts in frequency come from different values for the projected
+velocity along the LOS. 
+As presented in \cite{CLARA}, using the analytical solution for the
+\lya sphectra of a static sphere plus the right frequency shifts
+computed from geometrical considerations, one is able to produce an
+analytical solution for the rotating sphere that reproduces the main
+features found with the full numerical simulation.
 

### 2016-08-08 paper/letter.tex
rewriting physical interpretation

@@
 
-\section*{MCMC constraints}
-
-\section*{Physical Interpretation}
-
-Interpretation by \cite{mashesse03}.
-
 There is an upper limit for the  
@@
 \cite{pustilnikmartin07}.
+
+Interpretation by \cite{mashesse03}.
+
+\section*{The Rotation Model}
+
+The rotation model corresponds to the work presented in
+\cite{GaravitoCamargo2014}. 
+In that model the Ly-$\alpha$ photons are propagated 
+within a spherical and homogeneous cloud of HI gas undergoing solid
+body rotation.
+The sphere is fully characterized by three parameters: the optical
+depth $\tau$ measured from the center to its surface, the HI
+temperature $T$, and the linear surface velocity $V_{\rm max}$.  
+Photons are emitted at their natural frequency from the center of the
+sphere. 
+Including the effect of dust only changes the overall line
+normalization but not its shape.  
+The results we report in the main body of the paper do not include any
+dust model.
+In the current work, the radiative transfer simulations were done
+using Monte Carlo simulations with the code \texttt{CLARA}
+\cite{CLARA}.
+
+The first important effect of rotation is that it breaks the spherical
+symmetry of the static case. 
+Now the line's observed morphology depends on the angle $\theta$ between the
+line-of-sight (LOS) and the rotation axis. 
+LOS parallel to the rotation axis tend to observed the line without
+any modification from rotation, while the perpendicular LOS will
+observe a maximal change in the line's morphology due to rotation.
+
+The main change in the line's morphology is that it broadens and the
+intensity at the center increases. 
+For high enough rotational velocities the intensity at the peak's
+center increases so much that the line goes from double to single
+peaked, sometimes slightly triple peaked.
+This is the feature that allows this model to fit the observational
+features of \tol.
+
+There is a concise analytical description for those features.
+This description takes into account how different parts of the
+sphere's surface shift in frequency the \lya photons. 
+Different shifts in frequency come from different values for the projected
+velocity along the LOS. 
+As presented in \cite{CLARA}, using the analytical solution for the
+\lya sphectra of a static sphere plus the right frequency shifts
+computed from geometrical considerations, one is able to produce an
+analytical solution for the rotating sphere that reproduces the main
+features found using the full numerical simulation.
+
+The analytical solution for the rotation sphere was the base to
+perform the Markov Chain Monte Carlo Calculation using the
+\texttt{emcee} implementation.
+We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
+$\theta$ using $XX$ steps.
+The results are summarized in Figure $XX$. 
+From this model we find that the fiducial parameters that could
+explain the broad features in \tol\ are $V_{\rm max}$, $\log \tau
+=XX$, $\log_{10} T = $ and  $\theta =$
+
+\section*{The Multiphase Model}
+
+The idealized multiphase model consists of spherical, cold, dens
+clumps of neutral hydrogen (and dust) embedded in a hot, ionized
+medium. 
+The clumps also have a random and an outflowing velocity
+component which totals the number of parameters describing the model
+to be $14$. 
+In order to map out this large parameter space, we randomly drew
+$2500$ sets of parameters within a observationally realistic range
+(based on the considerations of \cite{Laursen2013ApJ...766..124L})
+yielding a large variety of single-, double- and triple-peaked
+spectra. 
+The full analysis of the the spectral features as well as
+more details on the radiative transfer are presented in
+\cite{Gronke2016}.
+
+For the current work, we computed the $\chi^2$ for each of the $2500$
+parameters yielding the best fit parameters of $(...)$. Here, the
+subscripts ${}_{\rm cl}$ and ${}_{\rm ICM}$ stand for the quantities
+filling the clumps and the medium between the clumps,
+respectively. 
+Furthermore, we found that some parameters such as the magnitude of
+the random clump motion $\sigma_{\rm cl}$ improved the fit
+significantly whereas others did not.
+
+Qualitatively as \tol\ possesses a very wide spectrum which can be
+achieved by subsequent scatterings off (relatively) fast moving clumps
+while the multi-phase nature (i.e., the existence of low-density
+channels) ensures the high flux at line center as observed.
+
+\section*{Physical Interpretation}
+
+Both the rotation and the multiphase model constrain the typical
+velocity of the HI gas, with and additional constrain on the typical
+size for the emission region, $D$, on could estimate a dynamical mass with
+
+\begin{equation}
+M_{\rm dyn} = \frac{V^{2}D}{G} = 2.16\times10^{5}
+\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
+\end{equation}
+
+The multiphase model also sets a typical size for the region where the
+clumps are confined.
+In the rotation model the size of that region can be infered from the
+constraint on the total HI mass.
+
 From the optical depth of $10^7$ and the non-detection in the HI line,
@@
 
-\section*{The Rotation Model}
-
-The rotation model corresponds to the work presented in
-\cite{GaravitoCamargo2014}. 
-In that model the Ly-$\alpha$ photons are propagated 
-within a spherical and homogeneous cloud of HI gas undergoing solid
-body rotation.
-The sphere is fully characterized by three parameters: the optical
-depth $\tau$ measured from the center to its surface, the HI
-temperature $T$, and the linear surface velocity $V_{\rm max}$.  
-Photons are emitted at their natural frequency from the center of the
-sphere. 
-Including the effect of dust only changes the overall line
-normalization but not its shape.  
-The results we report in the main body of the paper do not include any
-dust model.
-In the current work, the radiative transfer simulations were done
-using Monte Carlo simulations with the code \texttt{CLARA}
-\cite{CLARA}.
-
-The first important effect of rotation is that it breaks the spherical
-symmetry of the static case. 
-Now the line's observed morphology depends on the angle between the
-line-of-sight (LOS) and the rotation axis. 
-LOS parallel to the rotation axis tend to observed the line without
-any modification from rotation, while the perpendicular LOS will
-observe a maximal change in the line's morphology due to rotation.
-
-The main change in the line's morphology is that it broadens and the
-intensity at the center increases. 
-For high enough rotational velocities the intensity at the peak's
-center increases so much that the line goes from double to single
-peaked, sometimes slightly triple peaked.
-This is the feature that allows this model to fit the observational
-features of \tol.
-
-There is a concise analytical description for those features.
-This description takes into account how different parts of the
-sphere's surface shift in frequency the \lya photons. 
-Different shifts in frequency come from different values for the projected
-velocity along the LOS. 
-As presented in \cite{CLARA}, using the analytical solution for the
-\lya sphectra of a static sphere plus the right frequency shifts
-computed from geometrical considerations, one is able to produce an
-analytical solution for the rotating sphere that reproduces the main
-features found with the full numerical simulation.
-
-\section*{The Multiphase Model}
-The idealized multiphase model consists of spherical, cold, dens
-clumps of neutral hydrogen (and dust) embedded in a hot, ionized
-medium. The clumps also have a random and an outflowing velocity
-component which totals the number of parameters describing the model
-to be $14$. In order to map out this large parameter space, we
-randomly drew $2500$ sets of parameters within a observationally
-realistic range (based on the considerations of
-\cite{Laursen2013ApJ...766..124L}) yielding a large variety of
-single-, double- and triple-peaked spectra. The full analysis of the
-the spectral features as well as more details on the radiative
-transfer are presented in \cite{Gronke2016}.
-
-\textbf{MG: I don't know how much details you want -- should we name
-  all of the $14$ (best fit) parameters? Just delete what is
-  unnecessary.}
-
-For the current work, we computed the $\chi^2$ for each of the $2500$
-parameters yielding the best fit parameters of $(...)$. Here, the
-subscripts ${}_{\rm cl}$ and $_{\rm ICM}$ stand for the quantities
-filling the clumps and the medium between the clumps,
-respectively. Furthermore, we found that some parameters such as the
-magnitude of the random clump motion $\sigma_{\rm cl}$ improved the
-fit significantly whereas others did not. This makes sense also
-qualitatively as \tol\ possesses a very wide spectrum which can be
-achieved by subsequent scatterings off (relatively) fast moving clumps
-while the multi-phase nature (i.e., the existence of low-density
-channels) ensures the high flux at line center as observed.
-
 \end{document}

### 2016-08-08 paper/letter.tex
dynamical mass multiphase

@@
 Both the rotation and the multiphase model constrain the typical
-velocity of the HI gas, with and additional constrain on the typical
-size for the emission region, $D$, on could estimate a dynamical mass with
+velocity $v$ of the HI gas, with and additional constrain on the typical
+size for the emission region $r$ on could estimate a dynamical mass with
 
 \begin{equation}
-M_{\rm dyn} = \frac{V^{2}D}{G} = 2.16\times10^{5}
-\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
+M_{\rm dyn} = \frac{v^{2}r}{G} = 1.16\times10^{9}
+\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
 \end{equation}
 
-The multiphase model also sets a typical size for the region where the
-clumps are confined.
+From the multiphase model we obtained $v=71_{-25}^{+16}$ \kms
+and $r=5$ kpc. 
+This corresponds to a dynamical mass of $M_{\rm
+  dyn}=5.9^{+3.1}_{-3.4}\times 10^{9}$ $M_{\odot}$ which is at least
+$20$ times the HI mass estimated from observations.
+
 In the rotation model the size of that region can be infered from the
 constraint on the total HI mass.
-
 From the optical depth of $10^7$ and the non-detection in the HI line,

### 2016-08-09 paper/letter.tex
streamlined physical interpretation

@@
 
-In the rotation model the size of that region can be infered from the
-constraint on the total HI mass.
-From the optical depth of $10^7$ and the non-detection in the HI line,
-we have an upper limit for the size where the Lya emission comes of
-$D<0.34$kpc.
+In the rotation model the size of the spherical region, $r_{s}$, can
+be infered from the relationship $\tau = \sigma_0 n r_s$, where
+$\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
+cross section at the  line's center, $n$ is the number density. 
+This expresion can be rewritten as
+\begin{equation}
+r_{s} = 0.055 \left(\frac{\tau}{10^7}\right) \left(
+\frac{\mathrm{atoms\ cm^{-3}}}{n}\right) \mathrm{kpc}.
+\end{equation}
+%
+Using this result and assuming a bound for the number density of
+$10^{-2}<n/\mathrm{atoms\ cm^{-3}}<1$ we have $5.5\times 10^{-2}
+< r_s/\mathrm{kpc}<5.5$.
 
- For an homogeneous sphere the HI optical depth from its can be
- written as $\tau = \sigma_0 n D/2$, where $\sigma_0=5.898\times
-10^{-14}$cm$^{-2}$ is the Lyman$\alpha$  optical depth at the 
-line's center, $n$ is the number density and $D$ is the sphere's
-diameter. 
-From this we can impose additional constrains on $D$ from the typical
-values of the Hydrogen number density and our constrain on
-$\tau=10^{7}$.  Using a range of $1<n/\mathrm{atoms/cm}^{-3} <
-10^{-3}$. This gives us a range of $0.11 < D/\mathrm{kpc}<100$. 
-Together from the total HI mass we have thus that the HI region should
-have a diameter of $0.11 < D/\mathrm{kpc}<0.34$.
+This is consistent with the  constraint on the total HI mass and the
+optical depth $\tau_0$ as we show next. The total HI mass can be
+approximated as $M_H = \frac{4\pi}{3} m_H n r_s^3$, where
+$m_H=1.67\times 10^{-24}$ gr is the mass of a single Hydrogen atom.
+This allows us to write the total hydrogen mass as
+\begin{equation}
+M_{H} = 5.70 \times 10^{6} \left(\frac{\tau}{10^{7}}\right)
+\left(\frac{r_s}{\mathrm{kpc}}\right)^2 M_{\odot}
+\end{equation}
+%
+The uppper limit from the HI mass non-detection imposes $r_{s} <
+6.81$ kpc, which is consistent with the bound we found in the first
+place, as we wanted to show.
 
-This can be rewritten in terms of the gas' temperature $T$ and column
-density $N_{H}$as $\tau = 3.31 \times 10^{-14} (10^{4}\mathrm{K}/T)^{1/2}
-(N_{H}/\mathrm{atoms\ cm}^{-2})$.
-
-This allows us to approximate the total hydrogen mass as
-\begin{equation}
-M_{H} = m_{H}  N_{H} D^{2} = 226\times \tau  \left(\frac{T}{10^4
-  \mathrm{K}}\right)^{1/2}\left(\frac{D}{\mathrm{kpc}}\right)^2M_{\odot}
-\end{equation}
-
-On the other hand, we have an estimate for the dynamical mass from the
-galaxy size $D$ and its rotational velocity $V$:
-
-\begin{equation}
-M_{T} = \frac{V^{2}D}{G} = 2.16\times10^{5}
-\left(\frac{V}{\mathrm{km\ s}^{-1}}\right)^2\left(\frac{D}{\mathrm{kpc}}\right) M_{\odot}
-\end{equation}
-
-From this limit and the rotational velocity of $300$ km/s and the
-limit in the size $D$ we have limits of for the dynamical mass of
-$2.1\times 10^{9}$M$_{\odot}$ $<M_D<$  $6.6\times 10^{9}$M$_{\odot}$.
-which is at least $7$ to $25$ times larger than the H$I$ mass. The
-mass to luminosity ratio is in turn between $2$ to $7$ times
-$L_{\odot}/M_{\odot}$ considering the total luminosity in the $V$
-band.
+Using those size bounds for the spherical model we find a constrain for
+the dynamical mass of $5.45\times 10^{8}M_{\odot} < M_{\rm dyn} <
+5.45\times 10^{10} M_{\odot}$.
 

### 2016-08-09 paper/letter.tex
update body

@@
 \\
-JEFR$^{1}$, MCRG$^1$, JNGC$^2$, MG$^3$, MD$^3$
+JEFR$^{1}$, MG$^3$, MCRG$^1$, JNGC$^2$, MD$^3$
 \\
@@
 interpretation so far. 
-We explain these features by two different models: an
-homogeneous sphere undergoing gas bulk rotation and an interstellar
+In this letter we explain these features by two different models: an
+homogeneous gaseous sphere undergoing bulk rotation and an interstellar
 medium composed by clumps with random motions.
 It is the first time that an observed \lya\ spectrum can be explained
-assuming these physical conditions.
+assuming either of these physical conditions.
 We find that both models independently require high velocities that
-translate into a dynamical mass at least $10$ times larger than the
+translate into a dynamical mass at least $20$ times larger than the
 neutral mass hydrogen in the galaxy. 
-We argue that a possibility to explain the high
-dynamical mass is the presence of a super-massive black hole. 
-Ionization emission lines present in this galaxy support the idea that
-\tol\ might have harbored an an Active Galactic Nucleus  
-The implications of our findings for the study of LAEs, including the
-first generation of galaxies are manifold. 
-It demonstrates the importance of considering rotation and multiphase
-physics under the possible conditions shaping the \lya\ spectra of the
-first galaxies. 
+We argue that a plaussible explanation for the high dynamical mass is
+the presence of a super-massive black hole.  
+This work demonstrates the importance of considering rotation and
+multiphase physics under the possible conditions shaping the
+\lya\ spectra of the first galaxies. 
 Additionally, if future kinematic maps of \tol\ confirm the high
 velocities postulated in our model, it would provide new
-evidence for dwarf galaxies as hosts of active supermassive black
+evidence for dwarf galaxies as hosts of supermassive black
 holes.  
@@
 effects that bulk rotation and a multiphase state in the interstellar
-medium should have on on the Lyman-$\alpha$ line.
+medium should have on the Lyman-$\alpha$ line.
 
@@
 velocity. 
-When the rotational velocity is close to the half-line width of the
-static line the line becomes single peaked and symmetric, a unique
-feature that other theoretical models find difficult to reproduce
-without introducing more complexity into the gas distribution.
+When the rotational velocity is high enough, the line becomes single
+peaked and symmetric, a unique feature that other theoretical models
+find difficult to reproduce without introducing more complexity into
+the gas distribution.
 
@@
 These two special features in \tol\ had evaded a physical
-interpretation so far, because bulk rotation and a multiphase ISM can
-independently explain the \lya\ line in \tol.
+interpretation so far. Using either bulk rotation or a multiphase ISM,
+we manage to explain the \lya\ line in \tol.
 
 Figure 1. summarizes our findings.
-Dots represent the observational data for \tol with the
+Dots represent the observational data for \tol\ with the
 overplot from our best fit models from the full radiative transfer
@@
 The assumed physical size and the velocity dispersion $\sigma_{\rm
-  cl}$ correspond to a  dynamical mass of  $3.0^{+1.5}_{-1.8}\times
-10^9$ M$_{\odot}$.
+  cl}$ correspond to a  dynamical mass of  $M_{\rm
+  dyn}=5.9^{+3.1}_{-3.4}\times 10^{9}$ $M_{\odot}$.
 
-Radio surveys of the 21cm line have put an upper limit to the neutral
-hydrogen mass in \tol\ of $M<2.65\times 10^{8}$ M$_{\odot}$ \cite{pustilnikmartin07}. 
-In the case of the rotation model, this information help us to constrain the
-diameter of the HI region where the \lya\ emission and transfer takes
-place. 
-We find this size to be in the range $0.11 < D/\mathrm{kpc}<0.34$, one
-order of magnitude smaller than \tol's size in the optical.   
-That size and the rotational velocity of $300$\kms put a constraint on
-the dynamical mass of $4.5^{+2.1}_{-2.4} \times 10^{9}$M$_{\odot}$.
+In the rotation model assuming reasonable bounds for the number
+density of neutral Hydrogen atoms (
+$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
+of the emission region can be bracketed to be in $0.55 <
+r_s/\mathrm{kpc}< 5.5$.
+Using $V_{\rm max}=300$km s$^{-1}$, we find a dynamical mass range of
+$5.45\times 10^{9}M_{\odot} < M_{\rm dyn} < 5.45\times 10^{10} M_{\odot}$.
 
-This is evidence for a dynamical mass at least 11 (multiphase case) to
-17 (rotation case) times higher than the mass in neutral hydrogen.  
+Radio surveys of the 21 cm line have put an upper limit to the neutral
+hydrogen mass in \tol\ of $M<2.65\times 10^{8}$ M$_{\odot}$
+\cite{pustilnikmartin07}.  
+Our models thus provide evidence for a dynamical mass at least 20 times
+higher than the mass in neutral hydrogen.   
 There are three main possibilities to explain the dynamical 
@@
 galaxies.  
+Ionization emission lines present in this galaxy support the idea that
+\tol\ might have harbored an an Active Galactic Nucleus.
 
@@
 
-From the multiphase model we obtained $v=71_{-25}^{+16}$ \kms
+From the multiphase model we obtained $v=71_{-25}^{+17}$ \kms
 and $r=5$ kpc. 
@@
 Using this result and assuming a bound for the number density of
-$10^{-2}<n/\mathrm{atoms\ cm^{-3}}<1$ we have $5.5\times 10^{-2}
+$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$ we have $0.55
 < r_s/\mathrm{kpc}<5.5$.
@@
 Using those size bounds for the spherical model we find a constrain for
-the dynamical mass of $5.45\times 10^{8}M_{\odot} < M_{\rm dyn} <
+the dynamical mass of $5.45\times 10^{9}M_{\odot} < M_{\rm dyn} <
 5.45\times 10^{10} M_{\odot}$.

### 2016-08-11 code/mc.py
mcmc includes now y_sigma in chisquared

@@ -4,135 +4,119 @@ import emcee
 import os
 
 #Constants
-
-z = 0
 c = 299792.458
 
 #Functions
 
 def model_to_data_interp(x_m, y_m, x_d):
 
-    f = interp1d(x_m, y_m, kind="linear")
+    f = interp1d(x_m, y_m, kind="linear", fill_value=0.0, bounds_error=False)    
+    x_m_new = x_d.copy()
+    y_m_new = f(x_m_new)
 
-    try:
-        x_m_new = x_d
-        y_m_new = f(x_d)
-
-        return x_m_new, y_m_new
-
-    except ValueError:
-
-        n = len(x_d)
-
-        x_m_new = x_d
-        y_m_new = zeros(n)
-
-        for i in range(n):
-
-            x_d_i = x_d[i]
-
-            if(x_d_i >= x_m[0] and x_d_i <= x_m[-1]):
-                y_m_new[i] = f(x_d_i)
-            else:
-                y_m_new[i] = 0.0
-
-        return x_m_new, y_m_new
+    return x_m_new, y_m_new
 
 
-def normalization(y_d, y_m):
+def normalization(x_d, y_d, x_m, y_m):
 
-    obs_int = sum(y_d)
-    teo_int = sum(y_m)
-    y_m = y_m*obs_int/teo_int
+    obs_int = trapz(y_d, x_d)
+    teo_int = trapz(y_m, x_m)
+    y_m = y_m * obs_int/teo_int
 
     return y_m
 
-def model(logtau, vmax, theta, logT, voff, x_d, y_d):
+def model(logtau, vmax, theta, logT, x_d, y_d):
 
-    os.system( ('./analytic_solution.x %f %f %f > "./model_lt%f_vm%f_th%f.dat"')%(10.0**logtau, vmax, theta, logtau, vmax, theta) )
+    filename = "model_lt{}_vm{}_th{}.dat".format(logtau, vmax, theta)
+    os.system( ('./analytic_solution.x {} {} {} > {}'.format(10.0**logtau, vmax, theta, filename)))
 
     try:
-	       mod = genfromtxt( ('./model_lt%f_vm%f_th%f.dat')%(logtau, vmax, theta) )
+        mod = genfromtxt(filename)
 
     except ValueError:
[…]

### 2016-08-12 code/mc.py
udpated mc with different sigma for inital walkers

@@ -58,7 +58,7 @@ def lnprior(param):
 
     logtau, vmax, theta, logT = param
 
-    if 6.0 < logtau < 8.0 and 200 < vmax < 500 and 0 < theta < 90 and 4 < logT < 4.5 :
+    if 6.0 < logtau < 9.0 and 200.0 < vmax < 600.0 and 0 < theta < 90 and 4 < logT < 4.5 :
         return 0.0
 
     return -inf
@@ -99,8 +99,8 @@ y_data_sigma = tol[:,2]
 
 logtau_0 = 7.0
 vmax_0 = 300
-theta_0 = 45.0
-logT_0 = 4.0
+theta_0 = 10.0
+logT_0 = 4.3
 
 #x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, x_data, y_data)
 
@@ -111,12 +111,12 @@ first_guess = [logtau_0, vmax_0, theta_0, logT_0]
 #Running emcee
 
 ndim = 4
-nwalkers = 8
-nsteps = 10
+nwalkers = 24
+nsteps = 500
 
-pos = [first_guess+ 1e-3*random.randn(ndim) for i in range(nwalkers)]
+pos = [first_guess+ array([0.2,20.0,5.0,0.01])*random.randn(ndim) for i in range(nwalkers)]
 
-sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data, y_data_sigma), threads=4)
+sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data, y_data_sigma), threads=24)
 
 print("Running MCMC...")
 sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())

### 2016-08-12 code/mc.py
writes chain as it runs

@@ -99,7 +99,7 @@ y_data_sigma = tol[:,2]
 
 logtau_0 = 7.0
 vmax_0 = 300
-theta_0 = 10.0
+theta_0 = 45.0
 logT_0 = 4.3
 
 #x_0, y_0 = model(logtau_0, vmax_0, theta_0, logT_0, x_data, y_data)
@@ -114,22 +114,33 @@ ndim = 4
 nwalkers = 24
 nsteps = 500
 
-pos = [first_guess+ array([0.2,20.0,5.0,0.01])*random.randn(ndim) for i in range(nwalkers)]
+pos0 = [first_guess+ array([0.2,20.0,5.0,0.01])*random.randn(ndim) for i in range(nwalkers)]
 
 sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data, y_data_sigma), threads=24)
 
-print("Running MCMC...")
-sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())
-print("Done!")
+#print("Running MCMC...")
+#sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())
+#print("Done!")
+
+f = open("chain.dat", "w")
+f.close()
+
+for result in sampler.sample(pos0, iterations=nsteps, storechain=False):
+    position = result[0]
+    f = open("chain.dat", "a")
+    print position
+    for k in range(position.shape[0]):
+        f.write("{} {}\n".format(k, " ".join(str(v) for v in position[k])))
+    f.close()
 
 
 # Saving results
 
-samples_fc = sampler.flatchain
+#samples_fc = sampler.flatchain
 
-savetxt('sampler_flatchain.dat', samples_fc, delimiter=',')
+#savetxt('sampler_flatchain.dat', samples_fc, delimiter=',')
 
-print("Mean acceptance fraction: {0:.3f}".format(mean(sampler.acceptance_fraction)))
+#print("Mean acceptance fraction: {0:.3f}".format(mean(sampler.acceptance_fraction)))
 
 #Links:
 # https://github.com/dfm/emcee/blob/master/examples/line.py

### 2016-08-15 code/mc.py
used mc code

@@ -118,29 +118,28 @@ pos0 = [first_guess+ array([0.2,20.0,5.0,0.01])*random.randn(ndim) for i in rang
 
 sampler = emcee.EnsembleSampler(nwalkers, ndim, lnprob, args=(x_data, y_data, y_data_sigma), threads=24)
 
-#print("Running MCMC...")
-#sampler.run_mcmc(pos, nsteps, rstate0=random.get_state())
-#print("Done!")
+print("Running MCMC...")
+sampler.run_mcmc(pos0, nsteps)# rstate0=random.get_state())
+print("Done!")
 
-f = open("chain.dat", "w")
-f.close()
+#f = open("chain.dat", "w")
+#f.close()
 
-for result in sampler.sample(pos0, iterations=nsteps, storechain=False):
-    position = result[0]
-    f = open("chain.dat", "a")
-    print position
-    for k in range(position.shape[0]):
-        f.write("{} {}\n".format(k, " ".join(str(v) for v in position[k])))
-    f.close()
+#for result in sampler.sample(pos0, iterations=nsteps, storechain=False):
+#    position = result[0]
+#    f = open("chain.dat", "a")
+#    print position
+#    for k in range(position.shape[0]):
+#        f.write("{} {}\n".format(k, " ".join(str(v) for v in position[k])))
+#    f.close()
 
 
 # Saving results
 
-#samples_fc = sampler.flatchain
+samples_fc = sampler.flatchain
+savetxt('sampler_flatchain.dat', samples_fc, delimiter=',')
 
-#savetxt('sampler_flatchain.dat', samples_fc, delimiter=',')
-
-#print("Mean acceptance fraction: {0:.3f}".format(mean(sampler.acceptance_fraction)))
+print("Mean acceptance fraction: {0:.3f}".format(mean(sampler.acceptance_fraction)))
 
 #Links:
 # https://github.com/dfm/emcee/blob/master/examples/line.py

### 2016-08-16 paper/letter.tex
title, authors, affiliations and exact values

@@
 \noindent
-\textbf{Þú ert jörðin}
+\textbf{Lyman-$\alpha$ sketches a massive dwarf}
 \\
 \\
-JEFR$^{1}$, MG$^3$, MCRG$^1$, JNGC$^2$, MD$^3$
+Jaime E. Forero-Romero$^{1}$, Max Groenke$^2$, Mar\'ia Camila
+Remolina-Guti\'errez$^1$, Juan Nicol\'as
+Garavito-Carmargo$^3$, Mark Dijkstra$^2$.
 \\
@@
 \scriptsize
-{$^1$ Bogota
+{$^1$ Departamento de Física, Universidad de los Andes, Cra. 1
+  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia 
 \\
-$^2$ Tucson
+$^2$ Institute of Theoretical Astrophysics, University of Oslo,
+Postboks 1029 Blindern, NO-0315 Oslo, Norway.
 \\
-$^3$ Oslo
+$^3$ Department of Astronomy, University of Arizona, 933 North Cherry
+Avenue, Tucson, AZ 85721, USA. 
 \normalsize
@@
 homogeneous gaseous sphere undergoing bulk rotation and an interstellar
-medium composed by clumps with random motions.
+medium composed by outflowing clumps with additional random motions.
 It is the first time that an observed \lya\ spectrum can be explained
 assuming either of these physical conditions.
-We find that both models independently require high velocities that
-translate into a dynamical mass at least $20$ times larger than the
-neutral mass hydrogen in the galaxy. 
+We find that both models independently require high velocities
+(either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
+dispersion of $71^{+17}_{-25}$ km s$^{-1}$ with outflows of
+$79^{+167}_{-60}$ km s$^{-1}$) consistent with a dynamical mass on
+the order of $5\times 10^9$ solar masses, which is at least $20$ times
+larger than the neutral mass hydrogen in the galaxy.   
 We argue that a plaussible explanation for the high dynamical mass is
@@
 This work demonstrates the importance of considering rotation and
-multiphase physics under the possible conditions shaping the
+multiphase physics among the possible conditions shaping the
 \lya\ spectra of the first galaxies. 
@@
 These two special features in \tol\ had evaded a physical
-interpretation so far. Using either bulk rotation or a multiphase ISM,
-we manage to explain the \lya\ line in \tol.
+interpretation so far. 
+Including the effects of either bulk rotation or a multiphase ISM, we
+manage to explain the \lya\ line in \tol.
 
@@
 \includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
-\caption{{\bf Broadn, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
+\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
   Dots correspond to the observational data. The line shows the results
@@
 From this model we find that the fiducial parameters that could
-explain the broad features in \tol\ are $V_{\rm max}$, $\log \tau
-=XX$, $\log_{10} T = $ and  $\theta =$
+explain the broad features in \tol\ are $V_{\rm max}=348^{+75}_{-48}$
+km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, $\log_{10} T/\mathrm
+{K} = 4.27^{+0.11}_{-0.18}$ and  $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
+\caption{{\bf Results from the Markov Chain Monte Carlo compuation for the rotation model.}}
+\end{center}
+\end{figure}
 

### 2016-08-16 paper/letter.tex
updated 1sigma values

@@
 (either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
-dispersion of $71^{+17}_{-25}$ km s$^{-1}$ with outflows of
-$79^{+167}_{-60}$ km s$^{-1}$) consistent with a dynamical mass on
-the order of $5\times 10^9$ solar masses, which is at least $20$ times
+dispersion of $71^{+12}_{-12}$ km s$^{-1}$ with outflows of
+$55^{+67}_{-37}$ km s$^{-1}$) consistent with a dynamical mass on
+the order of two billion solar masses, which is at least $20$ times
 larger than the neutral mass hydrogen in the galaxy.   
@@
 The best parameters in the rotation model are a rotational velocity of 
-$v_{max}=300^{+xx}_{-xx}$\kms, an optical depth $\log\tau=7^{+xx}_{-xx}$ and a temperature
-of $T=1.5^{+xx}_{-xx}\times 10^{4}$K. 
+$V_{\rm max}=348^{+75}_{-48}$ \kms, an optical depth $\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and a temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$. 
 This translates into a column density of $\log N_{HI} /
 \mathrm{atoms\ cm}^{-2} =  20.5^{+xx}_{-xx}$.  
-This model is also able to constrain the angle between the rotation
-axis and the observational line-of-sight to
-$\theta=65^{+xx}_{-xx}$$^{\circ}$.
+This model is also able to constrain the angle between the plane perpendicular to the rotation axis and the observational line-of-sight to
+$\theta = 35.78^{+2.13}_{-1.88}$ degrees.
 
 In the multiphase model the best constrained parameters are
-the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+17}_{-25}$ \kms,
-the clumps outflowing velocity $v_{\infty, \rm{cl}}=79^{+167}_{-60}$
+the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+12}_{-12}$ \kms,
+the clumps outflowing velocity $v_{\infty, \rm{cl}}=55^{+67}_{-37}$
 \kms and the fraction of the \lya emission that is  coming
 from the cold clumps  
-$P_{cl}=0.72^{+0.20}_{-0.32}$. 
+$P_{cl}=0.77^{+0.15}_{-0.44}$. 
 The multiphase model assumes that the clouds are distributed over a
@@
   cl}$ correspond to a  dynamical mass of  $M_{\rm
-  dyn}=5.9^{+3.1}_{-3.4}\times 10^{9}$ $M_{\odot}$.
+  dyn}=2.9^{+2.1}_{-0.9}\times 10^{9}$ $M_{\odot}$.
 

### 2016-08-16 paper/letter.tex
minor typo

@@
   cl}$ correspond to a  dynamical mass of  $M_{\rm
-  dyn}=2.9^{+2.1}_{-0.9}\times 10^{9}$ $M_{\odot}$.
+  dyn}=2.9^{+1.1}_{-0.9}\times 10^{9}$ $M_{\odot}$.
 

### 2016-08-18 paper/letter.tex
latest version of the letter. no black hole.

@@
 \noindent
-\textbf{Lyman-$\alpha$ sketches a massive dwarf}
+\textbf{Lyman-$\alpha$ emission reveals a dispersion-supported dwarf}
 \\
@@
 (either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
-dispersion of $71^{+12}_{-12}$ km s$^{-1}$ with outflows of
-$55^{+67}_{-37}$ km s$^{-1}$) consistent with a dynamical mass on
-the order of two billion solar masses, which is at least $20$ times
-larger than the neutral mass hydrogen in the galaxy.   
-We argue that a plaussible explanation for the high dynamical mass is
-the presence of a super-massive black hole.  
-This work demonstrates the importance of considering rotation and
-multiphase physics among the possible conditions shaping the
-\lya\ spectra of the first galaxies. 
-Additionally, if future kinematic maps of \tol\ confirm the high
-velocities postulated in our model, it would provide new
-evidence for dwarf galaxies as hosts of supermassive black
-holes.  
+dispersion of $69^{+17}_{-15}$ km s$^{-1}$ with outflows of
+$79^{+73}_{-42}$ km s$^{-1}$) consistent with a dynamical mass at
+least $10$ times larger than its baryonic mass.  
+We argue that the most plaussible explanation is provided by the
+multiphase model as it is a close match to the galaxy scaling relationship
+for a dark matter dominated dwarf elliptical supported by its
+velocity dispersion. 
+This work demonstrates the importance of considering multiphase
+physics among the possible conditions shaping the \lya\ spectra of the
+first galaxies.   Additionally, if future kinematic maps of
+\tol\ confirm the high velocities postulated in our model, it would
+help to stablish the \lya\ line morphology as an observational tracer to
+study the co-evolution of the first generation of galaxies and its
+host dark matter halos. 
 }
@@
 The best parameters in the rotation model are a rotational velocity of 
-$V_{\rm max}=348^{+75}_{-48}$ \kms, an optical depth $\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and a temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$. 
-This translates into a column density of $\log N_{HI} /
-\mathrm{atoms\ cm}^{-2} =  20.5^{+xx}_{-xx}$.  
-This model is also able to constrain the angle between the plane perpendicular to the rotation axis and the observational line-of-sight to
-$\theta = 35.78^{+2.13}_{-1.88}$ degrees.
+$V_{\rm max}=348^{+75}_{-48}$ \kms, an optical depth
+$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and a temperature of $\log_{10}
+T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.  
+This model is also able to constrain the angle between the plane
+perpendicular to the rotation axis and the observational line-of-sight
+to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
 
 In the multiphase model the best constrained parameters are
-the clump velocity dispersion  $\sigma_{\rm{cl}}=71^{+12}_{-12}$ \kms,
-the clumps outflowing velocity $v_{\infty, \rm{cl}}=55^{+67}_{-37}$
+the clump velocity dispersion  $\sigma_{\rm{cl}}=69^{+17}_{-15}$ \kms,
+the clumps outflowing velocity $v_{\infty, \rm{cl}}=79^{+73}_{-42}$
 \kms and the fraction of the \lya emission that is  coming
-from the cold clumps  
-$P_{cl}=0.77^{+0.15}_{-0.44}$. 
+from the cold clumps  $P_{cl}=0.78^{+0.16}_{-0.43}$. 
 The multiphase model assumes that the clouds are distributed over a
@@
   cl}$ correspond to a  dynamical mass of  $M_{\rm
-  dyn}=2.9^{+1.1}_{-0.9}\times 10^{9}$ $M_{\odot}$.
-
-In the rotation model assuming reasonable bounds for the number
-density of neutral Hydrogen atoms (
+  dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$. In the rotation
+model assuming reasonable bounds for the number density of neutral Hydrogen atoms (
 $0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
@@
 
-Radio surveys of the 21 cm line have put an upper limit to the neutral
-hydrogen mass in \tol\ of $M<2.65\times 10^{8}$ M$_{\odot}$
-\cite{pustilnikmartin07}.  
-Our models thus provide evidence for a dynamical mass at least 20 times
-higher than the mass in neutral hydrogen.   
-There are three main possibilities to explain the dynamical 
-mass: stars, dark matter and a supermassive black hole. 
-The stellar mass in old stars has been constrained by non-detections
-in the K-band to be $<XXX$M$_{\odot}$.
-Considering a standard dark matter halo, it can only contribute to
-$xx$ M$_{\odot}$ in the region of interest. 
-A super massive black hole remains an open possibility. 
-Recent observations of ultra-compact dwarf galaxies
-\cite{Seth2014} have confirmed the presence of super-massive black
-holes containing $15\%$ of the total object mass, suggesting that
-there is a large population of undetected black holes in dwarf
-galaxies.  
-Ionization emission lines present in this galaxy support the idea that
-\tol\ might have harbored an an Active Galactic Nucleus.
+Which solution is more plausible? If \tol\ followed the fundamental
+plane relationship between its mean surface brightness $I_e$, the
+projected half-light radius $R_e$ and the velocity dispersion
+$\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e +
+0.55$ \cite{2009ApJ...698.1590G,2011ApJ...726..108T},  
+the expected velocity dispersion would be on the order of $47\pm 3$
+\kms, which only presents a small tension with the multiphase model.   
+The solution of a high rotational velocity pushes \tol\ outside the
+scaling relationship for dwarfs. One could account for the high
+velocities if the galaxy had a supermassive black hole accounting for
+the mass that cannot be explained by baryonic or dark mass. The economy of
+assumptions makes it more reasonable to expect that the multiphase
+model could be a better match to reality.
 
@@
 
-These findings demonstrate the importance of including rotation and multiphase
-conditions as features to model the \lya\ line in high redshift
+These findings demonstrate the importance of including multiphase
+conditions as a feature to model the \lya\ line in high redshift
 galaxies.
-Additionally, if the hypothesis of a supermassive black
-hole in \tol\ proves to be consistent with future observational
-kinematic maps, it could correspond to a so far undetected black hole
-in a dwarf galaxy, providing a new way to test and probe
-theories on the co-evolution of galaxies and black holes in the first
-generation of galaxies.
+If the estimated velocity dispersion proves to be consistent with
+future observational kinematic maps, it could provide a new way to
+study velocity dispersions in distant gas rich starbursting galaxies, 
+opening the possibility to study the dynamical co-evolution of
+galaxies and dark matter halos in the first generation of galaxies.
 
@@
   Dots correspond to the observational data. The line shows the results
-of our best model from a full radiative transfer simulation both for the rotation and multiphase models.}
+of our best model from a full radiative transfer simulation both for
+the rotation and multiphase models.} 
 \end{center}
@@
 
-FIXME: Add non detection in 2MASS %\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
-
+%\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
+% TOLOLO 00021
+%https://ned.ipac.caltech.edu/cgi-bin/objsearch?objname=Tol+21&extend=no&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=RA+or+Longitude&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES
 \tol receding velocity is $7785\pm 50$km s$^{-1}$, which translates
@@
 fraction of $20$\% for Ly$\alpha$ radiation.
+The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
+L$_{\odot}$ as measured by GALEX.
 
@@
 
-Interpretation by \cite{mashesse03}.
+The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
+$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
+\cite{2008ApJ...678..804E}.  Using a convertion betwen fluxes and
+stellar mass calibrted on the Large Magellanic Cloud $M_{\star} =
+10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
+(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
+distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
+M_{\odot}$, with a $30\%$ uncertainty coming from the callibration
+process \cite{2012AJ....143..139E}.
 
@@
 
-From the multiphase model we obtained $v=71_{-25}^{+17}$ \kms
+From the multiphase model we obtained $v=69_{-15}^{+17}$ \kms
 and $r=5$ kpc. 
 This corresponds to a dynamical mass of $M_{\rm
-  dyn}=5.9^{+3.1}_{-3.4}\times 10^{9}$ $M_{\odot}$ which is at least
-$20$ times the HI mass estimated from observations.
+  dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$ which is at least
+$5$ times the HI mass plus the stellar mass estimated from
+observations.
 

### 2016-08-18 code/plane.py
plano

@@ -1,0 +1,30 @@
+import math
+
+L = 9.43E8 #UV bol lumgalex
+alpha = 0.53 # kpc scale radius from noeske
+R = 0.05
+I = L/(4.0* math.pi * R * 1E3 * R * 1E3)
+print 'R {}'.format(R)
+print 'log I {}'.format(math.log10(I))
+print 'log R {}'.format(math.log10(R))
+print 'log L {}'.format(math.log10(L))
+sigma = 10.0**((math.log10(I) + 1.21*math.log10(R)-0.55)/1.6)
+print 'log sigma {}'.format(math.log10(sigma))
+print 'sigma {}'.format(sigma)
+
+
+obs = True
+
+if obs:
+    import numpy as np
+
+    data = np.loadtxt('scale.dat')
+    log_sigma = data[:,0]
+    log_r = data[:,1]
+    log_lum = data[:,2]
+    ii = (log_sigma < np.log10(90.0)) & (log_sigma > np.log10(30.0)) 
+    ii = ii & (log_lum> np.log10(0.33*L))
+    print 10**log_sigma[ii]
+    print 10**log_r[ii]
+    print 10**log_lum[ii]
+    #print log_sigma

### 2016-08-29 paper/letter.tex
Max comments

@@
 \newcommand{\pasj}{PASJ}    
+\newcommand{\sigmaclump}{$69^{+17}_{-15}$ km s$^{-1}$}
+\newcommand{\inftyclump}{$79^{+73}_{-42}$ km s$^{-1}$}
+\newcommand{\probaclump}{$0.78^{+0.16}_{-0.43}$}
 \def\simgt{\lower.5ex\hbox{\gtsima}}
@@
 (either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
-dispersion of $69^{+17}_{-15}$ km s$^{-1}$ with outflows of
+dispersion of \sigmaclump with outflows of
 $79^{+73}_{-42}$ km s$^{-1}$) consistent with a dynamical mass at
@@
 In the multiphase model the best constrained parameters are
-the clump velocity dispersion  $\sigma_{\rm{cl}}=69^{+17}_{-15}$ \kms,
-the clumps outflowing velocity $v_{\infty, \rm{cl}}=79^{+73}_{-42}$
-\kms and the fraction of the \lya emission that is  coming
-from the cold clumps  $P_{cl}=0.78^{+0.16}_{-0.43}$. 
+the clump velocity dispersion  $\sigma_{\rm{cl}}=$\sigmaclump\
+the clumps outflowing velocity $v_{\infty, \rm{cl}}=$\inftyclump\
+and the fraction of the \lya\ emission that is  coming
+from the cold clumps  $P_{\rm cl}=$\probaclump.
 The multiphase model assumes that the clouds are distributed over a
@@
 Another observational test includes the measurement of the escape
-fraction of Ly continuum ionizing radiation. 
+fraction of \lya\ continuum ionizing radiation. 
 In the rotational model this fraction should be zero, while
@@
 \tol receding velocity is $7785\pm 50$km s$^{-1}$, which translates
-into a distance of $106.6$ Mpc (Hubble constant 73 Mpc km$^{-1}$
-s$^{1}$)
+into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
+Mpc km s$^{-1}$) 
 Its metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
@@
 As presented in \cite{CLARA}, using the analytical solution for the
-\lya sphectra of a static sphere plus the right frequency shifts
+\lya\ spectra of a static sphere plus the right frequency shifts
 computed from geometrical considerations, one is able to produce an
@@
 $\theta$ using $XX$ steps.
-The results are summarized in Figure $XX$. 
+The results are summarized in Figure \ref{emceeresults}. 
 From this model we find that the fiducial parameters that could
@@
 \includegraphics[width=1.0\textwidth]{emcee_results.pdf}
-\caption{{\bf Results from the Markov Chain Monte Carlo compuation for the rotation model.}}
+\caption{{\bf Results from the Markov Chain Monte Carlo compuation for
+    the rotation model.}\label{emceeresults}} 
 \end{center}
@@
 to be $14$.
+
 In order to map out this large parameter space, we randomly drew
@@
 For the current work, we computed the $\chi^2$ for each of the $2500$
-parameters yielding the best fit parameters of $(...)$. Here, the
-subscripts ${}_{\rm cl}$ and ${}_{\rm ICM}$ stand for the quantities
-filling the clumps and the medium between the clumps,
-respectively. 
 Furthermore, we found that some parameters such as the magnitude of
@@
 significantly whereas others did not.
+
+We find that the best constrained parameters are the clump velocity
+dispersion $\sigma_{\rm cl}=$\sigmaclump,  the outflowing clump
+velocity $v_{\infty {\rm, cl}}=$\inftyclump\ and the probability that
+the \lya\ emission comes from the clumps $P_{\rm cl}=$\probaclump.
 
@@
 
-From the multiphase model we obtained $v=69_{-15}^{+17}$ \kms
-and $r=5$ kpc. 
-This corresponds to a dynamical mass of $M_{\rm
+From the multiphase model we obtained $v=$\sigmaclump
+and $r=5$ kpc. This corresponds to a dynamical mass of $M_{\rm
   dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$ which is at least

### 2016-08-29 paper/letter.tex
Nico's comments

@@
 We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
-$\theta$ using $XX$ steps.
+$\theta$ using $500$ steps with $24$ walkers for a total of $12000$
+points.
 The results are summarized in Figure \ref{emceeresults}. 
@@
 \end{figure}
+
+\section*{The Outflow Model}
+The galaxy outflow model is a highly sucessful framework to fit
+and interprete \lya\ line observations.
 

### 2016-09-01 paper/letter.tex
comments from mark

@@
 require state-of-the-art Monte Carlo radiative transfer simulations.
-Recent advances in these computational models have explored the
-effects that bulk rotation and a multiphase state in the interstellar
-medium should have on the Lyman-$\alpha$ line.
-
-The most important consequence of bulk rotation is that, even for a
-spherical gas distribution, the line morphology now depends on the
-viewing angle respect to the rotation axis.  
-For a line of sight perpendicular to the rotation axis the intensity
-and the line center and the line width increase with rotational
-velocity. 
-When the rotational velocity is high enough, the line becomes single
-peaked and symmetric, a unique feature that other theoretical models
-find difficult to reproduce without introducing more complexity into
-the gas distribution.
-
-This is the case of a multiphase interstellar medium.
-The model is more complex as it must take into account the behavior
-of neutral dense hydrogen clumps dispersed in a tenuous intraclump medium.  
-Corresponding to the elaborate physical conditions in the model,
-there are a wide variety of possible emerging spectra.
-This variety includes single, double and triple peaked
-spectra with different degrees of symmetry around the line's center.
 
@@
 Commonly, the Ly-$\alpha$ line has a single or asymmetric double peak. 
-These two special features in \tol\ had evaded a physical
-interpretation so far. 
-Including the effects of either bulk rotation or a multiphase ISM, we
-manage to explain the \lya\ line in \tol.
+These two special features in \tol\ cannot be explained with
+conventional models.
 
+In this letter we show how the \tol's \lya\ profile can be explained
+either by rotation or the recently developed class of more complex
+multiphase models. These models predict a wider variety of spectra
+including, single, double and triply peaked spectra.  
 Figure 1. summarizes our findings.
 Dots represent the observational data for \tol\ with the
-overplot from our best fit models from the full radiative transfer
-simulations for a rotating sphere (continuous line) and a clumpy ISM
+overplot from our best fit models from the analytical solution for a
+rotating homogeneous gas sphere (continuous line) and a clumpy ISM
 (dashed line).
+This is the first time that these models have been introduced with
+success to explain the a \lya\ profile.
 

### 2016-09-01 paper/letter.tex
BH is back

@@
 \newcommand{\apjs}{ApJS}  
+\newcommand{\pasa}{PASA}  
 \newcommand{\apjl}{ApJL}  
@@
 \noindent
-\textbf{Lyman-$\alpha$ emission reveals a dispersion-supported dwarf}
+\textbf{Lyman-$\alpha$ emission sketches a massive dwarf}
 \\
@@
 least $10$ times larger than its baryonic mass.  
-We argue that the most plaussible explanation is provided by the
-multiphase model as it is a close match to the galaxy scaling relationship
-for a dark matter dominated dwarf elliptical supported by its
-velocity dispersion. 
+We argue that the most plausible explanation for this excess of
+dynamical mass is the presence of a supermassive black hole at the
+center of \tol. 
 This work demonstrates the importance of considering multiphase
-physics among the possible conditions shaping the \lya\ spectra of the
-first galaxies.   Additionally, if future kinematic maps of
-\tol\ confirm the high velocities postulated in our model, it would
-help to stablish the \lya\ line morphology as an observational tracer to
-study the co-evolution of the first generation of galaxies and its
-host dark matter halos. 
+physics and rotation among the possible conditions shaping the
+\lya\ spectra of the first galaxies.  
+Additionally, if future kinematic maps of \tol\ confirm the high
+velocities postulated in our model, it would provide new
+evidence for dwarf galaxies as hosts of supermassive black
+holes.  
 }
@@
 However, the physical interpretation of Ly-$\alpha$ observations is
-not straightforward. 
+not straightforward \cite{2015ApJ...805...14R}. 
 This is due to the resonant nature of the Ly-$\alpha$ line. 
@@
 These two special features in \tol\ cannot be explained with
-conventional models.
+conventional models \cite{2006A&A...460..397V,2015ApJ...812..123G}.
 
@@
 either by rotation or the recently developed class of more complex
-multiphase models. These models predict a wider variety of spectra
+multiphase models that predict a wider variety of spectra
 including, single, double and triply peaked spectra.  
@@
 Dots represent the observational data for \tol\ with the
-overplot from our best fit models from the analytical solution for a
-rotating homogeneous gas sphere (continuous line) and a clumpy ISM
-(dashed line).
+overplot from our best fits from the analytical solution for a
+rotating homogeneous gas sphere (continuous line) and the multiphase
+model (dashed line). 
 This is the first time that these models have been introduced with
-success to explain the a \lya\ profile.
+success to explain an observed \lya\ profile.
 
@@
 In the multiphase model the best constrained parameters are
-the clump velocity dispersion  $\sigma_{\rm{cl}}=$\sigmaclump\
-the clumps outflowing velocity $v_{\infty, \rm{cl}}=$\inftyclump\
+the clump velocity dispersion  $\sigma_{\rm{cl}}=$\sigmaclump\,
+the clump's outflowing velocity $v_{\infty, \rm{cl}}=$\inftyclump\
 and the fraction of the \lya\ emission that is  coming
@@
 
-Which solution is more plausible? If \tol\ followed the fundamental
-plane relationship between its mean surface brightness $I_e$, the
-projected half-light radius $R_e$ and the velocity dispersion
+Are these values atypical? If \tol\ followed the fundamental
+plane relationship between its mean surface brightness
+$I_e$, the projected half-light radius $R_e$ and the velocity dispersion
 $\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e +
-0.55$ \cite{2009ApJ...698.1590G,2011ApJ...726..108T},  
-the expected velocity dispersion would be on the order of $47\pm 3$
-\kms, which only presents a small tension with the multiphase model.   
-The solution of a high rotational velocity pushes \tol\ outside the
-scaling relationship for dwarfs. One could account for the high
-velocities if the galaxy had a supermassive black hole accounting for
-the mass that cannot be explained by baryonic or dark mass. The economy of
-assumptions makes it more reasonable to expect that the multiphase
-model could be a better match to reality.
+0.55$ \cite{2009ApJ...698.1590G},  the expected velocity dispersion
+should be on the order of $5 \pm 1$ 
+\kms, which is a factor of $\sim$ $12$ - $60$ lower than the 
+results from the multiphase-rotation models, respectively. 
+These are equivalente to factors of $\sim$ $140$ - $3600$ on the
+dynamical mass;
+\tol\ seems to be significantly more massive than the expectation from
+scaling relationships for dwarf ellipticals.
+A factor of $100$ in dynamical mass could be accounted by dark matter if
+\tol\ was hosted by a dark matter halo of  $\sim 10^{16}$ M$_{\odot}$
+\cite{2011ApJ...726..108T}, which is very unlikely as it would mean that
+\tol\ is at the center of a super rich cluster of galaxies,
+contradicting observational evidence.
+The remaining possibility is that \tol\ hosts a supermassive black hole of
+$\sim 5\times 10^{9}$ M$_{\odot}$, corresponding to $10$ times its
+estimated stellar and gaseous mass.
 
-A future observational test to clarify the physical nature of
-\tol\ would require integral field unit measurements spatially
-resolving its spatial extent. 
+A new observational test is needed to clarify the physical nature of
+\tol. 
+We suggest that integral field unit measurements spatially
+resolving its spatial extent is up to the task. 
 \tol\ spans a region of $4$ arcseconds,
-an instrument such as the Multi Unit Spectroscopic Explorer with its
+an instrument such as the Multi Unit Spectroscopic Explorer
+\cite{2014Msngr.157...13B} with its
 nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
@@
 In the rotational model this fraction should be zero, while
-the multiphase model predicts that in this case it should be around
-$0.5^{+1.0}_{-0.4}$\%.
+the multiphase model predicts that averaging over all sightlines
+it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
+variations depending on viewing angle.
 
@@
 brightness glow, which may be connected to \lya\ halos, while also
-influencing the way LAEs can be used as a probe of reionization.
+influencing the way LAEs can be used as a probe of reionization
+\cite{2014PASA...31...40D}.
 
-These findings demonstrate the importance of including multiphase
-conditions as a feature to model the \lya\ line in high redshift
+These findings demonstrate the importance of including rotation and multiphase
+conditions as features to model the \lya\ line in high redshift
 galaxies.
-If the estimated velocity dispersion proves to be consistent with
-future observational kinematic maps, it could provide a new way to
-study velocity dispersions in distant gas rich starbursting galaxies, 
-opening the possibility to study the dynamical co-evolution of
-galaxies and dark matter halos in the first generation of galaxies.
+Additionally, if the hypothesis of a supermassive black
+hole in \tol\ proves to be consistent with future observational
+kinematic maps, it could correspond to a so far undetected black hole
+in a dwarf galaxy, providing a new way to test and probe
+theories on the co-evolution of galaxies and black holes in the first
+generation of galaxies.
 

### 2016-09-01 code/plane.py
removing old code

@@ -1,30 +1,0 @@
-import math
-
-L = 9.43E8 #UV bol lumgalex
-alpha = 0.53 # kpc scale radius from noeske
-R = 0.05
-I = L/(4.0* math.pi * R * 1E3 * R * 1E3)
-print 'R {}'.format(R)
-print 'log I {}'.format(math.log10(I))
-print 'log R {}'.format(math.log10(R))
-print 'log L {}'.format(math.log10(L))
-sigma = 10.0**((math.log10(I) + 1.21*math.log10(R)-0.55)/1.6)
-print 'log sigma {}'.format(math.log10(sigma))
-print 'sigma {}'.format(sigma)
-
-
-obs = True
-
-if obs:
-    import numpy as np
-
-    data = np.loadtxt('scale.dat')
-    log_sigma = data[:,0]
-    log_r = data[:,1]
-    log_lum = data[:,2]
-    ii = (log_sigma < np.log10(90.0)) & (log_sigma > np.log10(30.0)) 
-    ii = ii & (log_lum> np.log10(0.33*L))
-    print 10**log_sigma[ii]
-    print 10**log_r[ii]
-    print 10**log_lum[ii]
-    #print log_sigma

### 2016-09-19 paper/letter.tex
and
equivalente->equivalent

@@
 \kms, which is a factor of $\sim$ $12$ - $60$ lower than the 
-results from the multiphase-rotation models, respectively. 
-These are equivalente to factors of $\sim$ $140$ - $3600$ on the
+results from the multiphase and rotation models, respectively. 
+These are equivalent to factors of $\sim$ $140$ - $3600$ on the
 dynamical mass;

### 2016-09-21 paper/letter.tex
more explanation of emcee + some typos

@@
 %https://ned.ipac.caltech.edu/cgi-bin/objsearch?objname=Tol+21&extend=no&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=RA+or+Longitude&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES
-\tol receding velocity is $7785\pm 50$km s$^{-1}$, which translates
+\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
 into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
@@
 $7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
-\cite{2008ApJ...678..804E}.  Using a convertion betwen fluxes and
-stellar mass calibrted on the Large Magellanic Cloud $M_{\star} =
+\cite{2008ApJ...678..804E}.  Using a conversion between fluxes and
+stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
 10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
@@
 distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$, with a $30\%$ uncertainty coming from the callibration
+M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
 process \cite{2012AJ....143..139E}.
@@
 The analytical solution for the rotation sphere was the base to
-perform the Markov Chain Monte Carlo Calculation using the
-\texttt{emcee} implementation.
-We explore flat priors on $V_{\rm max}$ $\log_{10}\tau$, $\log_{10} T$ and
-$\theta$ using $500$ steps with $24$ walkers for a total of $12000$
-points.
-The results are summarized in Figure \ref{emceeresults}. 
-From this model we find that the fiducial parameters that could
-explain the broad features in \tol\ are $V_{\rm max}=348^{+75}_{-48}$
-km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, $\log_{10} T/\mathrm
-{K} = 4.27^{+0.11}_{-0.18}$ and  $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
+perform the Markov Chain Monte Carlo (MCMC) calculation using the
+\texttt{emcee} Python library \cite{2013PASP..125..306F}. \texttt{emcee} 
+is an open source optimized implementation of the affine-invariant 
+ensemble sampler for MCMC. The algorithm creates a number of walkers that,
+during a sufficient number of steps, generate parameters' combinations for
+a specific model. For each time, the code calculates the likelihood of the
+combination to be \textit{ideal} regarding the observational data. It 
+iterates then over the parameter space until it finds the set of
+parameters that maximizes the logarithm of likelihood (known as $\chi^2$).
+
+MCMC methods are optimal for sampling parameters at a high number of 
+dimensions. In this case we explore flat priors on four: $V_{\rm max}$, 
+$\log_{10}\tau$, $\log_{10} T$ and $\theta$ using $500$ steps with $24$ 
+walkers for a total of $12000$ points. The results are summarized in 
+Figure \ref{emceeresults}. From this model we find that the fiducial 
+parameters that could explain the broad features in \tol\ are 
+$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
+$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
+degrees.
 
@@
 \includegraphics[width=1.0\textwidth]{emcee_results.pdf}
-\caption{{\bf Results from the Markov Chain Monte Carlo compuation for
-    the rotation model.}\label{emceeresults}} 
+\caption{{\bf Results from the Markov Chain Monte Carlo computation for
+    the rotation model.} The dotted vertical lines in the outer histograms 
+	represent the percentiles 16\%, 50\% and 84\%. \label{emceeresults}} 
 \end{center}
@@
 \section*{The Outflow Model}
-The galaxy outflow model is a highly sucessful framework to fit
-and interprete \lya\ line observations.
+The galaxy outflow model is a highly successful framework to fit
+and interpret \lya\ line observations.
 
@@
 In the rotation model the size of the spherical region, $r_{s}$, can
-be infered from the relationship $\tau = \sigma_0 n r_s$, where
+be inferred from the relationship $\tau = \sigma_0 n r_s$, where
 $\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
 cross section at the  line's center, $n$ is the number density. 
-This expresion can be rewritten as
+This expression can be rewritten as
 \begin{equation}
@@
 %
-The uppper limit from the HI mass non-detection imposes $r_{s} <
+The upper limit from the HI mass non-detection imposes $r_{s} <
 6.81$ kpc, which is consistent with the bound we found in the first

### 2016-09-22 paper/letter.tex
new references

@@
 \noindent
-\textbf{Lyman-$\alpha$ emission sketches a massive dwarf}
+\textbf{Line sketches of a massive dwarf galaxy}
 \\
@@
 Here we report on one of such CDGs, \tol, which presents
-a broad symmetric Lyman-$\alpha$ emission that had evaded theoretical
+a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
 interpretation so far. 
@@
 emission.  
-This theoretical prediction was only confirmed thirty year later on
-distant, relatively young, not primordial, galaxies.
+This theoretical prediction was only confirmed thirty years later on
+distant, relatively young, not primordial, galaxies \cite{1998ApJ...498L..93D}.
 Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
@@
 There are very few analytically tools available to interpret the
-Ly-$\alpha$ line.
+emerging Ly-$\alpha$ line.
 They are applicable only in very few cases of highly symmetrical
@@
 For these reasons the interpretation of Ly-$\alpha$ observations
-require state-of-the-art Monte Carlo radiative transfer simulations.
+requires state-of-the-art Monte Carlo radiative transfer simulations.
 
@@
 strong Ly-$\alpha$ emission \cite{Thuan97} with two puzzling 
-features: it is symmetric and single peaked.
-Commonly, the Ly-$\alpha$ line has a single or asymmetric double peak. 
+features: the line is symmetric and single peaked.
+Usually the Ly-$\alpha$ line has a single or asymmetric double peak. 
 These two special features in \tol\ cannot be explained with
@@
 The best parameters in the rotation model are a rotational velocity of 
-$V_{\rm max}=348^{+75}_{-48}$ \kms, an optical depth
-$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and a temperature of $\log_{10}
-T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.  
+$V_{\rm max}=348^{+75}_{-48}$ \kms, a neutral Hydrogen optical depth of 
+$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.  
 This model is also able to constrain the angle between the plane
@@
 
-In the multiphase model the best constrained parameters are
-the clump velocity dispersion  $\sigma_{\rm{cl}}=$\sigmaclump\,
-the clump's outflowing velocity $v_{\infty, \rm{cl}}=$\inftyclump\
-and the fraction of the \lya\ emission that is  coming
-from the cold clumps  $P_{\rm cl}=$\probaclump.
-The multiphase model assumes that the clouds are distributed over a
-sphere of $5$kpc in radius, close to the $\approx 4$kpc physical size
-of \tol\ as determined by optical imaging.
-The assumed physical size and the velocity dispersion $\sigma_{\rm
-  cl}$ correspond to a  dynamical mass of  $M_{\rm
-  dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$. In the rotation
-model assuming reasonable bounds for the number density of neutral Hydrogen atoms (
-$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
-of the emission region can be bracketed to be in $0.55 <
-r_s/\mathrm{kpc}< 5.5$.
-Using $V_{\rm max}=300$km s$^{-1}$, we find a dynamical mass range of
-$5.45\times 10^{9}M_{\odot} < M_{\rm dyn} < 5.45\times 10^{10} M_{\odot}$.
+In the multiphase model the best constrained parameters by the
+observational data are the clump velocity dispersion
+$\sigma_{\rm{cl}}=$\sigmaclump\,  the clump's outflowing velocity
+$v_{\infty, \rm{cl}}=$\inftyclump\ and the fraction of the
+\lya\ emission that is  coming from the cold clumps  $P_{\rm cl}=$\probaclump.
+
+Assuming that the clumps are located in a spherical region of radius
+$r_s\approx 2.0$ kpc (corresponding to the estimated 3D half-light
+radius), 
+the results from the rotational velocity correspond to a
+dynamical mass of $M_{\rm dyn} \approx 5.45\times 10^{10} M_{\odot}$,
+while the velocity dispersion in the multiphase model corresponds to a
+$M_{\rm dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$.
+
+%In the rotation model assuming reasonable bounds for the number
+%density of neutral Hydrogen atoms (
+%$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
+%of the emission region can be bracketed to be in $0.55 < r_s/\mathrm{kpc}< 5.5$.
 
@@
 We suggest that integral field unit measurements spatially
-resolving its spatial extent is up to the task. 
+resolving its spatial extent are up to the task. 
 \tol\ spans a region of $4$ arcseconds,
@@
 ionization lines to infer a kinematic map.
-Another observational test includes the measurement of the escape
-fraction of \lya\ continuum ionizing radiation. 
+Another observational test includes the measurement of the
+\lya\ ionizing continuum escape fraction.
 In the rotational model this fraction should be zero, while
@@
 \bibliography{references}{}
-\bibliographystyle{plain}
+\bibliographystyle{ieeetr}
 
@@
 
-%\url{http://vizier.u-strasbg.fr/cgi-bin/VizieR?-source=B/2mass}
-% TOLOLO 00021
-%https://ned.ipac.caltech.edu/cgi-bin/objsearch?objname=Tol+21&extend=no&hconst=73&omegam=0.27&omegav=0.73&corr_z=1&out_csys=Equatorial&out_equinox=J2000.0&obj_sort=RA+or+Longitude&of=pre_text&zv_breaker=30000.0&list_limit=5&img_stamp=YES
 \tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates

### 2016-09-22 paper/letter.tex
referencias, nuevo texto

@@
 \newcommand{\pasj}{PASJ}    
-\newcommand{\sigmaclump}{$69^{+17}_{-15}$ km s$^{-1}$}
-\newcommand{\inftyclump}{$79^{+73}_{-42}$ km s$^{-1}$}
-\newcommand{\probaclump}{$0.78^{+0.16}_{-0.43}$}
+\newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
+\newcommand{\inftyclump}{$54.3\pm 5.1$ km s$^{-1}$}
+\newcommand{\probaclump}{$0.96\pm 0.01$}
 \def\simgt{\lower.5ex\hbox{\gtsima}}
@@
 \noindent
-\textbf{Line sketches of a massive dwarf galaxy}
+\textbf{Line Sketches of a Massive Dwarf Galaxy}
 \\
@@
 dispersion of \sigmaclump with outflows of
-$79^{+73}_{-42}$ km s$^{-1}$) consistent with a dynamical mass at
-least $10$ times larger than its baryonic mass.  
+\inftyclump) consistent with a dynamical mass of at
+least a billion solar masses, $7$ times larger than its baryonic mass.   
 We argue that the most plausible explanation for this excess of
@@
 features: the line is symmetric and single peaked.
-Usually the Ly-$\alpha$ line has a single or asymmetric double peak. 
+Usually the Ly-$\alpha$ line has an asymmetric single or double peak. 
 These two special features in \tol\ cannot be explained with
@@
 In this letter we show how the \tol's \lya\ profile can be explained
-either by rotation or the recently developed class of more complex
+either by rotation\cite{GaravitoCamargo2014}or the recently developed
+class of more complex 
 multiphase models that predict a wider variety of spectra
-including, single, double and triply peaked spectra.  
+including, single, double and triply peaked spectra \cite{Gronke2016}.  
 Figure 1. summarizes our findings.
@@
 overplot from our best fits from the analytical solution for a
-rotating homogeneous gas sphere (continuous line) and the multiphase
-model (dashed line). 
+rotating homogeneous gas sphere (thin line) and the multiphase
+model (thick line). 
 This is the first time that these models have been introduced with
@@
 observational data are the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump\,  the clump's outflowing velocity
+$\sigma_{\rm{cl}}=$\sigmaclump ,  the clump's outflowing velocity
 $v_{\infty, \rm{cl}}=$\inftyclump\ and the fraction of the
@@
 Assuming that the clumps are located in a spherical region of radius
-$r_s\approx 2.0$ kpc (corresponding to the estimated 3D half-light
+$r_s=2.0$ kpc (corresponding to \tol's estimated 3D half-light
 radius), 
-the results from the rotational velocity correspond to a
-dynamical mass of $M_{\rm dyn} \approx 5.45\times 10^{10} M_{\odot}$,
-while the velocity dispersion in the multiphase model corresponds to a
-$M_{\rm dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$.
+this corresponds to dynamical masses of $M_{\rm dyn} =
+2.8_{-0.8}^{+1.5}\times 10^{10} M_{\odot}$ and $M_{\rm
+  dyn}=1.71\pm0.04 \times 10^{9}$ $M_{\odot}$ for the
+rotation and multiphase models, respectively,
 
-%In the rotation model assuming reasonable bounds for the number
-%density of neutral Hydrogen atoms (
-%$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
-%of the emission region can be bracketed to be in $0.55 < r_s/\mathrm{kpc}< 5.5$.
+\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
+M_{\odot}$   \cite{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
+\cite{pustilnikmartin07}; the dynamical mass is at
+least 7 to 68 times the baryonic mass, depending if one
+considers the multiphase or rotation estimate.
 
-Are these values atypical? If \tol\ followed the fundamental
-plane relationship between its mean surface brightness
-$I_e$, the projected half-light radius $R_e$ and the velocity dispersion
-$\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e +
-0.55$ \cite{2009ApJ...698.1590G},  the expected velocity dispersion
-should be on the order of $5 \pm 1$ 
-\kms, which is a factor of $\sim$ $12$ - $60$ lower than the 
+A dynamical mass of $10^{9} M_{\odot}$ in a sphere of 2 kpc could be
+accomodated by a dark matter halo of at least $10^{13}$
+M$_{\odot}$ in mass \cite{2011ApJ...726..108T}, which
+seems unlikely as it would mean that  \tol\ is at the center of a
+galaxy group.
+The remaining possibility is that \tol\ hosts a supermassive black hole of
+at least $10^{9} M_{\odot}$.
+
+Another perspective to appreciate the atypically high dynamical mass
+estimates comes from the observed scaling relations for dwarf
+galaxies.
+Assuming that \tol\ followed the fundamental plane relationship
+between its mean surface brightness $I_e$, the projected half-light
+radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
+I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \cite{2009ApJ...698.1590G},
+the expected velocity dispersion should be on the order of $5 \pm 1$ 
+\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
 results from the multiphase and rotation models, respectively. 
-These are equivalent to factors of $\sim$ $140$ - $3600$ on the
-dynamical mass;
-\tol\ seems to be significantly more massive than the expectation from
-scaling relationships for dwarf ellipticals.
-A factor of $100$ in dynamical mass could be accounted by dark matter if
-\tol\ was hosted by a dark matter halo of  $\sim 10^{16}$ M$_{\odot}$
-\cite{2011ApJ...726..108T}, which is very unlikely as it would mean that
-\tol\ is at the center of a super rich cluster of galaxies,
-contradicting observational evidence.
-The remaining possibility is that \tol\ hosts a supermassive black hole of
-$\sim 5\times 10^{9}$ M$_{\odot}$, corresponding to $10$ times its
-estimated stellar and gaseous mass.
+These are equivalent to factors of $\sim$ $100$ - $3600$ on the
+dynamical mass.
+Once again,  \tol\ seems to be significantly more massive than
+expected.
 
@@
 
-The optical emission  comes from a   region with approximate diameter
-4 kpc \cite{Fricke01}.
-
 There is an upper limit for the  
@@
 
+We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
+from the surface intensity profiles reported by.
+\cite{2003A&A...410..481N}. 
+Assuming spherical geometry, one can translate this value into a 3D
+half-luminosity radius of $r_s=3R_s/2=2.0$ kpc.
+
 \section*{The Rotation Model}
@@
 The rotation model corresponds to the work presented in
-\cite{GaravitoCamargo2014}. 
+\cite{GaravitoCamargo2014} based on the Monte Carlo code
+\texttt{CLARA} \cite{CLARA}. 
 In that model the Ly-$\alpha$ photons are propagated 
@@
 body rotation.
-The sphere is fully characterized by three parameters: the optical
+The sphere is fully characterized by three parameters: the HI optical
 depth $\tau$ measured from the center to its surface, the HI
@@
 dust model.
-In the current work, the radiative transfer simulations were done
-using Monte Carlo simulations with the code \texttt{CLARA}
-\cite{CLARA}.
+In this letter we use an analytical solution that captures the most
+important effects of rotation onto the \lya\ line.
 
@@
 
-\section*{The Outflow Model}
-The galaxy outflow model is a highly successful framework to fit
-and interpret \lya\ line observations.
+%In the rotation model assuming reasonable bounds for the number
+%density of neutral Hydrogen atoms (
+%$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
+%of the emission region can be bracketed to be in $0.55 < r_s/\mathrm{kpc}< 5.5$.
 

### 2016-09-22 paper/letter.tex
bound of flat priors

@@
 
-There is a concise analytical description for those features.
+\cite{GaravitoCamargo2014} derive a concise analytical description for
+those features. 
 This description takes into account how different parts of the
-sphere's surface shift in frequency the \lya photons. 
+sphere's surface shift in frequency the \lya\ photons. 
 Different shifts in frequency come from different values for the projected
 velocity along the LOS. 
-As presented in \cite{CLARA}, using the analytical solution for the
-\lya\ spectra of a static sphere plus the right frequency shifts
-computed from geometrical considerations, one is able to produce an
-analytical solution for the rotating sphere that reproduces the main
-features found using the full numerical simulation.
+Using the analytical solution for the \lya\ spectra of a static sphere
+plus the right frequency shifts  computed from geometrical
+considerations, one is able to compute an analytical solution for the
+rotating sphere that reproduces the main features found using the full
+numerical simulation.
 
@@
 a specific model. For each time, the code calculates the likelihood of the
-combination to be \textit{ideal} regarding the observational data. It 
-iterates then over the parameter space until it finds the set of
-parameters that maximizes the logarithm of likelihood (known as $\chi^2$).
+combination with respect to the observational data. The walkers ecplore
+the parameter space sampling the likelihood function.
 
 MCMC methods are optimal for sampling parameters at a high number of 
-dimensions. In this case we explore flat priors on four: $V_{\rm max}$, 
-$\log_{10}\tau$, $\log_{10} T$ and $\theta$ using $500$ steps with $24$ 
-walkers for a total of $12000$ points. The results are summarized in 
-Figure \ref{emceeresults}. From this model we find that the fiducial 
+dimensions. In this case we explore flat priors on four parameters:
+$200<V_{\rm max}/\mathrm{km\ s}^{-1} <600$,  
+$6.0<\log_{10}\tau<9.0$, $4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and
+$0<\theta<90$ using $500$ steps with $24$ walkers for a total of
+$12000$ points in the chain. 
+The results are summarized in 
+Figure \ref{emceeresults}. 
+From this model we find that the fiducial 
 parameters that could explain the broad features in \tol\ are 

### 2016-09-22 paper/letter.tex
updated references and text

@@
 The remaining possibility is that \tol\ hosts a supermassive black hole of
-at least $10^{9} M_{\odot}$.
+$10^{9} M_{\odot}$. This is two orders of magnitude higher
+than the supermassive black hole found in the compact dwarf galaxy
+M60-UCD1 \cite{2014Natur.513..398S}, which has a similar stellar mass
+as \tol.
 
@@
 \cite{Gronke2016}.    
+ For the current work, we computed the $\chi^2$ for each of the $2500$
+models. We selected the best $50$ models with the lowest $\chi^2$. The
+$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
+$\chi^2$ is close to $1200$. The total number of degrees of freedom is
+$104$.
 
-For the current work, we computed the $\chi^2$ for each of the $2500$
-Furthermore, we found that some parameters such as the magnitude of
-the random clump motion $\sigma_{\rm cl}$ improved the fit
-significantly whereas others did not.
+Then we performed a Kolmogorov-Smirnov test to compare each parameter
+distribution in the best $50$ models against the parent distribution
+of $2500$ models. 
+If we obtain a p-value $<0.05$ for a given parameter, we conclude that
+this parameter does influence the $\chi^2$ fit, as the distribution for
+the best $\chi^2$ models is statistically different to the
+distribution from the global sample of $2500$ models.
 
-We find that the best constrained parameters are the clump velocity
-dispersion $\sigma_{\rm cl}=$\sigmaclump,  the outflowing clump
-velocity $v_{\infty {\rm, cl}}=$\inftyclump\ and the probability that
-the \lya\ emission comes from the clumps $P_{\rm cl}=$\probaclump.
+From this test we found that only three parameters influence the
+$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
+$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
+$10^{-4}$) and the probability that the \lya\ emission comes from the
+clumps $P_{\rm cl}$ (p-value $10^{-4}$).
+
+The best values for those parameters that we report here correspond to
+the values that produce the minimum
+$\chi^2$. The 1-$\sigma$ uncertainty comes from a parabolic fit to the
+$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
+$P_{\rm cl}$ around its corresponding minimum.
+Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
+$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
 
@@
 
-\section*{Physical Interpretation}
+\section*{Dynamical Mass Estimates}
 
@@
 
-From the multiphase model we obtained $v=$\sigmaclump
-and $r=5$ kpc. This corresponds to a dynamical mass of $M_{\rm
-  dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$ which is at least
-$5$ times the HI mass plus the stellar mass estimated from
-observations.
+As described in the main the letter, we use the 3D half-luminosity
+radius, $r_{s}$, as the typical size for the HI region.
 
-In the rotation model the size of the spherical region, $r_{s}$, can
-be inferred from the relationship $\tau = \sigma_0 n r_s$, where
-$\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
-cross section at the  line's center, $n$ is the number density. 
-This expression can be rewritten as
-\begin{equation}
-r_{s} = 0.055 \left(\frac{\tau}{10^7}\right) \left(
-\frac{\mathrm{atoms\ cm^{-3}}}{n}\right) \mathrm{kpc}.
-\end{equation}
+%From the multiphase model we obtained $v=$\sigmaclump
+%and $r=5$ kpc. This corresponds to a dynamical mass of $M_{\rm
+%  dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$ which is at least
+%$5$ times the HI mass plus the stellar mass estimated from
+%observations.
+
+%In the rotation model the size of the spherical region, $r_{s}$, can
+%be inferred from the relationship $\tau = \sigma_0 n r_s$, where
+%$\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
+%cross section at the  line's center, $n$ is the number density. 
+%This expression can be rewritten as
+%\begin{equation}
+%r_{s} = 0.055 \left(\frac{\tau}{10^7}\right) \left(
+%\frac{\mathrm{atoms\ cm^{-3}}}{n}\right) \mathrm{kpc}.
+%\end{equation}
 %
-Using this result and assuming a bound for the number density of
-$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$ we have $0.55
-< r_s/\mathrm{kpc}<5.5$.
+%Using this result and assuming a bound for the number density of
+%$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$ we have $0.55
+%< r_s/\mathrm{kpc}<5.5$.
 
-This is consistent with the  constraint on the total HI mass and the
-optical depth $\tau_0$ as we show next. The total HI mass can be
-approximated as $M_H = \frac{4\pi}{3} m_H n r_s^3$, where
-$m_H=1.67\times 10^{-24}$ gr is the mass of a single Hydrogen atom.
-This allows us to write the total hydrogen mass as
-\begin{equation}
-M_{H} = 5.70 \times 10^{6} \left(\frac{\tau}{10^{7}}\right)
-\left(\frac{r_s}{\mathrm{kpc}}\right)^2 M_{\odot}
-\end{equation}
+%This is consistent with the  constraint on the total HI mass and the
+%optical depth $\tau_0$ as we show next. The total HI mass can be
+%approximated as $M_H = \frac{4\pi}{3} m_H n r_s^3$, where
+%$m_H=1.67\times 10^{-24}$ gr is the mass of a single Hydrogen atom.
+%This allows us to write the total hydrogen mass as
+%\begin{equation}
+%M_{H} = 5.70 \times 10^{6} \left(\frac{\tau}{10^{7}}\right)
+%\left(\frac{r_s}{\mathrm{kpc}}\right)^2 M_{\odot}
+%\end{equation}
 %
-The upper limit from the HI mass non-detection imposes $r_{s} <
-6.81$ kpc, which is consistent with the bound we found in the first
-place, as we wanted to show.
+%The upper limit from the HI mass non-detection imposes $r_{s} <
+%6.81$ kpc, which is consistent with the bound we found in the first
+%place, as we wanted to show.
 
-Using those size bounds for the spherical model we find a constrain for
-the dynamical mass of $5.45\times 10^{9}M_{\odot} < M_{\rm dyn} <
-5.45\times 10^{10} M_{\odot}$.
+%Using those size bounds for the spherical model we find a constrain for
+%the dynamical mass of $5.45\times 10^{9}M_{\odot} < M_{\rm dyn} <
+%5.45\times 10^{10} M_{\odot}$.
 

### 2016-09-23 paper/letter.tex
latest letter

@@
 \noindent
-\textbf{Line Sketches of a Massive Dwarf Galaxy}
+\textbf{Lyman-$\alpha$ Line Sketches a Supermassive Dwarf Galaxy}
 \\
@@
 least a billion solar masses, $7$ times larger than its baryonic mass.   
-We argue that the most plausible explanation for this excess of
+We argue that a possible explanation for this excess of
 dynamical mass is the presence of a supermassive black hole at the
@@
 
-A dynamical mass of $10^{9} M_{\odot}$ in a sphere of 2 kpc could be
-accomodated by a dark matter halo of at least $10^{13}$
-M$_{\odot}$ in mass \cite{2011ApJ...726..108T}, which
-seems unlikely as it would mean that  \tol\ is at the center of a
-galaxy group.
-The remaining possibility is that \tol\ hosts a supermassive black hole of
+We lean towards the lower dynamical mass estimate from the multiphase
+model as it seems easier to reconcile with the following two
+astrophysical mechanisms for its origin.
+The first way to explain a dynamical mass of $10^{9} M_{\odot}$
+in a sphere of 2 kpc could be having a dark matter halo of at
+least $10^{12}$ M$_{\odot}$ in mass \cite{2011ApJ...726..108T}, which
+leaves open the question as to why  \tol\ is not more similar to the
+Milky Way galaxy as it is hosted by a dark matter halo of similar
+mass. 
+A second possibility is that \tol\ hosts a supermassive black hole of
 $10^{9} M_{\odot}$. This is two orders of magnitude higher
@@
 hole in \tol\ proves to be consistent with future observational
-kinematic maps, it could correspond to a so far undetected black hole
-in a dwarf galaxy, providing a new way to test and probe
-theories on the co-evolution of galaxies and black holes in the first
-generation of galaxies.
+kinematic maps, it could correspond to a so far undetected
+supermassive black hole in a dwarf galaxy, providing a new way to test
+and probe theories on the co-evolution of galaxies and black holes in
+the first generation of galaxies.
 

### 2016-09-23 paper/letter.tex
one more sentence

@@
 A second possibility is that \tol\ hosts a supermassive black hole of
-$10^{9} M_{\odot}$. This is two orders of magnitude higher
+$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
 than the supermassive black hole found in the compact dwarf galaxy
 M60-UCD1 \cite{2014Natur.513..398S}, which has a similar stellar mass
-as \tol.
+as \tol. This also leaves open the question for the formation process
+of such an system.
 

### 2016-09-23 paper/letter.tex
updated numbers and eqs

@@
 \inftyclump) consistent with a dynamical mass of at
-least a billion solar masses, $7$ times larger than its baryonic mass.   
+least a billion solar masses, $6$ times larger than its baryonic mass.   
 We argue that a possible explanation for this excess of
@@
 Assuming that the clumps are located in a spherical region of radius
-$r_s=2.0$ kpc (corresponding to \tol's estimated 3D half-light
+$r_s=2.25$ kpc (corresponding to \tol's estimated 3D half-light
 radius), 
 this corresponds to dynamical masses of $M_{\rm dyn} =
-2.8_{-0.8}^{+1.5}\times 10^{10} M_{\odot}$ and $M_{\rm
-  dyn}=1.71\pm0.04 \times 10^{9}$ $M_{\odot}$ for the
+3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$ and $M_{\rm
+  dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$ for the
 rotation and multiphase models, respectively,
@@
 M_{\odot}$   \cite{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
-\cite{pustilnikmartin07}; the dynamical mass is at
-least 7 to 68 times the baryonic mass, depending if one
-considers the multiphase or rotation estimate.
+\cite{pustilnikmartin07}; the dynamical mass is at least 6 to 80 times
+the baryonic mass, depending if one considers the multiphase or
+rotation estimate.
 
@@
 M60-UCD1 \cite{2014Natur.513..398S}, which has a similar stellar mass
-as \tol. This also leaves open the question for the formation process
-of such an system.
+as \tol. This would leave open the question about the formation
+process of such a system.
 
@@
 Assuming spherical geometry, one can translate this value into a 3D
-half-luminosity radius of $r_s=3R_s/2=2.0$ kpc.
+half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.
 
@@
 
-Both the rotation and the multiphase model constrain the typical
-velocity $v$ of the HI gas, with and additional constrain on the typical
-size for the emission region $r$ on could estimate a dynamical mass with
+Having constrains for  velocity dipersion $\sigma$ of some dynamical
+tracers (clumps in the case of the multiphase model) in a spherical
+system located in a region of size $r$ we estimate the dynamical mass
+within $r$.
 
 \begin{equation}
-M_{\rm dyn} = \frac{v^{2}r}{G} = 1.16\times10^{9}
-\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
+M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
+\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
 \end{equation}
@@
 radius, $r_{s}$, as the typical size for the HI region.
+
+In the case of rotational velocity $v$ in a region of size $r$ we
+estimate the dynamical mass by
+
+\begin{equation}
+M_{\rm dyn} = \frac{v ^{2}r}{G} = 1.16\times10^{9}
+\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot} 
+\end{equation}
 

### 2016-09-26 paper/letter.tex
letter diff
submitted version

@@
 \noindent
-\textbf{Lyman-$\alpha$ Line Sketches a Supermassive Dwarf Galaxy}
+\textbf{Line Traces of a Supermassive Dwarf Galaxy}
 \\
@@
 \inftyclump) consistent with a dynamical mass of at
-least a billion solar masses, $6$ times larger than its baryonic mass.   
+least a billion solar masses, ten times larger than its baryonic mass.   
 We argue that a possible explanation for this excess of
@@
 In this letter we show how the \tol's \lya\ profile can be explained
-either by rotation\cite{GaravitoCamargo2014}or the recently developed
+either by rotation \cite{GaravitoCamargo2014} or the recently developed
 class of more complex 
@@
 Assuming that the clumps are located in a spherical region of radius
-$r_s=2.25$ kpc (corresponding to \tol's estimated 3D half-light
+$r_s=2.25$ kpc (corresponding to \tol's estimated 3D half-luminosity
 radius), 
@@
 M_{\odot}$   \cite{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
-\cite{pustilnikmartin07}; the dynamical mass is at least 6 to 80 times
+\cite{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
 the baryonic mass, depending if one considers the multiphase or
@@
 The first way to explain a dynamical mass of $10^{9} M_{\odot}$
-in a sphere of 2 kpc could be having a dark matter halo of at
+in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
 least $10^{12}$ M$_{\odot}$ in mass \cite{2011ApJ...726..108T}, which
 leaves open the question as to why  \tol\ is not more similar to the
-Milky Way galaxy as it is hosted by a dark matter halo of similar
+Milky Way galaxy as it would be hosted by a dark matter halo of similar
 mass. 
@@
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle.
+variations depending on viewing angle \cite{2014MNRAS.444.1095G}.
 
@@
 8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \cite{Thuan97}
-and a Equivalent Width of $70$\AA and its H$\beta$ flux is 
+and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
 $1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
@@
 4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
-$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA
+$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA\ 
 bandwidth, which in turns translates  into a star formation rate of
@@
 body rotation.
-The sphere is fully characterized by three parameters: the HI optical
-depth $\tau$ measured from the center to its surface, the HI
+The sphere is fully characterized by three parameters: the HI line's
+center optical  depth $\tau$ measured from the center to its surface, the HI
 temperature $T$, and the linear surface velocity $V_{\rm max}$.  
@@
 
-\cite{GaravitoCamargo2014} derive a concise analytical description for
+\cite{GaravitoCamargo2014} derived a concise analytical description for
 those features. 
@@
     the rotation model.} The dotted vertical lines in the outer histograms 
-	represent the percentiles 16\%, 50\% and 84\%. \label{emceeresults}} 
+	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
 \end{center}
 \end{figure}
-
-%In the rotation model assuming reasonable bounds for the number
-%density of neutral Hydrogen atoms (
-%$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$) and using $\tau=10^7$ the radius
-%of the emission region can be bracketed to be in $0.55 < r_s/\mathrm{kpc}< 5.5$.
 
@@
 $10^{-4}$) and the probability that the \lya\ emission comes from the
-clumps $P_{\rm cl}$ (p-value $10^{-4}$).
+clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
+parameters do not influence the resulting spectra at all; it means
+that they cannot be constrained from \tol's observations.
 
@@
 
-%From the multiphase model we obtained $v=$\sigmaclump
-%and $r=5$ kpc. This corresponds to a dynamical mass of $M_{\rm
-%  dyn}=2.8^{+1.3}_{-1.2}\times 10^{9}$ $M_{\odot}$ which is at least
-%$5$ times the HI mass plus the stellar mass estimated from
-%observations.
-
-%In the rotation model the size of the spherical region, $r_{s}$, can
-%be inferred from the relationship $\tau = \sigma_0 n r_s$, where
-%$\sigma_0=5.898\times 10^{-14}$cm$^{-2}$ is the Lyman$\alpha$
-%cross section at the  line's center, $n$ is the number density. 
-%This expression can be rewritten as
-%\begin{equation}
-%r_{s} = 0.055 \left(\frac{\tau}{10^7}\right) \left(
-%\frac{\mathrm{atoms\ cm^{-3}}}{n}\right) \mathrm{kpc}.
-%\end{equation}
-%
-%Using this result and assuming a bound for the number density of
-%$0.01<n/\mathrm{atoms\ cm^{-3}}<0.1$ we have $0.55
-%< r_s/\mathrm{kpc}<5.5$.
-
-%This is consistent with the  constraint on the total HI mass and the
-%optical depth $\tau_0$ as we show next. The total HI mass can be
-%approximated as $M_H = \frac{4\pi}{3} m_H n r_s^3$, where
-%$m_H=1.67\times 10^{-24}$ gr is the mass of a single Hydrogen atom.
-%This allows us to write the total hydrogen mass as
-%\begin{equation}
-%M_{H} = 5.70 \times 10^{6} \left(\frac{\tau}{10^{7}}\right)
-%\left(\frac{r_s}{\mathrm{kpc}}\right)^2 M_{\odot}
-%\end{equation}
-%
-%The upper limit from the HI mass non-detection imposes $r_{s} <
-%6.81$ kpc, which is consistent with the bound we found in the first
-%place, as we wanted to show.
-
-%Using those size bounds for the spherical model we find a constrain for
-%the dynamical mass of $5.45\times 10^{9}M_{\odot} < M_{\rm dyn} <
-%5.45\times 10^{10} M_{\odot}$.
-
 \end{document}

### 2017-01-16 paper/letter.tex
Fixed Max' name
mnras style

@@
-\documentclass[a4paper, usenatbib, 12pt]{article}
-\usepackage{subfig}
-\usepackage{float}
-\usepackage{wrapfig}
-\usepackage{graphicx}
+\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
+%=========================================================================
 \usepackage{amsmath} 
 \usepackage{amssymb} 
+\usepackage {graphicx}
+\usepackage[dvips]{epsfig}
+\usepackage{epsfig}  
+\usepackage{color}
+\usepackage[normalem]{ulem}
+\usepackage{hyperref}
+\usepackage{caption}
+%Non reposionated tables
+\usepackage{float}
+\restylefloat{table}
+%Multiple columns support for tables
+\usepackage{array}
 \usepackage{booktabs}
-\usepackage{cite}
-\usepackage[icelandic,spanish,english]{babel}
-\usepackage[T1]{fontenc}
-\usepackage[utf8]{inputenc}
-\usepackage[top=3.5cm, bottom=2.5cm, left=3.5cm,right=3.5cm]{geometry}
+\setlength{\heavyrulewidth}{1.5pt}
+\setlength{\abovetopsep}{4pt}
 
-%----------------------New commands -------------------
+%=========================================================================
+%		INTERNAL MACROS
+%=========================================================================
+\def\be{\begin{equation}}
+\def\ee{\end{equation}}
+\def\ba{\begin{eqnarray}}
+\def\ea{\end{eqnarray}}
+
+% To highlight comments 
+\definecolor{red}{rgb}{1,0.0,0.0}
+\newcommand{\red}{\color{red}}
+\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
+\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
+\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
+\newcommand{\before}[1]{\textcolor{red}{ #1}}
+\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
 
@@
 \def\simlt{\lower.5ex\hbox{\ltsima}}
-%------------------------------------------------------
 
 \begin{document}
-\pagestyle{empty}
-\noindent
-\textbf{Line Traces of a Supermassive Dwarf Galaxy}
-\\
-\\
-Jaime E. Forero-Romero$^{1}$, Max Groenke$^2$, Mar\'ia Camila
-Remolina-Guti\'errez$^1$, Juan Nicol\'as
-Garavito-Carmargo$^3$, Mark Dijkstra$^2$.
-\\
-\\
-\scriptsize
-{$^1$ Departamento de Física, Universidad de los Andes, Cra. 1
-  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia 
-\\
+
+%=========================================================================
+%		FRONT MATTER
+%=========================================================================
+\title[Atypical Dwarf LAE]{
+Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase
+gas and rotation.}
+\author[J.E. Forero-Romero et al.]
+{Jaime E. Forero-Romero $^{1}$ \thanks{je.forero@uniandes.edu.co},
+Max Gronke$^2$, 
+Mar\'ia Camila Remolina-Guti\'errez$^1$,
+\newauthor
+Nicol\'as Garavito-Camargo$^3$, 
+Mark Dijkstra$^2$\\
+%%
+$^1$ Departamento de F\'isica, Universidad de los Andes, Cra. 1
+  No. 18A-10 Edificio Ip, CP 111711, Bogot\'a, Colombia \\
 $^2$ Institute of Theoretical Astrophysics, University of Oslo,
-Postboks 1029 Blindern, NO-0315 Oslo, Norway.
-\\
+Postboks 1029 Blindern, NO-0315 Oslo, Norway.\\
 $^3$ Department of Astronomy, University of Arizona, 933 North Cherry
 Avenue, Tucson, AZ 85721, USA. 
-\normalsize
-\\
-\\
-\textbf{
+}
+
+%\vspace*{6pt}\\
+
+%}
+\maketitle
+
+\begin{abstract}
+Example.
+\end{abstract}
+
+\begin{keywords}
+Methods: data analysis - numerical 
+\end{keywords}
+
+%=========================================================================
+%		PAPER CONTENT
+%=========================================================================
+
+%*************************************************************************
+\section{Introduction}
+\label{sec:introduction}
+
   Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
@@
 holes.
-}
 
@@
 
-Almost fifty years ago \cite{PartridgePeebles} it was realized that
+Almost fifty years ago \citep{PartridgePeebles} it was realized that
 young galaxies could be detected through a strong Lyman-$\alpha$ line
 emission.
+
 This theoretical prediction was only confirmed thirty years later on
-distant, relatively young, not primordial, galaxies \cite{1998ApJ...498L..93D}.
+distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
 Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
@@
 Ly-$\alpha$ emission in nearby dwarf star forming galaxies 
-\cite{LARS}. 
+\citep{LARS}. 
 The study of nearby LAE samples has allowed the study of other
@@
 However, the physical interpretation of Ly-$\alpha$ observations is
-not straightforward \cite{2015ApJ...805...14R}. 
+not straightforward \citep{2015ApJ...805...14R}. 
 This is due to the resonant nature of the Ly-$\alpha$ line. 
@@
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong Ly-$\alpha$ emission \cite{Thuan97} with two puzzling 
+strong Ly-$\alpha$ emission \citep{Thuan97} with two puzzling 
 features: the line is symmetric and single peaked.
@@
 These two special features in \tol\ cannot be explained with
-conventional models \cite{2006A&A...460..397V,2015ApJ...812..123G}.
+conventional models \citep{2006A&A...460..397V,2015ApJ...812..123G}.
 
 In this letter we show how the \tol's \lya\ profile can be explained
-either by rotation \cite{GaravitoCamargo2014} or the recently developed
+either by rotation \citep{GaravitoCamargo2014} or the recently developed
 class of more complex 
 multiphase models that predict a wider variety of spectra
-including, single, double and triply peaked spectra \cite{Gronke2016}.  
+including, single, double and triply peaked spectra \citep{Gronke2016}.  
 Figure 1. summarizes our findings.
@@
 \tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$   \cite{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
-\cite{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
+M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
+\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
 the baryonic mass, depending if one considers the multiphase or
@@
 in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
-least $10^{12}$ M$_{\odot}$ in mass \cite{2011ApJ...726..108T}, which
+least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}, which
 leaves open the question as to why  \tol\ is not more similar to the
@@
 than the supermassive black hole found in the compact dwarf galaxy
-M60-UCD1 \cite{2014Natur.513..398S}, which has a similar stellar mass
+M60-UCD1 \citep{2014Natur.513..398S}, which has a similar stellar mass
 as \tol. This would leave open the question about the formation
@@
 radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
-I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \cite{2009ApJ...698.1590G},
+I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
 the expected velocity dispersion should be on the order of $5 \pm 1$ 
@@
 an instrument such as the Multi Unit Spectroscopic Explorer
-\cite{2014Msngr.157...13B} with its
+\citep{2014Msngr.157...13B} with its
 nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
@@
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle \cite{2014MNRAS.444.1095G}.
+variations depending on viewing angle \citep{2014MNRAS.444.1095G}.
 
@@
 influencing the way LAEs can be used as a probe of reionization
-\cite{2014PASA...31...40D}.
+\citep{2014PASA...31...40D}.
 
@@
 
-\begin{figure}
+\begin{figure*}
 \begin{center}
@@
 \end{center}
-\end{figure}
-
-\bibliography{references}{}
-\bibliographystyle{ieeetr}
-
-\newpage
+\end{figure*}
 
@@
 \caption{Basic observational characteristics of TOL1214-277
-  \cite{Thuan97}\\} 
+  \citep{Thuan97}\\} 
 \end{table}
@@
 Mpc km s$^{-1}$) 
-Its metallicity is $\sim Z_{\odot}/24$ \cite{Izotov04} as derived from optical
+Its metallicity is $\sim Z_{\odot}/24$ \citep{Izotov04} as derived from optical
 spectroscopy.
@@
 The observed flux for the Lyman alpha line is $\sim
-8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \cite{Thuan97}
+8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
 and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
 $1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
-\cite{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
+\citep{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
 4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
@@
 Comparing this ratio with the theoretical expectation from case B
-recombination of $23.3$ \cite{Hummer1987} one can estimate an escape
+recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
 fraction of $20$\% for Ly$\alpha$ radiation.
@@
 upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
-\cite{pustilnikmartin07}.
+\citep{pustilnikmartin07}.
 
@@
 $7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
-\cite{2008ApJ...678..804E}.  Using a conversion between fluxes and
+\citep{2008ApJ...678..804E}.  Using a conversion between fluxes and
 stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
@@
 M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
-process \cite{2012AJ....143..139E}.
+process \citep{2012AJ....143..139E}.
 
@@
 from the surface intensity profiles reported by.
-\cite{2003A&A...410..481N}. 
+\citep{2003A&A...410..481N}. 
 Assuming spherical geometry, one can translate this value into a 3D
@@
 The rotation model corresponds to the work presented in
-\cite{GaravitoCamargo2014} based on the Monte Carlo code
-\texttt{CLARA} \cite{CLARA}. 
+\citep{GaravitoCamargo2014} based on the Monte Carlo code
+\texttt{CLARA} \citep{CLARA}. 
 In that model the Ly-$\alpha$ photons are propagated 
@@
 
-\cite{GaravitoCamargo2014} derived a concise analytical description for
+\citep{GaravitoCamargo2014} derived a concise analytical description for
 those features. 
@@
 perform the Markov Chain Monte Carlo (MCMC) calculation using the
-\texttt{emcee} Python library \cite{2013PASP..125..306F}. \texttt{emcee} 
+\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
 is an open source optimized implementation of the affine-invariant 
@@
 \end{center}
-\end{figure}
+\end{figure*}
 
@@
 $2500$ sets of parameters within a observationally realistic range
-(based on the considerations of \cite{Laursen2013ApJ...766..124L})
+(based on the considerations of \citep{Laursen2013ApJ...766..124L})
 yielding a large variety of single-, double- and triple-peaked
@@
 more details on the radiative transfer are presented in
-\cite{Gronke2016}.    
+\citep{Gronke2016}.    
  For the current work, we computed the $\chi^2$ for each of the $2500$
@@
 
+\bibliographystyle{mn2e}
+\bibliography{references}
+
 \end{document}

### 2017-01-19 paper/letter.tex
abstract
secciones

@@
 \begin{abstract}
-Example.
-\end{abstract}
-
-\begin{keywords}
-Methods: data analysis - numerical 
-\end{keywords}
-
-%=========================================================================
-%		PAPER CONTENT
-%=========================================================================
-
-%*************************************************************************
-\section{Introduction}
-\label{sec:introduction}
-
   Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
@@
 interpretation so far. 
-In this letter we explain these features by two different models: an
+In this paper we explain these features by two different models: an
 homogeneous gaseous sphere undergoing bulk rotation and an interstellar
@@
 holes.  
+\end{abstract}
+
+\begin{keywords}
+Methods: data analysis - numerical 
+\end{keywords}
+
+%=========================================================================
+%		PAPER CONTENT
+%=========================================================================
+
+%*************************************************************************
+\section{Introduction}
+\label{sec:introduction}
 
@@
 
-In this letter we show how the \tol's \lya\ profile can be explained
+In this paper we show how the \tol's \lya\ profile can be explained
 either by rotation \citep{GaravitoCamargo2014} or the recently developed
@@
 including, single, double and triply peaked spectra \citep{Gronke2016}.
+
+\section{\tol}
+
+\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
+into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
+Mpc km s$^{-1}$) 
+Its metallicity is $\sim Z_{\odot}/24$ \citep{Izotov04} as derived from optical
+spectroscopy.
+
+The observed flux for the Lyman alpha line is $\sim
+8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
+and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
+$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
+\citep{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
+4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
+$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA\ 
+bandwidth, which in turns translates  into a star formation rate of
+$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
+luminosity and star formation rate of $9.1\times 10^{-43}$
+$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
+The absolute magnitude in the $V$ band translates into a luminosity of
+$8.9\times 10^{8}$ L$_{\odot}$.
+% using http://tomdwelly.com/tools_fluxtolum.php
+Comparing this ratio with the theoretical expectation from case B
+recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
+fraction of $20$\% for Ly$\alpha$ radiation.
+The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
+L$_{\odot}$ as measured by GALEX.
+
+There is an upper limit for the  
+integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
+upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
+\citep{pustilnikmartin07}.
+
+The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
+$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
+\citep{2008ApJ...678..804E}.  Using a conversion between fluxes and
+stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
+10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
+(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
+distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
+M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
+process \citep{2012AJ....143..139E}.
+
+We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
+from the surface intensity profiles reported by.
+\citep{2003A&A...410..481N}. 
+Assuming spherical geometry, one can translate this value into a 3D
+half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.
+
+\begin{table}
+\begin{center}
+\begin{tabular}{lc}
+$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
+$\delta$(2000)$^{b}$ & -28d02m32s\\
+$l$, $b$ (deg) & 294, 34\\
+$m_V$ & 17.5\\
+  M$_V$ & -17.6\\ 
+$v$(km s$^{-1}$) & 7795\\
+Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
+Ly-$\alpha$ EW & $70$\AA\\
+H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
+$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
+\end{tabular}
+\end{center}
+\caption{Basic observational characteristics of TOL1214-277
+  \citep{Thuan97}\\} 
+\end{table}
+
+\section{Theoretical Models}
+
+\subsection{Rotation Model}
+
+The rotation model corresponds to the work presented in
+\citep{GaravitoCamargo2014} based on the Monte Carlo code
+\texttt{CLARA} \citep{CLARA}. 
+In that model the Ly-$\alpha$ photons are propagated 
+within a spherical and homogeneous cloud of HI gas undergoing solid
+body rotation.
+The sphere is fully characterized by three parameters: the HI line's
+center optical  depth $\tau$ measured from the center to its surface, the HI
+temperature $T$, and the linear surface velocity $V_{\rm max}$.  
+Photons are emitted at their natural frequency from the center of the
+sphere. 
+Including the effect of dust only changes the overall line
+normalization but not its shape.  
+The results we report in the main body of the paper do not include any
+dust model.
+In this paper we use an analytical solution that captures the most
+important effects of rotation onto the \lya\ line.
+
+The first important effect of rotation is that it breaks the spherical
+symmetry of the static case. 
+Now the line's observed morphology depends on the angle $\theta$ between the
+line-of-sight (LOS) and the rotation axis. 
+LOS parallel to the rotation axis tend to observed the line without
+any modification from rotation, while the perpendicular LOS will
+observe a maximal change in the line's morphology due to rotation.
+
+The main change in the line's morphology is that it broadens and the
+intensity at the center increases. 
+For high enough rotational velocities the intensity at the peak's
+center increases so much that the line goes from double to single
+peaked, sometimes slightly triple peaked.
+This is the feature that allows this model to fit the observational
+features of \tol.
+
+\citep{GaravitoCamargo2014} derived a concise analytical description for
+those features. 
+This description takes into account how different parts of the
+sphere's surface shift in frequency the \lya\ photons. 
+Different shifts in frequency come from different values for the projected
+velocity along the LOS. 
+Using the analytical solution for the \lya\ spectra of a static sphere
+plus the right frequency shifts  computed from geometrical
+considerations, one is able to compute an analytical solution for the
+rotating sphere that reproduces the main features found using the full
+numerical simulation.
+
+The analytical solution for the rotation sphere was the base to
+perform the Markov Chain Monte Carlo (MCMC) calculation using the
+\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
+is an open source optimized implementation of the affine-invariant 
+ensemble sampler for MCMC. The algorithm creates a number of walkers that,
+during a sufficient number of steps, generate parameters' combinations for
+a specific model. For each time, the code calculates the likelihood of the
+combination with respect to the observational data. The walkers ecplore
+the parameter space sampling the likelihood function.
+
+\subsection{Multiphase Model}
+
+The idealized multiphase model consists of spherical, cold, dens
+clumps of neutral hydrogen (and dust) embedded in a hot, ionized
+medium. 
+The clumps also have a random and an outflowing velocity
+component which totals the number of parameters describing the model
+to be $14$.
+
+In order to map out this large parameter space, we randomly drew
+$2500$ sets of parameters within a observationally realistic range
+(based on the considerations of \citep{Laursen2013ApJ...766..124L})
+yielding a large variety of single-, double- and triple-peaked
+spectra. 
+The full analysis of the the spectral features as well as
+more details on the radiative transfer are presented in
+\citep{Gronke2016}.
+
+\section{Results}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
+\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
+  Dots correspond to the observational data. The line shows the results
+of our best model from a full radiative transfer simulation both for
+the rotation and multiphase models.} 
+\end{center}
+\end{figure*}
+
 Figure 1. summarizes our findings.
@@
 
+MCMC methods are optimal for sampling parameters at a high number of 
+dimensions. In this case we explore flat priors on four parameters:
+$200<V_{\rm max}/\mathrm{km\ s}^{-1} <600$,  
+$6.0<\log_{10}\tau<9.0$, $4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and
+$0<\theta<90$ using $500$ steps with $24$ walkers for a total of
+$12000$ points in the chain. 
+The results are summarized in 
+Figure \ref{emceeresults}. 
+From this model we find that the fiducial 
+parameters that could explain the broad features in \tol\ are 
+$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
+$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
+degrees.
+
 The best parameters in the rotation model are a rotational velocity of 
@@
 to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
+
+ For the current work, we computed the $\chi^2$ for each of the $2500$
+models. We selected the best $50$ models with the lowest $\chi^2$. The
+$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
+$\chi^2$ is close to $1200$. The total number of degrees of freedom is
+$104$.
+
+Then we performed a Kolmogorov-Smirnov test to compare each parameter
+distribution in the best $50$ models against the parent distribution
+of $2500$ models. 
+If we obtain a p-value $<0.05$ for a given parameter, we conclude that
+this parameter does influence the $\chi^2$ fit, as the distribution for
+the best $\chi^2$ models is statistically different to the
+distribution from the global sample of $2500$ models.
+
+From this test we found that only three parameters influence the
+$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
+$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
+$10^{-4}$) and the probability that the \lya\ emission comes from the
+clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
+parameters do not influence the resulting spectra at all; it means
+that they cannot be constrained from \tol's observations.
+
+The best values for those parameters that we report here correspond to
+the values that produce the minimum
+$\chi^2$. The 1-$\sigma$ uncertainty comes from a parabolic fit to the
+$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
+$P_{\rm cl}$ around its corresponding minimum.
+Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
+$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
+
+Qualitatively as \tol\ possesses a very wide spectrum which can be
+achieved by subsequent scatterings off (relatively) fast moving clumps
+while the multi-phase nature (i.e., the existence of low-density
+channels) ensures the high flux at line center as observed.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
+\caption{Results from the Markov Chain Monte Carlo computation for
+    the rotation model. The dotted vertical lines in the outer histograms 
+	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
+\end{center}
+\end{figure*}
+
+\section{Interpretation}
+
+\subsection{Dynamical Mass Estimates}
+
+Having constrains for  velocity dipersion $\sigma$ of some dynamical
+tracers (clumps in the case of the multiphase model) in a spherical
+system located in a region of size $r$ we estimate the dynamical mass
+within $r$.
+
+\begin{equation}
+M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
+\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
+\end{equation}
+
+We use the 3D half-luminosity
+radius, $r_{s}$, as the typical size for the HI region.
+
+In the case of rotational velocity $v$ in a region of size $r$ we
+estimate the dynamical mass by
+
+\begin{equation}
+M_{\rm dyn} = \frac{v ^{2}r}{G} = 1.16\times10^{9}
+\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot} 
+\end{equation}
 
@@
 
+\section{Conclusions}
+
 A new observational test is needed to clarify the physical nature of
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.8\textwidth]{CLARA-TOL-main.pdf}
-\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
-  Dots correspond to the observational data. The line shows the results
-of our best model from a full radiative transfer simulation both for
-the rotation and multiphase models.} 
-\end{center}
-\end{figure*}
-
-\section*{\tol\ characteristics}
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lc}
-$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
-$\delta$(2000)$^{b}$ & -28d02m32s\\
-$l$, $b$ (deg) & 294, 34\\
-$m_V$ & 17.5\\
-  M$_V$ & -17.6\\ 
-$v$(km s$^{-1}$) & 7795\\
-Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
-Ly-$\alpha$ EW & $70$\AA\\
-H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
-$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
-\end{tabular}
-\end{center}
-\caption{Basic observational characteristics of TOL1214-277
-  \citep{Thuan97}\\} 
-\end{table}
-
-\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
-into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
-Mpc km s$^{-1}$) 
-Its metallicity is $\sim Z_{\odot}/24$ \citep{Izotov04} as derived from optical
-spectroscopy.
-
-The observed flux for the Lyman alpha line is $\sim
-8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
-and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
-$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
-\citep{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
-4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
-$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA\ 
-bandwidth, which in turns translates  into a star formation rate of
-$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
-luminosity and star formation rate of $9.1\times 10^{-43}$
-$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
-The absolute magnitude in the $V$ band translates into a luminosity of
-$8.9\times 10^{8}$ L$_{\odot}$.
-% using http://tomdwelly.com/tools_fluxtolum.php
-Comparing this ratio with the theoretical expectation from case B
-recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
-fraction of $20$\% for Ly$\alpha$ radiation.
-The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
-L$_{\odot}$ as measured by GALEX.
-
-There is an upper limit for the  
-integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
-upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
-\citep{pustilnikmartin07}.
-
-The near-infrared fluxes at $3.6$ $\mu$m and $4.5$ $\mu$m are
-$7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
-\citep{2008ApJ...678..804E}.  Using a conversion between fluxes and
-stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
-10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
-(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
-distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$, with a $30\%$ uncertainty coming from the calibration
-process \citep{2012AJ....143..139E}.
-
-We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
-from the surface intensity profiles reported by.
-\citep{2003A&A...410..481N}. 
-Assuming spherical geometry, one can translate this value into a 3D
-half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.
-
-\section*{The Rotation Model}
-
-The rotation model corresponds to the work presented in
-\citep{GaravitoCamargo2014} based on the Monte Carlo code
-\texttt{CLARA} \citep{CLARA}. 
-In that model the Ly-$\alpha$ photons are propagated 
-within a spherical and homogeneous cloud of HI gas undergoing solid
-body rotation.
-The sphere is fully characterized by three parameters: the HI line's
-center optical  depth $\tau$ measured from the center to its surface, the HI
-temperature $T$, and the linear surface velocity $V_{\rm max}$.  
-Photons are emitted at their natural frequency from the center of the
-sphere. 
-Including the effect of dust only changes the overall line
-normalization but not its shape.  
-The results we report in the main body of the paper do not include any
-dust model.
-In this letter we use an analytical solution that captures the most
-important effects of rotation onto the \lya\ line.
-
-The first important effect of rotation is that it breaks the spherical
-symmetry of the static case. 
-Now the line's observed morphology depends on the angle $\theta$ between the
-line-of-sight (LOS) and the rotation axis. 
-LOS parallel to the rotation axis tend to observed the line without
-any modification from rotation, while the perpendicular LOS will
-observe a maximal change in the line's morphology due to rotation.
-
-The main change in the line's morphology is that it broadens and the
-intensity at the center increases. 
-For high enough rotational velocities the intensity at the peak's
-center increases so much that the line goes from double to single
-peaked, sometimes slightly triple peaked.
-This is the feature that allows this model to fit the observational
-features of \tol.
-
-\citep{GaravitoCamargo2014} derived a concise analytical description for
-those features. 
-This description takes into account how different parts of the
-sphere's surface shift in frequency the \lya\ photons. 
-Different shifts in frequency come from different values for the projected
-velocity along the LOS. 
-Using the analytical solution for the \lya\ spectra of a static sphere
-plus the right frequency shifts  computed from geometrical
-considerations, one is able to compute an analytical solution for the
-rotating sphere that reproduces the main features found using the full
-numerical simulation.
-
-The analytical solution for the rotation sphere was the base to
-perform the Markov Chain Monte Carlo (MCMC) calculation using the
-\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
-is an open source optimized implementation of the affine-invariant 
-ensemble sampler for MCMC. The algorithm creates a number of walkers that,
-during a sufficient number of steps, generate parameters' combinations for
-a specific model. For each time, the code calculates the likelihood of the
-combination with respect to the observational data. The walkers ecplore
-the parameter space sampling the likelihood function.
-
-MCMC methods are optimal for sampling parameters at a high number of 
-dimensions. In this case we explore flat priors on four parameters:
-$200<V_{\rm max}/\mathrm{km\ s}^{-1} <600$,  
-$6.0<\log_{10}\tau<9.0$, $4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and
-$0<\theta<90$ using $500$ steps with $24$ walkers for a total of
-$12000$ points in the chain. 
-The results are summarized in 
-Figure \ref{emceeresults}. 
-From this model we find that the fiducial 
-parameters that could explain the broad features in \tol\ are 
-$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
-$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
-degrees.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=1.0\textwidth]{emcee_results.pdf}
-\caption{{\bf Results from the Markov Chain Monte Carlo computation for
-    the rotation model.} The dotted vertical lines in the outer histograms 
-	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
-\end{center}
-\end{figure*}
-
-\section*{The Multiphase Model}
-
-The idealized multiphase model consists of spherical, cold, dens
-clumps of neutral hydrogen (and dust) embedded in a hot, ionized
-medium. 
-The clumps also have a random and an outflowing velocity
-component which totals the number of parameters describing the model
-to be $14$.
-
-In order to map out this large parameter space, we randomly drew
-$2500$ sets of parameters within a observationally realistic range
-(based on the considerations of \citep{Laursen2013ApJ...766..124L})
-yielding a large variety of single-, double- and triple-peaked
-spectra. 
-The full analysis of the the spectral features as well as
-more details on the radiative transfer are presented in
-\citep{Gronke2016}.    
- For the current work, we computed the $\chi^2$ for each of the $2500$
-models. We selected the best $50$ models with the lowest $\chi^2$. The
-$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
-$\chi^2$ is close to $1200$. The total number of degrees of freedom is
-$104$.
-
-Then we performed a Kolmogorov-Smirnov test to compare each parameter
-distribution in the best $50$ models against the parent distribution
-of $2500$ models. 
-If we obtain a p-value $<0.05$ for a given parameter, we conclude that
-this parameter does influence the $\chi^2$ fit, as the distribution for
-the best $\chi^2$ models is statistically different to the
-distribution from the global sample of $2500$ models.
-
-From this test we found that only three parameters influence the
-$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
-$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
-$10^{-4}$) and the probability that the \lya\ emission comes from the
-clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
-parameters do not influence the resulting spectra at all; it means
-that they cannot be constrained from \tol's observations.
-
-The best values for those parameters that we report here correspond to
-the values that produce the minimum
-$\chi^2$. The 1-$\sigma$ uncertainty comes from a parabolic fit to the
-$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
-$P_{\rm cl}$ around its corresponding minimum.
-Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
-$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
-
-Qualitatively as \tol\ possesses a very wide spectrum which can be
-achieved by subsequent scatterings off (relatively) fast moving clumps
-while the multi-phase nature (i.e., the existence of low-density
-channels) ensures the high flux at line center as observed.
-
-\section*{Dynamical Mass Estimates}
-
-Having constrains for  velocity dipersion $\sigma$ of some dynamical
-tracers (clumps in the case of the multiphase model) in a spherical
-system located in a region of size $r$ we estimate the dynamical mass
-within $r$.
-
-\begin{equation}
-M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
-\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
-\end{equation}
-
-As described in the main the letter, we use the 3D half-luminosity
-radius, $r_{s}$, as the typical size for the HI region.
-
-In the case of rotational velocity $v$ in a region of size $r$ we
-estimate the dynamical mass by
-
-\begin{equation}
-M_{\rm dyn} = \frac{v ^{2}r}{G} = 1.16\times10^{9}
-\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot} 
-\end{equation}
-
 \bibliographystyle{mn2e}

### 2017-01-19 paper/letter.tex
sections

@@
 
-\section{\tol}
+\section{Observations}
 
@@
 
-\subsection{Rotation Model}
+\subsection{Rotation}
 
@@
 
-\subsection{Multiphase Model}
+\subsection{Multiphase ISM}
 
@@
 \includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
-\caption{{\bf Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.}
+\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
   Dots correspond to the observational data. The line shows the results
@@
 
-\section{Interpretation}
-
-\subsection{Dynamical Mass Estimates}
+\section{Discussion}
 
@@
 \tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$
+M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$. 
 \citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times

### 2017-02-07 paper/letter.tex
updated sections
updated intro

@@
 
-The first generation of galaxies trace our cosmic origins. 
-They were the first steps in the evolution of galaxies such as the Milky
-Way. 
-In the standard Big Bang cosmology the only chemical elements that
-were created in the nucleosynthesis process were Hydrogen, Helium and
-Lithium.  
-Heavier elements must have been created in stellar evolution process. 
-Therefore, we expect the first generation of
-galaxies to be metal free and rich in Hydrogen. 
-This kind of primordial galaxies have not been detected yet. 
+Primordial galaxies have not been detected yet. 
 However, dwarf star forming galaxies with a low metallicity content
 are seen as templates to understand the early galaxy evolution process. 
-
 Almost fifty years ago \citep{PartridgePeebles} it was realized that
@@
 We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
-from the surface intensity profiles reported by.
-\citep{2003A&A...410..481N}. 
+from the surface intensity profiles reported by \citep{2003A&A...410..481N}. 
 Assuming spherical geometry, one can translate this value into a 3D
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.6\textwidth]{CLARA-TOL-main.pdf}
+\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
+  Dots correspond to the observational data. The line shows the results
+of our best model from a full radiative transfer simulation both for
+the rotation and multiphase models.} 
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
+  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
+  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
+\caption{Results from the multiphase model\label{multiphaseresults}}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
+\caption{Results from the Markov Chain Monte Carlo computation for
+    the rotation model. The dotted vertical lines in the outer histograms 
+	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
+\end{center}
+\end{figure*}
+
 \section{Theoretical Models}
 
-\subsection{Rotation}
+\subsection{Multiphase ISM}
+
+The idealized multiphase model consists of spherical, cold, dens
+clumps of neutral hydrogen (and dust) embedded in a hot, ionized
+medium. 
+The clumps also have a random and an outflowing velocity
+component which totals the number of parameters describing the model
+to be $14$.
+
+In order to map out this large parameter space, we randomly drew
+$2500$ sets of parameters within a observationally realistic range
+(based on the considerations of \citep{Laursen2013ApJ...766..124L})
+yielding a large variety of single-, double- and triple-peaked
+spectra. 
+The full analysis of the the spectral features as well as
+more details on the radiative transfer are presented in
+\citep{Gronke2016}.
+
+\subsection{Bulk Rotation}
 
@@
 
-\subsection{Multiphase ISM}
-
-The idealized multiphase model consists of spherical, cold, dens
-clumps of neutral hydrogen (and dust) embedded in a hot, ionized
-medium. 
-The clumps also have a random and an outflowing velocity
-component which totals the number of parameters describing the model
-to be $14$.
-
-In order to map out this large parameter space, we randomly drew
-$2500$ sets of parameters within a observationally realistic range
-(based on the considerations of \citep{Laursen2013ApJ...766..124L})
-yielding a large variety of single-, double- and triple-peaked
-spectra. 
-The full analysis of the the spectral features as well as
-more details on the radiative transfer are presented in
-\citep{Gronke2016}.
-
 \section{Results}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.7\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
-  Dots correspond to the observational data. The line shows the results
-of our best model from a full radiative transfer simulation both for
-the rotation and multiphase models.} 
-\end{center}
-\end{figure*}
 
@@
 channels) ensures the high flux at line center as observed.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
-\caption{Results from the Markov Chain Monte Carlo computation for
-    the rotation model. The dotted vertical lines in the outer histograms 
-	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
-\end{center}
-\end{figure*}
 
@@
 
+\section*{Acknowledgments}
+
 \bibliographystyle{mn2e}

### 2017-02-07 paper/letter.tex
abstract, intro, obs characteristics

@@
 \title[Atypical Dwarf LAE]{
-Atypical Lyman-$\alpha$ emission in a dwarf galaxy via multiphase
-gas and rotation.}
+Lyman-$\alpha$ line emission sketches of a massive dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 interpretation so far. 
-In this paper we explain these features by two different models: an
-homogeneous gaseous sphere undergoing bulk rotation and an interstellar
-medium composed by outflowing clumps with additional random motions.
+In this paper we explain these features by two different models: 
+an interstellar medium composed by outflowing clumps with additional
+random motions and an homogeneous gaseous sphere undergoing bulk rotation.
 It is the first time that an observed \lya\ spectrum can be explained
@@
 We find that both models independently require high velocities
-(either a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$ or a clump velocity
-dispersion of \sigmaclump with outflows of
-\inftyclump) consistent with a dynamical mass of at
-least a billion solar masses, ten times larger than its baryonic mass.   
+(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
+\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
+consistent with a dynamical mass of at 
+least a $10^{10}$ M$_{\odot}$, ten times larger than its baryonic mass.   
 We argue that a possible explanation for this excess of
@@
 In this paper we show how the \tol's \lya\ profile can be explained
-either by rotation \citep{GaravitoCamargo2014} or the recently developed
-class of more complex 
-multiphase models that predict a wider variety of spectra
-including, single, double and triply peaked spectra \citep{Gronke2016}.
-
+either by  or the recently developed class of complex multiphase models 
+\citep{Gronke2016} or by a simple rotation model
+\citep{GaravitoCamargo2014}. 
 \section{Observations}
 
-\tol\ receding velocity is $7785\pm 50$km s$^{-1}$, which translates
+\tol's basic observational characteristics are summarized in Table \ref{obstable}.
+Its receding velocity is $7785\pm 50$km s$^{-1}$, which translates
 into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
 Mpc km s$^{-1}$)
-Its metallicity is $\sim Z_{\odot}/24$ \citep{Izotov04} as derived from optical
-spectroscopy.
 
@@
 The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
-L$_{\odot}$ as measured by GALEX.
+L$_{\odot}$ as measured by GALEX. Its metallicity is $\sim
+Z_{\odot}/24$ \citep{Izotov04} as derived from optical spectroscopy.
 
@@
 \begin{center}
-\begin{tabular}{lc}
+\begin{tabular}{lc}\hline
 $\alpha$(2000)$^{a}$ & 12h17min17.1s\\
@@
 Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
-Ly-$\alpha$ EW & $70$\AA\\
-H$\beta$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$) & $1.62\times 10^{-14}$ \\
-$21$cm (Jy km s$^{-1}$)& $<0.10$ \\
+Ly-$\alpha$ Equivalent Width (\AA) & $70$\\
+$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
 \end{tabular}
@@
 \caption{Basic observational characteristics of TOL1214-277
-  \citep{Thuan97}\\} 
+  \citep{Thuan97}\label{obstable}} 
 \end{table}

### 2017-02-07 paper/letter.tex
theory

@@
 
-\section{Theoretical Models}
+\section{Theoretical Models and Parameter Exploration}
 
@@
 component which totals the number of parameters describing the model
-to be $14$.
+to be $14$.  {\bf These parameters are: MAX}
 
@@
 temperature $T$, and the linear surface velocity $V_{\rm max}$.  
-Photons are emitted at their natural frequency from the center of the
-sphere. 
 Including the effect of dust only changes the overall line
 normalization but not its shape.  
-The results we report in the main body of the paper do not include any
-dust model.
+The results we report do not include any dust model.
 In this paper we use an analytical solution that captures the most
-important effects of rotation onto the \lya\ line.
+important effects of rotation onto the \lya\ line as explained by \citet{GaravitoCamargo2014}.
 
-The first important effect of rotation is that it breaks the spherical
-symmetry of the static case. 
-Now the line's observed morphology depends on the angle $\theta$ between the
-line-of-sight (LOS) and the rotation axis. 
-LOS parallel to the rotation axis tend to observed the line without
-any modification from rotation, while the perpendicular LOS will
-observe a maximal change in the line's morphology due to rotation.
-
-The main change in the line's morphology is that it broadens and the
-intensity at the center increases. 
-For high enough rotational velocities the intensity at the peak's
-center increases so much that the line goes from double to single
-peaked, sometimes slightly triple peaked.
-This is the feature that allows this model to fit the observational
-features of \tol.
-
-\citep{GaravitoCamargo2014} derived a concise analytical description for
-those features. 
-This description takes into account how different parts of the
-sphere's surface shift in frequency the \lya\ photons. 
-Different shifts in frequency come from different values for the projected
-velocity along the LOS. 
-Using the analytical solution for the \lya\ spectra of a static sphere
-plus the right frequency shifts  computed from geometrical
-considerations, one is able to compute an analytical solution for the
-rotating sphere that reproduces the main features found using the full
-numerical simulation.
-
-The analytical solution for the rotation sphere was the base to
+The analytical solution for the rotation sphere is the base to
 perform the Markov Chain Monte Carlo (MCMC) calculation using the
@@
 is an open source optimized implementation of the affine-invariant 
-ensemble sampler for MCMC. The algorithm creates a number of walkers that,
-during a sufficient number of steps, generate parameters' combinations for
-a specific model. For each time, the code calculates the likelihood of the
+ensemble sampler for MCMC. 
+The algorithm creates a number of walkers that,
+during a sufficient number of steps, generate parameters' combinations
+for a specific model. For each time, the code calculates the likelihood of the
 combination with respect to the observational data. The walkers ecplore

### 2017-02-09 paper/letter.tex
title
caption

@@
 \title[Atypical Dwarf LAE]{
-Lyman-$\alpha$ line emission sketches of a massive dwarf galaxy}
+Lyman-$\alpha$ emission line outlines a massive dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
   \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
-\caption{Results from the multiphase model\label{multiphaseresults}}
+\caption{Results from the multiphase
+  model\label{multiphaseresults}.
+  The left column corresponds to the parameter's integrated distributions for
+  models with the lowest $\chi^2$ values (dotted line) compared against the
+  parameter's integrated distributions (continous line) used as a prior.
+  These are the only three parameters that show a significant statistical difference from
+  the prior distributions, for all the other eleven parameters we
+  cannot find any significant difference.}  
 \end{center}

### 2017-02-23 paper/letter.tex
model selection

@@
 %=========================================================================
-\title[Atypical Dwarf LAE]{
-Lyman-$\alpha$ emission line outlines a massive dwarf galaxy}
+\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
+Ouflows and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 
+We compare each resulting spectra to the observational results from
+\tol\ after normalizing the observed and simulated spectra to have a a
+flux integral of one.
+We then build a $\chi^2$ on the normalized flux measurements for each one
+of the $2500$ models, and then select for further analysis the best
+$1\%$ models according to the lowest $\chi^2$ values.
+These best $50$ models have a large span in $\chi^2$ going from values
+of $1000$ to $3000$.
+
 \subsection{Bulk Rotation}
@@
 
+In this paper we presented two theoretical models that explain the main
+observational feature of \tol, which have been unexplained so far.
+One model is based on a multiphase ISM and the other on gas rotation,  
+It is the first time that an observed \lya\ profile can be fully
+reproduced by either of these two conditions.
+Furthermore, the kinematics of both models suggest a dynamical mass
+ten times larger than the baryonic mass infered from observations.
+
 A new observational test is needed to clarify the physical nature of

### 2017-02-23 paper/letter.tex
subsections

@@
 \title[An atypical Lyman-$\alpha$ dwarf galaxy]{
-Ouflows and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
+Clumpiness and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 $1\%$ models according to the lowest $\chi^2$ values.
-These best $50$ models have a large span in $\chi^2$ going from values
-of $1000$ to $3000$.
+The
+$\chi^2$ gap in those $25$ models is close to $3000$, the lowest
+$\chi^2$ being close to $1200$.
+The total number of degrees of freedom is
+$104$.
+
+Then we performed a Kolmogorov-Smirnov test to compare each parameter
+distribution in the best $25$ models against the parent distribution
+of $2500$ models. 
+If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
+this parameter does influence the $\chi^2$ fit, as the distribution for
+the best $\chi^2$ models is statistically different to the
+distribution from the global sample of $2500$ models.
+
+The best values for the influential parameters correspond to
+the values that produce the minimum
+$\chi^2$.
+The 1-$\sigma$ uncertainty comes from a parabolic fit to the
+$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
+$P_{\rm cl}$ around its corresponding minimum.
 
@@
 overplot from our best fits from the analytical solution for a
-rotating homogeneous gas sphere (thin line) and the multiphase
+urotating homogeneous gas sphere (thin line) and the multiphase
 model (thick line).
-This is the first time that these models have been introduced with
-success to explain an observed \lya\ profile.
+
+In spite of the simplicity of our models, this is the first time that
+the main \tol\ features can be reproduced: a wide, centered,
+single-peaked \lya\ line.
+This result does not demonstrate that our models are unique to
+reproduce \tol's features, but is a significant step forward to
+understand why this source is atypical.
+
+\subsection{Multiphase ISM}
+Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
+$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
+
+From this test we found that only three parameters influence the
+$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
+$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
+$10^{-4}$) and the probability that the \lya\ emission comes from the
+clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
+parameters do not influence the resulting spectra at all; it means
+that they cannot be constrained from \tol's observations.
+
+Qualitatively as \tol\ possesses a very wide spectrum which can be
+achieved by subsequent scatterings off (relatively) fast moving clumps
+while the multi-phase nature (i.e., the existence of low-density
+channels) ensures the high flux at line center as observed.
+
+\subsection{Bulk Rotation}
 
@@
 to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
-
- For the current work, we computed the $\chi^2$ for each of the $2500$
-models. We selected the best $50$ models with the lowest $\chi^2$. The
-$\chi^2$ gap in those $50$ models is close to $3000$, the lowest
-$\chi^2$ is close to $1200$. The total number of degrees of freedom is
-$104$.
-
-Then we performed a Kolmogorov-Smirnov test to compare each parameter
-distribution in the best $50$ models against the parent distribution
-of $2500$ models. 
-If we obtain a p-value $<0.05$ for a given parameter, we conclude that
-this parameter does influence the $\chi^2$ fit, as the distribution for
-the best $\chi^2$ models is statistically different to the
-distribution from the global sample of $2500$ models.
-
-From this test we found that only three parameters influence the
-$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
-$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
-$10^{-4}$) and the probability that the \lya\ emission comes from the
-clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
-parameters do not influence the resulting spectra at all; it means
-that they cannot be constrained from \tol's observations.
-
-The best values for those parameters that we report here correspond to
-the values that produce the minimum
-$\chi^2$. The 1-$\sigma$ uncertainty comes from a parabolic fit to the
-$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
-$P_{\rm cl}$ around its corresponding minimum.
-Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
-$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
-
-Qualitatively as \tol\ possesses a very wide spectrum which can be
-achieved by subsequent scatterings off (relatively) fast moving clumps
-while the multi-phase nature (i.e., the existence of low-density
-channels) ensures the high flux at line center as observed.
 

### 2017-02-23 paper/letter.tex
percentiles

@@
 
-\section{Theoretical Models and Parameter Exploration}
+\section{Theoretical Models and Parameter Estimation}
 
@@
 $\chi^2$ being close to $1200$.
-The total number of degrees of freedom is
-$104$.
+The total number of degrees of freedom is $104$.
 
@@
 The results we report do not include any dust model.
-In this paper we use an analytical solution that captures the most
-important effects of rotation onto the \lya\ line as explained by \citet{GaravitoCamargo2014}.
+Here we use an analytical solution that captures the most important
+effects of rotation onto the \lya\ line as explained by
+\citet{GaravitoCamargo2014} and allows us a full parameter space
+exploaration.
 
 The analytical solution for the rotation sphere is the base to
-perform the Markov Chain Monte Carlo (MCMC) calculation using the
+perform a Markov Chain Monte Carlo (MCMC) calculation using the
 \texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
@@
 for a specific model. For each time, the code calculates the likelihood of the
-combination with respect to the observational data. The walkers ecplore
-the parameter space sampling the likelihood function.
+combination with respect to the observational data. The walkers explore
+the parameter space sampling the likelihood function built as $\propto
+\exp(\chi^2/2)$, where the $\chi^2$ is computed from each bin in the
+spectra after normalization.
+
+We explore flat priors on four parameters: $200<V_{\rm
+  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
+$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
+steps with $24$ walkers for a total of $12000$ points in the chain.
+We estimate the parameter values from the 16th, 50th and 84th
+percentiles.
 
@@
 
-Figure 1. summarizes our findings.
+Figure 1. summarizes our main finding.
 Dots represent the observational data for \tol\ with the
-overplot from our best fits from the analytical solution for a
-urotating homogeneous gas sphere (thin line) and the multiphase
-model (thick line).
+overplot from our best fits from the analytical solution for the multiphase model (thick line). 
+and the rotating homogeneous gas sphere (thin line).
 
@@
 
-MCMC methods are optimal for sampling parameters at a high number of 
-dimensions. In this case we explore flat priors on four parameters:
-$200<V_{\rm max}/\mathrm{km\ s}^{-1} <600$,  
-$6.0<\log_{10}\tau<9.0$, $4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and
-$0<\theta<90$ using $500$ steps with $24$ walkers for a total of
-$12000$ points in the chain. 
 The results are summarized in 

### 2017-02-28 paper/letter.tex
intro
title intro

@@
 \title[An atypical Lyman-$\alpha$ dwarf galaxy]{
-Clumpiness and rotation: possible causes for an atypical Lyman-$\alpha$ dwarf galaxy}
+Possible kinematics of an atypical Lyman-$\alpha$ dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 It is the first time that an observed \lya\ spectrum can be explained
-assuming either of these physical conditions.
+assuming either of these kinematic conditions.
 We find that both models independently require high velocities
@@
 This work demonstrates the importance of considering multiphase
-physics and rotation among the possible conditions shaping the
+kinematics and rotation among the possible conditions shaping the
 \lya\ spectra of the first galaxies.  
@@
 \citep{GaravitoCamargo2014}. 
+The models we use correspond to simplified geometrical configurations
+to allow a deep exploration of parameter space and gain, for the firs time,
+some physical insight into the \tol's kinematic properties.
+
 \section{Observations}
-
 \tol's basic observational characteristics are summarized in Table \ref{obstable}.
@@
 The
-$\chi^2$ gap in those $25$ models is close to $3000$, the lowest
-$\chi^2$ being close to $1200$.
+$\chi^2$ gap in those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
+$\chi^2$ being close to $\chi^2_{min}=1200$.
 The total number of degrees of freedom is $104$.
 
-Then we performed a Kolmogorov-Smirnov test to compare each parameter
+Then we perform a Kolmogorov-Smirnov test to compare each parameter
 distribution in the best $25$ models against the parent distribution
@@
 The 1-$\sigma$ uncertainty comes from a parabolic fit to the
-$\chi^2$ as a function of $v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
-$P_{\rm cl}$ around its corresponding minimum.
+$\chi^2$ as a function of the influential parameters around its
+corresponding minimum.  
+%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
+%$P_{\rm cl}$
 

### 2017-02-28 paper/letter.tex
latest version

@@
 \title[An atypical Lyman-$\alpha$ dwarf galaxy]{
-Possible kinematics of an atypical Lyman-$\alpha$ dwarf galaxy}
+Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 interpretation so far. 
-In this paper we explain these features by two different models: 
-an interstellar medium composed by outflowing clumps with additional
-random motions and an homogeneous gaseous sphere undergoing bulk rotation.
+In this paper we explain these features by two different kinematic models: 
+an interstellar medium composed by outflowing clumps with 
+random motions and an homogeneous gaseous sphere undergoing solid body
+rotation.
 It is the first time that an observed \lya\ spectrum can be explained
@@
 consistent with a dynamical mass of at 
-least a $10^{10}$ M$_{\odot}$, ten times larger than its baryonic mass.   
+least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
 We argue that a possible explanation for this excess of
@@
 \lya\ spectra of the first galaxies.  
-Additionally, if future kinematic maps of \tol\ confirm the high
-velocities postulated in our model, it would provide new
+Additionally, if future kinematic maps of \tol\ confirm the 
+velocities found by our models, it would provide new
 evidence for dwarf galaxies as hosts of supermassive black
@@
 \begin{center}
-\includegraphics[width=0.6\textwidth]{CLARA-TOL-main.pdf}
+\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
 \caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
@@
 \caption{Results from the multiphase
-  model\label{multiphaseresults}.
+  model.
   The left column corresponds to the parameter's integrated distributions for
@@
   the prior distributions, for all the other eleven parameters we
-  cannot find any significant difference.}  
+  cannot find any significant difference.
+  \label{multiphaseresults}
+}  
 \end{center}
@@
 
-The idealized multiphase model consists of spherical, cold, dens
+The idealized multiphase model consists of spherical, cold, dense
 clumps of neutral hydrogen (and dust) embedded in a hot, ionized
@@
 component which totals the number of parameters describing the model
-to be $14$.  {\bf These parameters are: MAX}
+to be $14$, which also include information about the spatial
+distribution and thermal state of the clumps and the intraclump
+medium.
 
@@
 flux integral of one.
-We then build a $\chi^2$ on the normalized flux measurements for each one
-of the $2500$ models, and then select for further analysis the best
-$1\%$ models according to the lowest $\chi^2$ values.
-The
-$\chi^2$ gap in those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
-$\chi^2$ being close to $\chi^2_{min}=1200$.
-The total number of degrees of freedom is $104$.
+We build a $\chi^2$ on the normalized flux measurements for each one
+of the $2500$ models
+
+\begin{equation}
+\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
+\label{eq:chi2}
+\end{equation}
+
+where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
+$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
+model estimated flux.
+
+We select for further analysis the best $1\%$ models according to the
+lowest $\chi^2$ values.
+We note that the $\chi^2$ gap in those $25$ models is close to
+$\Delta\chi^2 = 3000$, the lowest $\chi^2$ being close to
+$\chi^2_{min}=1200$.
+To have a sense of scale, the total number of degrees of freedom is
+$104$.
 
@@
 $\chi^2$.
-The 1-$\sigma$ uncertainty comes from a parabolic fit to the
+We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
 $\chi^2$ as a function of the influential parameters around its
@@
 during a sufficient number of steps, generate parameters' combinations
-for a specific model. For each time, the code calculates the likelihood of the
-combination with respect to the observational data. The walkers explore
+for a specific model.
+For each timestep, the code calculates the likelihood of the
+combination with respect to the observational data.
+The walkers explore
 the parameter space sampling the likelihood function built as $\propto
-\exp(\chi^2/2)$, where the $\chi^2$ is computed from each bin in the
-spectra after normalization.
+\exp(\chi^2/2)$, where the $\chi^2$ follows the definition in Equation
+\ref{eq:chi2}.
 
@@
 Dots represent the observational data for \tol\ with the
-overplot from our best fits from the analytical solution for the multiphase model (thick line). 
-and the rotating homogeneous gas sphere (thin line).
+overplot from our best fits from the analytical solution for the
+multiphase model (thick line)  and the rotating homogeneous gas sphere
+(thin line).
 
@@
 single-peaked \lya\ line.
-This result does not demonstrate that our models are unique to
-reproduce \tol's features, but is a significant step forward to
-understand why this source is atypical.
+This result does not demonstrate that the kinematic features we
+include in our models are necessary to reproduce \tol's features, but
+at least they show that they are a sufficient condition.
+This is a significant step forward to understand the influence that
+different kinematics have in producing the atypical line profile shown
+by \tol.
+
+In what follows we summarize the values of the kinematic parameters
+that managed to explain \tol\'s \lya\ profile.
 
 \subsection{Multiphase ISM}
+
+From the K-S tests we find that only three parameters can be
+constrained by the observations: the clump outflow velocity
+$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), the clump velocity
+dispersion $\sigma_{\rm cl}$ (p-value $10^{-4}$) and the probability
+that the \lya\ emission comes from the clumps $P_{\rm cl}$ (p-value
+$10^{-4}$).
+This does not mean the other parameters do not influence the resulting
+spectra at all; it means that they cannot be constrained from \tol's
+observations.
+
+The results are summarized in Figure \ref{multiphaseresults}.
+Left panels show the difference between the integrated distributions
+of the full sample (2500 input models) and the models with the lowest
+$\chi^2$. 
+The right panel shows the actual $\chi^2$ values and its corresponding
+parameter value. 
 Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
@@
 
-From this test we found that only three parameters influence the
-$\chi^2$: the clump outflow velocity $v_{\infty,\rm{cl}}$ (p-value 
-$10^{-18}$), the clump velocity dispersion $\sigma_{\rm cl}$ (p-value
-$10^{-4}$) and the probability that the \lya\ emission comes from the
-clumps $P_{\rm cl}$ (p-value $10^{-4}$). This does not mean the other
-parameters do not influence the resulting spectra at all; it means
-that they cannot be constrained from \tol's observations.
-
-Qualitatively as \tol\ possesses a very wide spectrum which can be
+Qualitatively, as \tol\ possesses a very wide spectrum which can be
 achieved by subsequent scatterings off (relatively) fast moving clumps
@@
 channels) ensures the high flux at line center as observed.
+A lower velocity dispersion would produce a thiner line than the
+observed.
+From the lower right panel in \ref{multiphaseresults} we find that it
+is unlikely that the clump velocity dispersion is lower than
+$50$\kms.
 
@@
 
-The results are summarized in 
-Figure \ref{emceeresults}. 
-From this model we find that the fiducial 
-parameters that could explain the broad features in \tol\ are 
-$V_{\rm max}=348^{+75}_{-48}$ km s$^{-1}$, $\log \tau = 6.96^{+0.26}_{-0.18}$, 
-$\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$ and $\theta = 35.78^{+2.13}_{-1.88}$ 
-degrees.
-
-The best parameters in the rotation model are a rotational velocity of 
-$V_{\rm max}=348^{+75}_{-48}$ \kms, a neutral Hydrogen optical depth of 
-$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.  
+The results are summarized in  Figure \ref{emceeresults}. 
+From this analysis we find that the best parameters in the rotation
+model are a rotational velocity of  $V_{\rm max}=348^{+75}_{-48}$
+\kms, a neutral Hydrogen optical depth of
+$\log_{10}\tau=6.96^{+0.26}_{-0.18}$,  and an inter-stellar medium
+temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.   
 This model is also able to constrain the angle between the plane
@@
 
+Lower rotational velocities are disfavored by the fact that the line
+is single peaked.
+Fixing the optical depth at a high value of $10^7$ ensures that the line width
+is close to its observed value.
+A lower rotational velocity would produce a double peaked line.
+The fact that the velocity and optical depth priors were wide enough,
+allows us to think that the current values found by the MCMC are
+robust given the observational constraints.
+
 \section{Discussion}
 
-Having constrains for  velocity dipersion $\sigma$ of some dynamical
-tracers (clumps in the case of the multiphase model) in a spherical
-system located in a region of size $r$ we estimate the dynamical mass
-within $r$.
+Using the constrains for the velocity dipersion $\sigma$ and the
+maximum rotational velocity $V_m$ in a spherical system localized in a
+region of size $r$ we can estimate two different values for the
+dynamical mass within $r$:
 
@@
 M_{\rm dyn} = 3 \frac{\sigma ^{2}r}{G} = 3.48\times10^{9}
-\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right) M_{\odot}
+\left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
+M_{\odot}, 
 \end{equation}
+%
+and
+%
+\begin{equation}
+M_{\rm dyn} = \frac{V_m ^{2}r}{G} = 1.16\times10^{9}
+\left(\frac{V_m}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot}, 
+\end{equation}
+%
+for the multiphase and rotation model, respectively.
+Assuming that the \lya\ emission is entirely powered by star formation 
+we use the 3D half-luminosity radius $r_s=2.25$ kpc as the typical size
+for the HI region,
 
-We use the 3D half-luminosity
-radius, $r_{s}$, as the typical size for the HI region.
-
-In the case of rotational velocity $v$ in a region of size $r$ we
-estimate the dynamical mass by
-
-\begin{equation}
-M_{\rm dyn} = \frac{v ^{2}r}{G} = 1.16\times10^{9}
-\left(\frac{v}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot} 
-\end{equation}
-
-In the multiphase model the best constrained parameters by the
-observational data are the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump ,  the clump's outflowing velocity
-$v_{\infty, \rm{cl}}=$\inftyclump\ and the fraction of the
-\lya\ emission that is  coming from the cold clumps  $P_{\rm cl}=$\probaclump.
-
-Assuming that the clumps are located in a spherical region of radius
-$r_s=2.25$ kpc (corresponding to \tol's estimated 3D half-luminosity
-radius), 
-this corresponds to dynamical masses of $M_{\rm dyn} =
-3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$ and $M_{\rm
-  dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$ for the
-rotation and multiphase models, respectively,
+In the multiphase model the clump velocity dispersion
+$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
+$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, while the
+rotational velocity of $V_{\rm max}=348^{+75}_{-48}$\kms corresponds
+$M_{\rm dyn} = 3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$.
 
@@
 the baryonic mass, depending if one considers the multiphase or
-rotation estimate.
-
+bulk rotation estimate. 
 We lean towards the lower dynamical mass estimate from the multiphase
@@
 astrophysical mechanisms for its origin.
-The first way to explain a dynamical mass of $10^{9} M_{\odot}$
+
+A first possibility to explain a dynamical mass of $10^{9} M_{\odot}$
 in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
@@
 mass.
+
 A second possibility is that \tol\ hosts a supermassive black hole of
@@
 
-Another perspective to appreciate the atypically high dynamical mass
-estimates comes from the observed scaling relations for dwarf
-galaxies.
-Assuming that \tol\ followed the fundamental plane relationship
-between its mean surface brightness $I_e$, the projected half-light
-radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
-I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
-the expected velocity dispersion should be on the order of $5 \pm 1$ 
-\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
-results from the multiphase and rotation models, respectively. 
-These are equivalent to factors of $\sim$ $100$ - $3600$ on the
-dynamical mass.
-Once again,  \tol\ seems to be significantly more massive than
-expected.
+%Another perspective to appreciate the atypically high dynamical mass
+%estimates comes from the observed scaling relations for dwarf
+%galaxies.
+%Assuming that \tol\ followed the fundamental plane relationship
+%between its mean surface brightness $I_e$, the projected half-light
+%radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
+%I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
+%the expected velocity dispersion should be on the order of $5 \pm 1$ 
+%\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
+%results from the multiphase and rotation models, respectively. 
+%These are equivalent to factors of $\sim$ $100$ - $3600$ on the
+%dynamical mass.
+%Once again,  \tol\ seems to be significantly more massive than
+%expected.
 
-\section{Conclusions}
-
-In this paper we presented two theoretical models that explain the main
-observational feature of \tol, which have been unexplained so far.
-One model is based on a multiphase ISM and the other on gas rotation,  
-It is the first time that an observed \lya\ profile can be fully
-reproduced by either of these two conditions.
-Furthermore, the kinematics of both models suggest a dynamical mass
-ten times larger than the baryonic mass infered from observations.
-
-A new observational test is needed to clarify the physical nature of
+A new observational test is needed to clarify the kinematical nature of
 \tol. 
-We suggest that integral field unit measurements spatially
+We suggest that integral field unit measurements 
 resolving its spatial extent are up to the task. 
@@
 ionization lines to infer a kinematic map.
+We note that archival Chandra X-ray archival
+data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
+detection for \tol\. This lack of observations also puts an upper
+limit on the intensity of recent black hole activity.
+
 Another observational test includes the measurement of the
@@
 variations depending on viewing angle \citep{2014MNRAS.444.1095G}. 
+recent
+
+\section{Conclusions}
+
+In this paper we presented two kinematic models that independently
+reproduce the so far unexplained observational features of \tol's
+\lya\ emission line.
+
+One model is based on a multiphase ISM with random clump motions and
+the other on gas bulk solid body rotation.
+It is the first time that an observed \lya\ profile can be fully
+reproduced by either of these two kinematic conditions.
+Furthermore, the kinematics of both models suggest a dynamical mass
+at least ten times larger than the baryonic mass infered from observations.
+We suggest that additional integral field unit observations are the
+only way to be certain about the detailed kinematic structure in \tol.
 
@@
 These findings demonstrate the importance of including rotation and multiphase
-conditions as features to model the \lya\ line in high redshift
+conditions as kinematic features to model the \lya\ line in high redshift
 galaxies.
@@
 \section*{Acknowledgments}
+We thanks J. M. Mas-Hesse for providing us with \tol's observational
+\lya\ data in electronic format. This data was used to prepare Figure
+1.
 

### 2017-03-07 paper/letter.tex
some typos

@@
 Max Gronke$^2$, 
-Mar\'ia Camila Remolina-Guti\'errez$^1$,
+Maria Camila Remolina-Guti\'errez$^1$,
 \newauthor
@@
 The models we use correspond to simplified geometrical configurations
-to allow a deep exploration of parameter space and gain, for the firs time,
+to allow a deep exploration of parameter space and gain, for the first time,
 some physical insight into the \tol's kinematic properties.
@@
 $2500$ sets of parameters within a observationally realistic range
-(based on the considerations of \citep{Laursen2013ApJ...766..124L})
+(based on the considerations of \cite{Laursen2013ApJ...766..124L})
 yielding a large variety of single-, double- and triple-peaked

### 2017-03-08 paper/letter.tex
other typos

@@
 \citet{GaravitoCamargo2014} and allows us a full parameter space
-exploaration.
+exploration.
 
@@
 data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
-detection for \tol\. This lack of observations also puts an upper
+detection for \tol. This lack of observations also puts an upper
 limit on the intensity of recent black hole activity.
@@
 variations depending on viewing angle \citep{2014MNRAS.444.1095G}.
-recent
 
@@
 \section*{Acknowledgments}
-We thanks J. M. Mas-Hesse for providing us with \tol's observational
+We thank J. M. Mas-Hesse for providing us with \tol's observational
 \lya\ data in electronic format. This data was used to prepare Figure

### 2017-03-13 paper/letter.tex
new referencies

@@
 Ly-$\alpha$ emission.
+A careful clustering analysis of LAEs can also yield clues about their link
+to dark matter halos \cite{2016ApJ...828....5M}.
 
 The Ly-$\alpha$ emission line is not exclusive of distant galaxies. 
-Any galaxy with low dust content and ongoing star formation has the
-right conditions to show this line.  
-There are, for instance,  local Universe surveys that target
-Ly-$\alpha$ emission in nearby dwarf star forming galaxies 
-\citep{LARS}. 
+There are local Universe surveys that target Ly-$\alpha$ emission in nearby dwarf star forming galaxies  \citep{LARS}. 
 The study of nearby LAE samples has allowed the study of other
@@
 There are very few analytically tools available to interpret the
-emerging Ly-$\alpha$ line.
+emerging Ly-$\alpha$ line
+\cite{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
 They are applicable only in very few cases of highly symmetrical
@@
 These two special features in \tol\ cannot be explained with
-conventional models \citep{2006A&A...460..397V,2015ApJ...812..123G}.
+conventional shell models
+\citep{2006A&A...460..397V,2015A&A...578A...7V, 2015ApJ...812..123G}.
 

### 2017-03-13 paper/letter.tex
SFR

@@
 Usually the Ly-$\alpha$ line has an asymmetric single or double peak. 
-These two special features in \tol\ cannot be explained with
-conventional shell models
-\citep{2006A&A...460..397V,2015A&A...578A...7V, 2015ApJ...812..123G}.
+These two special features in \tol\ cannot be explained quantitatively
+tith conventional shell models
+\citep{Mas-Hesse09,2015A&A...578A...7V,2015ApJ...812..123G}.
 
@@
 \citep{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
-4.9$\pm$0.1. The Ly-$\alpha$ flux values correspond to luminosities of
-$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$ over a $20$\AA\ 
-bandwidth, which in turns translates  into a star formation rate of
-$2.0$ M$_{\odot}$ yr$^{-1}$ using a standard conversion factor between
-luminosity and star formation rate of $9.1\times 10^{-43}$
-$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
+4.9$\pm$0.1.
+The Ly-$\alpha$ flux values correspond to luminosities of
+$L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
+translates  into a star formation rate of $2.0$ M$_{\odot}$ yr$^{-1}$
+using a standard conversion factor between luminosity and star
+formation rate of $9.1\times 10^{-43}$ $L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
 The absolute magnitude in the $V$ band translates into a luminosity of
@@
 The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
-L$_{\odot}$ as measured by GALEX. Its metallicity is $\sim
-Z_{\odot}/24$ \citep{Izotov04} as derived from optical spectroscopy.
-
-There is an upper limit for the  
-integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
-upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
-\citep{pustilnikmartin07}.
+L$_{\odot}$ as measured by GALEX, without any correction by extinction
+and following the empirical relation by \cite{Kennicutt98}, this
+corresponds to a star formation rate of $0.35\pm 0.05$ M$_{\odot}$
+yr$^{-1}$. Its metallicity is $\sim Z_{\odot}/24$ as derived from
+optical spectroscopy \citep{Izotov04}.
 
@@
 $7.71\pm0.55\times 10^{-5}$ Jy and $7.98\pm0.71\times 10^{-5}$ Jy
-\citep{2008ApJ...678..804E}.  Using a conversion between fluxes and
+\citep{2008ApJ...678..804E}.
+Using a conversion between fluxes and
 stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
@@
 half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.
+
+There is an upper limit for the  
+integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
+upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
+\citep{pustilnikmartin07}.
 
@@
 We thank J. M. Mas-Hesse for providing us with \tol's observational
-\lya\ data in electronic format. This data was used to prepare Figure
-1.
+\lya\ data \citep{Mas-Hesse09} in electronic format. This data was
+used to prepare Figure 1.
 

### 2017-03-13 paper/letter.tex
refs caption

@@
 of our best model from a full radiative transfer simulation both for
-the rotation and multiphase models.} 
+the rotation and multiphase models.
+The observational points corresponds to the data as shown in
+\citep{mashesse03}.}   
 \end{center}
@@
   cannot find any significant difference.
+  The right column shows a scatter plot of $\chi^2/1000$
+  and its corresponding physical parameters.
+  Only the  25 models with the lowest $\chi^2$ are included.
   \label{multiphaseresults}
@@
 steps with $24$ walkers for a total of $12000$ points in the chain.
-We estimate the parameter values from the 16th, 50th and 84th
+Previous exploratory work shows that it is impossible to fit the
+observed line outside thsese priors.
+Finally, we estimate the parameter values from the 16th, 50th and 84th
 percentiles.
@@
 in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
-least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}, which
-leaves open the question as to why  \tol\ is not more similar to the
-Milky Way galaxy as it would be hosted by a dark matter halo of similar
-mass.
+least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}.
+This estimate is based on computing the integrated mass profile of a
+spherical dark matter halo with a Navarro-Frenk-White profile with its
+concentration following the \emph{median} mass-concentration
+relationship found in the Bolshoi simulation
+\citep{2012MNRAS.423.3018P}. 
+This estimate leaves open the question as to why  \tol\ is not more
+similar to the Milky Way galaxy as it would be hosted by a dark matter
+halo of similar mass.
 
@@
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle \citep{2014MNRAS.444.1095G}.
+variations depending on viewing angle \citep{Gronke2016}.
 
@@
 We thank J. M. Mas-Hesse for providing us with \tol's observational
-\lya\ data \citep{Mas-Hesse09} in electronic format. This data was
+\lya\ data \citep{mashesse03} in electronic format. This data was
 used to prepare Figure 1.

### 2017-03-13 paper/letter.tex
lya abbrev

@@
 %=========================================================================
-\title[An atypical Lyman-$\alpha$ dwarf galaxy]{
-Modelling the gas kinematics of an atypical Lyman-$\alpha$ emitting compact dwarf galaxy}
+\title[An atypical \lya\ dwarf galaxy]{
+Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 Here we report on one of such CDGs, \tol, which presents
-a broad symmetric Lyman-$\alpha$ line emission that had evaded theoretical
+a broad symmetric \lya\ line emission that had evaded theoretical
 interpretation so far. 
@@
 are seen as templates to understand the early galaxy evolution process. 
-Almost fifty years ago \citep{PartridgePeebles} it was realized that
-young galaxies could be detected through a strong Lyman-$\alpha$ line
+Over fifty years ago \citep{PartridgePeebles} it was realized that
+young galaxies could be detected through a strong \lya\ line
 emission.
@@
 in surveys. 
-The presence of the Ly-$\alpha$ emission line provides confirmation of
+The presence of the \lya\ emission line provides confirmation of
 the distance of a galaxy while provides clues about the stellar
 population and inter-stellar medium conditions regulating the
-Ly-$\alpha$ emission.
+\lya\ emission.
 A careful clustering analysis of LAEs can also yield clues about their link
@@
 
-The Ly-$\alpha$ emission line is not exclusive of distant galaxies. 
-There are local Universe surveys that target Ly-$\alpha$ emission in nearby dwarf star forming galaxies  \citep{LARS}. 
+The \lya\ emission line is not exclusive of distant galaxies. 
+There are local Universe surveys that target \lya\ emission in nearby dwarf star forming galaxies  \citep{LARS}. 
 The study of nearby LAE samples has allowed the study of other
@@
 
-However, the physical interpretation of Ly-$\alpha$ observations is
+However, the physical interpretation of \lya\ observations is
 not straightforward \citep{2015ApJ...805...14R}. 
-This is due to the resonant nature of the Ly-$\alpha$ line. 
-A Ly-$\alpha$ photon follows a diffusion-like process before escaping
+This is due to the resonant nature of the \lya\ line. 
+A \lya\ photon follows a diffusion-like process before escaping
 the galaxy or being absorbed by dust. 
@@
 There are very few analytically tools available to interpret the
-emerging Ly-$\alpha$ line
+emerging \lya\ line
 \cite{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
@@
 conditions, which are hardly met in real astrophysical systems.
-For these reasons the interpretation of Ly-$\alpha$ observations
+For these reasons the interpretation of \lya\ observations
 requires state-of-the-art Monte Carlo radiative transfer simulations.
@@
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong Ly-$\alpha$ emission \citep{Thuan97} with two puzzling 
+strong \lya\ emission \citep{Thuan97} with two puzzling 
 features: the line is symmetric and single peaked.
-Usually the Ly-$\alpha$ line has an asymmetric single or double peak. 
+Usually the \lya\ line has an asymmetric single or double peak. 
 These two special features in \tol\ cannot be explained quantitatively
@@
 
-The observed flux for the Lyman alpha line is $\sim
+The observed flux for the \lya\ line is $\sim
 8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
@@
 $1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
-\citep{Izotov04} which gives a Ly$\alpha$/H$\beta$ flux ratio of
+\citep{Izotov04} which gives a \lya/H$\beta$ flux ratio of
 4.9$\pm$0.1.
-The Ly-$\alpha$ flux values correspond to luminosities of
+The \lya\ flux values correspond to luminosities of
 $L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
@@
 recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
-fraction of $20$\% for Ly$\alpha$ radiation.
+fraction of $20$\% for \lya\ radiation.
 The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
@@
 $v$(km s$^{-1}$) & 7795\\
-Ly-$\alpha$ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
-Ly-$\alpha$ Equivalent Width (\AA) & $70$\\
+\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
+\lya\ Equivalent Width (\AA) & $70$\\
 $21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
@@
 \includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and symmetric Ly-$\alpha$ emission of \tol.
+\caption{Broad, single peaked and symmetric \lya\ emission of \tol.
   Dots correspond to the observational data. The line shows the results
@@
   cannot find any significant difference.
-  The right column shows a scatter plot of $\chi^2/1000$
+  The right column shows a scatter plot of $\chi^2$ (rescaled by a $1000$)
   and its corresponding physical parameters.
@@
 \texttt{CLARA} \citep{CLARA}. 
-In that model the Ly-$\alpha$ photons are propagated 
+In that model the \lya\ photons are propagated 
 within a spherical and homogeneous cloud of HI gas undergoing solid
@@
 data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
-detection for \tol. This lack of observations also puts an upper
-limit on the intensity of recent black hole activity.
+detection for \tol.
+This lack of detection would also put an upper limit on the intensity
+of recent black hole activity due to accretion.
 

### 2017-03-13 paper/letter.tex
intro

@@
 The \lya\ emission line is not exclusive of distant galaxies. 
-There are local Universe surveys that target \lya\ emission in nearby dwarf star forming galaxies  \citep{LARS}. 
+There are local Universe surveys that target \lya\ emission in nearby
+dwarf star forming galaxies.
 The study of nearby LAE samples has allowed the study of other
@@
 such as morphology, dust attenuation, neutral hydrogen contents and
-ionization state.
+ionization state. (see \citep{Hayes15} and references therein for a review.)
 
 However, the physical interpretation of \lya\ observations is
-not straightforward \citep{2015ApJ...805...14R}. 
+not straightforward \citep{LARS,2015ApJ...805...14R}. 
 This is due to the resonant nature of the \lya\ line. 
@@
 strong \lya\ emission \citep{Thuan97} with two puzzling 
-features: the line is symmetric and single peaked.
+features: the line is symmetric, single peaked and wide around the
+line's center.
 Usually the \lya\ line has an asymmetric single or double peak. 
@@
 
-In this paper we show how the \tol's \lya\ profile can be explained
+Here we show how the \tol's \lya\ profile can be explained
 either by  or the recently developed class of complex multiphase models 
@@
 
+In this paper we review first the observational characteristics of
+\tol, then we summarize the main feature of the multiphase and
+rotation models and explain how we fit the free parameters in the
+model to the \lya\ line shape in \tol.
+We use the kinematic result to interpret them in terms of the
+dynamical mass that should be present in \tol.
+We close by discussing the physical scenarios that open up by our
+results and the additional observational information needed to clarify
+the kinematic nature of \tol.
+
 \section{Observations}
@@
 into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
-Mpc km s$^{-1}$)
+km s$^{-1}$ Mpc$^{-1}$.)
 
@@
 In order to map out this large parameter space, we randomly drew
-$2500$ sets of parameters within a observationally realistic range
-(based on the considerations of \cite{Laursen2013ApJ...766..124L})
+$2500$ sets of parameters within a observationally realistic range,
+based on the considerations of \cite{Laursen2013ApJ...766..124L}, 
 yielding a large variety of single-, double- and triple-peaked

### 2017-03-13 paper/letter.tex
moving parts

@@
 These two special features in \tol\ cannot be explained quantitatively
-tith conventional shell models
+with conventional shell models
 \citep{Mas-Hesse09,2015A&A...578A...7V,2015ApJ...812..123G}.
+
+This kind of profile also raises the question whether some high redshift
+LAEs have asymmetric lines because the blue half was truncated by the
+intergalactic medium \citep{2007MNRAS.377.1175D}. 
+In this case the \lya\ radiation could emerge as a low surface
+brightness glow, which may be connected to \lya\ halos, while also
+influencing the way LAEs can be used as a probe of reionization
+\citep{2014PASA...31...40D}.
 
@@
 
-In this paper we review first the observational characteristics of
-\tol, then we summarize the main feature of the multiphase and
-rotation models and explain how we fit the free parameters in the
-model to the \lya\ line shape in \tol.
-We use the kinematic result to interpret them in terms of the
-dynamical mass that should be present in \tol.
+We review first the observational characteristics of
+\tol, then we summarize the main features in the multiphase and
+rotation models to explain how we fit their free parameters 
+to the \tol's \lya\ line shape.
+We use the results to interpret them in terms of the galaxy's
+dynamical mass. 
 We close by discussing the physical scenarios that open up by our
@@
 $2500$ sets of parameters within a observationally realistic range,
-based on the considerations of \cite{Laursen2013ApJ...766..124L}, 
+based on the considerations of \citet{Laursen2013ApJ...766..124L}, 
 yielding a large variety of single-, double- and triple-peaked
@@
 The full analysis of the the spectral features as well as
-more details on the radiative transfer are presented in
-\citep{Gronke2016}.
+more details on the radiative transfer are presented by
+\citet{Gronke2016}.
 
@@
 
-Then we perform a Kolmogorov-Smirnov test to compare each parameter
+Then we perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
 distribution in the best $25$ models against the parent distribution
@@
 temperature $T$, and the linear surface velocity $V_{\rm max}$.  
-Including the effect of dust only changes the overall line
-normalization but not its shape.  
+In this model, dust only changes the overall line
+normalization and only weakly its shape.  
 The results we report do not include any dust model.
@@
 is an open source optimized implementation of the affine-invariant 
-ensemble sampler for MCMC. 
+MCMC sampler \citep{goodman2010ensemble}. 
 The algorithm creates a number of walkers that,
@@
 combination with respect to the observational data.
-The walkers explore
-the parameter space sampling the likelihood function built as $\propto
-\exp(\chi^2/2)$, where the $\chi^2$ follows the definition in Equation
-\ref{eq:chi2}.
+The walkers explore the parameter space sampling the Gaussian likelihood
+function built as $\propto \exp(-\chi^2/2)$, where the $\chi^2$ follows
+the definition in Equation \ref{eq:chi2}.
 
@@
 channels) ensures the high flux at line center as observed.
-A lower velocity dispersion would produce a thiner line than the
+In turn, a lower velocity dispersion would produce a thiner line than the
 observed.
@@
 $50$\kms.
+
+Why is it that the other parameters do not seem to matter? Probably
+because $P_{cl}$ (the probability for a \lya\ to be emitted in a
+clump) is high and most photons are produced at
+large radii making the radiative tranfer effects in the center less
+important.  
+We cannot discard that another region of parameter spacem with similar
+velocity structure but empty interclump medium, relatively dense
+clumps and at least a few clumps per sightline 
+could also work \citep{Hansen06}.
+This possibility does not change our conclusions about the
+kinematic parameters, but it might be interesting to explore in the
+future with a higher sampling of the parameter space once new
+observations clarify the kinematic nature of \tol.
 
@@
 
-Using the constrains for the velocity dipersion $\sigma$ and the
+\tol\ shows one of the most atypical \lya\ spectra observed so far.
+Its flux at the line's center is high compared to other LAEs at low
+redshift and the wide symmetrical peak is virtually absent from other
+LAEs at low and high redshift \citep{LARS,Erb14,Trainor16}. Simple
+shell models fail to reproduce such a spectrum
+\cite{2015A&A...578A...7V}.  
+In the previous sections we show how these characteristics can be
+explained by rather extreme kinematic characteristics.
+Now we discuss and frame those results in terms of the dynamical mass
+that could explain the velocities obtained in the model.
+
+Using the constraints for the velocity dipersion $\sigma$ and the
 maximum rotational velocity $V_m$ in a spherical system localized in a
@@
 \tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$. 
+M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass
+is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$ 
 \citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
@@
 \tol\ spans a region of $4$ arcseconds,
-an instrument such as the Multi Unit Spectroscopic Explorer
+an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
 \citep{2014Msngr.157...13B} with its
@@
 in wide-field mode could provide a coarse mapping of different
-ionization lines to infer a kinematic map.
+ionization lines to infer a kinematic map in the H$\alpha$ line,
+following the kind of work presented by \citet{Herenz16} done with the Potsdam
+Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
+\lya\ emitting galaxies.
 We note that archival Chandra X-ray archival
@@
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle \citep{Gronke2016}.
+variations depending on viewing angle (i.e. some sightlines can have
+an escape fraction close to $100\%$)\citep{Gronke2016} .
 
@@
 \lya\ emission line.  
-
 One model is based on a multiphase ISM with random clump motions and
 the other on gas bulk solid body rotation.
+
 It is the first time that an observed \lya\ profile can be fully
@@
 symmetric line is interesting. 
-It raises the question whether some high redshift LAEs have asymmetric
-lines because the blue half was truncated by the intergalactic medium.
-In this case the \lya\ radiation could emerge as a low surface
-brightness glow, which may be connected to \lya\ halos, while also
-influencing the way LAEs can be used as a probe of reionization
-\citep{2014PASA...31...40D}.
+\tol's line shape is different to others and reveals an unexpected
+kinematic structure.
+Our findings highlight the importance of including multiphase and/or
+rotation conditions as kinematic features to model the \lya\ line.
 
-These findings demonstrate the importance of including rotation and multiphase
-conditions as kinematic features to model the \lya\ line in high redshift
-galaxies.
 Additionally, if the hypothesis of a supermassive black

### 2017-03-19 paper/paper.tex
rename delete
bib in main text

--- 2017-03-13 paper/letter.tex
@@
 A careful clustering analysis of LAEs can also yield clues about their link
-to dark matter halos \cite{2016ApJ...828....5M}.
+to dark matter halos \citep{2016ApJ...828....5M}.
 
@@
 \end{center}
-\caption{Basic observational characteristics of TOL1214-277
+\caption{Basic observational characteristics of \tol\ 
   \citep{Thuan97}\label{obstable}} 
@@
   models with the lowest $\chi^2$ values (dotted line) compared against the
-  parameter's integrated distributions (continous line) used as a prior.
+  parameter's integrated distributions (continuous line) used as a prior.
   These are the only three parameters that show a significant statistical difference from
@@
 Previous exploratory work shows that it is impossible to fit the
-observed line outside thsese priors.
+observed line outside these priors.
 Finally, we estimate the parameter values from the 16th, 50th and 84th
@@
 clump) is high and most photons are produced at
-large radii making the radiative tranfer effects in the center less
+large radii making the radiative transfer effects in the center less
 important.  
-We cannot discard that another region of parameter spacem with similar
+We cannot discard that another region of parameter space with similar
 velocity structure but empty interclump medium, relatively dense
@@
 
-Using the constraints for the velocity dipersion $\sigma$ and the
+Using the constraints for the velocity dispersion $\sigma$ and the
 maximum rotational velocity $V_m$ in a spherical system localized in a
@@
 
-A new observational test is needed to clarify the kinematical nature of
+A new observational test is needed to clarify the kinematic nature of
 \tol. 
@@
 reproduce the so far unexplained observational features of \tol's
-\lya\ emission line.  
-One model is based on a multiphase ISM with random clump motions and
+\lya\ emission line.  One model is based on a multiphase ISM with random clump motions and
 the other on gas bulk solid body rotation.
@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
+  et~al.}{2014}]{2014Msngr.157...13B}
+{Bacon} R.  et~al., 2014, The Messenger, 157, 13
+
+\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham} \&
+  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
+{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,    {Chaffee} F.~H.,
+  1998, \apjl, 498, L93
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
+{Dijkstra} M.,  2014, \pasa, 31, e040
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz} \& {Wyithe}}{{Dijkstra}
+  et~al.}{2007}]{2007MNRAS.377.1175D}
+{Dijkstra} M.,  {Lidz} A.,    {Wyithe} J.~S.~B.,  2007, \mnras, 377, 1175
+
+\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
+  {Werner}, {Moustakas}, {Willmer} \& {Vanzi}}{{Engelbracht}
+  et~al.}{2008}]{2008ApJ...678..804E}
+{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
+  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,    {Vanzi} L.,  2008,
+  \apj, 678, 804
+
+\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
+{Erb} D.~K.  et~al., 2014, \apj, 795, 33
+
+\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky} \& {Meidt}}{{Eskew}
+  et~al.}{2012}]{2012AJ....143..139E}
+{Eskew} M.,  {Zaritsky} D.,    {Meidt} S.,  2012, \aj, 143, 139
+
+\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
+  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
+{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
+  125, 306
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666
+
+\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero} \&
+  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
+{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,    {Dijkstra} M.,  2014,
+  \apj, 795, 120
+
+\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
+  Weare}{2010}]{goodman2010ensemble}
+Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
+  computational science, 5, 65
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Bull} \& {Dijkstra}}{{Gronke}
+  et~al.}{2015}]{2015ApJ...812..123G}
+{Gronke} M.,  {Bull} P.,    {Dijkstra} M.,  2015, \apj, 812, 123
+
+\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
+  {Dijkstra}}{2016}]{Gronke2016}
+{Gronke} M.,  {Dijkstra} M.,  2016, \apj, 826, 14
+
+\bibitem[\protect\citeauthoryear{{Hansen} \& {Oh}}{{Hansen} \&
+  {Oh}}{2006}]{Hansen06}
+{Hansen} M.,  {Oh} S.~P.,  2006, \mnras, 367, 979
+
+\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
+{Harrington} J.~P.,  1973, \mnras, 162, 43
+
+\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
+{Hayes} M.,  2015, \pasa, 32, e027
+
+\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
+  et~al.}{2016}]{Herenz16}
+{Herenz} E.~C.  et~al., 2016, \aap, 587, A78
+
+\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
+  {Storey}}{1987}]{Hummer1987}
+{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mnras, 224, 801
+
+\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke} \&
+  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
+{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,    {Thuan}
+  T.~X.,  2004, \aap, 421, 539
+
+\bibitem[\protect\citeauthoryear{{Kennicutt}
+  Jr.}{{Kennicutt}}{1998}]{Kennicutt98}
+{Kennicutt} Jr. R.~C.,  1998, \araa, 36, 189
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013ApJ...766..124L}
+{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124
+
+\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
+  {Rybicki}}{1999}]{LoebRybicki}
+{Loeb} A.,  {Rybicki} G.~B.,  1999, \apj, 524, 527
+
+\bibitem[\protect\citeauthoryear{{Madden} et~al.,}{{Madden}
+  et~al.}{2014}]{2014PASP..126.1079M}
+{Madden} S.~C.  et~al., 2014, \pasp, 126, 1079
+
+\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
+  {Leitherer}, {Terlevich} \& {Terlevich}}{{Mas-Hesse}
+  et~al.}{2003}]{mashesse03}
+{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
+  {Terlevich} R.~J.,    {Terlevich} E.,  2003, \apj, 598, 858
+
+\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
+{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \apj, 828, 5
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
+{Neufeld} D.~A.,  1991, \apjl, 370, L85
+
+\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s} \&
+  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
+{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,    {Fricke} K.~J.,  2003,
+  \aap, 410, 481
+
+\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
+  et~al.}{2014}]{LARS}
+{{\"O}stlin} G.  et~al., 2014, \apj, 797, 11
+
+\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
+  {Peebles}}{1967}]{PartridgePeebles}
+{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \apj, 147, 868
+
+\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
+  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
+{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
+  {Primack} J.,  2012, \mnras, 423, 3018
+
+\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
+  {Martin}}{2007}]{pustilnikmartin07}
+{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \aap, 464, 859
+
+\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
+  et~al.}{2015}]{2015ApJ...805...14R}
+{Rivera-Thorsen} T.~E.  et~al., 2015, \apj, 805, 14
+
+\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
+{Roth} M.~M.  et~al., 2005, \pasp, 117, 620
+
+\bibitem[\protect\citeauthoryear{{Seth} et~al.,}{{Seth}
+  et~al.}{2014}]{2014Natur.513..398S}
+{Seth} A.~C.  et~al., 2014, \nat, 513, 398
+
+\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
+{Tasitsiomi} A.,  2006, \apj, 645, 792
+
+\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
+  {Izotov}}{1997}]{Thuan97}
+{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, 489, 623
+
+\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves} \&
+  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
+{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,    {Wolf} J.,  2011, \apj,
+  726, 108
+
+\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel} \&
+  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
+{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,    {Rudie} G.~C.,  2016,
+  \apj, 832, 171
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer} \&
+  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
+{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,    {Hayes} M.,  2015, \aap,
+  578, A7
+
+\end{thebibliography}
 

### 2017-06-12 paper/paper.tex
fewer referee isues

--- 2017-03-13 paper/letter.tex
@@
   Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
-  pristine conditions of the first galaxies in the Universe.    
-Before the observational detection of the first galaxies becomes
-reality, CDGs are the best systems to test our ideas on primordial
+  pristine conditions of the first galaxies in the Universe and
+  are the best systems to test models on primordial
 galaxy formation and evolution.    
@@
 We find that both models independently require high velocities
-(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
+(either a clump velocity dispersion of \sigmaclump\ with outflows of
 \inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
 consistent with a dynamical mass of at 
-least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
+least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated
+baryonic mass.     
 We argue that a possible explanation for this excess of
@@
 center of \tol. 
-This work demonstrates the importance of considering multiphase
+This work suggests the importance of considering multiphase
 kinematics and rotation among the possible conditions shaping the
@@
 \begin{keywords}
-Methods: data analysis - numerical 
+galaxies: dwarf --- galaxies: individual:\tol\ --- radiative transfer --- Methods: numerical 
 \end{keywords}
@@
 are seen as templates to understand the early galaxy evolution process. 
-Over fifty years ago \citep{PartridgePeebles} it was realized that
-young galaxies could be detected through a strong \lya\ line
-emission.
+Over fifty years ago it was realized that young galaxies could be
+detected through a strong \lya\ line emission \citep{PartridgePeebles}.
 
@@
 The presence of the \lya\ emission line provides confirmation of
-the distance of a galaxy while provides clues about the stellar
+the distance to a galaxy while provides clues about the stellar
 population and inter-stellar medium conditions regulating the
@@
 A careful clustering analysis of LAEs can also yield clues about their link
-to dark matter halos \cite{2016ApJ...828....5M}.
+to dark matter halos
+\citep{2004AJ....128.2073H,2007ApJ...671..278G,2007ApJ...668...15K,2008MNRAS.391.1589O,2010MNRAS.409..184P,2013MNRAS.431.1777G,2016ApJ...828....5M}.
 
@@
 indicators that might be more difficult to obtain for distant galaxies
-such as morphology, dust attenuation, neutral hydrogen contents and
-ionization state. (see \citep{Hayes15} and references therein for a review.)
+such as galaxy morphology, dust attenuation, neutral hydrogen contents and
+ionization state. See \citep{Hayes15}, and references therein for a review.
 
@@
 We compare each resulting spectra to the observational results from
-\tol\ after normalizing the observed and simulated spectra to have a a
+\tol\ after normalizing the observed and simulated spectra to have a 
 flux integral of one.

### 2017-06-12 paper/paper.tex
less issues

@@
 such as galaxy morphology, dust attenuation, neutral hydrogen contents and
-ionization state. See \citep{Hayes15}, and references therein for a review.
+ionization state. See \cite{Hayes15} and references therein for a review.
 
@@
 and thermal conditions in the interstellar medium. 
-There are very few analytically tools available to interpret the
+There are few analytical tools available to interpret the
 emerging \lya\ line
-\cite{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
-They are applicable only in very few cases of highly symmetrical
-conditions, which are hardly met in real astrophysical systems.
+\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
+They are applicable only in cases of highly symmetrical
+conditions of the gaseous hydrogen distribution in the galaxy model,
+which are hardly met in real astrophysical systems. 
 For these reasons the interpretation of \lya\ observations
@@
 with conventional shell models
-\citep{Mas-Hesse09,2015A&A...578A...7V,2015ApJ...812..123G}.
+\citep{mashesse03,2012ApJ...751...29Y,2015A&A...578A...7V,2015ApJ...812..123G}.
 
@@
 influencing the way LAEs can be used as a probe of reionization
-\citep{2014PASA...31...40D}.
+See the review by \cite{2014PASA...31...40D} and the references therein.
 
@@
 dynamical mass. 
-We close by discussing the physical scenarios that open up by our
+We close by discussing the physical scenarios opened up by our
 results and the additional observational information needed to clarify
@@
 4.9$\pm$0.1.
-The \lya\ flux values correspond to luminosities of
+The \lya\ flux values correspond to a luminosity of
 $L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
-translates  into a star formation rate of $2.0$ M$_{\odot}$ yr$^{-1}$
-using a standard conversion factor between luminosity and star
-formation rate of $9.1\times 10^{-43}$ $L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
-The absolute magnitude in the $V$ band translates into a luminosity of
-$8.9\times 10^{8}$ L$_{\odot}$.
-% using http://tomdwelly.com/tools_fluxtolum.php
-Comparing this ratio with the theoretical expectation from case B
-recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
-fraction of $20$\% for \lya\ radiation.
+translates  into a lower bound for the star formation rate of $2.0$
+M$_{\odot}$ yr$^{-1}$ after using a standard conversion factor between
+luminosity and star formation rate of $9.1\times 10^{-43}$
+$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$ \citep{Kennicutt98} without any
+correction by extinction.  
+Comparing the \lya/H$\beta$ ratio with the theoretical
+expectation from case B recombination of $23.3$ \citep{Hummer1987} one
+can estimate an escape fraction of $20$\% for \lya\ radiation.
+
 The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
@@
 corresponds to a star formation rate of $0.35\pm 0.05$ M$_{\odot}$
-yr$^{-1}$. Its metallicity is $\sim Z_{\odot}/24$ as derived from
+yr$^{-1}$. 
+Its metallicity is $\sim Z_{\odot}/24$ as derived from
 optical spectroscopy \citep{Izotov04}.
+
+%The absolute magnitude in the $V$ band translates into a luminosity of
+%$8.9\times 10^{8}$ L$_{\odot}$.  
+% using http://tomdwelly.com/tools_fluxtolum.php
+%
 
@@
 \citep{2008ApJ...678..804E}.
-Using a conversion between fluxes and
-stellar mass calibrated on the Large Magellanic Cloud $M_{\star} =
+Using the conversion between fluxes and
+stellar mass, $M_{\star} =
 10^{5.65} \times F_{3.6}^{2.85} \times F_{4.5}^{-1.85} \times
-(D/0.05)^2 M_{\odot}$, where fluxes are in Jy and $D$ is the luminosity
+(D/0.05)^2 M_{\odot}$,  calibrated on the Large Magellanic Cloud 
+and  where fluxes are in Jy and $D$ is the luminosity
 distance to the source in Mpc, we find $M_{\star} = 1.45\pm0.45\times 10^{8}
@@
 
-We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
-from the surface intensity profiles reported by \citep{2003A&A...410..481N}. 
+We computed the projected half-light radius to be $R_s=1.5\pm0.1$ kpc 
+from the surface brightness profiles reported by \cite{2003A&A...410..481N}. 
 Assuming spherical geometry, one can translate this value into a 3D
-half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.
+half-light radius of $r_s=3R_s/2=2.25$ kpc.
 
 There is an upper limit for the  
-integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
-upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
-\citep{pustilnikmartin07}.
+integrated flux of $<0.10$ Jy km s$^{-1}$ \citep{pustilnikmartin07},
+which translates into a upper limit for the HI mass of $M<2.65\times
+10^{8}$ M$_{\odot}$.
 
@@
 Assuming that the \lya\ emission is entirely powered by star formation 
-we use the 3D half-luminosity radius $r_s=2.25$ kpc as the typical size
+we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
 for the HI region,

### 2017-06-12 paper/paper.tex
fewer issues

@@
 
-There is an upper limit for the  
-integrated flux of $<0.10$ Jy km s$^{-1}$ \citep{pustilnikmartin07},
-which translates into a upper limit for the HI mass of $M<2.65\times
-10^{8}$ M$_{\odot}$.
+There is an upper limit for the  21 cm line integrated flux of $<0.10$
+Jy km s$^{-1}$ \citep{pustilnikmartin07}, which translates into a
+upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$.
 
@@
 \caption{Broad, single peaked and symmetric \lya\ emission of \tol.
-  Dots correspond to the observational data. The line shows the results
-of our best model from a full radiative transfer simulation both for
-the rotation and multiphase models.
-The observational points corresponds to the data as shown in
-\citep{mashesse03}.}   
+  Dots correspond to the observational data \citep{mashesse03}. 
+The thick red and thin blue curves represent our best fit
+to the data using the full radiative transfer simulation with a
+rotation and multiphase model, respectively. 
+These two different models are able to reproduce the main morphological
+features of \tol's \lya\ line emission.}
 \end{center}
@@
 lowest $\chi^2$ values.
-We note that the $\chi^2$ gap in those $25$ models is close to
-$\Delta\chi^2 = 3000$, the lowest $\chi^2$ being close to
-$\chi^2_{min}=1200$.
-To have a sense of scale, the total number of degrees of freedom is
-$104$.
+We note that the difference between the lowest and highest $\chi^2$ values in
+those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
+$\chi^2$ being close to $\chi^2_{min}=1200$. To have a sense of scale,
+the total number of degrees of freedom is $104$.
 
@@
 In this model, dust only changes the overall line
-normalization and only weakly its shape.  
-The results we report do not include any dust model.
-Here we use an analytical solution that captures the most important
+normalization and only weakly its shape, i.e. 
+dust cannot change the line symmetry or induce a change in the number
+of line peaks, moreover it does not change the line width by more than
+$1\%$ ($5$ \kms\ in the case of \tol), an effect too small to be
+observed at the resolution at which we have \tol's line profile and
+also negligeable compared to the influence of the other free parameters in the model.
+For these reasons we do not include any dust model.
+
+We use an analytical solution that captures the most important
 effects of rotation onto the \lya\ line as explained by
-\citet{GaravitoCamargo2014} and allows us a full parameter space
-exploration.
-
-The analytical solution for the rotation sphere is the base to
-perform a Markov Chain Monte Carlo (MCMC) calculation using the
+\citet{GaravitoCamargo2014} and allows us to fully explore the
+parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
 \texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 

### 2017-06-13 paper/paper.tex
less issues

@@
 temperature $T$, and the linear surface velocity $V_{\rm max}$.  
+The observed line profile also depends on $\theta$,  the angle between the plane
+perpendicular to the rotation axis and the observational
+line-of-sight.  
 In this model, dust only changes the overall line
@@
 temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.   
-This model is also able to constrain the angle between the plane
+We are also able to constrain the angle between the plane
 perpendicular to the rotation axis and the observational line-of-sight

### 2017-06-15 paper/paper.tex
one less issue

@@
   \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
-\caption{Results from the multiphase
-  model.
+\caption{Results from the multiphase  model.
+  We only show results for the three parameters with a significant
+  statistical difference between the models with the lowest $\chi^2$
+  values and its prior distribution. 
+  These three parameters are the clump radial velocity at infinity 
+  $v_{\infty, \rm{cl}}$; the probability that  the \lya\ photons were
+  emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
+  $\sigma_{\rm cl}$.
   The left column corresponds to the parameter's integrated distributions for
   models with the lowest $\chi^2$ values (dotted line) compared against the
-  parameter's integrated distributions (continuous line) used as a prior.
-  These are the only three parameters that show a significant statistical difference from
-  the prior distributions, for all the other eleven parameters we
-  cannot find any significant difference.
-  The right column shows a scatter plot of $\chi^2$ (rescaled by a $1000$)
-  and its corresponding physical parameters.
-  Only the  25 models with the lowest $\chi^2$ are included.
+  parameter's prior integrated distributions (continuous line).
+  The right column shows a scatter plot of $\chi^2$ (normalized by the
+  degrees of freedom) and its corresponding physical parameters.
+  This shows that the clump kinematic state is the key ingredient to
+  reproduce \tol's \lya\ line morphology.
   \label{multiphaseresults}

### 2017-06-15 paper/paper.tex
one less issue

@@
   degrees of freedom) and its corresponding physical parameters.
-  This shows that the clump kinematic state is the key ingredient to
+  The clump kinematic state is the key ingredient to
   reproduce \tol's \lya\ line morphology.
@@
 \caption{Results from the Markov Chain Monte Carlo computation for
-    the rotation model. The dotted vertical lines in the outer histograms 
-	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
+    the rotation model. 
+    The gray scale indicates the point density in parameter space. 
+    The dotted vertical lines in the histograms in the diagonal panels
+    represent the 16th, 50th and 84th percentiles. 
+    All parameters in the rotation model can be succesfuly constrained by \tol's
+    \lya\ line morphology to the values written in the top region of
+    the diagonal panels.
+    \label{emceeresults}} 
 \end{center}
@@
 $\chi^2$. 
-The right panel shows the actual $\chi^2$ values and its corresponding
-parameter value. 
+The right panel shows the actual $\chi^2$ values (normalized by the
+degrees of freedom) and its corresponding parameter value. 
 Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
@@
 
-Qualitatively, as \tol\ possesses a very wide spectrum which can be
-achieved by subsequent scatterings off (relatively) fast moving clumps
-while the multi-phase nature (i.e., the existence of low-density
-channels) ensures the high flux at line center as observed.
-In turn, a lower velocity dispersion would produce a thiner line than the
-observed.
-From the lower right panel in \ref{multiphaseresults} we find that it
+Qualitatively this can be understood as follows. The broad \lya\ line
+is the result of subsequent \lya\ photon scatterings due to
+(relatively) fast moving clumps while the multi-phase nature (i.e., the existence of low-density
+inter-clump regions where \lya\ photons can freely prograpagate)
+ensures the high flux at line center as observed.  
+In turn, a lower velocity dispersion would produce a thiner line than
+it is observed.
+From the lower right panel in Figure \ref{multiphaseresults} we find that it
 is unlikely that the clump velocity dispersion is lower than
@@
 We cannot discard that another region of parameter space with similar
-velocity structure but empty interclump medium, relatively dense
+velocity structure but an empty inter-clump medium, relatively dense
 clumps and at least a few clumps per sightline 

### 2017-06-18 paper/paper.tex
small issues solved

@@
 km s$^{-1}$ Mpc$^{-1}$.)
+
+Archival Chandra X-ray data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
+detection for \tol. 
+This lack of detection motivates our assumption that \lya\ emission is
+powered by star formation only.
 
@@
 future with a higher sampling of the parameter space once new 
-observations clarify the kinematic nature of \tol.
+observations  clarify the kinematic nature of \tol \footnote{In Section \S \ref{sec:conclusions} we describe  in more detail what kind of observations could be performed in the
+  near future to improve our understanding of \tol's kinematics.} .
 
@@
 is single peaked.
-Fixing the optical depth at a high value of $10^7$ ensures that the line width
-is close to its observed value.
-A lower rotational velocity would produce a double peaked line.
+The observed line width is better reproduced with a
+high optical depth value $\sim10^7$ as we found.
+For such optical depth values a lower rotational velocity would
+produce a double peaked line \citep{GaravitoCamargo2014}. 
 The fact that the velocity and optical depth priors were wide enough,
-allows us to think that the current values found by the MCMC are
+allows us to suggest that the current values found by the MCMC are
 robust given the observational constraints.
@@
 redshift and the wide symmetrical peak is virtually absent from other
-LAEs at low and high redshift \citep{LARS,Erb14,Trainor16}. Simple
+LAEs at low and high redshift \citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. Simple
 shell models fail to reproduce such a spectrum
@@
 \lya\ emitting galaxies.
-We note that archival Chandra X-ray archival
-data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
-detection for \tol.
-This lack of detection would also put an upper limit on the intensity
-of recent black hole activity due to accretion.
 
@@
 \section{Conclusions}
+\label{sec:conclusions}
 

### 2017-06-18 paper/paper.tex
reply to detailed comments

@@
 \newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
-
+\newcommand{\hs}{{\hspace{1mm}}}  
 \newcommand{\tol}{Tololo 1214-277}
@@
 
+We focus on showing how  two physically motivated models that can be suceessful
+in reproducing \tol's \lya\ line morphology. 
+It is not our aim to reject the existence of different models
+that reproduce the observed features in \tol. 
+Indeed more complex models with multiple kinematic components could
+be also sucessful.
+
 We review first the observational characteristics of
@@
   M$_V$ & -17.6\\ 
-$v$(km s$^{-1}$) & 7795\\
+$v$(km s$^{-1}$) & $7785\pm 50$\\
+$z$ & $0.0259\pm0.0002$ \\
 \lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
@@
 clumps of neutral hydrogen (and dust) embedded in a hot, ionized
-medium. 
+medium \citep{Gronke2016}. 
 The clumps also have a random and an outflowing velocity
@@
 \end{equation}
-
+%
 where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
@@
 model estimated flux.
+
+We do not have analytic expression for $\hat{f}$. 
+For the multi-phase model the results of the MonteCarlo are used to
+build histograms that play the role of $\hat{f}$. 
+For the rotation model $\hat{f}$ is computed 
+has to be computed by numerical integration of analytical
+approximations found in  \citet{GaravitoCamargo2014}.
 
@@
 
-We use an analytical solution that captures the most important
-effects of rotation onto the \lya\ line as explained by
-\citet{GaravitoCamargo2014} and allows us to fully explore the
+We use an analytical approximation that captures the most important
+effects of rotation onto the \lya\ line. 
+We defer the reader to \citet{GaravitoCamargo2014} for complete
+details on the explicit form of this approximation.
+To fully explore the
 parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
@@
 
-Lower rotational velocities are disfavored by the fact that the line
-is single peaked.
-The observed line width is better reproduced with a
-high optical depth value $\sim10^7$ as we found.
-For such optical depth values a lower rotational velocity would
-produce a double peaked line \citep{GaravitoCamargo2014}. 
+Lower rotational velocities than the favored value would produce a
+double peaked line as the different doppler shifts produced on
+different regions of the rotating sphere would not be large enough to
+smear the double peaks into a single peak
+\citep{GaravitoCamargo2014}. 
+For the same reason, higher rotation velocities could produce a single
+peak but the line would be broader than it is observed.
 The fact that the velocity and optical depth priors were wide enough,
-allows us to suggest that the current values found by the MCMC are
-robust given the observational constraints.
+allows us to suggest that the current values for the spherical model
+found by the MCMC are robust given the observational constraints.
 

### 2017-06-19 paper/paper.tex
new abstract

@@
 baryonic mass.     
-We argue that a possible explanation for this excess of
-dynamical mass is the presence of a supermassive black hole at the
-center of \tol. 
-This work suggests the importance of considering multiphase
+This work shows the importance of considering multiphase
 kinematics and rotation among the possible conditions shaping the

### 2017-06-20 paper/paper.tex
main issues

@@
 Here we report on one of such CDGs, \tol, which presents
-a broad symmetric \lya\ line emission that had evaded theoretical
-interpretation so far. 
+a broad, single peaked, highly symmetric \lya\ line emission that had
+evaded theoretical interpretation so far.  
 In this paper we explain these features by two different kinematic models: 
@@
 Additionally, if future kinematic maps of \tol\ confirm the 
-velocities found by our models, it would provide new
-evidence for dwarf galaxies as hosts of supermassive black
-holes.  
+velocities found by our models, it would provide additional support to
+radiative transfer modelling as a technique to constrain 
+the kinematical state of \lya\ emitting galaxies.
 \end{abstract}
+%\lya\ modelling as complementary way to estimate dynamical masses in
+%\lya\ emitting galaxies.
 
@@
 
+Observed \lya\ line profiles usually present a single peak shifted
+redwards from the line's center. 
+Sometimes a double peak is present but the asymmetry persists with 
+the peak on the red side being stronger. 
+This can be explained as a result of an outflowing shell of neutral Hydrogen.
+\citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.
+
 \tol\ is a compact star forming dwarf galaxy that presents a
 strong \lya\ emission \citep{Thuan97} with two puzzling 
-features: the line is symmetric, single peaked and wide around the
+features: the line is highly symmetric, single peaked and wide around the
 line's center.
-Usually the \lya\ line has an asymmetric single or double peak. 
-These two special features in \tol\ cannot be explained quantitatively
-with conventional shell models
-\citep{mashesse03,2012ApJ...751...29Y,2015A&A...578A...7V,2015ApJ...812..123G}.
+Attempts to explain these to features with conventional models have
+not been succesfyul \citep{mashesse03,2015A&A...578A...7V}.
 
-This kind of profile also raises the question whether some high redshift
-LAEs have asymmetric lines because the blue half was truncated by the
-intergalactic medium \citep{2007MNRAS.377.1175D}. 
+This kind of profile also raises the question whether some high
+redshift LAEs have asymmetric lines because the blue half was
+truncated by the intergalactic medium \citep{2007MNRAS.377.1175D}. 
 In this case the \lya\ radiation could emerge as a low surface
@@
 
-We focus on showing how  two physically motivated models that can be suceessful
+We focus on showing how two physically motivated models can be sucessful
 in reproducing \tol's \lya\ line morphology. 
-It is not our aim to reject the existence of different models
-that reproduce the observed features in \tol. 
-Indeed more complex models with multiple kinematic components could
-be also sucessful.
+We do not claim that we have discarded the existence of different
+undiscovered models that reproduce the observed features in \tol.
+More involved models with multiple kinematic components could
+in principple be also sucessful.
+We only present the existence of two simple good models.
 

### 2017-06-21 paper/paper.tex
answering the second main point

@@
 \usepackage{amssymb} 
-\usepackage {graphicx}
+\usepackage{graphicx}
 \usepackage[dvips]{epsfig}
@@
 \usepackage{color}
-\usepackage[normalem]{ulem}
-\usepackage{hyperref}
 \usepackage{caption}
+\usepackage[draft]{hyperref}
 %Non reposionated tables
-\usepackage{float}
-\restylefloat{table}
-%Multiple columns support for tables
-\usepackage{array}
-\usepackage{booktabs}
-\setlength{\heavyrulewidth}{1.5pt}
-\setlength{\abovetopsep}{4pt}
 
@@
 \newcommand{\probaclump}{$0.96\pm 0.01$}
-\def\simgt{\lower.5ex\hbox{\gtsima}}
-\def\simlt{\lower.5ex\hbox{\ltsima}}
 
@@
 evaded theoretical interpretation so far.  
-In this paper we explain these features by two different kinematic models: 
+In this paper we explain these features by two different physically
+motivated kinematic models: 
 an interstellar medium composed by outflowing clumps with 
@@
 \lya\ spectra of the first galaxies.
-Additionally, if future kinematic maps of \tol\ confirm the 
-velocities found by our models, it would provide additional support to
-radiative transfer modelling as a technique to constrain 
-the kinematical state of \lya\ emitting galaxies.
+Additionally, if future kinematic maps of tol confirm the velocities
+found by either of our models, it would completeley justify the need for
+detailed studies to understand the reasons behind a such a high
+dynamical mass for a compact dwarf galaxy.
 \end{abstract}
-%\lya\ modelling as complementary way to estimate dynamical masses in
-%\lya\ emitting galaxies.
 
@@
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong \lya\ emission \citep{Thuan97} with two puzzling 
+strong \lya\ emission with two puzzling 
 features: the line is highly symmetric, single peaked and wide around the
-line's center.
-Attempts to explain these to features with conventional models have
-not been succesfyul \citep{mashesse03,2015A&A...578A...7V}.
-
+line's center \citep{Thuan97}.
 This kind of profile also raises the question whether some high
@@
 
-Here we show how the \tol's \lya\ profile can be explained
-either by  or the recently developed class of complex multiphase models 
-\citep{Gronke2016} or by a simple rotation model
-\citep{GaravitoCamargo2014}. 
-The models we use correspond to simplified geometrical configurations
-to allow a deep exploration of parameter space and gain, for the first time,
-some physical insight into the \tol's kinematic properties.
+Attempts to explain the atypical \lya\ features in \tol\ with
+conventional models based on a expanding shell have not been succesful
+so far \citep{mashesse03,2015A&A...578A...7V}. 
+This justifies a new study using two new physically motivated
+situations: a multiphase outflowing interstellar medium and bulk rotation for a
+galaxy without outflows.
 
-We focus on showing how two physically motivated models can be sucessful
-in reproducing \tol's \lya\ line morphology. 
-We do not claim that we have discarded the existence of different
-undiscovered models that reproduce the observed features in \tol.
+The main motivation for the outflowing multiphase model (as presented
+in \cite{Gronke2016}) is that some dwarf galaxies are expected to
+present outflows.  
+Observationally, outflows have been detected in few local dwarf galaxies
+\citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
+Clumpy multiphase outflows are capable to explain \lya\ features around
+star-forming galaxies
+\citep{2010ApJ...717..289S,2012MNRAS.424.1672D}. 
+From this evidence we decide to try a multiphase model.
+
+The motivation for the rotation without outflows (as presented in \cite{GaravitoCamargo2014})is that
+dwarf galaxies show coherent rotation features
+\citep{2009A&A...493..871S} and it is expected that some of them have
+high neutral gas contents with long quiescent phases without high gas
+outflows triggered by supernova activity
+\citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.  
+For these reasons we also explore a model with a spherical gas
+distribution with solid body rotation and without any outflows.
+
+The models we use correspond to simplified geometrical configurations.
+This allows us to perform a deep exploration of parameter space and
+gain some physical insight into \tol's kinematic properties.
+In this paper we show, for the first time in the literature, that \tol's
+\lya\ profile can be explicitly modeled be either of these two
+models.
+
+We do not claim that our findings discard the existence of different
+undiscovered models that could reproduce the observed features in \tol.
 More involved models with multiple kinematic components could
 in principple be also sucessful.
-We only present the existence of two simple good models.
+We focus on the existence of two simple and succesful models that
+manage, for the first time, to account for \tol's \lya\ line main
+features.
 
@@
 \section{Observations}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{lc}\hline
+$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
+$\delta$(2000)$^{b}$ & -28d02m32s\\
+$l$, $b$ (deg) & 294, 34\\
+$m_V$ & 17.5\\
+  M$_V$ & -17.6\\ 
+$v$(km s$^{-1}$) & $7785\pm 50$\\
+$z$ & $0.0259\pm0.0002$ \\
+\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
+\lya\ Equivalent Width (\AA) & $70$\\
+$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
+\end{tabular}
+\end{center}
+\caption{Basic observational characteristics of \tol\ 
+  \citep{Thuan97}\label{obstable}} 
+\end{table}
+
 \tol's basic observational characteristics are summarized in Table \ref{obstable}.
-Its receding velocity is $7785\pm 50$km s$^{-1}$, which translates
-into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
-km s$^{-1}$ Mpc$^{-1}$.)
+Its receding velocity is $7785\pm 50$km s$^{-1}$ translates
+into a distance of $106.6$ Mpc, using a Hubble constant value of $H_{0}$=73
+km s$^{-1}$ Mpc$^{-1}$.
 
@@
 There is an upper limit for the  21 cm line integrated flux of $<0.10$
-Jy km s$^{-1}$ \citep{pustilnikmartin07}, which translates into a
-upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$.
-
-\begin{table}
-\begin{center}
-\begin{tabular}{lc}\hline
-$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
-$\delta$(2000)$^{b}$ & -28d02m32s\\
-$l$, $b$ (deg) & 294, 34\\
-$m_V$ & 17.5\\
-  M$_V$ & -17.6\\ 
-$v$(km s$^{-1}$) & $7785\pm 50$\\
-$z$ & $0.0259\pm0.0002$ \\
-\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
-\lya\ Equivalent Width (\AA) & $70$\\
-$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
-\end{tabular}
-\end{center}
-\caption{Basic observational characteristics of \tol\ 
-  \citep{Thuan97}\label{obstable}} 
-\end{table}
+Jy km s$^{-1}$  which translates into a upper limit for the HI mass of
+$M<2.65\times 10^{8}$ M$_{\odot}$ \citep{pustilnikmartin07}.
 
@@
 
-Additionally, if the hypothesis of a supermassive black
-hole in \tol\ proves to be consistent with future observational
-kinematic maps, it could correspond to a so far undetected
-supermassive black hole in a dwarf galaxy, providing a new way to test
-and probe theories on the co-evolution of galaxies and black holes in
-the first generation of galaxies.
+We acknowledge that a final confirmation of our kinematic findings has
+to be provided by the new observational tests we suggest.
+If that were the case, this would open up a new line of more detailed
+enquiries to understand how a compact dwarf galaxy can have such a
+large dynamical mass.
 

### 2017-06-21 paper/paper.tex
closer, in better shape

@@
 yr$^{-1}$. 
+The absolute magnitude in the $V$ band translates into a luminosity of
+$8.9\times 10^{8}$ L$_{\odot}$.  
 Its metallicity is $\sim Z_{\odot}/24$ as derived from
 optical spectroscopy \citep{Izotov04}. 
-
-%The absolute magnitude in the $V$ band translates into a luminosity of
-%$8.9\times 10^{8}$ L$_{\odot}$.  
 % using http://tomdwelly.com/tools_fluxtolum.php
@@
 explained by rather extreme kinematic characteristics.
-Now we discuss and frame those results in terms of the dynamical mass
-that could explain the velocities obtained in the model.
 
-Using the constraints for the velocity dispersion $\sigma$ and the
-maximum rotational velocity $V_m$ in a spherical system localized in a
-region of size $r$ we can estimate two different values for the
-dynamical mass within $r$:
+A first perspective to put in context \tol's kinematic is comes the
+observed scaling relations for elliptic galaxies.
+Assuming that \tol\ follows the fundamental plane relationship
+between its mean surface brightness $I_e=L_V/2\pi R_{e}^2$, the
+projected half-light radius $R_e$ and the velocity dispersion
+$\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
+the expected velocity dispersion should be on the order of $5\pm 1$
+\kms, which is a factor of $\sim\ 10$ - $60$ lower than the   
+results from the multiphase and rotation models, respectively.
+
+However, \tol's structural properties, seem to be closer to observed dwarf
+elliptical galaxies \citep{2003AJ....126.1794G}. 
+Galaxies such as IC 3344 and NGC 4482 have similar absolute $M_V$
+magnitudes  and size as \tol. 
+These galaxies have velocity dispersions in the range $30$-$45$ \kms. 
+The rotational velocities of those systems is lower than $1$\kms. 
+This gives support to the idea that the multiphase model might be
+closer to be the correct model describing \tol, as it provides at
+least kinematic consistency with other dwarf galaxy populations.
+
+Using the constraints for the velocity dispersion $\sigma$  in a
+spherical system localized in a region of size $r$ we can estimate a
+value or the dynamical mass within $r$:
 
@@
 \end{equation}
-%
-and
-%
-\begin{equation}
-M_{\rm dyn} = \frac{V_m ^{2}r}{G} = 1.16\times10^{9}
-\left(\frac{V_m}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot}, 
-\end{equation}
-%
-for the multiphase and rotation model, respectively.
+
 Assuming that the \lya\ emission is entirely powered by star formation 
 we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
-for the HI region,
+for the HI region, in the multiphase model the clump velocity dispersion
+$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
+$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$.
 
-In the multiphase model the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
-$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, while the
-rotational velocity of $V_{\rm max}=348^{+75}_{-48}$\kms corresponds
-$M_{\rm dyn} = 3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$.
-
-\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass
-is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$ 
-\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
-the baryonic mass, depending if one considers the multiphase or
-bulk rotation estimate. 
-We lean towards the lower dynamical mass estimate from the multiphase
-model as it seems easier to reconcile with the following two
-astrophysical mechanisms for its origin.
-
-A first possibility to explain a dynamical mass of $10^{9} M_{\odot}$
-in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
-least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}.
+Following the results of \cite{2011ApJ...726..108T}, who made a
+detailed analysis for dwarf ellipticals, we have that such dynamical
+mass can be explained if \tol\ is hosted by a dark matter halo of at
+least $10^{11}$ M$_{\odot}$ in mass. 
 This estimate is based on computing the integrated mass profile of a
@@
 concentration following the \emph{median} mass-concentration
-relationship found in the Bolshoi simulation
-\citep{2012MNRAS.423.3018P}. 
-This estimate leaves open the question as to why  \tol\ is not more
-similar to the Milky Way galaxy as it would be hosted by a dark matter
-halo of similar mass.
+relationship found in the Bolshoi simulation \citep{2012MNRAS.423.3018P}.
 
-A second possibility is that \tol\ hosts a supermassive black hole of
-$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
-than the supermassive black hole found in the compact dwarf galaxy
-M60-UCD1 \citep{2014Natur.513..398S}, which has a similar stellar mass
-as \tol. This would leave open the question about the formation
-process of such a system.
+This results would imply that \tol\ is part of the dwarf ellipticals
+class. However, there are two problems that remain. First, dwarf
+ellipticals are found either in clusters or groups of galaxies; while
+\tol\ does not belong either to a group or a cluster
+\citep{2001AJ....121..169F,}. The second problem is that, unlike dwarf
+ellipticals, \tol\ hosts bright an compact startburst; imaging and
+spectroscopy studies suggest that the startburst started less than 4
+Myr ago, while the low surface brightness regins are consistent with
+an age below one Gyr \citep{2001AJ....121..169F}.
 
-%Another perspective to appreciate the atypically high dynamical mass
-%estimates comes from the observed scaling relations for dwarf
-%galaxies.
-%Assuming that \tol\ followed the fundamental plane relationship
-%between its mean surface brightness $I_e$, the projected half-light
-%radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
-%I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
-%the expected velocity dispersion should be on the order of $5 \pm 1$ 
-%\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
-%results from the multiphase and rotation models, respectively. 
-%These are equivalent to factors of $\sim$ $100$ - $3600$ on the
-%dynamical mass.
-%Once again,  \tol\ seems to be significantly more massive than
-%expected.
-
-A new observational test is needed to clarify the kinematic nature of
+New observational tests are needed to clarify the kinematic nature of
 \tol. 
@@
 reproduce the so far unexplained observational features of \tol's
-\lya\ emission line.  One model is based on a multiphase ISM with random clump motions and
-the other on gas bulk solid body rotation.
+\lya\ emission line.  One model is based on a multiphase ISM with
+random clump motions and the other on gas bulk solid body rotation.
 
@@
 We acknowledge that a final confirmation of our kinematic findings has
-to be provided by the new observational tests we suggest.
+to be provided by new observational tests of the kind we suggest.
 If that were the case, this would open up a new line of more detailed

### 2017-06-21 paper/paper.tex
new abstract

@@
 assuming either of these kinematic conditions.
-We find that both models independently require high velocities
-(either a clump velocity dispersion of \sigmaclump\ with outflows of
-\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
-consistent with a dynamical mass of at 
-least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated
-baryonic mass.     
+We find that both models independently require high velocities, either
+a clump velocity dispersion of \sigmaclump\ with outflows of
+\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
+The velocity dispersion in the multiphase model is consistent with a dynamical
+mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
+which can be explained if \tol\ is hosted by a dark matter halo of at least
+$10^{11}$ M$_{\odot}$. 
+These conditions are similar to Dwarf Elliptical Galaxies.
 This work shows the importance of considering multiphase
-kinematics and rotation among the possible conditions shaping the
-\lya\ spectra of the first galaxies.
-Additionally, if future kinematic maps of tol confirm the velocities
-found by either of our models, it would completeley justify the need for
-detailed studies to understand the reasons behind a such a high
-dynamical mass for a compact dwarf galaxy.
+and rotation kinematics among the possible conditions shaping the
+\lya\ spectra.
+If future kinematic maps of \tol\ confirm the velocities found by the
+multiphase model, it will be the basis to study new processes that
+might be at play during priomordial galaxy evolution.
 \end{abstract}
@@
 In the previous sections we show how these characteristics can be
-explained by rather extreme kinematic characteristics.
+explained by two different kinematic models. Which model should we prefer?
 
-A first perspective to put in context \tol's kinematic is comes the
-observed scaling relations for elliptic galaxies.
-Assuming that \tol\ follows the fundamental plane relationship
-between its mean surface brightness $I_e=L_V/2\pi R_{e}^2$, the
-projected half-light radius $R_e$ and the velocity dispersion
-$\sigma$, described by $\log I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
-the expected velocity dispersion should be on the order of $5\pm 1$
-\kms, which is a factor of $\sim\ 10$ - $60$ lower than the   
-results from the multiphase and rotation models, respectively.
-
-However, \tol's structural properties, seem to be closer to observed dwarf
+\tol's structural properties seem to be similar to observed dwarf
 elliptical galaxies \citep{2003AJ....126.1794G}. 
@@
 The rotational velocities of those systems is lower than $1$\kms. 
-This gives support to the idea that the multiphase model might be
-closer to be the correct model describing \tol, as it provides at
-least kinematic consistency with other dwarf galaxy populations.
+This supports the idea that the multiphase model the correct model
+describing \tol, as it provides at least some consistency with
+kinematic properties of other dwarf elliptical galaxies.
 

### 2017-06-23 paper/paper.tex
consistent picture

@@
 which can be explained if \tol\ is hosted by a dark matter halo of at least
-$10^{11}$ M$_{\odot}$. 
-These conditions are similar to Dwarf Elliptical Galaxies.
+$10^{11}$ M$_{\odot}$; cconditions similar to those of Dwarf Elliptical Galaxies.
 This work shows the importance of considering multiphase
@@
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong \lya\ emission with two puzzling 
-features: the line is highly symmetric, single peaked and wide around the
+strong \lya\ emission with puzzling 
+features: the line is highly symmetric, single peaked and broad around the
 line's center \citep{Thuan97}.
@@
 \citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
-From this evidence we decide to try a multiphase model.
 
@@
 \citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.
-For these reasons we also explore a model with a spherical gas
-distribution with solid body rotation and without any outflows.
 
@@
 in principple be also sucessful.
-We focus on the existence of two simple and succesful models that
+We focus on presenting two simple and succesful models that
 manage, for the first time, to account for \tol's \lya\ line main
@@
 We use the results to interpret them in terms of the galaxy's
-dynamical mass. 
+dynamical mass and explain why the multiphase model should be prefered
+over the rotation model.
 We close by discussing the physical scenarios opened up by our
@@
 These two different models are able to reproduce the main morphological
-features of \tol's \lya\ line emission.}
+features of \tol's \lya\ line emission.\label{fig:results}}
 \end{center}
@@
 medium. 
+We do not explore inflowing clumps given the slight line asymmetry
+redwards to the line center (see the dots in Figure \ref{fig:results})
 
@@
 model estimated flux.
-
-We do not have analytic expression for $\hat{f}$. 
-For the multi-phase model the results of the MonteCarlo are used to
-build histograms that play the role of $\hat{f}$. 
-For the rotation model $\hat{f}$ is computed 
-has to be computed by numerical integration of analytical
-approximations found in  \citet{GaravitoCamargo2014}.
+We do not have analytic expression for $\hat{f}$, instead we use the
+results of the MonteCarlo to build histograms that play the role of
+$\hat{f}$.
 
@@
 the definition in Equation \ref{eq:chi2}. 
+We do not have an analytic expresion for $\hat{f}$, we compute it
+by numerical integration of the analytical approximations found in
+\citet{GaravitoCamargo2014}.
 
@@
 
-In spite of the simplicity of our models, this is the first time that
-the main \tol\ features can be reproduced: a wide, centered,
+The fit to the observations is not perfect. However, in spite of the
+simplicity of our models, this is the first time that the main
+\tol\ features can be reproduced: a broad, highly symmetric,
 single-peaked \lya\ line.
+
 This result does not demonstrate that the kinematic features we
@@
 
-Qualitatively this can be understood as follows. The broad \lya\ line
-is the result of subsequent \lya\ photon scatterings due to
-(relatively) fast moving clumps while the multi-phase nature (i.e., the existence of low-density
-inter-clump regions where \lya\ photons can freely prograpagate)
-ensures the high flux at line center as observed.  
+We tested with a set of 100 additional Monte-Carlo simulations
+with random values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$ and
+$P_{\rm cl}$ within the derived constraints (and random values for the
+other parameters over the whole parameter range) and found that $30$
+models result in $\chi^2$ values  
+continue to provide a similar $\chi^2$ values as the best $25$ models.
+
+Qualitatively this result can be understood as follows. 
+The broad \lya\ line is the result of subsequent \lya\ photon
+scatterings due to (relatively) fast moving clumps while the
+multi-phase nature (i.e., the existence of low-density inter-clump
+regions where \lya\ photons can freely prograpagate)  ensures the high
+flux at line center as observed.   
 In turn, a lower velocity dispersion would produce a thiner line than
@@
 
-Why is it that the other parameters do not seem to matter? Probably
-because $P_{cl}$ (the probability for a \lya\ to be emitted in a
-clump) is high and most photons are produced at
-large radii making the radiative transfer effects in the center less
-important.  
+Having constrained only 3 parameters, one migh wonder why the other 11
+parameters do not seem to matter. 
+However, this view is misleading. 
+Event if for clumply models the line profile is most sensitive to only
+a few parameters \citep{Gronke}, there are the rest of parameters
+which affect the line profile at a level that cannot be neglected,
+i.e. we cannot randomly pick 11 random, reasonable values for these
+parameters, and expect to fit the line profile while only varying the
+other 3.
+
 We cannot discard that another region of parameter space with similar
@@
 future with a higher sampling of the parameter space once new 
-observations  clarify the kinematic nature of \tol \footnote{In Section \S \ref{sec:conclusions} we describe  in more detail what kind of observations could be performed in the
-  near future to improve our understanding of \tol's kinematics.} .
+observations  clarify the kinematic nature of \tol \footnote{In
+  Section \S \ref{sec:conclusions} we describe  in more detail what
+  kind of observations could be performed in the near future to
+  improve our understanding of \tol's kinematics.} .
 
@@
 Its flux at the line's center is high compared to other LAEs at low
-redshift and the wide symmetrical peak is virtually absent from other
-LAEs at low and high redshift \citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. Simple
-shell models fail to reproduce such a spectrum
-\cite{2015A&A...578A...7V}.  
+redshift and the broad, highly symmetrical peak is virtually absent from other
+LAEs at low and high redshift
+\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. Simple shell models
+fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
 In the previous sections we show how these characteristics can be
@@
 magnitudes and size as \tol. 
-These galaxies have velocity dispersions in the range $30$-$45$ \kms. 
-The rotational velocities of those systems is lower than $1$\kms. 
+These galaxies have velocity dispersions in the range $30$-$45$ \kms
+and their rotational velocities are lower than $1$\kms. 
 This supports the idea that the multiphase model the correct model

### 2017-06-24 paper/paper.tex
new figure

@@
 \begin{center}
+\includegraphics[width=0.95\textwidth]{tree_result.pdf}
+\caption{A representative result from the tree classification algorithm. 
+Each box describes the condition over the parameter of interest, the
+level of sample impurity, the number of samples and the value of the
+number of samples in each of the classification classes.  We use two
+classes: low $\chi^2/d.o.f. < 35$ and $\chi^2/d.o.f>35$. 
+In this example the best way to increase the probability to find a
+model with  low $\chi^2/d.o.f.$ is having $v_{\infty,{\rm cl}}<157.0$ \kms,
+$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
+\label{fig:tree}}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
 \includegraphics[width=0.8\textwidth]{emcee_results.pdf}

### 2017-06-25 paper/paper.tex
new figure

--- 2017-06-23 paper/paper.tex
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
+\caption{Broad, single peaked and symmetric \lya\ emission of \tol.
+  Dots correspond to the observational data \citep{mashesse03}. 
+The thick red and thin blue curves represent our best fit
+to the data using the full radiative transfer simulation with a
+rotation and multiphase model, respectively. 
+These two different models are able to reproduce the main morphological
+features of \tol's \lya\ line emission.\label{fig:results}}
+\end{center}
+\end{figure*}
+
 \tol's basic observational characteristics are summarized in Table \ref{obstable}.
@@
 \begin{center}
-\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and symmetric \lya\ emission of \tol.
-  Dots correspond to the observational data \citep{mashesse03}. 
-The thick red and thin blue curves represent our best fit
-to the data using the full radiative transfer simulation with a
-rotation and multiphase model, respectively. 
-These two different models are able to reproduce the main morphological
-features of \tol's \lya\ line emission.\label{fig:results}}
+\includegraphics[width=0.95\textwidth]{tree_result.pdf}
+\caption{Classification tree example. 
+The aim is to find the parameters that separate two
+classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
+Each box describes the condition over the parameter of interest, the
+level of sample impurity, the number of samples and the value of the
+number of samples in each classes.  
+In this example we start with $28$ models in the first class and
+$1962$ models in the second class; the best way to increase the probability to find a
+a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
+$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
+All other parameters are also importatn but these three are the most relevant.
+\label{fig:tree}}
 \end{center}
@@
 those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
-$\chi^2$ being close to $\chi^2_{min}=1200$. To have a sense of scale,
-the total number of degrees of freedom is $104$.
+$\chi^2$ being close to $\chi^2_{min}=1200$. 
+The total number of degrees of freedom, $d.o.f$, is $104$.
 
-Then we perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
+We divide the results in two classes: low $\chi^2/d.o.f.<35$ and high
+$\chi^2/d.o.f.35>$.
+We apply a random forest classification algorithm to find the
+parameters more relevant in splitting the results into these two
+classes. The algorithm uses $500$ trees for the classification and a
+maximum of $3$ depth levels. 
+To check for tability we repeat the computation $10$ times by
+randomly subsampling the input data to use $80\%$ of the data as a
+training set.
+
+We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
 distribution in the best $25$ models against the parent distribution
@@
 If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
-this parameter does influence the $\chi^2$ fit, as the distribution for
+this parameter does influence the $\chi^2$ result, as the distribution for
 the best $\chi^2$ models is statistically different to the
@@
 
-The best values for the influential parameters correspond to
-the values that produce the minimum
-$\chi^2$.
+We finally compute the best values for the influential parameters as
+the values that produce the minimum $\chi^2$.  
 We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
@@
 corresponding minimum.
-%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
-%$P_{\rm cl}$
 
@@
 
-From the K-S tests we find that only three parameters can be
-constrained by the observations: the clump outflow velocity
-$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), the clump velocity
-dispersion $\sigma_{\rm cl}$ (p-value $10^{-4}$) and the probability
-that the \lya\ emission comes from the clumps $P_{\rm cl}$ (p-value
-$10^{-4}$).
-This does not mean the other parameters do not influence the resulting
-spectra at all; it means that they cannot be constrained from \tol's
-observations.
+With $14$ free parameters our first concern is discovering which are
+the most relevant in reproducing \tol's line shape.
+The results of the random forest classifier yield that the clump outflow velocity
+$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
+that the \lya\ emission comes from the clumps $P_{\rm cl}$ are the
+most influential parameters in finding a model with low
+$\chi^2/d.o.f.$.
 
-The results are summarized in Figure \ref{multiphaseresults}.
-Left panels show the difference between the integrated distributions
+Figure \ref{fig:tree} shows the results for one of such tree. 
+Starting with $28$ and $1962$ models in the low and high
+$\chi^2/d.o.f.$ classes respectively, we find that the best separation
+yields $13$ and $44$ models after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
+$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
+The split is not perfect. This means that the three parameters in the
+model are the most influential, but that some combinations of the
+other 11 parameters are also relevant to find a good fit.
+
+From the K-S tests we confirm that the same three parameters are the
+only ones that can be constrained by observations;
+$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
+$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
+Once again, this test does not mean the other parameters do not
+influence the resulting spectra at all; it means that they cannot be
+constrained from \tol's observations.
+
+The best models are summarized in Figure \ref{multiphaseresults}.
+Left column show the difference between the integrated distributions
 of the full sample (2500 input models) and the models with the lowest
-$\chi^2$. 
-The right panel shows the actual $\chi^2$ values (normalized by the
-degrees of freedom) and its corresponding parameter value. 
+$\chi^2/d.o.f.$. 
+The right column shows the actual $\chi^2/d.o.f.$ 
+and its corresponding parameter value. 
 Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
@@
 
-We tested with a set of 100 additional Monte-Carlo simulations
-with random values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$ and
-$P_{\rm cl}$ within the derived constraints (and random values for the
-other parameters over the whole parameter range) and found that $30$
-models result in $\chi^2$ values  
-continue to provide a similar $\chi^2$ values as the best $25$ models.
+As a test, we ran a small set of 100 additional Monte-Carlo simulations
+with random values for all parameters, except for $\sigma_{\rm cl}$,
+$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which where within the derived
+constraints.
+Consistent with the results from the random forest algorithm,
+illustrated by the classification tree of Figure \ref{fig:tree}, we
+found that $30$ models showed $\chi^2/d.o.f.<35$ values
 
@@
 Event if for clumply models the line profile is most sensitive to only
-a few parameters \citep{Gronke}, there are the rest of parameters
+a few parameters \citep{Gronke2016}, there are the rest of parameters
 which affect the line profile at a level that cannot be neglected,

### 2017-06-25 paper/paper.tex
revised rotation model

@@
 
-Figure \ref{fig:tree} shows the results for one of such tree. 
+Figure \ref{fig:tree} shows as an illustriation the results for one of such tree. 
 Starting with $28$ and $1962$ models in the low and high
@@
 $50$\kms. 
+This is also supported by the classification tree example in Figure
+\ref{fig:tree}.
 
@@
 
+The results for this model are easier to interpret due to the fewer
+number of free parameters and its explicit influence on the
+semi-analytic solution.
 The results are summarized in  Figure \ref{emceeresults}. 
@@
 to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
+This model cannot reproduce the slight asymmetry present in \tol's
+\lya\ line; most probably this would require an small amount of
+outflows, a feature that is not present in the model provided by
+\cite{GaravitoCamargo2014}.
 
+The prefered value for the rotational velocity can be explained as
+follows. 
 Lower rotational velocities than the favored value would produce a

### 2017-06-25 paper/paper.tex
discussion

@@
 $\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
-All other parameters are also importatn but these three are the most relevant.
+This classification example shows that all other parameters are also
+important but these three are the most relevant. 
 \label{fig:tree}}
@@
 parameters, and expect to fit the line profile while only varying the
-other 3.
+other 3, as the results for the classification tree example show in
+Figure \ref{fig:tree}.
 
@@
 LAEs at low and high redshift
-\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. Simple shell models
+\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
+Simple shell models
 fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
@@
 \tol's structural properties seem to be similar to observed dwarf
-elliptical galaxies \citep{2003AJ....126.1794G}. 
-Galaxies such as IC 3344 and NGC 4482 have similar absolute $M_V$
-magnitudes and size as \tol. 
-These galaxies have velocity dispersions in the range $30$-$45$ \kms
-and their rotational velocities are lower than $1$\kms. 
-This supports the idea that the multiphase model the correct model
-describing \tol, as it provides at least some consistency with
+elliptical galaxies. 
+The sample of 7 dwarf ellipticals (dE) observed by
+\cite{2003AJ....126.1794G} show similar properties as \tol. 
+For instance, the dE IC 3344 and IC 794 have similar absolute $M_V$
+magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) than
+\tol. These galaxies have velocity dispersions of $31.1$ \kms and
+$44.6$ \kms, respectively,  and their rotational velocities are lower
+than $1$\kms.  
+This coincidence supports the idea that the multiphase model is
+the correct one as it provides at least some consistency with
 kinematic properties of other dwarf elliptical galaxies.

### 2017-06-25 paper/paper.tex
conclusions

@@
 $44.6$ \kms, respectively,  and their rotational velocities are lower
-than $1$\kms.  
-This coincidence supports the idea that the multiphase model is
-the correct one as it provides at least some consistency with
-kinematic properties of other dwarf elliptical galaxies.
+than $1$ \kms.  
+This coincidence leads us to prefer the multiphase model as it
+provides at least some consistency with kinematic properties of other
+dwarf elliptical galaxies.
 
-Using the constraints for the velocity dispersion $\sigma$  in a
-spherical system localized in a region of size $r$ we can estimate a
-value or the dynamical mass within $r$:
+Following the results of \cite{2011ApJ...726..108T}, who made a
+detailed analysis for dwarf ellipticals, we can estimate a
+value or the dynamical mass within $r$ using the constraints for the
+velocity dispersion $\sigma$  in a spherical system localized in a
+region of size $r$
 
@@
 \end{equation}
-
+%
 Assuming that the \lya\ emission is entirely powered by star formation 
@@
 
-Following the results of \cite{2011ApJ...726..108T}, who made a
-detailed analysis for dwarf ellipticals, we have that such dynamical
+\cite{2011ApJ...726..108T} showed that  that such dynamical
 mass can be explained if \tol\ is hosted by a dark matter halo of at
@@
 concentration following the \emph{median} mass-concentration
-relationship found in the Bolshoi simulation \citep{2012MNRAS.423.3018P}.
+relationship found in the Bolshoi simulation
+\citep{2012MNRAS.423.3018P}.
 
-This results would imply that \tol\ is part of the dwarf ellipticals
-class. However, there are two problems that remain. First, dwarf
-ellipticals are found either in clusters or groups of galaxies; while
+These results would imply that \tol\ is part of the dwarf ellipticals
+class. However, there are two puzzles that are opened up by this. 
+First, dwarf ellipticals are found either in clusters or groups of galaxies; while
 \tol\ does not belong either to a group or a cluster
-\citep{2001AJ....121..169F,}. The second problem is that, unlike dwarf
+\citep{2001AJ....121..169F,}. 
+The second problem is that, unlike dwarf
 ellipticals, \tol\ hosts bright an compact startburst; imaging and
@@
 
-New observational tests are needed to clarify the kinematic nature of
-\tol. 
-We suggest that integral field unit measurements 
-resolving its spatial extent are up to the task. 
+We suggest that new observational tests are needed to clarify the
+kinematic nature of \tol\ and be sure about \tol's kinematic
+structure. 
+Integral field unit measurements resolving its spatial extent are up to the task. 
 \tol\ spans a region of $4$ arcseconds,
 an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
-\citep{2014Msngr.157...13B} with its
-nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
-in wide-field mode could provide a coarse mapping of different
-ionization lines to infer a kinematic map in the H$\alpha$ line,
+\citep{2014Msngr.157...13B} with its nominal $0.2$ arcseconds spatial
+sampling over a $1.0$ arcminute field in wide-field mode could provide
+a coarse mapping of different ionization lines to infer a kinematic map in the H$\alpha$ line,
 following the kind of work presented by \citet{Herenz16} done with the Potsdam
-Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
+Multi-Aperture Spectrometer (PMAS) \citep{PMAS} on nearby
 \lya\ emitting galaxies.
 
-Another observational test includes the measurement of the
-\lya\ ionizing continuum escape fraction.
-In the rotational model this fraction should be zero, while
-the multiphase model predicts that averaging over all sightlines
+Another observational test to confirm the picture provided by the
+multiphase model includes the measurement of the \lya\ ionizing
+continuum escape fraction. 
+This model model predicts that averaging over all sightlines
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
 variations depending on viewing angle (i.e. some sightlines can have
-an escape fraction close to $100\%$)\citep{Gronke2016} .
+an escape fraction close to $100\%$) \citep{Gronke2016} .
 
@@
 reproduce the so far unexplained observational features of \tol's
-\lya\ emission line.  One model is based on a multiphase ISM with
-random clump motions and the other on gas bulk solid body rotation.
+\lya\ emission line.  
+One model is based on a multiphase ISM with random clump motions and
+the other on gas bulk solid body rotation.
 
@@
 reproduced by either of these two kinematic conditions.
-Furthermore, the kinematics of both models suggest a dynamical mass
-at least ten times larger than the baryonic mass infered from observations.
+The structural conditions in \tol\ are similar to those in dwarf
+ellipticals. 
+However, it environment and star forming activity are radically
+different.
 We suggest that additional integral field unit observations are the
@@
 If that were the case, this would open up a new line of more detailed
-enquiries to understand how a compact dwarf galaxy can have such a
-large dynamical mass.
+enquiries to understand how a compact dwarf galaxy can have the
+structural characteristics similar to a dwarf elliptical while being
+at the same time isolated and sustaining large starburst.
 

### 2017-06-25 paper/paper.tex
conclusions

@@
 multiphase model, it will be the basis to study new processes that
-might be at play during priomordial galaxy evolution.
+might be at play during primordial galaxy evolution.
 \end{abstract}
@@
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle (i.e. some sightlines can have
-an escape fraction close to $100\%$) \citep{Gronke2016} .
+variations depending on viewing angle, i.e. some sightlines can have
+an escape fraction close to $100\%$, \citep{Gronke2016}.
 
@@
 at the same time isolated and sustaining large starburst.
+If an evolutionary link is stablished between a phase where a \tol and dE this would b
 
@@
 used to prepare Figure 1.
+J. E. F-R. ackwnoledges the support of J. L. Guerra in the last
+writing stages of this paper.
 

### 2017-06-25 paper/paper.tex
discussion

@@
 which can be explained if \tol\ is hosted by a dark matter halo of at least
-$10^{11}$ M$_{\odot}$; cconditions similar to those of Dwarf Elliptical Galaxies.
+$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical Galaxies.
 This work shows the importance of considering multiphase
@@
 If future kinematic maps of \tol\ confirm the velocities found by the
-multiphase model, it will be the basis to study new processes that
+multiphase model, it will be the basis to study evolutionary processes that
 might be at play during primordial galaxy evolution.
@@
 $v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
-that the \lya\ emission comes from the clumps $P_{\rm cl}$ are the
+that the \lya\ emission comes from the clumps $P_{\rm cl}$, are the
 most influential parameters in finding a model with low
@@
 
-Figure \ref{fig:tree} shows as an illustriation the results for one of such tree. 
-Starting with $28$ and $1962$ models in the low and high
-$\chi^2/d.o.f.$ classes respectively, we find that the best separation
-yields $13$ and $44$ models after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
+Figure \ref{fig:tree} shows as an illustration the results for a
+classification tree.  
+The tree starts with $28$ and $1962$ models in the low and high
+$\chi^2/d.o.f.$ classes, respectively. 
+We find that the best classification
+yields $13$ and $44$ models in the low and high $\chi^2\d.o.f.$
+classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
 $\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
-The split is not perfect. This means that the three parameters in the
+The split in two classes is not perfect. 
+This means that the 3 parameters in the
 model are the most influential, but that some combinations of the
@@
 
-From the K-S tests we confirm that the same three parameters are the
+From the K-S tests we confirm that the same 3 parameters are the
 only ones that can be constrained by observations;
@@
 
-As a test, we ran a small set of 100 additional Monte-Carlo simulations
-with random values for all parameters, except for $\sigma_{\rm cl}$,
-$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which where within the derived
-constraints.
-Consistent with the results from the random forest algorithm,
-illustrated by the classification tree of Figure \ref{fig:tree}, we
-found that $30$ models showed $\chi^2/d.o.f.<35$ values
-
 Qualitatively this result can be understood as follows. 
@@
 
+As a test, we run a small set of 100 additional radiative transfer simulations
+with random values for all parameters, except for $\sigma_{\rm cl}$,
+$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are within the derived
+constraints.
+Consistent with the results from the random forest algorithm,
+illustrated by the classification tree of Figure \ref{fig:tree}, we
+find that $30$ models show $\chi^2/d.o.f.<35$.
+
 Having constrained only 3 parameters, one migh wonder why the other 11
@@
 However, this view is misleading. 
-Event if for clumply models the line profile is most sensitive to only
+Even if for clumply models the line profile is most sensitive to only
 a few parameters \citep{Gronke2016}, there are the rest of parameters
@@
 In the previous sections we show how these characteristics can be
-explained by two different kinematic models. Which model should we prefer?
+explained by two different kinematic models: multiphase ISM and solid
+body rotation.
 
-\tol's structural properties seem to be similar to observed dwarf
+Which model has more
+chances to be correct?  
+We discard the rotation model by considering that the rotational
+velocity of $\sim350$ \kms\ is too high for such a low
+mass system. 
+\tol's infered rotational velocity is larger than the
+Milky Way's ($\sim200$\kms) while its baryonic mass is one order
+of magnitude smaller. 
+Furthermore, \tol's structural properties seem to be similar to known dwarf
 elliptical galaxies. 
@@
 \cite{2003AJ....126.1794G} show similar properties as \tol. 
-For instance, the dE IC 3344 and IC 794 have similar absolute $M_V$
-magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) than
-\tol. These galaxies have velocity dispersions of $31.1$ \kms and
+For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
+magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
+\tol. 
+These dE galaxies have velocity dispersions of $31.1$ \kms and
 $44.6$ \kms, respectively,  and their rotational velocities are lower
 than $1$ \kms.  
-This coincidence leads us to prefer the multiphase model as it
-provides at least some consistency with kinematic properties of other
-dwarf elliptical galaxies.
+This leads us to prefer the multiphase model as it provides at least
+some consistency with kinematic properties of dE galaxies.
 
 Following the results of \cite{2011ApJ...726..108T}, who made a
-detailed analysis for dwarf ellipticals, we can estimate a
-value or the dynamical mass within $r$ using the constraints for the
-velocity dispersion $\sigma$  in a spherical system localized in a
+detailed analysis for all kind of elliptical galaxies including, we
+estimate a value for the dynamical mass using the constraints for
+thevelocity dispersion $\sigma$  in a spherical system localized in a
 region of size $r$
@@
 $\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
-$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$.
+$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
+times the estimated baryonic mass in \tol.
 
 \cite{2011ApJ...726..108T} showed that  that such dynamical
-mass can be explained if \tol\ is hosted by a dark matter halo of at
+mass can be explained if a dwarf galaxy is hosted by a dark matter halo of at
 least $10^{11}$ M$_{\odot}$ in mass. 
@@
 
-These results would imply that \tol\ is part of the dwarf ellipticals
-class. However, there are two puzzles that are opened up by this. 
-First, dwarf ellipticals are found either in clusters or groups of galaxies; while
-\tol\ does not belong either to a group or a cluster
+These results would imply that \tol\ is part of the dE
+class. 
+However, there are two puzzles that are opened up by this hypothesis. 
+First, dwarf ellipticals are found either in clusters or groups of
+galaxies; while \tol\ does not belong either to a group or a cluster
 \citep{2001AJ....121..169F,}. 
-The second problem is that, unlike dwarf
-ellipticals, \tol\ hosts bright an compact startburst; imaging and
-spectroscopy studies suggest that the startburst started less than 4
-Myr ago, while the low surface brightness regins are consistent with
-an age below one Gyr \citep{2001AJ....121..169F}.
+The second problem is that, unlike dE, \tol\ hosts a bright and compact
+startburst; imaging and spectroscopy studies suggest that the
+startburst started less than 4 Myr ago, while the low surface
+brightness regins are consistent with an age below one Gyr
+\citep{2001AJ....121..169F}.
 
@@
 structure. 
-Integral field unit measurements resolving its spatial extent are up to the task. 
+Integral field unit measurements resolving its spatial extent are up
+to the task.  
 \tol\ spans a region of $4$ arcseconds,
@@
 sampling over a $1.0$ arcminute field in wide-field mode could provide
-a coarse mapping of different ionization lines to infer a kinematic map in the H$\alpha$ line,
-following the kind of work presented by \citet{Herenz16} done with the Potsdam
-Multi-Aperture Spectrometer (PMAS) \citep{PMAS} on nearby
-\lya\ emitting galaxies.
+a coarse mapping of different ionization lines to infer a kinematic
+map in the H$\alpha$ line, following the kind of work presented by
+\citet{Herenz16} done with the Potsdam Multi-Aperture Spectrometer
+(PMAS) \citep{PMAS} on nearby \lya\ emitting galaxies.
 
@@
 reproduced by either of these two kinematic conditions.
-The structural conditions in \tol\ are similar to those in dwarf
-ellipticals. 
-However, it environment and star forming activity are radically
-different.
+We give preference to the multiphase model as it produces kinematic
+conditions that are similar to those in dwarf ellipticals, while the
+rotational model produces rotational velocities to high for a dwarf
+galaxy.
+
+However, \tol's environment and star forming activity are radically
+different from dwarf ellipticals.
 We suggest that additional integral field unit observations are the
@@
 We acknowledge that a final confirmation of our kinematic findings has
-to be provided by new observational tests of the kind we suggest.
-If that were the case, this would open up a new line of more detailed
+to be provided by new observational tests with integral field unit
+spectroscopy. 
+If our results are confirmed, this would open up a new line of more detailed
 enquiries to understand how a compact dwarf galaxy can have the
@@
 at the same time isolated and sustaining large starburst.
-If an evolutionary link is stablished between a phase where a \tol and dE this would b
+Such and investigation could provide an evolutionary between star forming
+and quiescent stages of dwarf galaxy evolution.
 
@@
 \bibliographystyle{mn2e}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+
+\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
+  et~al.}{2014}]{2014Msngr.157...13B}
+{Bacon} R.  et~al., 2014, The Messenger, 157, 13
+
+\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur} \&
+  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
+{Begum} A.,  {Chengalur} J.~N.,    {Karachentsev} I.~D.,  2005, \aap, 433, L1
+
+\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham} \&
+  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
+{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,    {Chaffee} F.~H.,
+  1998, \apjl, 498, L93
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
+{Dijkstra} M.,  2014, \pasa, 31, e040
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
+  {Kramer}}{2012}]{2012MNRAS.424.1672D}
+{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz} \& {Wyithe}}{{Dijkstra}
+  et~al.}{2007}]{2007MNRAS.377.1175D}
+{Dijkstra} M.,  {Lidz} A.,    {Wyithe} J.~S.~B.,  2007, \mnras, 377, 1175
+
+\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
+  {Werner}, {Moustakas}, {Willmer} \& {Vanzi}}{{Engelbracht}
+  et~al.}{2008}]{2008ApJ...678..804E}
+{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
+  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,    {Vanzi} L.,  2008,
+  \apj, 678, 804
+
+\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
+{Erb} D.~K.  et~al., 2014, \apj, 795, 33
+
+\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky} \& {Meidt}}{{Eskew}
+  et~al.}{2012}]{2012AJ....143..139E}
+{Eskew} M.,  {Zaritsky} D.,    {Meidt} S.,  2012, \aj, 143, 139
+
+\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
+  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
+{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
+  125, 306
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666
+
+\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva} \&
+  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
+{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,    {Thuan}
+  T.~X.,  2001, \aj, 121, 169
+
+\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero} \&
+  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
+{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,    {Dijkstra} M.,  2014,
+  \apj, 795, 120
+
+\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}} \&
+  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
+{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,    {D{\'{\i}}az} {\'A}.~I.,
+   2013, \mnras, 434, 2491
+
+\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
+  et~al.}{2007}]{2007ApJ...671..278G}
+{Gawiser} E.  et~al., 2007, \apj, 671, 278
+
+\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta} \& {van der
+  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
+{Geha} M.,  {Guhathakurta} P.,    {van der Marel} R.~P.,  2003, \aj, 126, 1794
+
+\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
+  Weare}{2010}]{goodman2010ensemble}
+Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
+  computational science, 5, 65
+
+\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu} \& {Wyithe}}{{Greig}
+  et~al.}{2013}]{2013MNRAS.431.1777G}
+{Greig} B.,  {Komatsu} E.,    {Wyithe} J.~S.~B.,  2013, \mnras, 431, 1777
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Bull} \& {Dijkstra}}{{Gronke}
+  et~al.}{2015}]{2015ApJ...812..123G}
+{Gronke} M.,  {Bull} P.,    {Dijkstra} M.,  2015, \apj, 812, 123
+
+\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
+  {Dijkstra}}{2016}]{Gronke2016}
+{Gronke} M.,  {Dijkstra} M.,  2016, \apj, 826, 14
+
+\bibitem[\protect\citeauthoryear{{Hansen} \& {Oh}}{{Hansen} \&
+  {Oh}}{2006}]{Hansen06}
+{Hansen} M.,  {Oh} S.~P.,  2006, \mnras, 367, 979
+
+\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
+{Harrington} J.~P.,  1973, \mnras, 162, 43
+
+\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
+  et~al.}{2004}]{2004AJ....128.2073H}
+{Hayashino} T.  et~al., 2004, \aj, 128, 2073
+
+\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
+{Hayes} M.,  2015, \pasa, 32, e027
+
+\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
+  et~al.}{2016}]{Herenz16}
+{Herenz} E.~C.  et~al., 2016, \aap, 587, A78
+
+\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
+  {Storey}}{1987}]{Hummer1987}
+{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mnras, 224, 801
+
+\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke} \&
+  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
+{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,    {Thuan}
+  T.~X.,  2004, \aap, 421, 539
+
+\bibitem[\protect\citeauthoryear{{Kennicutt}
+  Jr.}{{Kennicutt}}{1998}]{Kennicutt98}
+{Kennicutt} Jr. R.~C.,  1998, \araa, 36, 189
+
+\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
+  {Malhotra} \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
+{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,
+  {Wang} J.,  2007, \apj, 668, 15
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013ApJ...766..124L}
+{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124
+
+\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
+  {Rybicki}}{1999}]{LoebRybicki}
+{Loeb} A.,  {Rybicki} G.~B.,  1999, \apj, 524, 527
+
+\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
+{Martin} C.~L.,  1998, \apj, 506, 222
+
+\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
+  {Leitherer}, {Terlevich} \& {Terlevich}}{{Mas-Hesse}
+  et~al.}{2003}]{mashesse03}
+{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
+  {Terlevich} R.~J.,    {Terlevich} E.,  2003, \apj, 598, 858
+
+\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
+{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \apj, 828, 5
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
+{Neufeld} D.~A.,  1991, \apjl, 370, L85
+
+\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s} \&
+  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
+{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,    {Fricke} K.~J.,  2003,
+  \aap, 410, 481
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
+  et~al.}{2012}]{Orsi12}
+{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh} \& {Infante}}{{Orsi}
+  et~al.}{2008}]{2008MNRAS.391.1589O}
+{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,    {Infante} L.,  2008, \mnras, 391,
+  1589
+
+\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
+  et~al.}{2014}]{LARS}
+{{\"O}stlin} G.  et~al., 2014, \apj, 797, 11
+
+\bibitem[\protect\citeauthoryear{{Ott}, {Walter} \& {Brinks}}{{Ott}
+  et~al.}{2005}]{2005MNRAS.358.1453O}
+{Ott} J.,  {Walter} F.,    {Brinks} E.,  2005, \mnras, 358, 1453
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
+  {Gonz{\'a}lez}, {Guaita} \& {Infante}}{{Padilla}
+  et~al.}{2010}]{2010MNRAS.409..184P}
+{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
+  {Guaita} L.,    {Infante} L.,  2010, \mnras, 409, 184
+
+\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
+  {Peebles}}{1967}]{PartridgePeebles}
+{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \apj, 147, 868
+
+\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
+  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
+{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
+  {Primack} J.,  2012, \mnras, 423, 3018
+
+\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
+  {Martin}}{2007}]{pustilnikmartin07}
+{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \aap, 464, 859
+
+\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
+  et~al.}{2015}]{2015ApJ...805...14R}
+{Rivera-Thorsen} T.~E.  et~al., 2015, \apj, 805, 14
+
+\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
+{Roth} M.~M.  et~al., 2005, \pasp, 117, 620
+
+\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie} \& {Rakic}}{{Steidel}
+  et~al.}{2010}]{2010ApJ...717..289S}
+{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
+  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,    {Rakic} O.,  2010, \apj, 717, 289
+
+\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada} \& {van der
+  Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
+{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,    {van der Hulst} J.~M.,
+  2009, \aap, 493, 871
+
+\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
+{Tasitsiomi} A.,  2006, \apj, 645, 792
+
+\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov} \& {Gnedin}}{{Tassis}
+  et~al.}{2008}]{2008ApJ...672..888T}
+{Tassis} K.,  {Kravtsov} A.~V.,    {Gnedin} N.~Y.,  2008, \apj, 672, 888
+
+\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
+  {Izotov}}{1997}]{Thuan97}
+{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, 489, 623
+
+\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves} \&
+  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
+{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,    {Wolf} J.,  2011, \apj,
+  726, 108
+
+\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel} \&
+  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
+{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,    {Rudie} G.~C.,  2016,
+  \apj, 832, 171
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer} \&
+  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
+{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,    {Hayes} M.,  2015, \aap,
+  578, A7
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
+  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
+{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397
+
+\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
+  {Morimoto} \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
+{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
+  {Umemura} M.,  2012, \apj, 751, 29
+
+\end{thebibliography}
 

### 2017-06-25 paper/old_paper.tex
first version

--- 2017-03-13 paper/letter.tex
@@
 consistent with a dynamical mass of at 
-least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
+least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated
+baryonic mass.     
 We argue that a possible explanation for this excess of

### 2017-06-25 paper/paper.tex
new structure

@@
 \begin{abstract}
-  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
-  pristine conditions of the first galaxies in the Universe and
-  are the best systems to test models on primordial
+  The conditions in star-forming Compact Dwarf Galaxies (CDGs) 
+  place them as the best systems to test models on primordial
 galaxy formation and evolution.    
@@
 assuming either of these kinematic conditions.
-We find that both models independently require high velocities, either
-a clump velocity dispersion of \sigmaclump\ with outflows of
-\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$. 
-The velocity dispersion in the multiphase model is consistent with a dynamical
-mass of $2\times 10^{9}$ M$_{\odot}$, ten times its baryonic mass,
-which can be explained if \tol\ is hosted by a dark matter halo of at least
-$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical Galaxies.
-This work shows the importance of considering multiphase
+The multiphase model requires a clump velocity dispersion of
+\sigmaclump\ with outflows of \inftyclump\ while the bulk rotation
+velocity is constrained to be $348^{+75}_{-48}$ \kms.
+This shows the importance of considering multiphase
 and rotation kinematics among the possible conditions shaping the
 \lya\ spectra.
+However, we consider that the multiphase model has more chances to
+agree with \tol's reality. 
+The clump velocity dispersion implies a dynamical mass of $2\times
+10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
+explained if \tol\ is hosted by a dark matter halo of at least
+$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical
+Galaxies. 
 If future kinematic maps of \tol\ confirm the velocities found by the
-multiphase model, it will be the basis to study evolutionary processes that
-might be at play during primordial galaxy evolution.
+multiphase model, it could provide a new perspective to study
+evolutionary processes linking star-forming with quiescent phases in
+primordial galaxy evolution. 
 \end{abstract}
@@
 at the same time isolated and sustaining large starburst.
-Such and investigation could provide an evolutionary between star forming
+Such and investigation could provide an evolutionary link between star-forming
 and quiescent stages of dwarf galaxy evolution.

### 2017-06-25 paper/paper.tex
updated referee reply

@@
 The multiphase model requires a clump velocity dispersion of
-\sigmaclump\ with outflows of \inftyclump\ while the bulk rotation
-velocity is constrained to be $348^{+75}_{-48}$ \kms.
+at least \sigmaclump\ with outflows of \inftyclump\ at most, while the
+bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
 This shows the importance of considering multiphase
@@
 agree with \tol's reality. 
-The clump velocity dispersion implies a dynamical mass of $2\times
+The clump velocity dispersion implies a dynamical mass of at least $2\times
 10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
@@
 half-light radius of $r_s=3R_s/2=2.25$ kpc.
+Imaging observations by \cite{2001AJ....121..169F} show that \tol\ is
+an isolated field galaxy not belonging to a group or cluster.
 
@@
 We apply a random forest classification algorithm to find the
-parameters more relevant in splitting the results into these two
-classes. The algorithm uses $500$ trees for the classification and a
+more relevant parameters in splitting the results into these two
+classes. 
+The algorithm uses $500$ trees for the classification and a
 maximum of $3$ depth levels. 
@@
 
-The fit to the observations is not perfect. However, in spite of the
+The fit to the observations is not perfect. 
+However, in spite of the
 simplicity of our models, this is the first time that the main
@@
 This means that the 3 parameters in the
-model are the most influential, but that some combinations of the
-other 11 parameters are also relevant to find a good fit.
+model are the most influential in finding models with low
+$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
+are also relevant to find a good fit.
 
@@
 
-As a test, we run a small set of 100 additional radiative transfer simulations
-with random values for all parameters, except for $\sigma_{\rm cl}$,
-$v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are within the derived
+As a test, we also run a small set of 100 additional radiative
+transfer simulations with random values for all parameters, except for
+$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are within the derived
 constraints.
@@
 
-We cannot discard that another region of parameter space with similar
-velocity structure but an empty inter-clump medium, relatively dense
-clumps and at least a few clumps per sightline 
-could also work \citep{Hansen06}.
-This possibility does not change our conclusions about the
-kinematic parameters, but it might be interesting to explore in the
+We cannot discard that another region of parameter space
+could also work.
+It might be interesting to explore in the
 future with a higher sampling of the parameter space once new 
@@
   improve our understanding of \tol's kinematics.} .
+
+Considering this sparse sampling of parameter space and the results
+from the random forest classifier, it is reasonable to consider that
+the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
+  cl}$ are actually lower/upper/lower bounds, respectively.
 
@@
 times the estimated baryonic mass in \tol.
+Considering that the results for $\sigma_{\rm{cl}}$ are most probably
+a lower bound, the results for the dynamical mass should also be
+considered as a lower bound.
 
@@
 
-We acknowledge that a final confirmation of our kinematic findings has
+A definitive confirmation of our kinematic findings has
 to be provided by new observational tests with integral field unit

### 2017-06-26 paper/paper.tex
small changes

@@
 explained if \tol\ is hosted by a dark matter halo of at least
-$10^{11}$ M$_{\odot}$; conditions similar to those of Dwarf Elliptical
-Galaxies. 
+$10^{11}$ M$_{\odot}$; conditions similar to those of dwarf elliptical
+galaxies. 
 If future kinematic maps of \tol\ confirm the velocities found by the
@@
 
-The motivation for the rotation without outflows (as presented in \cite{GaravitoCamargo2014})is that
-dwarf galaxies show coherent rotation features
-\citep{2009A&A...493..871S} and it is expected that some of them have
-high neutral gas contents with long quiescent phases without high gas
-outflows triggered by supernova activity
+The motivation for the rotation without outflows (as presented in
+\cite{GaravitoCamargo2014}) is that dwarf galaxies show coherent
+rotation features  \citep{2009A&A...493..871S} and it is expected that
+some of them have high neutral gas contents with long quiescent phases
+without high gas outflows triggered by supernova activity
 \citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.
@@
   M$_V$ & -17.6\\ 
-$v$(km s$^{-1}$) & $7785\pm 50$\\
-$z$ & $0.0259\pm0.0002$ \\
-\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
-\lya\ Equivalent Width (\AA) & $70$\\
-$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
+$z$ & $0.0259\pm0.0002$ \\\hline
 \end{tabular}
@@
 The observed flux for the \lya\ line is $\sim
-8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
-and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
+8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
+The \lya\ Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
 $1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
-\citep{Izotov04} which gives a \lya/H$\beta$ flux ratio of
-4.9$\pm$0.1.
+which gives a \lya/H$\beta$ flux ratio of
+4.9$\pm$0.1 \citep{Izotov04}.
 The \lya\ flux values correspond to a luminosity of
@@
 luminosity and star formation rate of $9.1\times 10^{-43}$
-$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$ \citep{Kennicutt98} without any
-correction by extinction.  
+$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$ 
+without any
+correction by extinction
+\citep{Kennicutt98}.
 Comparing the \lya/H$\beta$ ratio with the theoretical
@@
 The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
-L$_{\odot}$ as measured by GALEX, without any correction by extinction
+L$_{\odot}$ as measured by GALEX. Without any correction by extinction
 and following the empirical relation by \cite{Kennicutt98}, this
@@
 
-There is an upper limit for the  21 cm line integrated flux of $<0.10$
+There is an upper limit for the  $21$ cm line integrated flux of $<0.10$
 Jy km s$^{-1}$  which translates into a upper limit for the HI mass of
@@
 number of samples in each classes.  
-In this example we start with $28$ models in the first class and
-$1962$ models in the second class; the best way to increase the probability to find a
-a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
+In this example we randomly sample $80\%$ of the full set of models to
+start with $28$ models in the first class and
+$1962$ models in the second class; the best way to increase the
+probability to find a  a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
 $\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
-This classification example shows that all other parameters are also
-important but these three are the most relevant. 
+The final classification is not perfect, showing that all other
+parameters are also important but these three are the most relevant.  
 \label{fig:tree}}
@@
   improve our understanding of \tol's kinematics.} . 
-
-Considering this sparse sampling of parameter space and the results
-from the random forest classifier, it is reasonable to consider that
+Considering the sparse sampling of parameter space and the results
+from the random forest classifier, it is safer to consider that
 the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
@@
 than $1$ \kms.  
-This leads us to prefer the multiphase model as it provides at least
-some consistency with kinematic properties of dE galaxies.
+This leads us to prefer the multiphase model as it provides 
+a broad consistency with kinematic properties of dE galaxies.
 
@@
 spherical dark matter halo with a Navarro-Frenk-White profile with its
-concentration following the \emph{median} mass-concentration
+concentration following the median mass-concentration
 relationship found in the Bolshoi simulation
@@
 However, there are two puzzles that are opened up by this hypothesis. 
-First, dwarf ellipticals are found either in clusters or groups of
+First, dE galaxies are found either in clusters or groups of
 galaxies; while \tol\ does not belong either to a group or a cluster
-\citep{2001AJ....121..169F,}. 
-The second problem is that, unlike dE, \tol\ hosts a bright and compact
+\citep{2001AJ....121..169F}. 
+The second problem is that, unlike a dE, \tol\ hosts a bright and compact
 startburst; imaging and spectroscopy studies suggest that the
@@
 the other on gas bulk solid body rotation. 
-
 It is the first time that an observed \lya\ profile can be fully
 reproduced by either of these two kinematic conditions.
-We give preference to the multiphase model as it produces kinematic
-conditions that are similar to those in dwarf ellipticals, while the
+Our findings highlight the importance of including multiphase and/or
+rotation conditions as kinematic features to model the \lya\ line.
+
+We prefer the multiphase model becasue it has kinematic
+conditions similar to those in dwarf ellipticals, while the
 rotational model produces rotational velocities to high for a dwarf
@@
 However, \tol's environment and star forming activity are radically
-different from dwarf ellipticals.
+different from those of dwarf ellipticals.
 We suggest that additional integral field unit observations are the
@@
 kinematic structure.
-Our findings highlight the importance of including multiphase and/or
-rotation conditions as kinematic features to model the \lya\ line.
-
 A definitive confirmation of our kinematic findings has
@@
 spectroscopy. 
-If our results are confirmed, this would open up a new line of more detailed
-enquiries to understand how a compact dwarf galaxy can have the
-structural characteristics similar to a dwarf elliptical while being
-at the same time isolated and sustaining large starburst.
-Such and investigation could provide an evolutionary link between star-forming
-and quiescent stages of dwarf galaxy evolution.
+If our results are confirmed, this would give robustness to our models
+as tools to study the evolutionary link between star-forming and
+quiescent stages of dwarf galaxy evolution.
 
 \section*{Acknowledgments}
+We thank the referee for detailed comments and suggestions that
+improved this paper. 
 We thank J. M. Mas-Hesse for providing us with \tol's observational

### 2017-06-26 paper/paper.tex
details

@@
 spectroscopy. 
-If our results are confirmed, this would give robustness to our models
-as tools to study the evolutionary link between star-forming and
+If our results are confirmed, this would support the multiphase model
+as a tool to study the evolutionary link between star-forming and
 quiescent stages of dwarf galaxy evolution.

### 2017-06-26 paper/paper.tex
details

@@
 All in all, the mere existence of a strong LAE galaxy with a broad,
-symmetric line is interesting. 
-\tol's line shape is different to others and reveals an unexpected
-kinematic structure.
-A definitive confirmation of our kinematic findings has
-to be provided by new observational tests with integral field unit
-spectroscopy. 
-If our results are confirmed, this would support the multiphase model
+highly symmetric line is interesting. 
+\tol's line shape is different to others and seems to reveal an
+unexpected kinematic structure.
+A definitive confirmation of our findings has to be provided by new
+observational tests with integral field unit spectroscopy. 
+A confirmation of our results would support the multiphase model
 as a tool to study the evolutionary link between star-forming and

### 2017-06-29 paper/paper.tex
abstract

@@
 \begin{abstract}
-  The conditions in star-forming Compact Dwarf Galaxies (CDGs) 
-  place them as the best systems to test models on primordial
-galaxy formation and evolution.    
+
+Star-forming Compact Dwarf Galaxies (CDGs) 
+resemble the expected pristine conditions of the first galaxies in the
+Universe and are the best systems to test models on primordial galaxy
+formation and evolution. 
 Here we report on one of such CDGs, \tol, which presents
-a broad, single peaked, highly symmetric \lya\ line emission that had
+a broad, single peaked, highly symmetric \lya\ emission line that had
 evaded theoretical interpretation so far.  
@@
 The multiphase model requires a clump velocity dispersion of
-at least \sigmaclump\ with outflows of \inftyclump\ at most, while the
+at least \sigmaclump\ with outflows of \inftyclump\, while the
 bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
-This shows the importance of considering multiphase
-and rotation kinematics among the possible conditions shaping the
-\lya\ spectra.
-However, we consider that the multiphase model has more chances to
-agree with \tol's reality. 
+We argue that the multiphase model has more chances to be correct.
 The clump velocity dispersion implies a dynamical mass of at least $2\times
@@
 explained if \tol\ is hosted by a dark matter halo of at least
-$10^{11}$ M$_{\odot}$; conditions similar to those of dwarf elliptical
-galaxies. 
-If future kinematic maps of \tol\ confirm the velocities found by the
-multiphase model, it could provide a new perspective to study
-evolutionary processes linking star-forming with quiescent phases in
-primordial galaxy evolution. 
+$10^{11}$ M$_{\odot}$.
+If future kinematic maps of \tol\ confirm the velocities suggested by the
+multiphase model, it would provide additional support to expect this
+condition to be present  in primordial \lya\ emitting galaxies.  
 \end{abstract}

### 2017-06-29 paper/paper.tex
introduction

@@
 the peak on the red side being stronger. 
-This can be explained as a result of an outflowing shell of neutral Hydrogen.
+This can be explained as the results of multiple \lya\ photon
+scatterings through an outflowing shell of neutral Hydrogen
 \citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.
@@
 strong \lya\ emission with puzzling 
-features: the line is highly symmetric, single peaked and broad around the
-line's center \citep{Thuan97}.
+features: the line is highly symmetric, single peaked and broad 
+\citep{Thuan97}.
 This kind of profile also raises the question whether some high
@@
 brightness glow, which may be connected to \lya\ halos, while also
-influencing the way LAEs can be used as a probe of reionization
-See the review by \cite{2014PASA...31...40D} and the references therein.
+influencing the way LAEs can be used as a probe of reionization,
+see the review by \cite{2014PASA...31...40D} and the references
+therein.
 
@@
 \citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
-Clumpy multiphase outflows are capable to explain \lya\ features around
+Besides, clumpy multiphase outflows are capable to explain \lya\ features around
 star-forming galaxies
@@
 undiscovered models that could reproduce the observed features in \tol.
-More involved models with multiple kinematic components could
-in principple be also sucessful.
+More involved models with multiple kinematic components can
+in principle also be sucessful.
 We focus on presenting two simple and succesful models that
@@
 
-We review first the observational characteristics of
+In the next section We review the observational characteristics of
 \tol, then we summarize the main features in the multiphase and
@@
 We use the results to interpret them in terms of the galaxy's
-dynamical mass and explain why the multiphase model should be prefered
+dynamical mass and argue why the multiphase model should be prefered
 over the rotation model.
-We close by discussing the physical scenarios opened up by our
-results and the additional observational information needed to clarify
-the kinematic nature of \tol.
+We close by discussing the additional observational information needed
+to clarify the kinematic nature of \tol.
 

### 2017-06-29 paper/paper.tex
multiphase table

@@
 \usepackage{graphicx}
+\usepackage{grffile}
 \usepackage[dvips]{epsfig}
@@
 \newcommand{\tol}{Tololo 1214-277}
-\newcommand{\lya}{Ly$\alpha$}
+\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
+\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
+\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
+\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
+\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
+\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
+\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
+%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\vek}[1]{\bm{#1}}
+%\newcommand{\lya}{Ly$\alpha$}
 \newcommand{\hb}{H$\beta$}
@@
 
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and symmetric \lya\ emission of \tol.
-  Dots correspond to the observational data \citep{mashesse03}. 
-The thick red and thin blue curves represent our best fit
-to the data using the full radiative transfer simulation with a
-rotation and multiphase model, respectively. 
-These two different models are able to reproduce the main morphological
-features of \tol's \lya\ line emission.\label{fig:results}}
-\end{center}
-\end{figure*}
+\begin{table*}
+  \centering
+\begin{tabular}{l|lrrr}
+\hline
+  Parameter  & Description & Fiducial value & Allowed range & Units \\ \hline\hline
+$v_{\infty,\,{\rm cl}}$ & Radial cloud velocity & $100.0$ & [$0.0$, $800.0$] & $\,{\rm km\,s}^{-1}$ \\
+$\sigma_{\rm {\rm cl}}$ & Random cloud motion &$40.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
+$P_{\rm {\rm cl}}$ & Probability to be emitted in cloud & $0.35$ & [$0.0$, $1.0$] &  \\
+$r_{\rm {\rm cl}}$ & Cloud radius & $100.0$ & [$30.0$, $200.0$] & $\,{\rm pc}$ \\
+$H_{\rm em}$ & Emission scale radius & $1000.0$ & [$500.0$, $3.0\times 10^{3}$] & $\,{\rm pc}$ \\
+$f_{\rm {\rm cl}}$ & Cloud covering factor & $3.5$ & [$0.8$, $8.0$] &  \\
+$T_{\rm {\rm ICM}}$${}^{\dagger}$ & Temperature of ICM & $10^{6}$ & [$3.0\times 10^{5}$, $5.0\times 10^{7}$] & $\,{\rm K}$ \\
+$n_{\rm HI,\,{\rm ICM}}$${}^{\dagger}$ & \HI number density in ICM & $5.0\times 10^{-8}$ & [$10^{-12}$, $10^{-6}$] & $\,{\rm cm}^{-3}$ \\
+$\sigma_{\rm i}$ & Width of emission profile & $50.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
+$T_{\rm {\rm cl}}$${}^{\dagger}$ & Temperature in clouds & $10^{4}$ & [$5.0\times 10^{3}$, $5.0\times 10^{4}$] & $\,{\rm K}$ \\
+$\beta_{\rm cl}$ & Steepness of the radial velocity profile & $1.5$ & [$1.1$, $2.5$] &  \\
+$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps & $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] & $\,\cm^{2}$ \\
+$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance & $0.01$ & [$10^{-4}$, $0.1$] &  \\
+$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
+\hline
+\end{tabular}
+  \caption{Overview of the parameters in the multiphase model and its fiducial
+    values. Variables marked with ${}^{\dagger}$ were drawn in
+    log-space. Details of the implementation are in \citet{Gronke2016}.}
+  \label{tab:models}
+\end{table*}
 
@@
 4.9$\pm$0.1 \citep{Izotov04}.
+Comparing the \lya/H$\beta$ ratio with the theoretical
+expectation from case B recombination of $23.3$ \citep{Hummer1987} one
+can estimate an escape fraction of $20$\% for \lya\ radiation.
+
 The \lya\ flux values correspond to a luminosity of
@@
 \citep{Kennicutt98}.
-Comparing the \lya/H$\beta$ ratio with the theoretical
-expectation from case B recombination of $23.3$ \citep{Hummer1987} one
-can estimate an escape fraction of $20$\% for \lya\ radiation.
 
@@
 process \citep{2012AJ....143..139E}.  
+There is an upper limit for the  $21$ cm line integrated flux of $<0.10$
+Jy km s$^{-1}$  which translates into a upper limit for the neutral
+Hydrogen mass of $M<2.65\times 10^{8}$ M$_{\odot}$
+\citep{pustilnikmartin07}.
 
@@
 
-There is an upper limit for the  $21$ cm line integrated flux of $<0.10$
-Jy km s$^{-1}$  which translates into a upper limit for the HI mass of
-$M<2.65\times 10^{8}$ M$_{\odot}$ \citep{pustilnikmartin07}.
+\section{Theoretical Models and Parameter Estimation}
+
+\subsection{Multiphase ISM}
+
+The idealized multiphase model consists of spherical, cold, dense
+clumps of neutral hydrogen (and dust) embedded in a hot, ionized
+medium \citep{Gronke2016}. 
+The clumps also have a random and an outflowing velocity
+component which totals the number of parameters describing the model
+to be $14$, which also include information about the spatial
+distribution and thermal state of the clumps and the intraclump
+medium. 
+We do not explore inflowing clumps given the slight line asymmetry
+redwards to the line center (see the dots in Figure \ref{fig:results})
+
+In order to map out this large parameter space, we randomly drew
+$2500$ sets of parameters within a observationally realistic range,
+based on the considerations of \citet{Laursen2013ApJ...766..124L}, 
+yielding a large variety of single-, double- and triple-peaked
+spectra. 
+The full analysis of the the spectral features as well as
+more details on the radiative transfer are presented by
+\citet{Gronke2016}.
+
+We compare each resulting spectra to the observational results from
+\tol\ after normalizing the observed and simulated spectra to have a 
+flux integral of one.
+We build a $\chi^2$ on the normalized flux measurements for each one
+of the $2500$ models
+
+\begin{equation}
+\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
+\label{eq:chi2}
+\end{equation}
+%
+where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
+$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
+model estimated flux.
+We do not have analytic expression for $\hat{f}$, instead we use the
+results of the MonteCarlo to build histograms that play the role of
+$\hat{f}$.
+
+We select for further analysis the best $1\%$ models according to the
+lowest $\chi^2$ values.
+We note that the difference between the lowest and highest $\chi^2$ values in
+those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
+$\chi^2$ being close to $\chi^2_{min}=1200$. 
+The total number of degrees of freedom, $d.o.f$, is $104$.
+
+We divide the results in two classes: low $\chi^2/d.o.f.<35$ and high
+$\chi^2/d.o.f.35>$.
+We apply a random forest classification algorithm to find the
+more relevant parameters in splitting the results into these two
+classes. 
+The algorithm uses $500$ trees for the classification and a
+maximum of $3$ depth levels. 
+To check for tability we repeat the computation $10$ times by
+randomly subsampling the input data to use $80\%$ of the data as a
+training set.
+
+We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
+distribution in the best $25$ models against the parent distribution
+of $2500$ models. 
+If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
+this parameter does influence the $\chi^2$ result, as the distribution for
+the best $\chi^2$ models is statistically different to the
+distribution from the global sample of $2500$ models.
+
+We finally compute the best values for the influential parameters as
+the values that produce the minimum $\chi^2$.  
+We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
+$\chi^2$ as a function of the influential parameters around its
+corresponding minimum.
+
+\subsection{Bulk Rotation}
+
+The rotation model corresponds to the work presented in
+\citep{GaravitoCamargo2014} based on the Monte Carlo code
+\texttt{CLARA} \citep{CLARA}. 
+In that model the \lya\ photons are propagated 
+within a spherical and homogeneous cloud of HI gas undergoing solid
+body rotation.
+The sphere is fully characterized by three parameters: the HI line's
+center optical  depth $\tau$ measured from the center to its surface, the HI
+temperature $T$, and the linear surface velocity $V_{\rm max}$.  
+The observed line profile also depends on $\theta$,  the angle between the plane
+perpendicular to the rotation axis and the observational
+line-of-sight.  
+In this model, dust only changes the overall line
+normalization and only weakly its shape, i.e. 
+dust cannot change the line symmetry or induce a change in the number
+of line peaks, moreover it does not change the line width by more than
+$1\%$ ($5$ \kms\ in the case of \tol), an effect too small to be
+observed at the resolution at which we have \tol's line profile and
+also negligeable compared to the influence of the other free parameters in the model.
+For these reasons we do not include any dust model.
+
+We use an analytical approximation that captures the most important
+effects of rotation onto the \lya\ line. 
+We defer the reader to \citet{GaravitoCamargo2014} for complete
+details on the explicit form of this approximation.
+To fully explore the
+parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
+\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
+is an open source optimized implementation of the affine-invariant 
+MCMC sampler \citep{goodman2010ensemble}. 
+The algorithm creates a number of walkers that,
+during a sufficient number of steps, generate parameters' combinations
+for a specific model.
+For each timestep, the code calculates the likelihood of the
+combination with respect to the observational data.
+The walkers explore the parameter space sampling the Gaussian likelihood
+function built as $\propto \exp(-\chi^2/2)$, where the $\chi^2$ follows
+the definition in Equation \ref{eq:chi2}. 
+We do not have an analytic expresion for $\hat{f}$, we compute it
+by numerical integration of the analytical approximations found in
+\citet{GaravitoCamargo2014}.
+
+We explore flat priors on four parameters: $200<V_{\rm
+  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
+$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
+steps with $24$ walkers for a total of $12000$ points in the chain.
+Previous exploratory work shows that it is impossible to fit the
+observed line outside these priors.
+Finally, we estimate the parameter values from the 16th, 50th and 84th
+percentiles.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
+\caption{Broad, single peaked and highly symmetric \lya\ emission of \tol.
+  Dots correspond to the observational data \citep{mashesse03}. 
+The thick red and thin blue curves represent our best fit
+to the data using the full radiative transfer simulation with a
+rotation and multiphase model, respectively. 
+These two different models are able to reproduce the main morphological
+features of \tol's \lya\ line emission.\label{fig:results}}
+\end{center}
+\end{figure*}
 
@@
 
-\section{Theoretical Models and Parameter Estimation}
-
-\subsection{Multiphase ISM}
-
-The idealized multiphase model consists of spherical, cold, dense
-clumps of neutral hydrogen (and dust) embedded in a hot, ionized
-medium \citep{Gronke2016}. 
-The clumps also have a random and an outflowing velocity
-component which totals the number of parameters describing the model
-to be $14$, which also include information about the spatial
-distribution and thermal state of the clumps and the intraclump
-medium. 
-We do not explore inflowing clumps given the slight line asymmetry
-redwards to the line center (see the dots in Figure \ref{fig:results})
-
-In order to map out this large parameter space, we randomly drew
-$2500$ sets of parameters within a observationally realistic range,
-based on the considerations of \citet{Laursen2013ApJ...766..124L}, 
-yielding a large variety of single-, double- and triple-peaked
-spectra. 
-The full analysis of the the spectral features as well as
-more details on the radiative transfer are presented by
-\citet{Gronke2016}.
-
-We compare each resulting spectra to the observational results from
-\tol\ after normalizing the observed and simulated spectra to have a 
-flux integral of one.
-We build a $\chi^2$ on the normalized flux measurements for each one
-of the $2500$ models
-
-\begin{equation}
-\chi^2 = \sum_{i} \frac{({f}_i - \hat{f}_i)^2}{\sigma_i^2}, 
-\label{eq:chi2}
-\end{equation}
-%
-where $i$ iterates over velocity bins, $f_{i}$ is the observed flux,
-$\sigma_i$ is the observed flux uncertainty and $\hat{f}_i$ is the
-model estimated flux.
-We do not have analytic expression for $\hat{f}$, instead we use the
-results of the MonteCarlo to build histograms that play the role of
-$\hat{f}$.
-
-We select for further analysis the best $1\%$ models according to the
-lowest $\chi^2$ values.
-We note that the difference between the lowest and highest $\chi^2$ values in
-those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
-$\chi^2$ being close to $\chi^2_{min}=1200$. 
-The total number of degrees of freedom, $d.o.f$, is $104$.
-
-We divide the results in two classes: low $\chi^2/d.o.f.<35$ and high
-$\chi^2/d.o.f.35>$.
-We apply a random forest classification algorithm to find the
-more relevant parameters in splitting the results into these two
-classes. 
-The algorithm uses $500$ trees for the classification and a
-maximum of $3$ depth levels. 
-To check for tability we repeat the computation $10$ times by
-randomly subsampling the input data to use $80\%$ of the data as a
-training set.
-
-We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
-distribution in the best $25$ models against the parent distribution
-of $2500$ models. 
-If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
-this parameter does influence the $\chi^2$ result, as the distribution for
-the best $\chi^2$ models is statistically different to the
-distribution from the global sample of $2500$ models.
-
-We finally compute the best values for the influential parameters as
-the values that produce the minimum $\chi^2$.  
-We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
-$\chi^2$ as a function of the influential parameters around its
-corresponding minimum.
-
-\subsection{Bulk Rotation}
-
-The rotation model corresponds to the work presented in
-\citep{GaravitoCamargo2014} based on the Monte Carlo code
-\texttt{CLARA} \citep{CLARA}. 
-In that model the \lya\ photons are propagated 
-within a spherical and homogeneous cloud of HI gas undergoing solid
-body rotation.
-The sphere is fully characterized by three parameters: the HI line's
-center optical  depth $\tau$ measured from the center to its surface, the HI
-temperature $T$, and the linear surface velocity $V_{\rm max}$.  
-The observed line profile also depends on $\theta$,  the angle between the plane
-perpendicular to the rotation axis and the observational
-line-of-sight.  
-In this model, dust only changes the overall line
-normalization and only weakly its shape, i.e. 
-dust cannot change the line symmetry or induce a change in the number
-of line peaks, moreover it does not change the line width by more than
-$1\%$ ($5$ \kms\ in the case of \tol), an effect too small to be
-observed at the resolution at which we have \tol's line profile and
-also negligeable compared to the influence of the other free parameters in the model.
-For these reasons we do not include any dust model.
-
-We use an analytical approximation that captures the most important
-effects of rotation onto the \lya\ line. 
-We defer the reader to \citet{GaravitoCamargo2014} for complete
-details on the explicit form of this approximation.
-To fully explore the
-parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
-\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
-is an open source optimized implementation of the affine-invariant 
-MCMC sampler \citep{goodman2010ensemble}. 
-The algorithm creates a number of walkers that,
-during a sufficient number of steps, generate parameters' combinations
-for a specific model.
-For each timestep, the code calculates the likelihood of the
-combination with respect to the observational data.
-The walkers explore the parameter space sampling the Gaussian likelihood
-function built as $\propto \exp(-\chi^2/2)$, where the $\chi^2$ follows
-the definition in Equation \ref{eq:chi2}. 
-We do not have an analytic expresion for $\hat{f}$, we compute it
-by numerical integration of the analytical approximations found in
-\citet{GaravitoCamargo2014}.
-
-We explore flat priors on four parameters: $200<V_{\rm
-  max}/\mathrm{km\ s}^{-1} <600$,   $6.0<\log_{10}\tau<9.0$,
-$4.0<\log_{10} T/10^4\mathrm{K}< 4.5$ and $0<\theta<90$ using $500$
-steps with $24$ walkers for a total of $12000$ points in the chain.
-Previous exploratory work shows that it is impossible to fit the
-observed line outside these priors.
-Finally, we estimate the parameter values from the 16th, 50th and 84th
-percentiles.
-
 \section{Results}

### 2017-06-29 paper/paper.tex
full revision complete

@@
 \begin{center}
-\begin{tabular}{lc}\hline
-$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
-$\delta$(2000)$^{b}$ & -28d02m32s\\
+\begin{tabular}{lr}\hline
+$\alpha$(2000)& 12h17min17.1s\\
+$\delta$(2000)& -28d02m32s\\
 $l$, $b$ (deg) & 294, 34\\
@@
   M$_V$ & -17.6\\ 
-$z$ & $0.0259\pm0.0002$ \\\hline
+Redshift & $0.026\pm0.001$ \\\hline
 \end{tabular}
@@
   \centering
-\begin{tabular}{l|lrrr}
+\begin{tabular}{l|lrrl}
 \hline
@@
 $\beta_{\rm cl}$ & Steepness of the radial velocity profile & $1.5$ & [$1.1$, $2.5$] &  \\
-$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps & $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] & $\,\cm^{2}$ \\
-$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance & $0.01$ & [$10^{-4}$, $0.1$] &  \\
-$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
+$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps &
+  $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] &
+  $\,\cm^{2}$ \\
+$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance &
+  $0.01$ & [$10^{-4}$, $0.1$] & \\
+$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in
+  clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
 \hline
@@
 component which totals the number of parameters describing the model
-to be $14$, which also include information about the spatial
-distribution and thermal state of the clumps and the intraclump
-medium. 
+to be $14$.
 We do not explore inflowing clumps given the slight line asymmetry
 redwards to the line center (see the dots in Figure \ref{fig:results})
+and thus set $v_{\infty,\,{\rm cl}}>0$.
+The parameter description list is in Table \ref{tab:models}.
 
@@
 We build a $\chi^2$ on the normalized flux measurements for each one
-of the $2500$ models
+of the $2500$ models as
 
@@
 model estimated flux.
-We do not have analytic expression for $\hat{f}$, instead we use the
+As we do not have an analytic expression for $\hat{f}$; we use the
 results of the MonteCarlo to build histograms that play the role of
@@
 $\chi^2$ being close to $\chi^2_{min}=1200$.
-The total number of degrees of freedom, $d.o.f$, is $104$.
-
-We divide the results in two classes: low $\chi^2/d.o.f.<35$ and high
+
+Using the total number of degrees of freedom, $d.o.f.=104$ we divide
+the results in two classes: low $\chi^2/d.o.f.<35$ and high
 $\chi^2/d.o.f.35>$. 
@@
 maximum of $3$ depth levels. 
-To check for tability we repeat the computation $10$ times by
-randomly subsampling the input data to use $80\%$ of the data as a
-training set.
+To check for stability we repeat the computation $10$ times by
+randomly subsampling the input data to use $80\%$ of the data as
+the training set.
 
@@
 corresponding minimum.
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
+\caption{Broad, single peaked and highly symmetric \lya\ emission of \tol.
+  Dots correspond to the observational data \citep{mashesse03}. 
+The thick red and thin blue curves represent our best fit
+to the data using the full radiative transfer simulation with a
+rotation and multiphase model, respectively. 
+These two different models are able to reproduce the main morphological
+features of \tol's \lya\ line emission.\label{fig:results}}
+\end{center}
+\end{figure*}
 
@@
 the definition in Equation \ref{eq:chi2}. 
-We do not have an analytic expresion for $\hat{f}$, we compute it
+We do not have a closed analytic expresion for $\hat{f}$, we compute it
 by numerical integration of the analytical approximations found in
@@
 \begin{center}
-\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and highly symmetric \lya\ emission of \tol.
-  Dots correspond to the observational data \citep{mashesse03}. 
-The thick red and thin blue curves represent our best fit
-to the data using the full radiative transfer simulation with a
-rotation and multiphase model, respectively. 
-These two different models are able to reproduce the main morphological
-features of \tol's \lya\ line emission.\label{fig:results}}
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
 \includegraphics[width=0.95\textwidth]{tree_result.pdf}
@@
 Each box describes the condition over the parameter of interest, the
-level of sample impurity, the number of samples and the value of the
-number of samples in each classes.  
-In this example we randomly sample $80\%$ of the full set of models to
+level of sample impurity, the total number of samples and the value of the
+number of samples in each class.  
+In this example we randomly sample $80\%$ of the full data set of models to
 start with $28$ models in the first class and
 $1962$ models in the second class; the best way to increase the
-probability to find a  a result with low $\chi^2/d.o.f.$ ($13$ models) is having $v_{\infty,{\rm cl}}<157.0$ \kms,
-$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
+probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
+fourth bottom box, from left to the right)
+is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
+the clump velocity dipersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
+probability to have a \lya\ photon emitted in a clump, $P_{\rm cl}>0.683$.
 The final classification is not perfect, showing that all other
@@
   We only show results for the three parameters with a significant
-  statistical difference between the models with the lowest $\chi^2$
+  statistical difference between the models with the lowest $\chi^2/d.o.f.$
   values and its prior distribution. 
@@
   The left column corresponds to the parameter's integrated distributions for
-  models with the lowest $\chi^2$ values (dotted line) compared against the
+  models with the lowest $\chi^2/d.o.f.$ values (dotted line) compared against the
   parameter's prior integrated distributions (continuous line).
-  The right column shows a scatter plot of $\chi^2$ (normalized by the
-  degrees of freedom) and its corresponding physical parameters.
+  The right column shows a scatter plot of $\chi^2/d.o.f.$
+  and its corresponding physical parameters.
   The clump kinematic state is the key ingredient to
@@
 Figure \ref{fig:tree} shows as an illustration the results for a
-classification tree.  
+single classification tree.  
 The tree starts with $28$ and $1962$ models in the low and high
@@
 We find that the best classification
-yields $13$ and $44$ models in the low and high $\chi^2\d.o.f.$
+yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
 classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
@@
 
-The best models are summarized in Figure \ref{multiphaseresults}.
-Left column show the difference between the integrated distributions
+The best models are shown in Figure \ref{multiphaseresults}.
+Left column shows the difference between the integrated distributions
 of the full sample (2500 input models) and the models with the lowest
@@
 parameters, and expect to fit the line profile while only varying the
-other 3, as the results for the classification tree example show in
-Figure \ref{fig:tree}.
+other 3, as the results for the classification tree example in Figure
+\ref{fig:tree} shows.
 
@@
   improve our understanding of \tol's kinematics.} . 
-Considering the sparse sampling of parameter space and the results
+Furthermore, considering the sparse sampling of parameter space and the results
 from the random forest classifier, it is safer to consider that
@@
 
-\tol\ shows one of the most atypical \lya\ spectra observed so far.
+\tol\ presents one of the most atypical \lya\ spectra observed so far.
 Its flux at the line's center is high compared to other LAEs at low
@@
 Following the results of \cite{2011ApJ...726..108T}, who made a
-detailed analysis for all kind of elliptical galaxies including, we
+detailed analysis for all kind of elliptical galaxies including dE galaxies, we
 estimate a value for the dynamical mass using the constraints for
-thevelocity dispersion $\sigma$  in a spherical system localized in a
+thevelocity dispersion, $\sigma$,  in a spherical system localized in a
 region of size $r$
@@
 for the HI region, in the multiphase model the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
+$\sigma_{\rm{cl}}=$\sigmaclump thus corresponds to a dynamical mass of
 $M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
@@
 \cite{2011ApJ...726..108T} showed that  that such dynamical
-mass can be explained if a dwarf galaxy is hosted by a dark matter halo of at
+mass can be explained if a dE is hosted by a dark matter halo of at
 least $10^{11}$ M$_{\odot}$ in mass. 
@@
 \citep{2001AJ....121..169F}. 
-The second problem is that, unlike a dE, \tol\ hosts a bright and compact
+The second issue is that, unlike a dE, \tol\ hosts a bright and compact
 startburst; imaging and spectroscopy studies suggest that the
@@
 We suggest that new observational tests are needed to clarify the
-kinematic nature of \tol\ and be sure about \tol's kinematic
-structure. 
+kinematic nature of \tol\.
 Integral field unit measurements resolving its spatial extent are up
@@
 
-Another observational test to confirm the picture provided by the
-multiphase model includes the measurement of the \lya\ ionizing
-continuum escape fraction. 
-This model model predicts that averaging over all sightlines
+Another observational hint to clarify \tol's state could be
+the measurement of the \lya\ ionizing continuum escape fraction. 
+The multiphase model predicts that averaging over all sightlines
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
@@
 
-We prefer the multiphase model becasue it has kinematic
+In this particular case, we prefer the multiphase model becasue it has kinematic
 conditions similar to those in dwarf ellipticals, while the
-rotational model produces rotational velocities to high for a dwarf
+rotational model produces rotational velocities too high for a dwarf
 galaxy.
@@
 unexpected kinematic structure.
-A definitive confirmation of our findings has to be provided by new
-observational tests with integral field unit spectroscopy. 
-A confirmation of our results would support the multiphase model
-as a tool to study the evolutionary link between star-forming and
-quiescent stages of dwarf galaxy evolution.
+A confirmation of our results by new observations would support the multiphase model
+as an element to be included in the study of primordial \lya\ emitting
+galaxies.
 

### 2017-06-29 paper/paper.tex
comment on enclosed mass

@@
 explained if \tol\ is hosted by a dark matter halo of at least
-$10^{11}$ M$_{\odot}$.
+$6\times 10^{11}$ M$_{\odot}$.
 If future kinematic maps of \tol\ confirm the velocities suggested by the
@@
 
-\cite{2011ApJ...726..108T} showed that  that such dynamical
-mass can be explained if a dE is hosted by a dark matter halo of at
-least $10^{11}$ M$_{\odot}$ in mass. 
+Figure \ref{fig:mass} illustrates  how such dynamical
+mass can be explained if \tol\ is hosted by a dark matter halo of at
+least $6\times 10^{11}$ M$_{\odot}$ in virial mass. 
 This estimate is based on computing the integrated mass profile of a
@@
 class. 
-However, there are two puzzles that are opened up by this hypothesis. 
+However, this hypothesis opens up two puzzles.
 First, dE galaxies are found either in clusters or groups of
@@
 
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.46\textwidth]{enclosed_mass.pdf}
+\caption{Enclosed mass in a spherical system as a function of radius.
+  Lines correspond to the expectation for dark matter halos and the point
+  to the dynamical mass lower bounds for \tol.
+  The dynamical mass estimates for \tol\ are consistent with the
+  galaxy being hosted by a dark matter halo of at least
+  $6\times10^{11}$ M$_{\odot}$ in mass.
+    \label{fig:mass}} 
+\end{center}
+\end{figure}
+
 \section{Conclusions}

### 2017-06-29 paper/paper.tex
updated references

@@
 %=========================================================================
-\title[An atypical \lya\ dwarf galaxy]{
+\title[An atypical \lya dwarf galaxy]{
 Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy}
@@
 Here we report on one of such CDGs, \tol, which presents
-a broad, single peaked, highly symmetric \lya\ emission line that had
+a broad, single peaked, highly symmetric \lya emission line that had
 evaded theoretical interpretation so far.  
@@
 rotation.
-It is the first time that an observed \lya\ spectrum can be explained
+It is the first time that an observed \lya spectrum can be explained
 assuming either of these kinematic conditions.
@@
 multiphase model, it would provide additional support to expect this
-condition to be present  in primordial \lya\ emitting galaxies.  
+condition to be present  in primordial \lya emitting galaxies.  
 \end{abstract}
@@
 Over fifty years ago it was realized that young galaxies could be
-detected through a strong \lya\ line emission \citep{PartridgePeebles}.
+detected through a strong \lya line emission \citep{PartridgePeebles}.
 
@@
 in surveys. 
-The presence of the \lya\ emission line provides confirmation of
+The presence of the \lya emission line provides confirmation of
 the distance to a galaxy while provides clues about the stellar
 population and inter-stellar medium conditions regulating the
-\lya\ emission.
+\lya emission.
 A careful clustering analysis of LAEs can also yield clues about their link
@@
 
-The \lya\ emission line is not exclusive of distant galaxies. 
-There are local Universe surveys that target \lya\ emission in nearby
+The \lya emission line is not exclusive of distant galaxies. 
+There are local Universe surveys that target \lya emission in nearby
 dwarf star forming galaxies.
@@
 
-However, the physical interpretation of \lya\ observations is
+However, the physical interpretation of \lya observations is
 not straightforward \citep{LARS,2015ApJ...805...14R}. 
-This is due to the resonant nature of the \lya\ line. 
-A \lya\ photon follows a diffusion-like process before escaping
+This is due to the resonant nature of the \lya line. 
+A \lya photon follows a diffusion-like process before escaping
 the galaxy or being absorbed by dust. 
@@
 There are few analytical tools available to interpret the
-emerging \lya\ line
+emerging \lya line
 \citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
@@
 which are hardly met in real astrophysical systems. 
-For these reasons the interpretation of \lya\ observations
+For these reasons the interpretation of \lya observations
 requires state-of-the-art Monte Carlo radiative transfer simulations.
 
-Observed \lya\ line profiles usually present a single peak shifted
+Observed \lya line profiles usually present a single peak shifted
 redwards from the line's center. 
@@
 the peak on the red side being stronger. 
-This can be explained as the results of multiple \lya\ photon
+This can be explained as the results of multiple \lya photon
 scatterings through an outflowing shell of neutral Hydrogen
@@
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong \lya\ emission with puzzling 
+strong \lya emission with puzzling 
 features: the line is highly symmetric, single peaked and broad 
@@
 truncated by the intergalactic medium \citep{2007MNRAS.377.1175D}. 
-In this case the \lya\ radiation could emerge as a low surface
-brightness glow, which may be connected to \lya\ halos, while also
+In this case the \lya radiation could emerge as a low surface
+brightness glow, which may be connected to \lya halos, while also
 influencing the way LAEs can be used as a probe of reionization,
@@
 
-Attempts to explain the atypical \lya\ features in \tol\ with
+Attempts to explain the atypical \lya features in \tol\ with
 conventional models based on a expanding shell have not been succesful
@@
 \citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
-Besides, clumpy multiphase outflows are capable to explain \lya\ features around
+Besides, clumpy multiphase outflows are capable to explain \lya features around
 star-forming galaxies
@@
 In this paper we show, for the first time in the literature, that \tol's
-\lya\ profile can be explicitly modeled be either of these two
+\lya profile can be explicitly modeled be either of these two
 models.
@@
 We focus on presenting two simple and succesful models that
-manage, for the first time, to account for \tol's \lya\ line main
+manage, for the first time, to account for \tol's \lya line main
 features.
@@
 rotation models to explain how we fit their free parameters 
-to the \tol's \lya\ line shape.
+to the \tol's \lya line shape.
 We use the results to interpret them in terms of the galaxy's
@@
     values. Variables marked with ${}^{\dagger}$ were drawn in
-    log-space. Details of the implementation are in \citet{Gronke2016}.}
+    log-space. Table reproduced from \citet{Gronke2016}.}
   \label{tab:models}
@@
 detection for \tol. 
-This lack of detection motivates our assumption that \lya\ emission is
+This lack of detection motivates our assumption that \lya emission is
 powered by star formation only.
 
-The observed flux for the \lya\ line is $\sim
+The observed flux for the \lya line is $\sim
 8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
-The \lya\ Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
+The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
 $1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
@@
 expectation from case B recombination of $23.3$ \citep{Hummer1987} one
-can estimate an escape fraction of $20$\% for \lya\ radiation.
-
-The \lya\ flux values correspond to a luminosity of
+can estimate an escape fraction of $20$\% for \lya radiation.
+
+The \lya flux values correspond to a luminosity of
 $L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
@@
 
-We computed the projected half-light radius to be $R_s=1.5\pm0.1$ kpc 
+We compute the projected half-light radius to be $R_s=1.5\pm0.1$ kpc 
 from the surface brightness profiles reported by \cite{2003A&A...410..481N}. 
@@
 \includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and highly symmetric \lya\ emission of \tol.
+\caption{Broad, single peaked and highly symmetric \lya emission of \tol.
   Dots correspond to the observational data \citep{mashesse03}. 
@@
 These two different models are able to reproduce the main morphological
-features of \tol's \lya\ line emission.\label{fig:results}}
+features of \tol's \lya line emission.\label{fig:results}}
 \end{center}
@@
 \texttt{CLARA} \citep{CLARA}. 
-In that model the \lya\ photons are propagated 
+In that model the \lya photons are propagated 
 within a spherical and homogeneous cloud of HI gas undergoing solid
@@
 We use an analytical approximation that captures the most important
-effects of rotation onto the \lya\ line. 
+effects of rotation onto the \lya line. 
 We defer the reader to \citet{GaravitoCamargo2014} for complete
@@
 the clump velocity dipersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
-probability to have a \lya\ photon emitted in a clump, $P_{\rm cl}>0.683$.
+probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
 The final classification is not perfect, showing that all other
@@
   These three parameters are the clump radial velocity at infinity 
-  $v_{\infty, \rm{cl}}$; the probability that  the \lya\ photons were
+  $v_{\infty, \rm{cl}}$; the probability that  the \lya photons were
   emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
@@
   The clump kinematic state is the key ingredient to
-  reproduce \tol's \lya\ line morphology.
+  reproduce \tol's \lya line morphology.
   \label{multiphaseresults}
@@
     All parameters in the rotation model can be succesfuly constrained by \tol's
-    \lya\ line morphology to the values written in the top region of
+    \lya line morphology to the values written in the top region of
     the diagonal panels.
@@
 \tol\ features can be reproduced: a broad, highly symmetric,
-single-peaked \lya\ line.
+single-peaked \lya line.
 
@@
 In what follows we summarize the values of the kinematic parameters
-that managed to explain \tol\'s \lya\ profile.
+that managed to explain \tol\'s \lya profile.
 
@@
 $v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
-that the \lya\ emission comes from the clumps $P_{\rm cl}$, are the
+that the \lya emission comes from the clumps $P_{\rm cl}$, are the
 most influential parameters in finding a model with low
@@
 Qualitatively this result can be understood as follows. 
-The broad \lya\ line is the result of subsequent \lya\ photon
+The broad \lya line is the result of subsequent \lya photon
 scatterings due to (relatively) fast moving clumps while the
 multi-phase nature (i.e., the existence of low-density inter-clump
-regions where \lya\ photons can freely prograpagate)  ensures the high
+regions where \lya photons can freely prograpagate)  ensures the high
 flux at line center as observed.   
@@
 This model cannot reproduce the slight asymmetry present in \tol's
-\lya\ line; most probably this would require an small amount of
+\lya line; most probably this would require an small amount of
 outflows, a feature that is not present in the model provided by
@@
 
-\tol\ presents one of the most atypical \lya\ spectra observed so far.
+\tol\ presents one of the most atypical \lya spectra observed so far.
 Its flux at the line's center is high compared to other LAEs at low
@@
 %
-Assuming that the \lya\ emission is entirely powered by star formation 
+Assuming that the \lya emission is entirely powered by star formation 
 we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
@@
 relationship found in the Bolshoi simulation
-\citep{2012MNRAS.423.3018P}.
+\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.
 
@@
 \citet{Herenz16} done with the Potsdam Multi-Aperture Spectrometer
-(PMAS) \citep{PMAS} on nearby \lya\ emitting galaxies.
+(PMAS) \citep{PMAS} on nearby \lya emitting galaxies.
 
 Another observational hint to clarify \tol's state could be
-the measurement of the \lya\ ionizing continuum escape fraction. 
+the measurement of the \lya ionizing continuum escape fraction. 
 The multiphase model predicts that averaging over all sightlines
@@
 reproduce the so far unexplained observational features of \tol's
-\lya\ emission line.  
+\lya emission line.  
 One model is based on a multiphase ISM with random clump motions and
 the other on gas bulk solid body rotation. 
-It is the first time that an observed \lya\ profile can be fully
+It is the first time that an observed \lya profile can be fully
 reproduced by either of these two kinematic conditions.
 Our findings highlight the importance of including multiphase and/or
-rotation conditions as kinematic features to model the \lya\ line.
+rotation conditions as kinematic features to model the \lya line.
 
@@
 A confirmation of our results by new observations would support the multiphase model
-as an element to be included in the study of primordial \lya\ emitting
+as an element to be included in the study of primordial \lya emitting
 galaxies.
@@
 We thank J. M. Mas-Hesse for providing us with \tol's observational
-\lya\ data \citep{mashesse03} in electronic format. This data was
+\lya data \citep{mashesse03} in electronic format. This data was
 used to prepare Figure 1.
@@
 
-\bibitem[\protect\citeauthoryear{{Hansen} \& {Oh}}{{Hansen} \&
-  {Oh}}{2006}]{Hansen06}
-{Hansen} M.,  {Oh} S.~P.,  2006, \mnras, 367, 979
-
 \bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
@@
 
+\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero} \&
+  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
+{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,    {Mu{\~n}oz-Cuartas} J.~C.,
+  2016, \apj, 832, 169
+
 \bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}

### 2017-07-02 paper/paper.tex
updated caption
minor typos

@@
 The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
-$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
+$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$
 which gives a \lya/H$\beta$ flux ratio of
@@
 the results in two classes: low $\chi^2/d.o.f.<35$ and high
-$\chi^2/d.o.f.35>$. 
+$\chi^2/d.o.f.>35$. 
 We apply a random forest classification algorithm to find the
@@
 \caption{Enclosed mass in a spherical system as a function of radius.
-  Lines correspond to the expectation for dark matter halos and the point
+  Lines correspond to the expectation for dark matter halos with
+  different viral masses as shown in the legend, the arrow corresponds
   to the dynamical mass lower bounds for \tol.  

### 2017-07-04 paper/paper.tex
paper.tex

@@
 More involved models with multiple kinematic components can
-in principle also be sucessful.
-We focus on presenting two simple and succesful models that
+in principle also be successful.
+We focus on presenting two simple and successful models that
 manage, for the first time, to account for \tol's \lya line main
@@
 spectra. 
-The full analysis of the the spectral features as well as
+The full analysis of the spectral features as well as
 more details on the radiative transfer are presented by
@@
 As we do not have an analytic expression for $\hat{f}$; we use the
-results of the MonteCarlo to build histograms that play the role of
+results of the Monte Carlo to build histograms that play the role of
 $\hat{f}$.
@@
 is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
-the clump velocity dipersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
+the clump velocity dispersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
 probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
@@
 
-Figure 1. summarizes our main finding.
+Figure 1. Summarizes our main finding.
 Dots represent the observational data for \tol\ with the
@@
 In what follows we summarize the values of the kinematic parameters
-that managed to explain \tol\'s \lya profile.
+that managed to explain \tol's \lya profile.
 
@@
   kind of observations could be performed in the near future to
-  improve our understanding of \tol's kinematics.} . 
+  improve our understanding of \tol's kinematics.}.
 Furthermore, considering the sparse sampling of parameter space and the results
@@
 
-The prefered value for the rotational velocity can be explained as
+The preferred value for the rotational velocity can be explained as
 follows. 
@@
 mass system. 
-\tol's infered rotational velocity is larger than the
+\tol's inferred rotational velocity is larger than the
 Milky Way's ($\sim200$\kms) while its baryonic mass is one order
@@
 estimate a value for the dynamical mass using the constraints for
-thevelocity dispersion, $\sigma$,  in a spherical system localized in a
+the velocity dispersion, $\sigma$,  in a spherical system localized in a
 region of size $r$
@@
 The second issue is that, unlike a dE, \tol\ hosts a bright and compact
-startburst; imaging and spectroscopy studies suggest that the
-startburst started less than 4 Myr ago, while the low surface
+starburst; imaging and spectroscopy studies suggest that the
+starburst started less than 4 Myr ago, while the low surface
 brightness regins are consistent with an age below one Gyr
@@
 We suggest that new observational tests are needed to clarify the
-kinematic nature of \tol\.
+kinematic nature of \tol.
 Integral field unit measurements resolving its spatial extent are up
@@
 
-In this particular case, we prefer the multiphase model becasue it has kinematic
+In this particular case, we prefer the multiphase model because it has kinematic
 conditions similar to those in dwarf ellipticals, while the
@@
 used to prepare Figure 1.
-J. E. F-R. ackwnoledges the support of J. L. Guerra in the last
+J. E. F-R. acknowledges the support of J. L. Guerra in the last
 writing stages of this paper.

### 2017-07-08 paper/paper.tex
fixed typos and added a fig reference

@@
 in surveys. 
-The presence of the \lya emission line provides confirmation of
-the distance to a galaxy while provides clues about the stellar
+The presence of the \lya emission line gives confirmation of
+the distance to a galaxy and provides clues about the stellar
 population and inter-stellar medium conditions regulating the
@@
 Attempts to explain the atypical \lya features in \tol\ with
-conventional models based on a expanding shell have not been succesful
+conventional models based on a expanding shell have not been successful
 so far \citep{mashesse03,2015A&A...578A...7V}. 
@@
 In this paper we show, for the first time in the literature, that \tol's
-\lya profile can be explicitly modeled be either of these two
+\lya profile can be explicitly modeled by either of these two
 models.
@@
 
-In the next section We review the observational characteristics of
+In the next section we review the observational characteristics of
 \tol, then we summarize the main features in the multiphase and
@@
 We use the results to interpret them in terms of the galaxy's
-dynamical mass and argue why the multiphase model should be prefered
+dynamical mass and argue why the multiphase model should be preferred
 over the rotation model.
@@
 observed at the resolution at which we have \tol's line profile and
-also negligeable compared to the influence of the other free parameters in the model.
+also negligible compared to the influence of the other free parameters in the model.
 For these reasons we do not include any dust model.
@@
 the definition in Equation \ref{eq:chi2}. 
-We do not have a closed analytic expresion for $\hat{f}$, we compute it
+We do not have a closed analytic expression for $\hat{f}$, we compute it
 by numerical integration of the analytical approximations found in
@@
     represent the 16th, 50th and 84th percentiles. 
-    All parameters in the rotation model can be succesfuly constrained by \tol's
+    All parameters in the rotation model can be successfully constrained by \tol's
     \lya line morphology to the values written in the top region of

### 2017-07-11 paper/paper.tex
Minor changes in intro

@@
 Sometimes a double peak is present but the asymmetry persists with 
-the peak on the red side being stronger. 
+the peak on the red side being stronger \citep[e.g.][]{2010ApJ...717..289S,Erb14,Trainor16}. 
 This can be explained as the results of multiple \lya photon
@@
 brightness glow, which may be connected to \lya halos, while also
-influencing the way LAEs can be used as a probe of reionization,
-see the review by \cite{2014PASA...31...40D} and the references
-therein.
+influencing the way LAEs can be used as a probe of reionization
+\citep[see the review by][and references therein]{2014PASA...31...40D}.
 
@@
 
-The main motivation for the outflowing multiphase model (as presented
-in \cite{Gronke2016}) is that some dwarf galaxies are expected to
+The main motivation for the outflowing multiphase model \citep[as presented
+in][]{Gronke2016} is that some dwarf galaxies are expected to
 present outflows.  
@@
 \citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
+In addition, due to the cooling properties of gas multiphase media are expected
+in a range of astrophysical systems \citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.
 
@@
 
+\mg{I would remove the next paragraph as this seems clear and not necessary to start with an ``apology''.}
 We do not claim that our findings discard the existence of different

### 2017-07-11 paper/paper.tex
added `comment command'
Minor changes to sec 2 & 3

@@
 
+\newcommand{\mg}[1]{\textcolor{blue}{\bf MG: \textit{#1}}}
+
 \begin{document}
@@
 
-Archival Chandra X-ray data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
+Archival Chandra X-ray data\footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
 detection for \tol. 
@@
 model estimated flux.
-As we do not have an analytic expression for $\hat{f}$; we use the
-results of the Monte Carlo to build histograms that play the role of
-$\hat{f}$.
+As we do not have an analytic expression for $\hat{f}$;
+we obtain $\hat{f}$ from the binned results of the Monte Carlo radiative transfer simulations.
 
@@
 those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
-$\chi^2$ being close to $\chi^2_{min}=1200$.
+$\chi^2$ being close to $\chi^2_{\mathrm{min}}=1200$.
 
@@
 the results in two classes: low $\chi^2/d.o.f.<35$ and high
-$\chi^2/d.o.f.>35$. 
+$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}
 We apply a random forest classification algorithm to find the

### 2017-07-11 paper/paper.tex
Added some questions to Sec 4

@@
 single classification tree.
+\mg{Sorry but it is not clear to me what this Figure shows \& how it was assembled.
+I suggest: leave the KS test in the main text as it is straightforward to understand, and move the random trees with more technical details / references about the implementations to the appendix -- and then point to it as a second probe from the main tetx.
+This way it would break the flow less.}
 The tree starts with $28$ and $1962$ models in the low and high
@@
 $v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
+\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
 

### 2017-07-11 paper/paper.tex
Rewrote explanation in 4.1

@@
 Qualitatively this result can be understood as follows.
-The broad \lya line is the result of subsequent \lya photon
-scatterings due to (relatively) fast moving clumps while the
-multi-phase nature (i.e., the existence of low-density inter-clump
-regions where \lya photons can freely prograpagate)  ensures the high
-flux at line center as observed.   
-In turn, a lower velocity dispersion would produce a thiner line than
-it is observed.
+Due to the large fraction of \lya photons being emitted within the moving clumps ($P_{\rm cl}$), the `intrinsic' profile represents the kinematics of the clumps, that is, the width of the intrinsic line is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by $v_{\infty}$ \& $\beta_{\rm cl}$.
+Furthermore, the relatively low mean number of clumps per line of sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion of the clumps implies the 
+existence of low-density inter-clump
+regions where \lya photons can freely propagate which leads to an emergent spectrum close to the intrinsic one as well as to the high flux at line center as observed.
+Because the width of the observable spectrum is hence set primarily by $\sigma_{\rm cl}$, a lower velocity dispersion would produce a narrower line and thus a worse fit.
 From the lower right panel in Figure \ref{multiphaseresults} we find that it
@@
 
-As a test, we also run a small set of 100 additional radiative
+As a test, we also run a small set of $100$ additional radiative
 transfer simulations with random values for all parameters, except for
-$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are within the derived
-constraints.
+$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1-\sigma$
+constraints. \mg{Is $1\sigma$ correct?}
 Consistent with the results from the random forest algorithm,
@@
 
-Having constrained only 3 parameters, one migh wonder why the other 11
+Having constrained only 3 parameters, one might wonder why the other 11
 parameters do not seem to matter. 

### 2017-07-11 paper/paper.tex
Some changes to Sec 5

@@
 parameters do not seem to matter. 
-However, this view is misleading. 
-Even if for clumply models the line profile is most sensitive to only
-a few parameters \citep{Gronke2016}, there are the rest of parameters
-which affect the line profile at a level that cannot be neglected,
+However, this view is misleading because merely the best-fit values of (some of) those $3$ parameters, i.e., the corresponding constraint to a given sub-region in the parameter space, make the other parameters less important.
+For instance, in our case the large value of $P_{\rm cl}$ makes radiative transfer effects, and therefore other parameters such as the clump column density less relevant for the emergent line profile.
+However, for instance larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce additional radiative transfer effects and thus increase the number of relevant parameters \citep[see ][for details]{2017arXiv170406278G}.
+This means that even
+if for clumply models the line profile is most sensitive to only
+a few parameters \citep{Gronke2016}, the rest of parameters
+affect the line profile at a level that cannot be neglected,
+\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
 i.e. we cannot randomly pick 11 random, reasonable values for these
@@
 We cannot discard that another region of parameter space
-could also work.
-It might be interesting to explore in the
-future with a higher sampling of the parameter space once new 
+could also yield a good fit to the observed line-profile.
+This might be interesting to explore in the
+future with, e.g., a higher sampling of the parameter space once new 
 observations  clarify the kinematic nature of \tol \footnote{In
@@
   cl}$ are actually lower/upper/lower bounds, respectively.
+\mg{This is interesting. Why do you think that? Could we use that to increase the quoted errors? I am worried that the referee will complain about the small errors.}
 
@@
 velocity of $\sim350$ \kms\ is too high for such a low
-mass system. 
+mass system.  \mg{I am confused -- are much lower rotational velocities not exclude by the priors used?}
 \tol's inferred rotational velocity is larger than the
@@
 variations depending on viewing angle, i.e. some sightlines can have
-an escape fraction close to $100\%$, \citep{Gronke2016}.
+an escape fraction close to $100\%$ \citep{Gronke2016}.
 

### 2017-07-13 paper/paper.tex
new appendix

@@
 \newcommand{\mg}[1]{\textcolor{blue}{\bf MG: \textit{#1}}}
+\newcommand{\jefr}[1]{\textcolor{darkgreen}{\bf JEFR: \textit{#1}}}
 
@@
 models.
-
-\mg{I would remove the next paragraph as this seems clear and not necessary to start with an ``apology''.}
-We do not claim that our findings discard the existence of different
-undiscovered models that could reproduce the observed features in \tol.
-More involved models with multiple kinematic components can
-in principle also be successful.
-We focus on presenting two simple and successful models that
-manage, for the first time, to account for \tol's \lya line main
-features.
 
@@
 
-Using the total number of degrees of freedom, $d.o.f.=104$ we divide
-the results in two classes: low $\chi^2/d.o.f.<35$ and high
-$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}
-We apply a random forest classification algorithm to find the
-more relevant parameters in splitting the results into these two
-classes. 
-The algorithm uses $500$ trees for the classification and a
-maximum of $3$ depth levels. 
-To check for stability we repeat the computation $10$ times by
-randomly subsampling the input data to use $80\%$ of the data as
-the training set.
-
-We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
+We also a Kolmogorov-Smirnov (K-S) test to compare each parameter
 distribution in the best $25$ models against the parent distribution
 of $2500$ models. 
-If we obtain a p-value $<0.05$ for a given model parameter, we conclude that
-this parameter does influence the $\chi^2$ result, as the distribution for
+From a p-value $<0.05$ for a given model parameter, we conclude that
+this parameter can be constrained from the observations, as the distribution for
 the best $\chi^2$ models is statistically different to the
@@
 
-We finally compute the best values for the influential parameters as
+We finally compute the best values for the constrained parameters as
 the values that produce the minimum $\chi^2$.  
 We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
-$\chi^2$ as a function of the influential parameters around its
+$\chi^2$ as a function of the constrained parameters around its
 corresponding minimum.
@@
 percentiles.
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.95\textwidth]{tree_result.pdf}
-\caption{Classification tree example. 
-The aim is to find the parameters that separate two
-classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
-Each box describes the condition over the parameter of interest, the
-level of sample impurity, the total number of samples and the value of the
-number of samples in each class.  
-In this example we randomly sample $80\%$ of the full data set of models to
-start with $28$ models in the first class and
-$1962$ models in the second class; the best way to increase the
-probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
-fourth bottom box, from left to the right)
-is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
-the clump velocity dispersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
-probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
-The final classification is not perfect, showing that all other
-parameters are also important but these three are the most relevant.  
-\label{fig:tree}}
-\end{center}
-\end{figure*}
 
@@
 With $14$ free parameters our first concern is discovering which are
-the most relevant in reproducing \tol's line shape.
-The results of the random forest classifier yield that the clump outflow velocity
-$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
-that the \lya emission comes from the clumps $P_{\rm cl}$, are the
-most influential parameters in finding a model with low
-$\chi^2/d.o.f.$.
-
-Figure \ref{fig:tree} shows as an illustration the results for a
-single classification tree.
-\mg{Sorry but it is not clear to me what this Figure shows \& how it was assembled.
-I suggest: leave the KS test in the main text as it is straightforward to understand, and move the random trees with more technical details / references about the implementations to the appendix -- and then point to it as a second probe from the main tetx.
-This way it would break the flow less.}
-The tree starts with $28$ and $1962$ models in the low and high
-$\chi^2/d.o.f.$ classes, respectively. 
-We find that the best classification
-yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
-classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
-$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
-The split in two classes is not perfect. 
-This means that the 3 parameters in the
-model are the most influential in finding models with low
-$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
-are also relevant to find a good fit.
-
-From the K-S tests we confirm that the same 3 parameters are the
-only ones that can be constrained by observations;
+the parameters that can be safeley constrained by \tol's line shape.
+
+From the K-S tests we confirm that only 3 parameters 
+can be constrained by observations;
 $v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
 $10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
-Once again, this test does not mean the other parameters do not
-influence the resulting spectra at all; it means that they cannot be
-constrained from \tol's observations.
+This does not mean the other parameters do not influence the resulting
+spectra at all; it means that they cannot be constrained from \tol's
+observations.
 
@@
 \mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
+\jefr{The small uncertainty only says that the increase in
+  $\chi^2/dof$ is very steep. I don't think you can get larger errors
+  with the available date. By simple inspection of Figure 2 we can
+  see that the errors will be small with the data we have. The
+  paremeter uncertainty roughly corresponds to the width of the parabola
+  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
+  have there is a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
+  and the nearest data point. }
 
 Qualitatively this result can be understood as follows.
-Due to the large fraction of \lya photons being emitted within the moving clumps ($P_{\rm cl}$), the `intrinsic' profile represents the kinematics of the clumps, that is, the width of the intrinsic line is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by $v_{\infty}$ \& $\beta_{\rm cl}$.
-Furthermore, the relatively low mean number of clumps per line of sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion of the clumps implies the 
-existence of low-density inter-clump
-regions where \lya photons can freely propagate which leads to an emergent spectrum close to the intrinsic one as well as to the high flux at line center as observed.
-Because the width of the observable spectrum is hence set primarily by $\sigma_{\rm cl}$, a lower velocity dispersion would produce a narrower line and thus a worse fit.
+Due to the large fraction of \lya photons being emitted within the
+moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile represents
+the kinematics of the clumps, that is, the width of the intrinsic line
+is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
+$v_{\infty}$ \& $\beta_{\rm cl}$. 
+Furthermore, the relatively low mean number of clumps per line of
+sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion
+of the clumps implies the  existence of low-density inter-clump 
+regions where \lya photons can freely propagate which leads to an
+emergent spectrum close to the intrinsic one as well as to the high
+flux at line center as observed. 
+Because the width of the observable spectrum is hence set primarily by
+$\sigma_{\rm cl}$, a lower velocity dispersion would produce a
+narrower line and thus a worse fit. 
 From the lower right panel in Figure \ref{multiphaseresults} we find that it
@@
 $50$\kms.
-This is also supported by the classification tree example in Figure
-\ref{fig:tree}.
 
@@
 transfer simulations with random values for all parameters, except for
-$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1-\sigma$
-constraints. \mg{Is $1\sigma$ correct?}
+$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
+constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
+\mg{Is $1\sigma$ correct?}\jefr{What do you mean with
+  that question?}
 Consistent with the results from the random forest algorithm,
-illustrated by the classification tree of Figure \ref{fig:tree}, we
-find that $30$ models show $\chi^2/d.o.f.<35$.
+illustrated by the classification tree of Figure \ref{fig:tree},
 
@@
 \mg{I am not sure I understand the rest of this sentence. What do you mean there?}
-i.e. we cannot randomly pick 11 random, reasonable values for these
-parameters, and expect to fit the line profile while only varying the
-other 3, as the results for the classification tree example in Figure
-\ref{fig:tree} shows.
+i.e. we cannot randomly pick 11 random values for these
+parameters and expect to fit the line profile while only varying the
+other 3
 
@@
   improve our understanding of \tol's kinematics.}.
-Furthermore, considering the sparse sampling of parameter space and the results
-from the random forest classifier, it is safer to consider that
-the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
-  cl}$ are actually lower/upper/lower bounds, respectively.
-\mg{This is interesting. Why do you think that? Could we use that to increase the quoted errors? I am worried that the referee will complain about the small errors.}
 
@@
 %\bibliography{references}
+
 \begin{thebibliography}{}
@@
 
+\bibitem[\protect\citeauthoryear{{Gronke}, {Dijkstra}, {McCourt} \&
+  {Oh}}{{Gronke} et~al.}{2017}]{2017arXiv170406278G}
+{Gronke} M.,  {Dijkstra} M.,  {McCourt} M.,    {Oh} S.~P.,  2017, ArXiv
+  e-prints
+
 \bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
@@
 
+\bibitem[\protect\citeauthoryear{{McCourt}, {Oh}, {O'Leary} \&
+  {Madigan}}{{McCourt} et~al.}{2016}]{2016arXiv161001164M}
+{McCourt} M.,  {Oh} S.~P.,  {O'Leary} R.~M.,    {Madigan} A.-M.,  2016, ArXiv
+  e-prints
+
+\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
+  {Ostriker}}{1977}]{1977ApJ...218..148M}
+{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \apj, 218, 148
+
 \bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
@@
 
+\appendix
+\section{Random Forest Classification}
+\label{appendix}
+
+As a complement to the K-S tests on the multiphase data 
+we apply a random forest classification algorithm to find the
+more relevant parameters in the model to produce a low $\chi^2$
+result.
+
+Using the total number of degrees of freedom, $d.o.f.=104$ we divide
+the results in two classes: low $\chi^2/d.o.f.<35$ and high
+$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}\jefr{We
+  chose $35$ to match the cut that we used to make the  integrated
+  probability distributions. However the nuber itself is
+  arbitrary. Ideally we should only chose models with $\chi^/dof$
+  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
+  models in that range.}
+The algorithm uses $500$ trees for the classification and a
+maximum of $3$ depth levels. 
+To check for stability we repeat the computation $10$ times by
+randomly subsampling the input data to use $80\%$ of the data as
+the training set.
+
+Figure \ref{fig:tree} shows as an illustration the results for a
+single classification tree.
+The tree starts with $28$ and $1962$ models in the low and high
+$\chi^2/d.o.f.$ classes, respectively. 
+We find that the best classification
+yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
+classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
+$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
+The split in two classes is not perfect. 
+This means that these 3 parameters are the most useful parameters
+in finding models with low $\chi^2/d.o.f.$.
+Not having a perfect classification using these three parameter only,
+shows that some combinations of the other 11 parameters are also
+relevant to find a good fit.
+
+The results of the random forest classifier yield that the clump outflow velocity
+$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
+that the \lya emission comes from the clumps $P_{\rm cl}$, are the
+most influential parameters in finding a model with low
+$\chi^2/d.o.f.$.
+
+Furthermore, considering the sparse sampling of parameter space and the results
+from the random forest classifier, it is safer to consider that
+the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
+  cl}$ are actually lower/upper/lower bounds, respectively.
+\mg{This is interesting. Why do you think that? Could we use that to
+  increase the quoted errors? I am worried that the referee will
+  complain about the small errors.} \jefr{The referee didn't complain
+  about the small errors.}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{tree_result.pdf}
+\caption{Classification tree example. 
+The aim is to find the parameters that can be used to separate the
+results in two classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
+Each box describes the condition over the parameter of interest, the
+level of sample impurity, the total number of samples and the value of the
+number of samples in each class.  
+In this example we randomly sample $80\%$ of the full data set of models to
+start with $28$ models in the first class and
+$1962$ models in the second class; the best way to increase the
+probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
+fourth bottom box, from left to the right)
+is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
+the clump velocity dispersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
+probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
+The final classification is not perfect, showing that all other
+parameters are also important but these three are the most relevant.  
+\label{fig:tree}}
+\end{center}
+\end{figure*}
+
 \end{document}

### 2017-07-13 paper/paper.tex
update on the 1sigma test

@@
 In addition, due to the cooling properties of gas multiphase media are expected
-in a range of astrophysical systems \citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.
+in a range of astrophysical systems
+\citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.
 
@@
 
-As a test, we also run a small set of $100$ additional radiative
+As a test we run a small set of $100$ additional radiative
 transfer simulations with random values for all parameters, except for
-$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
+$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
 constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
-\mg{Is $1\sigma$ correct?}\jefr{What do you mean with
-  that question?}
-Consistent with the results from the random forest algorithm,
-illustrated by the classification tree of Figure \ref{fig:tree},
-
-Having constrained only 3 parameters, one might wonder why the other 11
+That is we have a $30\%$ chance to find good models compared with the
+lower $1\%$ success rate if the parameters were unconstrained. 
+\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
+  $P_{cl}$ were run within $1\sigma$. All the other parameters were unconstrained.}
+
+Having constrained only 3 parameters one might wonder why the other 11
 parameters do not seem to matter. 
-However, this view is misleading because merely the best-fit values of (some of) those $3$ parameters, i.e., the corresponding constraint to a given sub-region in the parameter space, make the other parameters less important.
-For instance, in our case the large value of $P_{\rm cl}$ makes radiative transfer effects, and therefore other parameters such as the clump column density less relevant for the emergent line profile.
-However, for instance larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce additional radiative transfer effects and thus increase the number of relevant parameters \citep[see ][for details]{2017arXiv170406278G}.
+However, this view is misleading because merely the best-fit values of
+(some of) those $3$ parameters, i.e., the corresponding constraint to
+a given sub-region in the parameter space, make the other parameters
+less important. 
+For instance, in our case the large value of $P_{\rm cl}$ makes
+radiative transfer effects, and therefore other parameters such as the
+clump column density less relevant for the emergent line
+profile. However, for instance larger values of $f_{\rm cl}$ --
+outside the here considered parameter range -- would re-introduce
+additional radiative transfer effects and thus increase the number of
+relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
 This means that even  

### 2017-07-13 paper/paper.tex
questions

@@
 (thin line). 
-
 The fit to the observations is not perfect. 
@@
 $10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
-This does not mean the other parameters do not influence the resulting
-spectra at all; it means that they cannot be constrained from \tol's
+All the other parameters cannot be constrained from \tol's
 observations.
@@
 is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
-$v_{\infty}$ \& $\beta_{\rm cl}$. 
+$v_{\infty,{\rm cl}}$ \& $\beta_{\rm cl}$. 
 Furthermore, the relatively low mean number of clumps per line of
@@
 transfer simulations with random values for all parameters, except for
-$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $1\sigma$
+$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
 constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
-That is we have a $30\%$ chance to find good models compared with the
-lower $1\%$ success rate if the parameters were unconstrained. 
+That is, we have a $30\%$ chance to find good models, which is
+significanty higher than the lower $1\%$ success rate if the
+parameters were unconstrained.  
 \mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
-  $P_{cl}$ were run within $1\sigma$. All the other parameters were unconstrained.}
+  $P_{cl}$ were run within $3\sigma$. All the other parameters,
+  including $v_{\infty}$were
+  unconstrained.}
 
@@
 parameters do not seem to matter.
-However, this view is misleading because merely the best-fit values of
-(some of) those $3$ parameters, i.e., the corresponding constraint to
-a given sub-region in the parameter space, make the other parameters
-less important. 
-For instance, in our case the large value of $P_{\rm cl}$ makes
-radiative transfer effects, and therefore other parameters such as the
-clump column density less relevant for the emergent line
-profile. However, for instance larger values of $f_{\rm cl}$ --
-outside the here considered parameter range -- would re-introduce
+In our case this can be explained by the large value of $P_{\rm cl}$
+favored by \tol's observations. 
+A large proability of having \lya\ photons emitted in the clumps
+makes radiative transfer effects, and therefore other parameters such
+as the clump column density, less relevant for the emergent line
+profile.
+
+\jefr{I find this paragraph confusing. Discussing an hypotetical case where
+all parameters matter undermines the explanation of our concrete case
+where only some parameters matter more. Probably we can remove it}.
+{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
 additional radiative transfer effects and thus increase the number of
@@
 a few parameters \citep{Gronke2016}, the rest of parameters
-affect the line profile at a level that cannot be neglected,
-\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
-i.e. we cannot randomly pick 11 random values for these
-parameters and expect to fit the line profile while only varying the
-other 3
-
-We cannot discard that another region of parameter space
+affect the line profile at a level that cannot be neglected.}
+
+However, we cannot discard that another region of parameter space
 could also yield a good fit to the observed line-profile.
@@
 future with, e.g., a higher sampling of the parameter space once new 
-observations  clarify the kinematic nature of \tol \footnote{In
+observations  clarify the kinematic nature of \tol.In
   Section \S \ref{sec:conclusions} we describe  in more detail what
   kind of observations could be performed in the near future to
-  improve our understanding of \tol's kinematics.}.
+  improve our understanding of \tol's kinematics.
 
@@
 velocity of $\sim350$ \kms\ is too high for such a low
-mass system.  \mg{I am confused -- are much lower rotational velocities not exclude by the priors used?}
+mass system.  \mg{I am confused -- are much lower rotational
+  velocities not exclude by the priors used?}\jefr{Yes, they are
+  discarded, but here we are talking about the most likely value of
+  350 km/s.}
 \tol's inferred rotational velocity is larger than the

### 2017-07-13 paper/paper.tex
restructure discussion of multiphase

@@
 
-With $14$ free parameters our first concern is discovering which are
-the parameters that can be safeley constrained by \tol's line shape.
-
-From the K-S tests we confirm that only 3 parameters 
-can be constrained by observations;
+With $14$ free parameters our first concern is discovering which 
+parameters matter the most.
+From the K-S tests we find that only 3 parameters 
+are confidently constrained by \tol's line shape;
 $v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
 $10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
-All the other parameters cannot be constrained from \tol's
-observations.
-
-The best models are shown in Figure \ref{multiphaseresults}.
+
+This illustrated by the results shown in Figure \ref{multiphaseresults}.
 Left column shows the difference between the integrated distributions
-of the full sample (2500 input models) and the models with the lowest
+of the full sample (2500 input models) and the $1\%$ models with the lowest
 $\chi^2/d.o.f.$.  
@@
 \jefr{The small uncertainty only says that the increase in
-  $\chi^2/dof$ is very steep. I don't think you can get larger errors
-  with the available date. By simple inspection of Figure 2 we can
-  see that the errors will be small with the data we have. The
+  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
+  with the available data. Simple inspection of Figure 2 shows
+  that the errors will be small with the data we have. The
   paremeter uncertainty roughly corresponds to the width of the parabola
   when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
-  have there is a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
+  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
   and the nearest data point. }
@@
 Due to the large fraction of \lya photons being emitted within the
-moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile represents
-the kinematics of the clumps, that is, the width of the intrinsic line
+moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile follows 
+the clump kinematics. In other words, the width of the intrinsic line
 is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
-$v_{\infty,{\rm cl}}$ \& $\beta_{\rm cl}$. 
+$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.. 
 Furthermore, the relatively low mean number of clumps per line of
-sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion
-of the clumps implies the  existence of low-density inter-clump 
-regions where \lya photons can freely propagate which leads to an
-emergent spectrum close to the intrinsic one as well as to the high
+sight, $f_{\mathrm{cl}}$, combined with the high velocity dispersion
+of the clumps implies existence of low-density inter-clump 
+regions where \lya photons can freely propagate.
+This gives result to an emergent spectrum close to the intrinsic one, explaining the high
 flux at line center as observed.
+
 Because the width of the observable spectrum is hence set primarily by
@@
 $50$\kms.
+
+Having constrained only 3 parameters one might wonder why the other 11
+parameters do not seem to matter.
+In our case this can be explained by the large value of $P_{\rm cl}$
+favored by \tol's observations. 
+A large proability of having \lya\ photons emitted in the clumps
+makes radiative transfer effects, and therefore other parameters such
+as the clump column density, less relevant for the emergent line
+profile.
+
+\jefr{I find this paragraph confusing. Discussing an hypotetical case where
+all parameters matter undermines the explanation of our concrete case
+where only some parameters matter more. Probably we can remove it}.
+{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
+additional radiative transfer effects and thus increase the number of
+relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
+This means that even  
+if for clumply models the line profile is most sensitive to only
+a few parameters \citep{Gronke2016}, the rest of parameters
+affect the line profile at a level that cannot be neglected.}
 
@@
   unconstrained.}
-
-Having constrained only 3 parameters one might wonder why the other 11
-parameters do not seem to matter.
-In our case this can be explained by the large value of $P_{\rm cl}$
-favored by \tol's observations. 
-A large proability of having \lya\ photons emitted in the clumps
-makes radiative transfer effects, and therefore other parameters such
-as the clump column density, less relevant for the emergent line
-profile.
-
-\jefr{I find this paragraph confusing. Discussing an hypotetical case where
-all parameters matter undermines the explanation of our concrete case
-where only some parameters matter more. Probably we can remove it}.
-{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
-additional radiative transfer effects and thus increase the number of
-relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
-This means that even  
-if for clumply models the line profile is most sensitive to only
-a few parameters \citep{Gronke2016}, the rest of parameters
-affect the line profile at a level that cannot be neglected.}
 

### 2017-07-13 paper/paper.tex
new references

@@
 \newcommand{\esa}{erg s$^{-1}$}
-\newcommand{\kms}{km s$^{-1}$}
+\newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
 \newcommand{\apj}{ApJ}  
@@
 is unlikely that the clump velocity dispersion is lower than
-$50$\kms.
+$50$ \kms.
 
@@
   $P_{cl}$ were run within $3\sigma$. All the other parameters,
-  including $v_{\infty}$were
+  including $v_{\infty}$, were
   unconstrained.}
@@
 chances to be correct?  
-We discard the rotation model by considering that the rotational
-velocity of $\sim350$ \kms\ is too high for such a low
-mass system.  \mg{I am confused -- are much lower rotational
+We discard the rotation model by considering that the prefered rotational
+velocity of $V_{m}\sim350$ \kms is of the same order as the largest rotational velocity of giant
+disc galaxies that have two orders of magnitude more baryonic mass
+than \tol\ \citep{2015MNRAS.448.1767C}. 
+\mg{I am confused -- are much lower rotational
   velocities not exclude by the priors used?}\jefr{Yes, they are
@@
   350 km/s.}
-\tol's inferred rotational velocity is larger than the
-Milky Way's ($\sim200$\kms) while its baryonic mass is one order
-of magnitude smaller. 
+
 Furthermore, \tol's structural properties seem to be similar to known dwarf
@@
 \left(\frac{\sigma}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)
-M_{\odot}, 
+M_{\odot}. 
 \end{equation}
-%
+
 Assuming that the \lya emission is entirely powered by star formation 
@@
 
-\begin{thebibliography}{}
-
-\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
-  et~al.}{2014}]{2014Msngr.157...13B}
-{Bacon} R.  et~al., 2014, The Messenger, 157, 13
-
-\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur} \&
-  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
-{Begum} A.,  {Chengalur} J.~N.,    {Karachentsev} I.~D.,  2005, \aap, 433, L1
-
-\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham} \&
-  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
-{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,    {Chaffee} F.~H.,
-  1998, \apjl, 498, L93
-
-\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
-{Dijkstra} M.,  2014, \pasa, 31, e040
-
-\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
-  {Kramer}}{2012}]{2012MNRAS.424.1672D}
-{Dijkstra} M.,  {Kramer} R.,  2012, \mnras, 424, 1672
-
-\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz} \& {Wyithe}}{{Dijkstra}
-  et~al.}{2007}]{2007MNRAS.377.1175D}
-{Dijkstra} M.,  {Lidz} A.,    {Wyithe} J.~S.~B.,  2007, \mnras, 377, 1175
-
-\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
-  {Werner}, {Moustakas}, {Willmer} \& {Vanzi}}{{Engelbracht}
-  et~al.}{2008}]{2008ApJ...678..804E}
-{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
-  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,    {Vanzi} L.,  2008,
-  \apj, 678, 804
-
-\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
-{Erb} D.~K.  et~al., 2014, \apj, 795, 33
-
-\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky} \& {Meidt}}{{Eskew}
-  et~al.}{2012}]{2012AJ....143..139E}
-{Eskew} M.,  {Zaritsky} D.,    {Meidt} S.,  2012, \aj, 143, 139
-
-\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang} \&
-  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
-{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,    {Goodman} J.,  2013, \pasp,
-  125, 306
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
-  {Knollmann}, {Cuesta} \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
-{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
-  {Cuesta} A.~J.,    {Prada} F.,  2011, \mnras, 415, 3666
-
-\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva} \&
-  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
-{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,    {Thuan}
-  T.~X.,  2001, \aj, 121, 169
-
-\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero} \&
-  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
-{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,    {Dijkstra} M.,  2014,
-  \apj, 795, 120
-
-\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}} \&
-  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
-{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,    {D{\'{\i}}az} {\'A}.~I.,
-   2013, \mnras, 434, 2491
-
-\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
-  et~al.}{2007}]{2007ApJ...671..278G}
-{Gawiser} E.  et~al., 2007, \apj, 671, 278
-
-\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta} \& {van der
-  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
-{Geha} M.,  {Guhathakurta} P.,    {van der Marel} R.~P.,  2003, \aj, 126, 1794
-
-\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
-  Weare}{2010}]{goodman2010ensemble}
-Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
-  computational science, 5, 65
-
-\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu} \& {Wyithe}}{{Greig}
-  et~al.}{2013}]{2013MNRAS.431.1777G}
-{Greig} B.,  {Komatsu} E.,    {Wyithe} J.~S.~B.,  2013, \mnras, 431, 1777
-
-\bibitem[\protect\citeauthoryear{{Gronke}, {Bull} \& {Dijkstra}}{{Gronke}
-  et~al.}{2015}]{2015ApJ...812..123G}
-{Gronke} M.,  {Bull} P.,    {Dijkstra} M.,  2015, \apj, 812, 123
-
-\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
-  {Dijkstra}}{2016}]{Gronke2016}
-{Gronke} M.,  {Dijkstra} M.,  2016, \apj, 826, 14
-
-\bibitem[\protect\citeauthoryear{{Gronke}, {Dijkstra}, {McCourt} \&
-  {Oh}}{{Gronke} et~al.}{2017}]{2017arXiv170406278G}
-{Gronke} M.,  {Dijkstra} M.,  {McCourt} M.,    {Oh} S.~P.,  2017, ArXiv
-  e-prints
-
-\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
-{Harrington} J.~P.,  1973, \mnras, 162, 43
-
-\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
-  et~al.}{2004}]{2004AJ....128.2073H}
-{Hayashino} T.  et~al., 2004, \aj, 128, 2073
-
-\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
-{Hayes} M.,  2015, \pasa, 32, e027
-
-\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
-  et~al.}{2016}]{Herenz16}
-{Herenz} E.~C.  et~al., 2016, \aap, 587, A78
-
-\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
-  {Storey}}{1987}]{Hummer1987}
-{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mnras, 224, 801
-
-\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke} \&
-  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
-{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,    {Thuan}
-  T.~X.,  2004, \aap, 421, 539
-
-\bibitem[\protect\citeauthoryear{{Kennicutt}
-  Jr.}{{Kennicutt}}{1998}]{Kennicutt98}
-{Kennicutt} Jr. R.~C.,  1998, \araa, 36, 189
-
-\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
-  {Malhotra} \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
-{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,
-  {Wang} J.,  2007, \apj, 668, 15
-
-\bibitem[\protect\citeauthoryear{{Laursen}, {Duval} \& {{\"O}stlin}}{{Laursen}
-  et~al.}{2013}]{Laursen2013ApJ...766..124L}
-{Laursen} P.,  {Duval} F.,    {{\"O}stlin} G.,  2013, \apj, 766, 124
-
-\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
-  {Rybicki}}{1999}]{LoebRybicki}
-{Loeb} A.,  {Rybicki} G.~B.,  1999, \apj, 524, 527
-
-\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
-{Martin} C.~L.,  1998, \apj, 506, 222
-
-\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
-  {Leitherer}, {Terlevich} \& {Terlevich}}{{Mas-Hesse}
-  et~al.}{2003}]{mashesse03}
-{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
-  {Terlevich} R.~J.,    {Terlevich} E.,  2003, \apj, 598, 858
-
-\bibitem[\protect\citeauthoryear{{McCourt}, {Oh}, {O'Leary} \&
-  {Madigan}}{{McCourt} et~al.}{2016}]{2016arXiv161001164M}
-{McCourt} M.,  {Oh} S.~P.,  {O'Leary} R.~M.,    {Madigan} A.-M.,  2016, ArXiv
-  e-prints
-
-\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
-  {Ostriker}}{1977}]{1977ApJ...218..148M}
-{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \apj, 218, 148
-
-\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
-  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
-  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
-{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \apj, 828, 5
-
-\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
-{Neufeld} D.~A.,  1991, \apjl, 370, L85
-
-\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s} \&
-  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
-{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,    {Fricke} K.~J.,  2003,
-  \aap, 410, 481
-
-\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey} \& {Baugh}}{{Orsi}
-  et~al.}{2012}]{Orsi12}
-{Orsi} A.,  {Lacey} C.~G.,    {Baugh} C.~M.,  2012, \mnras, 425, 87
-
-\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh} \& {Infante}}{{Orsi}
-  et~al.}{2008}]{2008MNRAS.391.1589O}
-{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,    {Infante} L.,  2008, \mnras, 391,
-  1589
-
-\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
-  et~al.}{2014}]{LARS}
-{{\"O}stlin} G.  et~al., 2014, \apj, 797, 11
-
-\bibitem[\protect\citeauthoryear{{Ott}, {Walter} \& {Brinks}}{{Ott}
-  et~al.}{2005}]{2005MNRAS.358.1453O}
-{Ott} J.,  {Walter} F.,    {Brinks} E.,  2005, \mnras, 358, 1453
-
-\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
-  {Gonz{\'a}lez}, {Guaita} \& {Infante}}{{Padilla}
-  et~al.}{2010}]{2010MNRAS.409..184P}
-{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
-  {Guaita} L.,    {Infante} L.,  2010, \mnras, 409, 184
-
-\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
-  {Peebles}}{1967}]{PartridgePeebles}
-{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \apj, 147, 868
-
-\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero} \&
-  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
-{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,    {Mu{\~n}oz-Cuartas} J.~C.,
-  2016, \apj, 832, 169
-
-\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
-  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
-{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
-  {Primack} J.,  2012, \mnras, 423, 3018
-
-\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
-  {Martin}}{2007}]{pustilnikmartin07}
-{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \aap, 464, 859
-
-\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
-  et~al.}{2015}]{2015ApJ...805...14R}
-{Rivera-Thorsen} T.~E.  et~al., 2015, \apj, 805, 14
-
-\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
-{Roth} M.~M.  et~al., 2005, \pasp, 117, 620
-
-\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
-  {Reddy}, {Bogosavljevi{\'c}}, {Rudie} \& {Rakic}}{{Steidel}
-  et~al.}{2010}]{2010ApJ...717..289S}
-{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
-  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,    {Rakic} O.,  2010, \apj, 717, 289
-
-\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada} \& {van der
-  Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
-{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,    {van der Hulst} J.~M.,
-  2009, \aap, 493, 871
-
-\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
-{Tasitsiomi} A.,  2006, \apj, 645, 792
-
-\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov} \& {Gnedin}}{{Tassis}
-  et~al.}{2008}]{2008ApJ...672..888T}
-{Tassis} K.,  {Kravtsov} A.~V.,    {Gnedin} N.~Y.,  2008, \apj, 672, 888
-
-\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
-  {Izotov}}{1997}]{Thuan97}
-{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, 489, 623
-
-\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves} \&
-  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
-{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,    {Wolf} J.,  2011, \apj,
-  726, 108
-
-\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel} \&
-  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
-{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,    {Rudie} G.~C.,  2016,
-  \apj, 832, 171
-
-\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer} \&
-  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
-{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,    {Hayes} M.,  2015, \aap,
-  578, A7
-
-\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer} \&
-  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
-{Verhamme} A.,  {Schaerer} D.,    {Maselli} A.,  2006, \aap, 460, 397
-
-\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
-  {Morimoto} \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
-{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
-  {Umemura} M.,  2012, \apj, 751, 29
-
-\end{thebibliography}
-
 \appendix
@@
 
-Using the total number of degrees of freedom, $d.o.f.=104$ we divide
+%Using the total number of degrees of freedom, $d.o.f.=104$ 
+We divide
 the results in two classes: low $\chi^2/d.o.f.<35$ and high
@@
   probability distributions. However the nuber itself is
-  arbitrary. Ideally we should only chose models with $\chi^/dof$
+  arbitrary to have the $1\%$ of the initial number of models. 
+Ideally we should only chose models with $\chi^/dof$
   higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
@@
 $\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
-The split in two classes is not perfect. 
 This means that these 3 parameters are the most useful parameters
 in finding models with low $\chi^2/d.o.f.$.
-Not having a perfect classification using these three parameter only,
-shows that some combinations of the other 11 parameters are also
-relevant to find a good fit.
 
@@
 probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
-The final classification is not perfect, showing that all other
-parameters are also important but these three are the most relevant.  
+The final classification shows that these three are the most relevant
+to select the best models.
 \label{fig:tree}}

### 2017-07-13 paper/paper.tex
appendix edited

--- 2017-07-13 paper/paper.tex
@@
 
-We also a Kolmogorov-Smirnov (K-S) test to compare each parameter
+We run a Kolmogorov-Smirnov (K-S) test to compare each parameter
 distribution in the best $25$ models against the parent distribution
@@
 distribution from the global sample of $2500$ models.  
+As a complement (Appendix \ref{appendix}) we also use a random forest
+classifier to find the most important parameters in selecting a low
+$\chi^2$ mode.
 
@@
 $v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
-$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
+$10^{-4}$) and $P_{\rm cl}$ (p-value $10^{-4}$).
 
@@
 of the full sample (2500 input models) and the $1\%$ models with the lowest
-$\chi^2/d.o.f.$.  
+$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
+$d.o.f.=104$. 
 The right column shows the actual $\chi^2/d.o.f.$ 
@@
 \jefr{I find this paragraph confusing. Discussing an hypotetical case where
-all parameters matter undermines the explanation of our concrete case
+all parameters are important undermines the explanation of our concrete case
 where only some parameters matter more. Probably we can remove it}.
@@
 
-As a test we run a small set of $100$ additional radiative
+{\bf As a test we run a small set of $100$ additional radiative
 transfer simulations with random values for all parameters, except for
@@
 significanty higher than the lower $1\%$ success rate if the
-parameters were unconstrained.  
+parameters were unconstrained.  }
 \mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
   $P_{cl}$ were run within $3\sigma$. All the other parameters,
-  including $v_{\infty}$were
-  unconstrained.}
+  including $v_{\infty}$, were
+  unconstrained. Should we mention this test given that we didn't run
+  with a constrain on $v_{\infty}$?}
 
@@
 chances to be correct?  
-We discard the rotation model by considering that the rotational
-velocity of $\sim350$ \kms\ is too high for such a low
-mass system.  \mg{I am confused -- are much lower rotational
+We discard the rotation model by considering that the prefered rotational
+velocity of $V_{m}\sim350$ \kms\ is of the same order as the largest rotational velocity of giant
+disc galaxies that have two orders of magnitude more baryonic mass
+than \tol\ \citep{2015MNRAS.448.1767C}. 
+\mg{I am confused -- are much lower rotational
   velocities not exclude by the priors used?}\jefr{Yes, they are
@@
 %\bibliography{references}
-
 \begin{thebibliography}{}
@@
 {Begum} A.,  {Chengalur} J.~N.,    {Karachentsev} I.~D.,  2005, \aap, 433, L1
+
+\bibitem[\protect\citeauthoryear{{Courtois}, {Zaritsky}, {Sorce} \&
+  {Pomar{\`e}de}}{{Courtois} et~al.}{2015}]{2015MNRAS.448.1767C}
+{Courtois} H.~M.,  {Zaritsky} D.,  {Sorce} J.~G.,    {Pomar{\`e}de} D.,  2015,
+  \mnras, 448, 1767
 
@@
 
-Using the total number of degrees of freedom, $d.o.f.=104$ we divide
+We divide
 the results in two classes: low $\chi^2/d.o.f.<35$ and high

### 2017-07-13 paper/paper.tex
updated references

--- 2017-07-13 paper/paper.tex
@@
-\documentclass[a4,useAMS,usenatbib,usegraphicx]{mn2e} 
+\documentclass[a4paper,fleqn,usenatbib]{mnras}
 %=========================================================================
@@
 \usepackage{caption}
-\usepackage[draft]{hyperref}
+\usepackage{hyperref}
+\usepackage{bm}
 %Non reposionated tables
@@
 \newcommand{\kms}{\ifmmode\mathrm{km\ s}^{-1}\else km s$^{-1}$\fi}
-\newcommand{\apj}{ApJ}  
-\newcommand{\jcap}{JCAP}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\pasa}{PASA}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}    
 \newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
@@
 The multiphase model requires a clump velocity dispersion of
-at least \sigmaclump\ with outflows of \inftyclump\, while the
+\sigmaclump\ with outflows of \inftyclump\, while the
 bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
 We argue that the multiphase model has more chances to be correct.
-The clump velocity dispersion implies a dynamical mass of at least $2\times
+The clump velocity dispersion implies a dynamical mass of $2\times
 10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
-explained if \tol\ is hosted by a dark matter halo of at least
-$6\times 10^{11}$ M$_{\odot}$.
-If future kinematic maps of \tol\ confirm the velocities suggested by the
-multiphase model, it would provide additional support to expect this
-condition to be present  in primordial \lya emitting galaxies.  
+explained if \tol\ is hosted by a dark matter halo $6\times 10^{11}$
+M$_{\odot}$. If future kinematic maps of \tol\ confirm the velocities
+suggested by the multiphase model, it would provide additional support
+to expect this condition to be present  in primordial \lya emitting
+galaxies.   
 \end{abstract}
@@
 \citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
-They are applicable only in cases of highly symmetrical
-conditions of the gaseous hydrogen distribution in the galaxy model,
-which are hardly met in real astrophysical systems. 
+They are applicable only in highly idealized conditions that
+are hardly met in real astrophysical systems. 
 For these reasons the interpretation of \lya observations
@@
 \citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
-In addition, due to the cooling properties of gas multiphase media are expected
+In addition, due to the cooling properties of gas, multiphase media are expected
 in a range of astrophysical systems
@@
 
-The motivation for the rotation without outflows (as presented in
-\cite{GaravitoCamargo2014}) is that dwarf galaxies show coherent
+The motivation for the rotation without outflows as presented in
+\citep[as presented in]{GaravitoCamargo2014} is that dwarf galaxies show coherent
 rotation features  \citep{2009A&A...493..871S} and it is expected that
@@
 The idealized multiphase model consists of spherical, cold, dense
-clumps of neutral hydrogen (and dust) embedded in a hot, ionized
+clumps of neutral hydrogen and dust embedded in a hot, ionized
 medium \citep{Gronke2016}. 
@@
 
-We also a Kolmogorov-Smirnov (K-S) test to compare each parameter
+We run a Kolmogorov-Smirnov (K-S) test to compare each parameter
 distribution in the best $25$ models against the parent distribution
 of $2500$ models. 
-From a p-value $<0.05$ for a given model parameter, we conclude that
+If we obtain a p-value $<0.05$ we conclude that
 this parameter can be constrained from the observations, as the distribution for
@@
 distribution from the global sample of $2500$ models.  
+In the Appendix \ref{appendix} we complement this analysis using a
+random forest classifier to find the most important parameters in
+selecting a low $\chi^2$ model.
 
@@
 We estimate the 1-$\sigma$ uncertainty from a parabolic fit to the
-$\chi^2$ as a function of the constrained parameters around its
+$\chi^2$ as a function of the best constrained parameters around its
 corresponding minimum.
@@
 
-The rotation model corresponds to the work presented in
-\citep{GaravitoCamargo2014} based on the Monte Carlo code
+The rotation model corresponds to the work presented by
+\cite{GaravitoCamargo2014} based on the Monte Carlo code
 \texttt{CLARA} \citep{CLARA}. 
@@
 $v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
-$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
+$10^{-4}$) and $P_{\rm cl}$ (p-value $10^{-4}$).
 
-This illustrated by the results shown in Figure \ref{multiphaseresults}.
+The low p-values are illustrated by the results shown in Figure \ref{multiphaseresults}.
 Left column shows the difference between the integrated distributions
 of the full sample (2500 input models) and the $1\%$ models with the lowest
-$\chi^2/d.o.f.$.  
+$\chi^2/d.o.f.$, where we use the total number of degrees of freedom,
+$d.o.f.=104$. 
 The right column shows the actual $\chi^2/d.o.f.$ 
@@
 is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
-$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.. 
+$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.
 Furthermore, the relatively low mean number of clumps per line of
@@
 This gives result to an emergent spectrum close to the intrinsic one, explaining the high
-flux at line center as observed.
+flux at the line's center.
 
@@
 narrower line and thus a worse fit. 
-From the lower right panel in Figure \ref{multiphaseresults} we find that it
-is unlikely that the clump velocity dispersion is lower than
-$50$ \kms.
+From the lower right panel in Figure \ref{multiphaseresults} we find
+that in fact it is unlikely that the clump velocity dispersion is
+lower than $50$ \kms.
 
@@
 significanty higher than the lower $1\%$ success rate if the
-parameters were unconstrained.  
+parameters were unconstrained.  }
 \mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
@@
   including $v_{\infty}$, were
-  unconstrained.}
+  unconstrained. Should we mention this test given that we didn't run
+  with a constrain on $v_{\infty}$?}
 
@@
 future with, e.g., a higher sampling of the parameter space once new 
-observations  clarify the kinematic nature of \tol.In
-  Section \S \ref{sec:conclusions} we describe  in more detail what
-  kind of observations could be performed in the near future to
-  improve our understanding of \tol's kinematics.
+observations  clarify the kinematic nature of \tol. 
+In Section \S \ref{sec:conclusions} we describe  in more detail what
+kind of observations could be performed in the near future to improve
+our understanding of \tol's kinematics.
 
@@
 chances to be correct?  
-We discard the rotation model by considering that the prefered rotational
-velocity of $V_{m}\sim350$ \kms is of the same order as the largest rotational velocity of giant
+We argue that that the rotation model should be discarded by
+considering that the prefered rotational velocity of $V_{m}\sim350$
+\kms\ is of the same order as the largest rotational velocity of giant
 disc galaxies that have two orders of magnitude more baryonic mass
@@
 Furthermore, \tol's structural properties seem to be similar to known dwarf
-elliptical galaxies. 
-The sample of 7 dwarf ellipticals (dE) observed by
-\cite{2003AJ....126.1794G} show similar properties as \tol. 
+elliptical (dE) galaxies. 
+The sample of 7 dE galaxies observed by
+\cite{2003AJ....126.1794G} shows similar properties as \tol. 
 For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
@@
 times the estimated baryonic mass in \tol.
-Considering that the results for $\sigma_{\rm{cl}}$ are most probably
-a lower bound, the results for the dynamical mass should also be
-considered as a lower bound.
 
@@
 mass can be explained if \tol\ is hosted by a dark matter halo of at
-least $6\times 10^{11}$ M$_{\odot}$ in virial mass. 
+$\sim 6\times 10^{11}$ M$_{\odot}$ in virial mass. 
 This estimate is based on computing the integrated mass profile of a
@@
   The dynamical mass estimates for \tol\ are consistent with the
-  galaxy being hosted by a dark matter halo of at least
-  $6\times10^{11}$ M$_{\odot}$ in mass.
+  galaxy being hosted by a dark matter halo of
+  $\sim 6\times10^{11}$ M$_{\odot}$ in mass.
     \label{fig:mass}} 
@@
 writing stages of this paper.
+We are thankful to the community developing and maintining open source
+packages fundamental to our work: Jupyter notebook \citep{IPython,jupyter},
+matplotlib \citep{matplotlib}, astropy \citep{astropy} and
+scikit-learn \citep{scikit-learn}.
 
-\bibliographystyle{mn2e}
-%\bibliography{references}
+\bibliographystyle{mnras}
+\bibliography{references}
 
@@
 As a complement to the K-S tests on the multiphase data 
-we apply a random forest classification algorithm to find the
+we apply a random forest classification algorithm
+\citep{james2014introduction} to find the
 more relevant parameters in the model to produce a low $\chi^2$
@@
 
-%Using the total number of degrees of freedom, $d.o.f.=104$ 
 We divide
 the results in two classes: low $\chi^2/d.o.f.<35$ and high
-$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}\jefr{We
+$\chi^2/d.o.f.>35$, that is the limit that divides the best $1\%$ of
+the models from the rest. \mg{Why was $35$ chosen as a boundary?}\jefr{We
   chose $35$ to match the cut that we used to make the  integrated
@@
 
-Furthermore, considering the sparse sampling of parameter space and the results
+{\bf Furthermore, considering the sparse sampling of parameter space and the results
 from the random forest classifier, it is safer to consider that
 the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
-  cl}$ are actually lower/upper/lower bounds, respectively.
+  cl}$ are actually lower/upper/lower bounds, respectively.}
 \mg{This is interesting. Why do you think that? Could we use that to
@@
   complain about the small errors.} \jefr{The referee didn't complain
-  about the small errors.}
+  about the small errors. And now that I see this with a bit more of
+  perspective, the tree classification always work with 'larger
+  than/less than' dualities. It would be unfair/unjustified to use that to justify
+our results as a lower bound. I suggest we remove this paragraph.}
 

### 2017-07-13 paper/old_paper.tex
new command in old paper
latest

--- 2017-03-13 paper/letter.tex
@@
 \usepackage{amssymb} 
-\usepackage {graphicx}
+\usepackage{graphicx}
+\usepackage{grffile}
 \usepackage[dvips]{epsfig}
@@
 \newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}
-
+\newcommand{\hs}{{\hspace{1mm}}}  
 \newcommand{\tol}{Tololo 1214-277}
-\newcommand{\lya}{Ly$\alpha$}
+\newcommand{\HI}{{\text{H\MakeUppercase{\romannumeral 1}}} }
+\newcommand{\HII}{{\text{H\MakeUppercase{\romannumeral 2}}} }
+\newcommand{\lya}{\ifmmode{{\rm Ly}\alpha}\else Ly$\alpha$\ \fi}
+\newcommand{\cm}{\ifmmode{{\rm cm}}\else cm\fi}
+\newcommand{\ccm}{\,\mathrm{cm}^{-3}}
+\newcommand{\ergps}{\,{\rm erg}\,{\rm s}\ifmmode{}^{-1}\else ${}^{-1}$\fi}
+\newcommand{\Mpch}{\,{\rm Mpc}\,\ifmmode h^{-1}\else $h^{-1}$\fi}
+%\newcommand{\kms}{\,\mathrm{km}\,\mathrm{s}^{-1}}
+\newcommand{\dd}{\mathrm{d}}
+\newcommand{\vek}[1]{\bm{#1}}
+%\newcommand{\lya}{Ly$\alpha$}
 \newcommand{\hb}{H$\beta$}
@@
 \newcommand{\kms}{km s$^{-1}$}
-\newcommand{\apj}{ApJ}  
-\newcommand{\jcap}{JCAP}  
-\newcommand{\apjs}{ApJS}  
-\newcommand{\pasa}{PASA}  
-\newcommand{\apjl}{ApJL}  
-\newcommand{\aj}{AJ}  
-\newcommand{\mnras}{MNRAS}  
-\newcommand{\mnrassub}{MNRAS accepted}  
-\newcommand{\aap}{A\&A}  
-\newcommand{\aaps}{A\&AS}  
-\newcommand{\araa}{ARA\&A}  
-\newcommand{\nat}{Nature}  
-\newcommand{\physrep}{PhR}
-\newcommand{\pasp}{PASP}    
-\newcommand{\pasj}{PASJ}    
 \newcommand{\sigmaclump}{$54.3\pm 0.6$ km s$^{-1}$}
@@
 \newcommand{\probaclump}{$0.96\pm 0.01$}
-\def\simgt{\lower.5ex\hbox{\gtsima}}
-\def\simlt{\lower.5ex\hbox{\ltsima}}
+
+\newcommand{\mg}[1]{\textcolor{blue}{\bf MG: \textit{#1}}}
 
@@
 \begin{abstract}
-  Star-forming Compact Dwarf Galaxies (CDGs) resemble the expected
-  pristine conditions of the first galaxies in the Universe.    
-Before the observational detection of the first galaxies becomes
-reality, CDGs are the best systems to test our ideas on primordial
-galaxy formation and evolution.    
+
+Star-forming Compact Dwarf Galaxies (CDGs) 
+resemble the expected pristine conditions of the first galaxies in the
+Universe and are the best systems to test models on primordial galaxy
+formation and evolution. 
 Here we report on one of such CDGs, \tol, which presents
-a broad symmetric \lya\ line emission that had evaded theoretical
-interpretation so far. 
-In this paper we explain these features by two different kinematic models: 
+a broad, single peaked, highly symmetric \lya emission line that had
+evaded theoretical interpretation so far.  
+In this paper we explain these features by two different physically
+motivated kinematic models: 
 an interstellar medium composed by outflowing clumps with 
@@
 rotation.
-It is the first time that an observed \lya\ spectrum can be explained
+It is the first time that an observed \lya spectrum can be explained
 assuming either of these kinematic conditions.
-We find that both models independently require high velocities
-(either a  a clump velocity dispersion of \sigmaclump\ with outflows of
-\inftyclump\ or a bulk rotation of $348^{+75}_{-48}$ km s$^{-1}$)
-consistent with a dynamical mass of at 
-least a $10^{10}$ M$_{\odot}$, ten times larger than its estimated baryonic mass.   
-We argue that a possible explanation for this excess of
-dynamical mass is the presence of a supermassive black hole at the
-center of \tol. 
-This work demonstrates the importance of considering multiphase
-kinematics and rotation among the possible conditions shaping the
-\lya\ spectra of the first galaxies.  
-Additionally, if future kinematic maps of \tol\ confirm the 
-velocities found by our models, it would provide new
-evidence for dwarf galaxies as hosts of supermassive black
-holes.  
+The multiphase model requires a clump velocity dispersion of
+at least \sigmaclump\ with outflows of \inftyclump\, while the
+bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
+We argue that the multiphase model has more chances to be correct.
+The clump velocity dispersion implies a dynamical mass of at least $2\times
+10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
+explained if \tol\ is hosted by a dark matter halo of at least
+$6\times 10^{11}$ M$_{\odot}$.
+If future kinematic maps of \tol\ confirm the velocities suggested by the
+multiphase model, it would provide additional support to expect this
+condition to be present  in primordial \lya emitting galaxies.  
 \end{abstract}
@@
 are seen as templates to understand the early galaxy evolution process. 
-Over fifty years ago \citep{PartridgePeebles} it was realized that
-young galaxies could be detected through a strong \lya\ line
-emission.
+Over fifty years ago it was realized that young galaxies could be
+detected through a strong \lya line emission \citep{PartridgePeebles}.
 
@@
 in surveys. 
-The presence of the \lya\ emission line provides confirmation of
-the distance of a galaxy while provides clues about the stellar
+The presence of the \lya emission line gives confirmation of
+the distance to a galaxy and provides clues about the stellar
 population and inter-stellar medium conditions regulating the
-\lya\ emission.
+\lya emission.
 A careful clustering analysis of LAEs can also yield clues about their link
-to dark matter halos \cite{2016ApJ...828....5M}.
+to dark matter halos
+\citep{2004AJ....128.2073H,2007ApJ...671..278G,2007ApJ...668...15K,2008MNRAS.391.1589O,2010MNRAS.409..184P,2013MNRAS.431.1777G,2016ApJ...828....5M}.
 
-The \lya\ emission line is not exclusive of distant galaxies. 
-There are local Universe surveys that target \lya\ emission in nearby
+The \lya emission line is not exclusive of distant galaxies. 
+There are local Universe surveys that target \lya emission in nearby
 dwarf star forming galaxies.
@@
 indicators that might be more difficult to obtain for distant galaxies
-such as morphology, dust attenuation, neutral hydrogen contents and
-ionization state. (see \citep{Hayes15} and references therein for a review.)
+such as galaxy morphology, dust attenuation, neutral hydrogen contents and
+ionization state. See \cite{Hayes15} and references therein for a review.
 
-However, the physical interpretation of \lya\ observations is
+However, the physical interpretation of \lya observations is
 not straightforward \citep{LARS,2015ApJ...805...14R}. 
-This is due to the resonant nature of the \lya\ line. 
-A \lya\ photon follows a diffusion-like process before escaping
+This is due to the resonant nature of the \lya line. 
+A \lya photon follows a diffusion-like process before escaping
 the galaxy or being absorbed by dust. 
@@
 and thermal conditions in the interstellar medium. 
-There are very few analytically tools available to interpret the
-emerging \lya\ line
-\cite{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
-They are applicable only in very few cases of highly symmetrical
-conditions, which are hardly met in real astrophysical systems.
-For these reasons the interpretation of \lya\ observations
+There are few analytical tools available to interpret the
+emerging \lya line
+\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
+They are applicable only in cases of highly symmetrical
+conditions of the gaseous hydrogen distribution in the galaxy model,
+which are hardly met in real astrophysical systems. 
+For these reasons the interpretation of \lya observations
 requires state-of-the-art Monte Carlo radiative transfer simulations.
 
+Observed \lya line profiles usually present a single peak shifted
+redwards from the line's center. 
+Sometimes a double peak is present but the asymmetry persists with 
+the peak on the red side being stronger \citep[e.g.][]{2010ApJ...717..289S,Erb14,Trainor16}. 
+This can be explained as the results of multiple \lya photon
+scatterings through an outflowing shell of neutral Hydrogen
+\citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.
+
 \tol\ is a compact star forming dwarf galaxy that presents a
-strong \lya\ emission \citep{Thuan97} with two puzzling 
-features: the line is symmetric, single peaked and wide around the
-line's center.
-Usually the \lya\ line has an asymmetric single or double peak. 
-These two special features in \tol\ cannot be explained quantitatively
-with conventional shell models
-\citep{Mas-Hesse09,2015A&A...578A...7V,2015ApJ...812..123G}.
+strong \lya emission with puzzling 
+features: the line is highly symmetric, single peaked and broad 
+\citep{Thuan97}.
+This kind of profile also raises the question whether some high
+redshift LAEs have asymmetric lines because the blue half was
+truncated by the intergalactic medium \citep{2007MNRAS.377.1175D}. 
+In this case the \lya radiation could emerge as a low surface
+brightness glow, which may be connected to \lya halos, while also
+influencing the way LAEs can be used as a probe of reionization
+\citep[see the review by][and references therein]{2014PASA...31...40D}.
 
-This kind of profile also raises the question whether some high redshift
-LAEs have asymmetric lines because the blue half was truncated by the
-intergalactic medium \citep{2007MNRAS.377.1175D}. 
-In this case the \lya\ radiation could emerge as a low surface
-brightness glow, which may be connected to \lya\ halos, while also
-influencing the way LAEs can be used as a probe of reionization
-\citep{2014PASA...31...40D}.
+Attempts to explain the atypical \lya features in \tol\ with
+conventional models based on a expanding shell have not been successful
+so far \citep{mashesse03,2015A&A...578A...7V}. 
+This justifies a new study using two new physically motivated
+situations: a multiphase outflowing interstellar medium and bulk rotation for a
+galaxy without outflows.
 
-Here we show how the \tol's \lya\ profile can be explained
-either by  or the recently developed class of complex multiphase models 
-\citep{Gronke2016} or by a simple rotation model
-\citep{GaravitoCamargo2014}. 
-The models we use correspond to simplified geometrical configurations
-to allow a deep exploration of parameter space and gain, for the first time,
-some physical insight into the \tol's kinematic properties.
+The main motivation for the outflowing multiphase model \citep[as presented
+in][]{Gronke2016} is that some dwarf galaxies are expected to
+present outflows.  
+Observationally, outflows have been detected in few local dwarf galaxies
+\citep{1998ApJ...506..222M,2005MNRAS.358.1453O}. 
+Besides, clumpy multiphase outflows are capable to explain \lya features around
+star-forming galaxies
+\citep{2010ApJ...717..289S,2012MNRAS.424.1672D}.
+In addition, due to the cooling properties of gas multiphase media are expected
+in a range of astrophysical systems \citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.
 
-We review first the observational characteristics of
+The motivation for the rotation without outflows (as presented in
+\cite{GaravitoCamargo2014}) is that dwarf galaxies show coherent
+rotation features  \citep{2009A&A...493..871S} and it is expected that
+some of them have high neutral gas contents with long quiescent phases
+without high gas outflows triggered by supernova activity
+\citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.
+
+The models we use correspond to simplified geometrical configurations.
+This allows us to perform a deep exploration of parameter space and
+gain some physical insight into \tol's kinematic properties.
+In this paper we show, for the first time in the literature, that \tol's
+\lya profile can be explicitly modeled by either of these two
+models.
+
+\mg{I would remove the next paragraph as this seems clear and not necessary to start with an ``apology''.}
+We do not claim that our findings discard the existence of different
+undiscovered models that could reproduce the observed features in \tol.
+More involved models with multiple kinematic components can
+in principle also be successful.
+We focus on presenting two simple and successful models that
+manage, for the first time, to account for \tol's \lya line main
+features.
+
+In the next section we review the observational characteristics of
 \tol, then we summarize the main features in the multiphase and
 rotation models to explain how we fit their free parameters 
-to the \tol's \lya\ line shape.
+to the \tol's \lya line shape.
 We use the results to interpret them in terms of the galaxy's
-dynamical mass. 
-We close by discussing the physical scenarios that open up by our
-results and the additional observational information needed to clarify
-the kinematic nature of \tol.
+dynamical mass and argue why the multiphase model should be preferred
+over the rotation model.
+We close by discussing the additional observational information needed
+to clarify the kinematic nature of \tol.
 
 \section{Observations}
+
+\begin{table}
+\begin{center}
+\begin{tabular}{lr}\hline
+$\alpha$(2000)& 12h17min17.1s\\
+$\delta$(2000)& -28d02m32s\\
+$l$, $b$ (deg) & 294, 34\\
+$m_V$ & 17.5\\
+  M$_V$ & -17.6\\ 
+Redshift & $0.026\pm0.001$ \\\hline
+\end{tabular}
+\end{center}
+\caption{Basic observational characteristics of \tol\ 
+  \citep{Thuan97}\label{obstable}} 
+\end{table}
+
+\begin{table*}
+  \centering
+\begin{tabular}{l|lrrl}
+\hline
+  Parameter  & Description & Fiducial value & Allowed range & Units \\ \hline\hline
+$v_{\infty,\,{\rm cl}}$ & Radial cloud velocity & $100.0$ & [$0.0$, $800.0$] & $\,{\rm km\,s}^{-1}$ \\
+$\sigma_{\rm {\rm cl}}$ & Random cloud motion &$40.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
+$P_{\rm {\rm cl}}$ & Probability to be emitted in cloud & $0.35$ & [$0.0$, $1.0$] &  \\
+$r_{\rm {\rm cl}}$ & Cloud radius & $100.0$ & [$30.0$, $200.0$] & $\,{\rm pc}$ \\
+$H_{\rm em}$ & Emission scale radius & $1000.0$ & [$500.0$, $3.0\times 10^{3}$] & $\,{\rm pc}$ \\
+$f_{\rm {\rm cl}}$ & Cloud covering factor & $3.5$ & [$0.8$, $8.0$] &  \\
+$T_{\rm {\rm ICM}}$${}^{\dagger}$ & Temperature of ICM & $10^{6}$ & [$3.0\times 10^{5}$, $5.0\times 10^{7}$] & $\,{\rm K}$ \\
+$n_{\rm HI,\,{\rm ICM}}$${}^{\dagger}$ & \HI number density in ICM & $5.0\times 10^{-8}$ & [$10^{-12}$, $10^{-6}$] & $\,{\rm cm}^{-3}$ \\
+$\sigma_{\rm i}$ & Width of emission profile & $50.0$ & [$5.0$, $100.0$] & $\,{\rm km\,s}^{-1}$ \\
+$T_{\rm {\rm cl}}$${}^{\dagger}$ & Temperature in clouds & $10^{4}$ & [$5.0\times 10^{3}$, $5.0\times 10^{4}$] & $\,{\rm K}$ \\
+$\beta_{\rm cl}$ & Steepness of the radial velocity profile & $1.5$ & [$1.1$, $2.5$] &  \\
+$\tilde\sigma_{\rm d, cl}$${}^{\dagger}$ & Dust content in clumps &
+  $3.2\times10^{-22}$ & [$4.7\times 10^{-24}$, $1.6\times 10^{-21}$] &
+  $\,\cm^{2}$ \\
+$\zeta_d$${}^{\dagger}$ & Ratio of ICM to cloud dust abundance &
+  $0.01$ & [$10^{-4}$, $0.1$] & \\
+$n_{\rm HI,\,{\rm cl}}$${}^{\dagger}$ & \HI number density in
+  clouds & $0.35$ & [$0.03$, $3.0$] & $\,{\rm cm}^{-3}$ \\
+\hline
+\end{tabular}
+  \caption{Overview of the parameters in the multiphase model and its fiducial
+    values. Variables marked with ${}^{\dagger}$ were drawn in
+    log-space. Table reproduced from \citet{Gronke2016}.}
+  \label{tab:models}
+\end{table*}
+
 \tol's basic observational characteristics are summarized in Table \ref{obstable}.
-Its receding velocity is $7785\pm 50$km s$^{-1}$, which translates
-into a distance of $106.6$ Mpc (with the Hubble constant $H_{0}$=73
-km s$^{-1}$ Mpc$^{-1}$.)
+Its receding velocity is $7785\pm 50$km s$^{-1}$ translates
+into a distance of $106.6$ Mpc, using a Hubble constant value of $H_{0}$=73
+km s$^{-1}$ Mpc$^{-1}$.
 
-The observed flux for the \lya\ line is $\sim
-8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}
-and a Equivalent Width of $70$\AA\ and its H$\beta$ flux is 
-$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA${-1}$
-\citep{Izotov04} which gives a \lya/H$\beta$ flux ratio of
-4.9$\pm$0.1.
-The \lya\ flux values correspond to luminosities of
+Archival Chandra X-ray data\footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
+detection for \tol. 
+This lack of detection motivates our assumption that \lya emission is
+powered by star formation only.
+
+The observed flux for the \lya line is $\sim
+8.1\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \citep{Thuan97}.
+The \lya Equivalent Width is $70$\AA\ and its H$\beta$ flux is 
+$1.62\times 10^{-14}$ erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$
+which gives a \lya/H$\beta$ flux ratio of
+4.9$\pm$0.1 \citep{Izotov04}.
+Comparing the \lya/H$\beta$ ratio with the theoretical
+expectation from case B recombination of $23.3$ \citep{Hummer1987} one
+can estimate an escape fraction of $20$\% for \lya radiation.
+
+The \lya flux values correspond to a luminosity of
 $L_{Ly\alpha}=2.2\times 10^{42}$ erg s$^{-1}$, which in turn
-translates  into a star formation rate of $2.0$ M$_{\odot}$ yr$^{-1}$
-using a standard conversion factor between luminosity and star
-formation rate of $9.1\times 10^{-43}$ $L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$. 
+translates  into a lower bound for the star formation rate of $2.0$
+M$_{\odot}$ yr$^{-1}$ after using a standard conversion factor between
+luminosity and star formation rate of $9.1\times 10^{-43}$
+$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$ 
+without any
+correction by extinction
+\citep{Kennicutt98}.
+
+The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
+L$_{\odot}$ as measured by GALEX. Without any correction by extinction
+and following the empirical relation by \cite{Kennicutt98}, this
+corresponds to a star formation rate of $0.35\pm 0.05$ M$_{\odot}$
+yr$^{-1}$. 
 The absolute magnitude in the $V$ band translates into a luminosity of
 $8.9\times 10^{8}$ L$_{\odot}$.  
+Its metallicity is $\sim Z_{\odot}/24$ as derived from
+optical spectroscopy \citep{Izotov04}. 
 % using http://tomdwelly.com/tools_fluxtolum.php
-Comparing this ratio with the theoretical expectation from case B
-recombination of $23.3$ \citep{Hummer1987} one can estimate an escape
-fraction of $20$\% for \lya\ radiation.
-The bolometric UV luminosity is $9.43\pm1.94 \times 10^{8}$
-L$_{\odot}$ as measured by GALEX, without any correction by extinction
-and following the empirical relation by \cite{Kennicutt98}, this
-corresponds to a star formation rate of $0.35\pm 0.05$ M$_{\odot}$
-yr$^{-1}$. Its metallicity is $\sim Z_{\odot}/24$ as derived from
-optical spectroscopy \citep{Izotov04}.
+%
 
@@
 process \citep{2012AJ....143..139E}.  
-
-We computed the projected half-luminosity radius to be $R_s=1.5\pm0.1$ kpc 
-from the surface intensity profiles reported by \citep{2003A&A...410..481N}. 
-Assuming spherical geometry, one can translate this value into a 3D
-half-luminosity radius of $r_s=3R_s/2=2.25$ kpc.
-
-There is an upper limit for the  
-integrated flux of $<0.10$ Jy km s$^{-1}$, which translates into a
-upper limit for the HI mass of $M<2.65\times 10^{8}$ M$_{\odot}$
+There is an upper limit for the  $21$ cm line integrated flux of $<0.10$
+Jy km s$^{-1}$  which translates into a upper limit for the neutral
+Hydrogen mass of $M<2.65\times 10^{8}$ M$_{\odot}$
 \citep{pustilnikmartin07}.
 
-\begin{table}
-\begin{center}
-\begin{tabular}{lc}\hline
-$\alpha$(2000)$^{a}$ & 12h17min17.1s\\
-$\delta$(2000)$^{b}$ & -28d02m32s\\
-$l$, $b$ (deg) & 294, 34\\
-$m_V$ & 17.5\\
-  M$_V$ & -17.6\\ 
-$v$(km s$^{-1}$) & 7795\\
-\lya\ (erg cm$^{-2}$ s$^{-1}$ \AA$^{-1}$)& $8.1\times 10^{-14}$ \\
-\lya\ Equivalent Width (\AA) & $70$\\
-$21$cm (Jy km s$^{-1}$)& $<0.10$ \\\hline
-\end{tabular}
-\end{center}
-\caption{Basic observational characteristics of TOL1214-277
-  \citep{Thuan97}\label{obstable}} 
-\end{table}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
-\caption{Broad, single peaked and symmetric \lya\ emission of \tol.
-  Dots correspond to the observational data. The line shows the results
-of our best model from a full radiative transfer simulation both for
-the rotation and multiphase models.
-The observational points corresponds to the data as shown in
-\citep{mashesse03}.}   
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
-  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
-  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
-\caption{Results from the multiphase
-  model.
-  The left column corresponds to the parameter's integrated distributions for
-  models with the lowest $\chi^2$ values (dotted line) compared against the
-  parameter's integrated distributions (continous line) used as a prior.
-  These are the only three parameters that show a significant statistical difference from
-  the prior distributions, for all the other eleven parameters we
-  cannot find any significant difference.
-  The right column shows a scatter plot of $\chi^2$ (rescaled by a $1000$)
-  and its corresponding physical parameters.
-  Only the  25 models with the lowest $\chi^2$ are included.
-  \label{multiphaseresults}
-}  
-\end{center}
-\end{figure*}
-
-\begin{figure*}
-\begin{center}
-\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
-\caption{Results from the Markov Chain Monte Carlo computation for
-    the rotation model. The dotted vertical lines in the outer histograms 
-	represent the 16th, 50th and 84th percentiles. \label{emceeresults}} 
-\end{center}
-\end{figure*}
+We compute the projected half-light radius to be $R_s=1.5\pm0.1$ kpc 
+from the surface brightness profiles reported by \cite{2003A&A...410..481N}. 
+Assuming spherical geometry, one can translate this value into a 3D
+half-light radius of $r_s=3R_s/2=2.25$ kpc.
+Imaging observations by \cite{2001AJ....121..169F} show that \tol\ is
+an isolated field galaxy not belonging to a group or cluster.
 
@@
 clumps of neutral hydrogen (and dust) embedded in a hot, ionized
-medium. 
+medium \citep{Gronke2016}. 
 The clumps also have a random and an outflowing velocity
 component which totals the number of parameters describing the model
-to be $14$, which also include information about the spatial
-distribution and thermal state of the clumps and the intraclump
-medium.
+to be $14$.
+We do not explore inflowing clumps given the slight line asymmetry
+redwards to the line center (see the dots in Figure \ref{fig:results})
+and thus set $v_{\infty,\,{\rm cl}}>0$.
+The parameter description list is in Table \ref{tab:models}.
 
@@
 We compare each resulting spectra to the observational results from
-\tol\ after normalizing the observed and simulated spectra to have a a
+\tol\ after normalizing the observed and simulated spectra to have a 
 flux integral of one.
 We build a $\chi^2$ on the normalized flux measurements for each one
-of the $2500$ models
+of the $2500$ models as
 
@@
 model estimated flux.
+As we do not have an analytic expression for $\hat{f}$;
+we obtain $\hat{f}$ from the binned results of the Monte Carlo radiative transfer simulations.
 
@@
 lowest $\chi^2$ values.
-We note that the $\chi^2$ gap in those $25$ models is close to
-$\Delta\chi^2 = 3000$, the lowest $\chi^2$ being close to
-$\chi^2_{min}=1200$.
-To have a sense of scale, the total number of degrees of freedom is
-$104$.
+We note that the difference between the lowest and highest $\chi^2$ values in
+those $25$ models is close to $\Delta\chi^2 = 3000$, the lowest
+$\chi^2$ being close to $\chi^2_{\mathrm{min}}=1200$.
 
-Then we perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
+Using the total number of degrees of freedom, $d.o.f.=104$ we divide
+the results in two classes: low $\chi^2/d.o.f.<35$ and high
+$\chi^2/d.o.f.>35$. \mg{Why was $35$ chosen as a boundary?}
+We apply a random forest classification algorithm to find the
+more relevant parameters in splitting the results into these two
+classes. 
+The algorithm uses $500$ trees for the classification and a
+maximum of $3$ depth levels. 
+To check for stability we repeat the computation $10$ times by
+randomly subsampling the input data to use $80\%$ of the data as
+the training set.
+
+We also perform a Kolmogorov-Smirnov (K-S) test to compare each parameter
 distribution in the best $25$ models against the parent distribution
@@
 corresponding minimum.
-%$v_{\infty,\rm{cl}}$, $\sigma_{\rm cl}$,
-%$P_{\rm cl}$
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.55\textwidth]{CLARA-TOL-main.pdf}
+\caption{Broad, single peaked and highly symmetric \lya emission of \tol.
+  Dots correspond to the observational data \citep{mashesse03}. 
+The thick red and thin blue curves represent our best fit
+to the data using the full radiative transfer simulation with a
+rotation and multiphase model, respectively. 
+These two different models are able to reproduce the main morphological
+features of \tol's \lya line emission.\label{fig:results}}
+\end{center}
+\end{figure*}
 
@@
 temperature $T$, and the linear surface velocity $V_{\rm max}$.  
+The observed line profile also depends on $\theta$,  the angle between the plane
+perpendicular to the rotation axis and the observational
+line-of-sight.  
 In this model, dust only changes the overall line
-normalization and only weakly its shape.  
-The results we report do not include any dust model.
-Here we use an analytical solution that captures the most important
-effects of rotation onto the \lya\ line as explained by
-\citet{GaravitoCamargo2014} and allows us a full parameter space
-exploration.
+normalization and only weakly its shape, i.e. 
+dust cannot change the line symmetry or induce a change in the number
+of line peaks, moreover it does not change the line width by more than
+$1\%$ ($5$ \kms\ in the case of \tol), an effect too small to be
+observed at the resolution at which we have \tol's line profile and
+also negligible compared to the influence of the other free parameters in the model.
+For these reasons we do not include any dust model.
 
-The analytical solution for the rotation sphere is the base to
-perform a Markov Chain Monte Carlo (MCMC) calculation using the
+We use an analytical approximation that captures the most important
+effects of rotation onto the \lya line. 
+We defer the reader to \citet{GaravitoCamargo2014} for complete
+details on the explicit form of this approximation.
+To fully explore the
+parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
 \texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
@@
 the definition in Equation \ref{eq:chi2}. 
+We do not have a closed analytic expression for $\hat{f}$, we compute it
+by numerical integration of the analytical approximations found in
+\citet{GaravitoCamargo2014}.
 
@@
 
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.95\textwidth]{tree_result.pdf}
+\caption{Classification tree example. 
+The aim is to find the parameters that separate two
+classes: low $\chi^2/d.o.f. < 35$ and high $\chi^2/d.o.f>35$. 
+Each box describes the condition over the parameter of interest, the
+level of sample impurity, the total number of samples and the value of the
+number of samples in each class.  
+In this example we randomly sample $80\%$ of the full data set of models to
+start with $28$ models in the first class and
+$1962$ models in the second class; the best way to increase the
+probability to find a result with low $\chi^2/d.o.f.$ ($13$ models,
+fourth bottom box, from left to the right)
+is having the clump radial velocity, $v_{\infty,{\rm cl}}<157.0$ \kms;
+the clump velocity dispersion, $\sigma_{{\rm cl}}>55.6$ \kms, and the
+probability to have a \lya photon emitted in a clump, $P_{\rm cl}>0.683$.
+The final classification is not perfect, showing that all other
+parameters are also important but these three are the most relevant.  
+\label{fig:tree}}
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+  \includegraphics[width=0.6\textwidth]{vinf_cl.pdf}
+  \includegraphics[width=0.6\textwidth]{P_cl.pdf}
+  \includegraphics[width=0.6\textwidth]{sigma_cl.pdf}
+\caption{Results from the multiphase  model.
+  We only show results for the three parameters with a significant
+  statistical difference between the models with the lowest $\chi^2/d.o.f.$
+  values and its prior distribution. 
+  These three parameters are the clump radial velocity at infinity 
+  $v_{\infty, \rm{cl}}$; the probability that  the \lya photons were
+  emitted in the clumps, $P_{\rm cl}$; the clump velocity dispersion,
+  $\sigma_{\rm cl}$.
+  The left column corresponds to the parameter's integrated distributions for
+  models with the lowest $\chi^2/d.o.f.$ values (dotted line) compared against the
+  parameter's prior integrated distributions (continuous line).
+  The right column shows a scatter plot of $\chi^2/d.o.f.$
+  and its corresponding physical parameters.
+  The clump kinematic state is the key ingredient to
+  reproduce \tol's \lya line morphology.
+  \label{multiphaseresults}
+}  
+\end{center}
+\end{figure*}
+
+\begin{figure*}
+\begin{center}
+\includegraphics[width=0.8\textwidth]{emcee_results.pdf}
+\caption{Results from the Markov Chain Monte Carlo computation for
+    the rotation model. 
+    The gray scale indicates the point density in parameter space. 
+    The dotted vertical lines in the histograms in the diagonal panels
+    represent the 16th, 50th and 84th percentiles. 
+    All parameters in the rotation model can be successfully constrained by \tol's
+    \lya line morphology to the values written in the top region of
+    the diagonal panels.
+    \label{emceeresults}} 
+\end{center}
+\end{figure*}
+
 \section{Results}
 
-Figure 1. summarizes our main finding.
+Figure 1. Summarizes our main finding.
 Dots represent the observational data for \tol\ with the
@@
 
-In spite of the simplicity of our models, this is the first time that
-the main \tol\ features can be reproduced: a wide, centered,
-single-peaked \lya\ line.
+The fit to the observations is not perfect. 
+However, in spite of the
+simplicity of our models, this is the first time that the main
+\tol\ features can be reproduced: a broad, highly symmetric,
+single-peaked \lya line.
+
 This result does not demonstrate that the kinematic features we
@@
 In what follows we summarize the values of the kinematic parameters
-that managed to explain \tol\'s \lya\ profile.
+that managed to explain \tol's \lya profile.
 
@@
 
-From the K-S tests we find that only three parameters can be
-constrained by the observations: the clump outflow velocity
-$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), the clump velocity
-dispersion $\sigma_{\rm cl}$ (p-value $10^{-4}$) and the probability
-that the \lya\ emission comes from the clumps $P_{\rm cl}$ (p-value
-$10^{-4}$).
-This does not mean the other parameters do not influence the resulting
-spectra at all; it means that they cannot be constrained from \tol's
-observations.
+With $14$ free parameters our first concern is discovering which are
+the most relevant in reproducing \tol's line shape.
+The results of the random forest classifier yield that the clump outflow velocity
+$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
+that the \lya emission comes from the clumps $P_{\rm cl}$, are the
+most influential parameters in finding a model with low
+$\chi^2/d.o.f.$.
 
-The results are summarized in Figure \ref{multiphaseresults}.
-Left panels show the difference between the integrated distributions
+Figure \ref{fig:tree} shows as an illustration the results for a
+single classification tree.
+\mg{Sorry but it is not clear to me what this Figure shows \& how it was assembled.
+I suggest: leave the KS test in the main text as it is straightforward to understand, and move the random trees with more technical details / references about the implementations to the appendix -- and then point to it as a second probe from the main tetx.
+This way it would break the flow less.}
+The tree starts with $28$ and $1962$ models in the low and high
+$\chi^2/d.o.f.$ classes, respectively. 
+We find that the best classification
+yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
+classes, respectively, after selecting for $v_{\infty,{\rm cl}}<157.0$ \kms,
+$\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$. 
+The split in two classes is not perfect. 
+This means that the 3 parameters in the
+model are the most influential in finding models with low
+$\chi^2/d.o.f.$, but that some combinations of the other 11 parameters
+are also relevant to find a good fit.
+
+From the K-S tests we confirm that the same 3 parameters are the
+only ones that can be constrained by observations;
+$v_{\infty,\rm{cl}}$ (p-value  $10^{-18}$), $\sigma_{\rm cl}$ (p-value
+$10^{-4}$) $P_{\rm cl}$ (p-value $10^{-4}$).
+Once again, this test does not mean the other parameters do not
+influence the resulting spectra at all; it means that they cannot be
+constrained from \tol's observations.
+
+The best models are shown in Figure \ref{multiphaseresults}.
+Left column shows the difference between the integrated distributions
 of the full sample (2500 input models) and the models with the lowest
-$\chi^2$. 
-The right panel shows the actual $\chi^2$ values and its corresponding
-parameter value. 
+$\chi^2/d.o.f.$. 
+The right column shows the actual $\chi^2/d.o.f.$ 
+and its corresponding parameter value. 
 Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
 $v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
+\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
 
-Qualitatively, as \tol\ possesses a very wide spectrum which can be
-achieved by subsequent scatterings off (relatively) fast moving clumps
-while the multi-phase nature (i.e., the existence of low-density
-channels) ensures the high flux at line center as observed.
-In turn, a lower velocity dispersion would produce a thiner line than the
-observed.
-From the lower right panel in \ref{multiphaseresults} we find that it
+Qualitatively this result can be understood as follows.
+Due to the large fraction of \lya photons being emitted within the moving clumps ($P_{\rm cl}$), the `intrinsic' profile represents the kinematics of the clumps, that is, the width of the intrinsic line is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by $v_{\infty}$ \& $\beta_{\rm cl}$.
+Furthermore, the relatively low mean number of clumps per line of sight ($f_{\mathrm{cl}}$) combined with the high velocity dispersion of the clumps implies the 
+existence of low-density inter-clump
+regions where \lya photons can freely propagate which leads to an emergent spectrum close to the intrinsic one as well as to the high flux at line center as observed.
+Because the width of the observable spectrum is hence set primarily by $\sigma_{\rm cl}$, a lower velocity dispersion would produce a narrower line and thus a worse fit.
+From the lower right panel in Figure \ref{multiphaseresults} we find that it
 is unlikely that the clump velocity dispersion is lower than
 $50$\kms. 
+This is also supported by the classification tree example in Figure
+\ref{fig:tree}.
 
-Why is it that the other parameters do not seem to matter? Probably
-because $P_{cl}$ (the probability for a \lya\ to be emitted in a
-clump) is high and most photons are produced at
-large radii making the radiative tranfer effects in the center less
-important.  
-We cannot discard that another region of parameter spacem with similar
-velocity structure but empty interclump medium, relatively dense
-clumps and at least a few clumps per sightline 
-could also work \citep{Hansen06}.
-This possibility does not change our conclusions about the
-kinematic parameters, but it might be interesting to explore in the
-future with a higher sampling of the parameter space once new
-observations clarify the kinematic nature of \tol.
+As a test, we also run a small set of $100$ additional radiative
+transfer simulations with random values for all parameters, except for
+$\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm cl}$ which are kept within the derived $1-\sigma$
+constraints. \mg{Is $1\sigma$ correct?}
+Consistent with the results from the random forest algorithm,
+illustrated by the classification tree of Figure \ref{fig:tree}, we
+find that $30$ models show $\chi^2/d.o.f.<35$.
+
+Having constrained only 3 parameters, one might wonder why the other 11
+parameters do not seem to matter. 
+However, this view is misleading because merely the best-fit values of (some of) those $3$ parameters, i.e., the corresponding constraint to a given sub-region in the parameter space, make the other parameters less important.
+For instance, in our case the large value of $P_{\rm cl}$ makes radiative transfer effects, and therefore other parameters such as the clump column density less relevant for the emergent line profile.
+However, for instance larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce additional radiative transfer effects and thus increase the number of relevant parameters \citep[see ][for details]{2017arXiv170406278G}.
+This means that even
+if for clumply models the line profile is most sensitive to only
+a few parameters \citep{Gronke2016}, the rest of parameters
+affect the line profile at a level that cannot be neglected,
+\mg{I am not sure I understand the rest of this sentence. What do you mean there?}
+i.e. we cannot randomly pick 11 random, reasonable values for these
+parameters, and expect to fit the line profile while only varying the
+other 3, as the results for the classification tree example in Figure
+\ref{fig:tree} shows.
+
+We cannot discard that another region of parameter space
+could also yield a good fit to the observed line-profile.
+This might be interesting to explore in the
+future with, e.g., a higher sampling of the parameter space once new 
+observations  clarify the kinematic nature of \tol \footnote{In
+  Section \S \ref{sec:conclusions} we describe  in more detail what
+  kind of observations could be performed in the near future to
+  improve our understanding of \tol's kinematics.}.
+Furthermore, considering the sparse sampling of parameter space and the results
+from the random forest classifier, it is safer to consider that
+the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
+  cl}$ are actually lower/upper/lower bounds, respectively.
+\mg{This is interesting. Why do you think that? Could we use that to increase the quoted errors? I am worried that the referee will complain about the small errors.}
 
@@
 temperature of $\log_{10} T/\mathrm {K} = 4.27^{+0.11}_{-0.18}$.   
-This model is also able to constrain the angle between the plane
+We are also able to constrain the angle between the plane
 perpendicular to the rotation axis and the observational line-of-sight
 to $\theta = 35.78^{+2.13}_{-1.88}$ degrees.
+This model cannot reproduce the slight asymmetry present in \tol's
+\lya line; most probably this would require an small amount of
+outflows, a feature that is not present in the model provided by
+\cite{GaravitoCamargo2014}.
 
-Lower rotational velocities are disfavored by the fact that the line
-is single peaked.
-Fixing the optical depth at a high value of $10^7$ ensures that the line width
-is close to its observed value.
-A lower rotational velocity would produce a double peaked line.
+The preferred value for the rotational velocity can be explained as
+follows. 
+Lower rotational velocities than the favored value would produce a
+double peaked line as the different doppler shifts produced on
+different regions of the rotating sphere would not be large enough to
+smear the double peaks into a single peak
+\citep{GaravitoCamargo2014}. 
+For the same reason, higher rotation velocities could produce a single
+peak but the line would be broader than it is observed.
 The fact that the velocity and optical depth priors were wide enough,
-allows us to think that the current values found by the MCMC are
-robust given the observational constraints.
+allows us to suggest that the current values for the spherical model
+found by the MCMC are robust given the observational constraints.
 
@@
 
-\tol\ shows one of the most atypical \lya\ spectra observed so far.
+\tol\ presents one of the most atypical \lya spectra observed so far.
 Its flux at the line's center is high compared to other LAEs at low
-redshift and the wide symmetrical peak is virtually absent from other
-LAEs at low and high redshift \citep{LARS,Erb14,Trainor16}. Simple
-shell models fail to reproduce such a spectrum
-\cite{2015A&A...578A...7V}.  
+redshift and the broad, highly symmetrical peak is virtually absent from other
+LAEs at low and high redshift
+\citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
+Simple shell models
+fail to reproduce such a spectrum as reported by \cite{2015A&A...578A...7V}.  
 In the previous sections we show how these characteristics can be
-explained by rather extreme kinematic characteristics.
-Now we discuss and frame those results in terms of the dynamical mass
-that could explain the velocities obtained in the model.
+explained by two different kinematic models: multiphase ISM and solid
+body rotation.
 
-Using the constraints for the velocity dipersion $\sigma$ and the
-maximum rotational velocity $V_m$ in a spherical system localized in a
-region of size $r$ we can estimate two different values for the
-dynamical mass within $r$:
+Which model has more
+chances to be correct?  
+We discard the rotation model by considering that the rotational
+velocity of $\sim350$ \kms\ is too high for such a low
+mass system.  \mg{I am confused -- are much lower rotational velocities not exclude by the priors used?}
+\tol's inferred rotational velocity is larger than the
+Milky Way's ($\sim200$\kms) while its baryonic mass is one order
+of magnitude smaller. 
+Furthermore, \tol's structural properties seem to be similar to known dwarf
+elliptical galaxies. 
+The sample of 7 dwarf ellipticals (dE) observed by
+\cite{2003AJ....126.1794G} show similar properties as \tol. 
+For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
+magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
+\tol. 
+These dE galaxies have velocity dispersions of $31.1$ \kms and
+$44.6$ \kms, respectively,  and their rotational velocities are lower
+than $1$ \kms.  
+This leads us to prefer the multiphase model as it provides 
+a broad consistency with kinematic properties of dE galaxies.
+
+Following the results of \cite{2011ApJ...726..108T}, who made a
+detailed analysis for all kind of elliptical galaxies including dE galaxies, we
+estimate a value for the dynamical mass using the constraints for
+the velocity dispersion, $\sigma$,  in a spherical system localized in a
+region of size $r$
 
@@
 %
-and
-%
-\begin{equation}
-M_{\rm dyn} = \frac{V_m ^{2}r}{G} = 1.16\times10^{9}
-\left(\frac{V_m}{100\ \mathrm{km\ s}^{-1}}\right)^2\left(\frac{r}{\mathrm{kpc}}\right)M_{\odot}, 
-\end{equation}
-%
-for the multiphase and rotation model, respectively.
-Assuming that the \lya\ emission is entirely powered by star formation 
-we use the 3D half-luminosity radius $r_s=2.25$ kpc as the typical size
-for the HI region,
+Assuming that the \lya emission is entirely powered by star formation 
+we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
+for the HI region, in the multiphase model the clump velocity dispersion
+$\sigma_{\rm{cl}}=$\sigmaclump thus corresponds to a dynamical mass of
+$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
+times the estimated baryonic mass in \tol.
+Considering that the results for $\sigma_{\rm{cl}}$ are most probably
+a lower bound, the results for the dynamical mass should also be
+considered as a lower bound.
 
-In the multiphase model the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump corresponds to a dynamical mass of
-$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, while the
-rotational velocity of $V_{\rm max}=348^{+75}_{-48}$\kms corresponds
-$M_{\rm dyn} = 3.2_{-1.0}^{+1.6}\times 10^{10} M_{\odot}$.
-
-\tol's stellar mass is  $M_{\star} = 1.45\pm0.45\times 10^{8}
-M_{\odot}$   \citep{2014PASP..126.1079M} and its total neutral HI mass
-is $M_{\rm HI}<2.65\times 10^{8}$ M$_{\odot}$ 
-\citep{pustilnikmartin07}; the dynamical mass is at least 12 to 160 times
-the baryonic mass, depending if one considers the multiphase or
-bulk rotation estimate. 
-We lean towards the lower dynamical mass estimate from the multiphase
-model as it seems easier to reconcile with the following two
-astrophysical mechanisms for its origin.
-
-A first possibility to explain a dynamical mass of $10^{9} M_{\odot}$
-in a sphere of 2.25 kpc in radius, could be a dark matter halo of at
-least $10^{12}$ M$_{\odot}$ in mass \citep{2011ApJ...726..108T}.
+Figure \ref{fig:mass} illustrates  how such dynamical
+mass can be explained if \tol\ is hosted by a dark matter halo of at
+least $6\times 10^{11}$ M$_{\odot}$ in virial mass. 
 This estimate is based on computing the integrated mass profile of a
 spherical dark matter halo with a Navarro-Frenk-White profile with its
-concentration following the \emph{median} mass-concentration
+concentration following the median mass-concentration
 relationship found in the Bolshoi simulation
-\citep{2012MNRAS.423.3018P}. 
-This estimate leaves open the question as to why  \tol\ is not more
-similar to the Milky Way galaxy as it would be hosted by a dark matter
-halo of similar mass.
+\citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.
 
-A second possibility is that \tol\ hosts a supermassive black hole of
-$10^{9} M_{\odot}$. This is almost two orders of magnitude higher
-than the supermassive black hole found in the compact dwarf galaxy
-M60-UCD1 \citep{2014Natur.513..398S}, which has a similar stellar mass
-as \tol. This would leave open the question about the formation
-process of such a system.
+These results would imply that \tol\ is part of the dE
+class. 
+However, this hypothesis opens up two puzzles.
+First, dE galaxies are found either in clusters or groups of
+galaxies; while \tol\ does not belong either to a group or a cluster
+\citep{2001AJ....121..169F}. 
+The second issue is that, unlike a dE, \tol\ hosts a bright and compact
+starburst; imaging and spectroscopy studies suggest that the
+starburst started less than 4 Myr ago, while the low surface
+brightness regins are consistent with an age below one Gyr
+\citep{2001AJ....121..169F}.
 
-%Another perspective to appreciate the atypically high dynamical mass
-%estimates comes from the observed scaling relations for dwarf
-%galaxies.
-%Assuming that \tol\ followed the fundamental plane relationship
-%between its mean surface brightness $I_e$, the projected half-light
-%radius $R_e$ and the velocity dispersion $\sigma$, described by $\log
-%I_e=1.6 \log\sigma - 1.21\log R_e + 0.55$ \citep{2009ApJ...698.1590G},
-%the expected velocity dispersion should be on the order of $5 \pm 1$ 
-%\kms, which is a factor of $\sim$ $10$ - $60$ lower than the 
-%results from the multiphase and rotation models, respectively. 
-%These are equivalent to factors of $\sim$ $100$ - $3600$ on the
-%dynamical mass.
-%Once again,  \tol\ seems to be significantly more massive than
-%expected.
-
-A new observational test is needed to clarify the kinematical nature of
-\tol. 
-We suggest that integral field unit measurements 
-resolving its spatial extent are up to the task. 
+We suggest that new observational tests are needed to clarify the
+kinematic nature of \tol.
+Integral field unit measurements resolving its spatial extent are up
+to the task.  
 \tol\ spans a region of $4$ arcseconds,
 an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
-\citep{2014Msngr.157...13B} with its
-nominal $0.2$ arcseconds spatial sampling over a $1.0$ arcminute field
-in wide-field mode could provide a coarse mapping of different
-ionization lines to infer a kinematic map in the H$\alpha$ line,
-following the kind of work presented by \citet{Herenz16} done with the Potsdam
-Multi-Aperture Spectrometer (PMAS) \citet{PMAS} on nearby
-\lya\ emitting galaxies.
-We note that archival Chandra X-ray archival
-data \footnote{\url{http://cxc.harvard.edu/cda/}} does not show any
-detection for \tol.
-This lack of detection would also put an upper limit on the intensity
-of recent black hole activity due to accretion.
+\citep{2014Msngr.157...13B} with its nominal $0.2$ arcseconds spatial
+sampling over a $1.0$ arcminute field in wide-field mode could provide
+a coarse mapping of different ionization lines to infer a kinematic
+map in the H$\alpha$ line, following the kind of work presented by
+\citet{Herenz16} done with the Potsdam Multi-Aperture Spectrometer
+(PMAS) \citep{PMAS} on nearby \lya emitting galaxies.
 
-Another observational test includes the measurement of the
-\lya\ ionizing continuum escape fraction.
-In the rotational model this fraction should be zero, while
-the multiphase model predicts that averaging over all sightlines
+Another observational hint to clarify \tol's state could be
+the measurement of the \lya ionizing continuum escape fraction. 
+The multiphase model predicts that averaging over all sightlines
 it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle (i.e. some sightlines can have
-an escape fraction close to $100\%$)\citep{Gronke2016} .
+variations depending on viewing angle, i.e. some sightlines can have
+an escape fraction close to $100\%$ \citep{Gronke2016}.
+
+\begin{figure}
+\begin{center}
+\includegraphics[width=0.46\textwidth]{enclosed_mass.pdf}
+\caption{Enclosed mass in a spherical system as a function of radius.
+  Lines correspond to the expectation for dark matter halos with
+  different viral masses as shown in the legend, the arrow corresponds
+  to the dynamical mass lower bounds for \tol.  
+  The dynamical mass estimates for \tol\ are consistent with the
+  galaxy being hosted by a dark matter halo of at least
+  $6\times10^{11}$ M$_{\odot}$ in mass.
+    \label{fig:mass}} 
+\end{center}
+\end{figure}
 
 \section{Conclusions}
+\label{sec:conclusions}
 
@@
 reproduce the so far unexplained observational features of \tol's
-\lya\ emission line.  
+\lya emission line.
 One model is based on a multiphase ISM with random clump motions and
 the other on gas bulk solid body rotation. 
+It is the first time that an observed \lya profile can be fully
+reproduced by either of these two kinematic conditions.
+Our findings highlight the importance of including multiphase and/or
+rotation conditions as kinematic features to model the \lya line.
 
-It is the first time that an observed \lya\ profile can be fully
-reproduced by either of these two kinematic conditions.
-Furthermore, the kinematics of both models suggest a dynamical mass
-at least ten times larger than the baryonic mass infered from observations.
+In this particular case, we prefer the multiphase model because it has kinematic
+conditions similar to those in dwarf ellipticals, while the
+rotational model produces rotational velocities too high for a dwarf
+galaxy.
+
+However, \tol's environment and star forming activity are radically
+different from those of dwarf ellipticals.
 We suggest that additional integral field unit observations are the
@@
 All in all, the mere existence of a strong LAE galaxy with a broad,
-symmetric line is interesting. 
-\tol's line shape is different to others and reveals an unexpected
-kinematic structure.
-Our findings highlight the importance of including multiphase and/or
-rotation conditions as kinematic features to model the \lya\ line.
-
-Additionally, if the hypothesis of a supermassive black
-hole in \tol\ proves to be consistent with future observational
-kinematic maps, it could correspond to a so far undetected
-supermassive black hole in a dwarf galaxy, providing a new way to test
-and probe theories on the co-evolution of galaxies and black holes in
-the first generation of galaxies.
+highly symmetric line is interesting. 
+\tol's line shape is different to others and seems to reveal an
+unexpected kinematic structure.
+A confirmation of our results by new observations would support the multiphase model
+as an element to be included in the study of primordial \lya emitting
+galaxies.
 
 \section*{Acknowledgments}
+We thank the referee for detailed comments and suggestions that
+improved this paper. 
 We thank J. M. Mas-Hesse for providing us with \tol's observational
-\lya\ data \citep{mashesse03} in electronic format. This data was
+\lya data \citep{mashesse03} in electronic format. This data was
 used to prepare Figure 1.
+J. E. F-R. acknowledges the support of J. L. Guerra in the last
+writing stages of this paper.
 
-\bibliographystyle{mn2e}
-\bibliography{references}
+\bibliographystyle{mnras}
+%\bibliography{references}
+
+\bibliographystyle{mnras}
+%\bibliography{references}
+\begin{thebibliography}{}
+\makeatletter
+\relax
+\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
+\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
+  {\mn@doi@[]}}
+\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
+  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
+  \endgroup}
+\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
+\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
+\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
+  {dblp:#1}}
+\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
+  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
+  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
+  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
+  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
+
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2013}]{astropy}
+{Astropy Collaboration} et~al., 2013, \mn@doi [\aap]
+  {10.1051/0004-6361/201322068}, \href
+  {http://adsabs.harvard.edu/abs/2013A%26A...558A..33A} {558, A33}
+
+\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
+  et~al.}{2014}]{2014Msngr.157...13B}
+{Bacon} R.,  et~al., 2014, The Messenger, \href
+  {http://adsabs.harvard.edu/abs/2014Msngr.157...13B} {157, 13}
+
+\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur}  \&
+  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
+{Begum} A.,  {Chengalur} J.~N.,   {Karachentsev} I.~D.,  2005, \mn@doi [\aap]
+  {10.1051/0004-6361:200500026}, \href
+  {http://adsabs.harvard.edu/abs/2005A%26A...433L...1B} {433, L1}
+
+\bibitem[\protect\citeauthoryear{{Courtois}, {Zaritsky}, {Sorce}  \&
+  {Pomar{\`e}de}}{{Courtois} et~al.}{2015}]{2015MNRAS.448.1767C}
+{Courtois} H.~M.,  {Zaritsky} D.,  {Sorce} J.~G.,   {Pomar{\`e}de} D.,  2015,
+  \mn@doi [\mnras] {10.1093/mnras/stv071}, \href
+  {http://adsabs.harvard.edu/abs/2015MNRAS.448.1767C} {448, 1767}
+
+\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham}  \&
+  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
+{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,   {Chaffee} F.~H.,
+  1998, \mn@doi [\apjl] {10.1086/311331}, \href
+  {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
+{Dijkstra} M.,  2014, \mn@doi [\pasa] {10.1017/pasa.2014.33}, \href
+  {http://adsabs.harvard.edu/abs/2014PASA...31...40D} {31, e040}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
+  {Kramer}}{2012}]{2012MNRAS.424.1672D}
+{Dijkstra} M.,  {Kramer} R.,  2012, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2012.21131.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.424.1672D} {424, 1672}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz}  \& {Wyithe}}{{Dijkstra}
+  et~al.}{2007}]{2007MNRAS.377.1175D}
+{Dijkstra} M.,  {Lidz} A.,   {Wyithe} J.~S.~B.,  2007, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2007.11666.x}, \href
+  {http://adsabs.harvard.edu/abs/2007MNRAS.377.1175D} {377, 1175}
+
+\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
+  {Werner}, {Moustakas}, {Willmer}  \& {Vanzi}}{{Engelbracht}
+  et~al.}{2008}]{2008ApJ...678..804E}
+{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
+  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,   {Vanzi} L.,  2008,
+  \mn@doi [\apj] {10.1086/529513}, \href
+  {http://adsabs.harvard.edu/abs/2008ApJ...678..804E} {678, 804}
+
+\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
+{Erb} D.~K.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/795/1/33}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...795...33E} {795, 33}
+
+\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky}  \& {Meidt}}{{Eskew}
+  et~al.}{2012}]{2012AJ....143..139E}
+{Eskew} M.,  {Zaritsky} D.,   {Meidt} S.,  2012, \mn@doi [\aj]
+  {10.1088/0004-6256/143/6/139}, \href
+  {http://adsabs.harvard.edu/abs/2012AJ....143..139E} {143, 139}
+
+\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang}  \&
+  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
+{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,   {Goodman} J.,  2013, \mn@doi
+  [\pasp] {10.1086/670067}, \href
+  {http://adsabs.harvard.edu/abs/2013PASP..125..306F} {125, 306}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta}  \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,   {Prada} F.,  2011, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2011.18983.x}, \href
+  {http://adsabs.harvard.edu/abs/2011MNRAS.415.3666F} {415, 3666}
+
+\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva}  \&
+  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
+{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,   {Thuan}
+  T.~X.,  2001, \mn@doi [\aj] {10.1086/318016}, \href
+  {http://adsabs.harvard.edu/abs/2001AJ....121..169F} {121, 169}
+
+\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero}  \&
+  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
+{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,   {Dijkstra} M.,  2014,
+  \mn@doi [\apj] {10.1088/0004-637X/795/2/120}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...795..120G} {795, 120}
+
+\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}}  \&
+  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
+{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,   {D{\'{\i}}az} {\'A}.~I.,
+  2013, \mn@doi [\mnras] {10.1093/mnras/stt1186}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.434.2491G} {434, 2491}
+
+\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
+  et~al.}{2007}]{2007ApJ...671..278G}
+{Gawiser} E.,  et~al., 2007, \mn@doi [\apj] {10.1086/522955}, \href
+  {http://adsabs.harvard.edu/abs/2007ApJ...671..278G} {671, 278}
+
+\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta}  \& {van der
+  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
+{Geha} M.,  {Guhathakurta} P.,   {van der Marel} R.~P.,  2003, \mn@doi [\aj]
+  {10.1086/377624}, \href {http://adsabs.harvard.edu/abs/2003AJ....126.1794G}
+  {126, 1794}
+
+\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
+  Weare}{2010}]{goodman2010ensemble}
+Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
+  computational science, 5, 65
+
+\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu}  \& {Wyithe}}{{Greig}
+  et~al.}{2013}]{2013MNRAS.431.1777G}
+{Greig} B.,  {Komatsu} E.,   {Wyithe} J.~S.~B.,  2013, \mn@doi [\mnras]
+  {10.1093/mnras/stt292}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.431.1777G} {431, 1777}
+
+\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
+  {Dijkstra}}{2016}]{Gronke2016}
+{Gronke} M.,  {Dijkstra} M.,  2016, \mn@doi [\apj]
+  {10.3847/0004-637X/826/1/14}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...826...14G} {826, 14}
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Bull}  \& {Dijkstra}}{{Gronke}
+  et~al.}{2015}]{2015ApJ...812..123G}
+{Gronke} M.,  {Bull} P.,   {Dijkstra} M.,  2015, \mn@doi [\apj]
+  {10.1088/0004-637X/812/2/123}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...812..123G} {812, 123}
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Dijkstra}, {McCourt}  \&
+  {Oh}}{{Gronke} et~al.}{2017}]{2017arXiv170406278G}
+{Gronke} M.,  {Dijkstra} M.,  {McCourt} M.,   {Oh} S.~P.,  2017, preprint,
+  \href {http://esoads.eso.org/abs/2017arXiv170406278G} {} (\mn@eprint {arXiv}
+  {1704.06278})
+
+\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
+{Harrington} J.~P.,  1973, \mnras, \href
+  {http://adsabs.harvard.edu/abs/1973MNRAS.162...43H} {162, 43}
+
+\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
+  et~al.}{2004}]{2004AJ....128.2073H}
+{Hayashino} T.,  et~al., 2004, \mn@doi [\aj] {10.1086/424935}, \href
+  {http://adsabs.harvard.edu/abs/2004AJ....128.2073H} {128, 2073}
+
+\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
+{Hayes} M.,  2015, \mn@doi [\pasa] {10.1017/pasa.2015.25}, \href
+  {http://adsabs.harvard.edu/abs/2015PASA...32...27H} {32, e027}
+
+\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
+  et~al.}{2016}]{Herenz16}
+{Herenz} E.~C.,  et~al., 2016, \mn@doi [\aap] {10.1051/0004-6361/201527373},
+  \href {http://adsabs.harvard.edu/abs/2016A%26A...587A..78H} {587, A78}
+
+\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
+  {Storey}}{1987}]{Hummer1987}
+{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mn@doi [\mnras]
+  {10.1093/mnras/224.3.801}, \href
+  {http://adsabs.harvard.edu/abs/1987MNRAS.224..801H} {224, 801}
+
+\bibitem[\protect\citeauthoryear{{Hunter}}{{Hunter}}{2007}]{matplotlib}
+{Hunter} J.~D.,  2007, \mn@doi [Computing in Science and Engineering]
+  {10.1109/MCSE.2007.55}, \href
+  {http://adsabs.harvard.edu/abs/2007CSE.....9...90H} {9, 90}
+
+\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke}  \&
+  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
+{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,   {Thuan}
+  T.~X.,  2004, \mn@doi [\aap] {10.1051/0004-6361:20035847}, \href
+  {http://adsabs.harvard.edu/abs/2004A%26A...421..539I} {421, 539}
+
+\bibitem[\protect\citeauthoryear{James, Witten  \& Hastie}{James
+  et~al.}{2014}]{james2014introduction}
+James G.,  Witten D.,   Hastie T.,  2014, An Introduction to Statistical
+  Learning: With Applications in R.
+
+\bibitem[\protect\citeauthoryear{{Kennicutt}}{{Kennicutt}}{1998}]{Kennicutt98}
+{Kennicutt} Jr. R.~C.,  1998, \mn@doi [\araa] {10.1146/annurev.astro.36.1.189},
+  \href {http://adsabs.harvard.edu/abs/1998ARA%26A..36..189K} {36, 189}
+
+\bibitem[\protect\citeauthoryear{Kluyver et~al.,}{Kluyver
+  et~al.}{2016}]{jupyter}
+Kluyver T.,  et~al., 2016, in ELPUB. pp 87--90
+
+\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
+  {Malhotra}  \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
+{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,   {Wang}
+  J.,  2007, \mn@doi [\apj] {10.1086/520668}, \href
+  {http://adsabs.harvard.edu/abs/2007ApJ...668...15K} {668, 15}
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval}  \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013ApJ...766..124L}
+{Laursen} P.,  {Duval} F.,   {{\"O}stlin} G.,  2013, \mn@doi [\apj]
+  {10.1088/0004-637X/766/2/124}, \href
+  {http://adsabs.harvard.edu/abs/2013ApJ...766..124L} {766, 124}
+
+\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
+  {Rybicki}}{1999}]{LoebRybicki}
+{Loeb} A.,  {Rybicki} G.~B.,  1999, \mn@doi [\apj] {10.1086/307844}, \href
+  {http://adsabs.harvard.edu/abs/1999ApJ...524..527L} {524, 527}
+
+\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
+{Martin} C.~L.,  1998, \mn@doi [\apj] {10.1086/306219}, \href
+  {http://adsabs.harvard.edu/abs/1998ApJ...506..222M} {506, 222}
+
+\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
+  {Leitherer}, {Terlevich}  \& {Terlevich}}{{Mas-Hesse}
+  et~al.}{2003}]{mashesse03}
+{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
+  {Terlevich} R.~J.,   {Terlevich} E.,  2003, \mn@doi [\apj] {10.1086/379116},
+  \href {http://adsabs.harvard.edu/abs/2003ApJ...598..858M} {598, 858}
+
+\bibitem[\protect\citeauthoryear{{McCourt}, {Oh}, {O'Leary}  \&
+  {Madigan}}{{McCourt} et~al.}{2016}]{2016arXiv161001164M}
+{McCourt} M.,  {Oh} S.~P.,  {O'Leary} R.~M.,   {Madigan} A.-M.,  2016,
+  preprint, \href {http://esoads.eso.org/abs/2016arXiv161001164M} {}
+  (\mn@eprint {arXiv} {1610.01164})
+
+\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
+  {Ostriker}}{1977}]{1977ApJ...218..148M}
+{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \mn@doi [\apj] {10.1086/155667}, \href
+  {http://esoads.eso.org/abs/1977ApJ...218..148M} {218, 148}
+
+\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
+{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \mn@doi [\apj]
+  {10.3847/0004-637X/828/1/5}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...828....5M} {828, 5}
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
+{Neufeld} D.~A.,  1991, \mn@doi [\apjl] {10.1086/185983}, \href
+  {http://adsabs.harvard.edu/abs/1991ApJ...370L..85N} {370, L85}
+
+\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s}  \&
+  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
+{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,   {Fricke} K.~J.,  2003,
+  \mn@doi [\aap] {10.1051/0004-6361:20031147}, \href
+  {http://adsabs.harvard.edu/abs/2003A%26A...410..481N} {410, 481}
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh}  \& {Infante}}{{Orsi}
+  et~al.}{2008}]{2008MNRAS.391.1589O}
+{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,   {Infante} L.,  2008, \mn@doi
+  [\mnras] {10.1111/j.1365-2966.2008.14010.x}, \href
+  {http://adsabs.harvard.edu/abs/2008MNRAS.391.1589O} {391, 1589}
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}  \& {Baugh}}{{Orsi}
+  et~al.}{2012}]{Orsi12}
+{Orsi} A.,  {Lacey} C.~G.,   {Baugh} C.~M.,  2012, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2012.21396.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.425...87O} {425, 87}
+
+\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
+  et~al.}{2014}]{LARS}
+{{\"O}stlin} G.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/797/1/11},
+  \href {http://adsabs.harvard.edu/abs/2014ApJ...797...11O} {797, 11}
+
+\bibitem[\protect\citeauthoryear{{Ott}, {Walter}  \& {Brinks}}{{Ott}
+  et~al.}{2005}]{2005MNRAS.358.1453O}
+{Ott} J.,  {Walter} F.,   {Brinks} E.,  2005, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2005.08863.x}, \href
+  {http://adsabs.harvard.edu/abs/2005MNRAS.358.1453O} {358, 1453}
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
+  {Gonz{\'a}lez}, {Guaita}  \& {Infante}}{{Padilla}
+  et~al.}{2010}]{2010MNRAS.409..184P}
+{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
+  {Guaita} L.,   {Infante} L.,  2010, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2010.17317.x}, \href
+  {http://adsabs.harvard.edu/abs/2010MNRAS.409..184P} {409, 184}
+
+\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
+  {Peebles}}{1967}]{PartridgePeebles}
+{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \mn@doi [\apj] {10.1086/149079},
+  \href {http://adsabs.harvard.edu/abs/1967ApJ...147..868P} {147, 868}
+
+\bibitem[\protect\citeauthoryear{Pedregosa et~al.,}{Pedregosa
+  et~al.}{2011}]{scikit-learn}
+Pedregosa F.,  et~al., 2011, Journal of Machine Learning Research, 12, 2825
+
+\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
+  Granger}{2007}]{IPython}
+P\'erez F.,  Granger B.~E.,  2007, \mn@doi [Computing in Science and
+  Engineering] {10.1109/MCSE.2007.53}, 9, 21
+
+\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero}  \&
+  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
+{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,   {Mu{\~n}oz-Cuartas} J.~C.,
+  2016, \mn@doi [\apj] {10.3847/0004-637X/832/2/169}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...832..169P} {832, 169}
+
+\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
+  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
+{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
+  {Primack} J.,  2012, \mn@doi [\mnras] {10.1111/j.1365-2966.2012.21007.x},
+  \href {http://adsabs.harvard.edu/abs/2012MNRAS.423.3018P} {423, 3018}
+
+\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
+  {Martin}}{2007}]{pustilnikmartin07}
+{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \mn@doi [\aap]
+  {10.1051/0004-6361:20066137}, \href
+  {http://cdsads.u-strasbg.fr/abs/2007A%26A...464..859P} {464, 859}
+
+\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
+  et~al.}{2015}]{2015ApJ...805...14R}
+{Rivera-Thorsen} T.~E.,  et~al., 2015, \mn@doi [\apj]
+  {10.1088/0004-637X/805/1/14}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...805...14R} {805, 14}
+
+\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
+{Roth} M.~M.,  et~al., 2005, \mn@doi [\pasp] {10.1086/429877}, \href
+  {http://adsabs.harvard.edu/abs/2005PASP..117..620R} {117, 620}
+
+\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}  \& {Rakic}}{{Steidel}
+  et~al.}{2010}]{2010ApJ...717..289S}
+{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
+  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,   {Rakic} O.,  2010, \mn@doi [\apj]
+  {10.1088/0004-637X/717/1/289}, \href
+  {http://adsabs.harvard.edu/abs/2010ApJ...717..289S} {717, 289}
+
+\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada}  \& {van
+  der Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
+{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,   {van der Hulst} J.~M.,
+  2009, \mn@doi [\aap] {10.1051/0004-6361:200810516}, \href
+  {http://adsabs.harvard.edu/abs/2009A%26A...493..871S} {493, 871}
+
+\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
+{Tasitsiomi} A.,  2006, \mn@doi [\apj] {10.1086/504460}, \href
+  {http://adsabs.harvard.edu/abs/2006ApJ...645..792T} {645, 792}
+
+\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov}  \& {Gnedin}}{{Tassis}
+  et~al.}{2008}]{2008ApJ...672..888T}
+{Tassis} K.,  {Kravtsov} A.~V.,   {Gnedin} N.~Y.,  2008, \mn@doi [\apj]
+  {10.1086/523880}, \href {http://adsabs.harvard.edu/abs/2008ApJ...672..888T}
+  {672, 888}
+
+\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
+  {Izotov}}{1997}]{Thuan97}
+{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, \href
+  {http://adsabs.harvard.edu/abs/1997ApJ...489..623T} {489, 623}
+
+\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves}  \&
+  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
+{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,   {Wolf} J.,  2011,
+  \mn@doi [\apj] {10.1088/0004-637X/726/2/108}, \href
+  {http://adsabs.harvard.edu/abs/2011ApJ...726..108T} {726, 108}
+
+\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel}  \&
+  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
+{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,   {Rudie} G.~C.,  2016,
+  \mn@doi [\apj] {10.3847/0004-637X/832/2/171}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...832..171T} {832, 171}
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer}  \&
+  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
+{Verhamme} A.,  {Schaerer} D.,   {Maselli} A.,  2006, \mn@doi [\aap]
+  {10.1051/0004-6361:20065554}, \href
+  {http://adsabs.harvard.edu/abs/2006A%26A...460..397V} {460, 397}
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer}  \&
+  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
+{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,   {Hayes} M.,  2015, \mn@doi
+  [\aap] {10.1051/0004-6361/201423978}, \href
+  {http://adsabs.harvard.edu/abs/2015A%26A...578A...7V} {578, A7}
+
+\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
+  {Morimoto}  \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
+{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
+  {Umemura} M.,  2012, \mn@doi [\apj] {10.1088/0004-637X/751/1/29}, \href
+  {http://adsabs.harvard.edu/abs/2012ApJ...751...29Y} {751, 29}
+
+\makeatother
+\end{thebibliography}
 

### 2017-07-13 paper/paper.tex
latest

@@
 \bibliographystyle{mnras}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+\makeatletter
+\relax
+\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
+\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
+  {\mn@doi@[]}}
+\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
+  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
+  \endgroup}
+\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
+\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
+\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
+  {dblp:#1}}
+\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
+  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
+  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
+  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
+  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
+
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2013}]{astropy}
+{Astropy Collaboration} et~al., 2013, \mn@doi [\aap]
+  {10.1051/0004-6361/201322068}, \href
+  {http://adsabs.harvard.edu/abs/2013A%26A...558A..33A} {558, A33}
+
+\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
+  et~al.}{2014}]{2014Msngr.157...13B}
+{Bacon} R.,  et~al., 2014, The Messenger, \href
+  {http://adsabs.harvard.edu/abs/2014Msngr.157...13B} {157, 13}
+
+\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur}  \&
+  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
+{Begum} A.,  {Chengalur} J.~N.,   {Karachentsev} I.~D.,  2005, \mn@doi [\aap]
+  {10.1051/0004-6361:200500026}, \href
+  {http://adsabs.harvard.edu/abs/2005A%26A...433L...1B} {433, L1}
+
+\bibitem[\protect\citeauthoryear{{Courtois}, {Zaritsky}, {Sorce}  \&
+  {Pomar{\`e}de}}{{Courtois} et~al.}{2015}]{2015MNRAS.448.1767C}
+{Courtois} H.~M.,  {Zaritsky} D.,  {Sorce} J.~G.,   {Pomar{\`e}de} D.,  2015,
+  \mn@doi [\mnras] {10.1093/mnras/stv071}, \href
+  {http://adsabs.harvard.edu/abs/2015MNRAS.448.1767C} {448, 1767}
+
+\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham}  \&
+  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
+{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,   {Chaffee} F.~H.,
+  1998, \mn@doi [\apjl] {10.1086/311331}, \href
+  {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
+{Dijkstra} M.,  2014, \mn@doi [\pasa] {10.1017/pasa.2014.33}, \href
+  {http://adsabs.harvard.edu/abs/2014PASA...31...40D} {31, e040}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
+  {Kramer}}{2012}]{2012MNRAS.424.1672D}
+{Dijkstra} M.,  {Kramer} R.,  2012, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2012.21131.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.424.1672D} {424, 1672}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz}  \& {Wyithe}}{{Dijkstra}
+  et~al.}{2007}]{2007MNRAS.377.1175D}
+{Dijkstra} M.,  {Lidz} A.,   {Wyithe} J.~S.~B.,  2007, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2007.11666.x}, \href
+  {http://adsabs.harvard.edu/abs/2007MNRAS.377.1175D} {377, 1175}
+
+\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
+  {Werner}, {Moustakas}, {Willmer}  \& {Vanzi}}{{Engelbracht}
+  et~al.}{2008}]{2008ApJ...678..804E}
+{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
+  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,   {Vanzi} L.,  2008,
+  \mn@doi [\apj] {10.1086/529513}, \href
+  {http://adsabs.harvard.edu/abs/2008ApJ...678..804E} {678, 804}
+
+\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
+{Erb} D.~K.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/795/1/33}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...795...33E} {795, 33}
+
+\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky}  \& {Meidt}}{{Eskew}
+  et~al.}{2012}]{2012AJ....143..139E}
+{Eskew} M.,  {Zaritsky} D.,   {Meidt} S.,  2012, \mn@doi [\aj]
+  {10.1088/0004-6256/143/6/139}, \href
+  {http://adsabs.harvard.edu/abs/2012AJ....143..139E} {143, 139}
+
+\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang}  \&
+  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
+{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,   {Goodman} J.,  2013, \mn@doi
+  [\pasp] {10.1086/670067}, \href
+  {http://adsabs.harvard.edu/abs/2013PASP..125..306F} {125, 306}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta}  \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,   {Prada} F.,  2011, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2011.18983.x}, \href
+  {http://adsabs.harvard.edu/abs/2011MNRAS.415.3666F} {415, 3666}
+
+\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva}  \&
+  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
+{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,   {Thuan}
+  T.~X.,  2001, \mn@doi [\aj] {10.1086/318016}, \href
+  {http://adsabs.harvard.edu/abs/2001AJ....121..169F} {121, 169}
+
+\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero}  \&
+  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
+{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,   {Dijkstra} M.,  2014,
+  \mn@doi [\apj] {10.1088/0004-637X/795/2/120}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...795..120G} {795, 120}
+
+\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}}  \&
+  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
+{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,   {D{\'{\i}}az} {\'A}.~I.,
+  2013, \mn@doi [\mnras] {10.1093/mnras/stt1186}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.434.2491G} {434, 2491}
+
+\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
+  et~al.}{2007}]{2007ApJ...671..278G}
+{Gawiser} E.,  et~al., 2007, \mn@doi [\apj] {10.1086/522955}, \href
+  {http://adsabs.harvard.edu/abs/2007ApJ...671..278G} {671, 278}
+
+\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta}  \& {van der
+  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
+{Geha} M.,  {Guhathakurta} P.,   {van der Marel} R.~P.,  2003, \mn@doi [\aj]
+  {10.1086/377624}, \href {http://adsabs.harvard.edu/abs/2003AJ....126.1794G}
+  {126, 1794}
+
+\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
+  Weare}{2010}]{goodman2010ensemble}
+Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
+  computational science, 5, 65
+
+\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu}  \& {Wyithe}}{{Greig}
+  et~al.}{2013}]{2013MNRAS.431.1777G}
+{Greig} B.,  {Komatsu} E.,   {Wyithe} J.~S.~B.,  2013, \mn@doi [\mnras]
+  {10.1093/mnras/stt292}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.431.1777G} {431, 1777}
+
+\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
+  {Dijkstra}}{2016}]{Gronke2016}
+{Gronke} M.,  {Dijkstra} M.,  2016, \mn@doi [\apj]
+  {10.3847/0004-637X/826/1/14}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...826...14G} {826, 14}
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Bull}  \& {Dijkstra}}{{Gronke}
+  et~al.}{2015}]{2015ApJ...812..123G}
+{Gronke} M.,  {Bull} P.,   {Dijkstra} M.,  2015, \mn@doi [\apj]
+  {10.1088/0004-637X/812/2/123}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...812..123G} {812, 123}
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Dijkstra}, {McCourt}  \&
+  {Oh}}{{Gronke} et~al.}{2017}]{2017arXiv170406278G}
+{Gronke} M.,  {Dijkstra} M.,  {McCourt} M.,   {Oh} S.~P.,  2017, preprint,
+  \href {http://esoads.eso.org/abs/2017arXiv170406278G} {} (\mn@eprint {arXiv}
+  {1704.06278})
+
+\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
+{Harrington} J.~P.,  1973, \mnras, \href
+  {http://adsabs.harvard.edu/abs/1973MNRAS.162...43H} {162, 43}
+
+\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
+  et~al.}{2004}]{2004AJ....128.2073H}
+{Hayashino} T.,  et~al., 2004, \mn@doi [\aj] {10.1086/424935}, \href
+  {http://adsabs.harvard.edu/abs/2004AJ....128.2073H} {128, 2073}
+
+\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
+{Hayes} M.,  2015, \mn@doi [\pasa] {10.1017/pasa.2015.25}, \href
+  {http://adsabs.harvard.edu/abs/2015PASA...32...27H} {32, e027}
+
+\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
+  et~al.}{2016}]{Herenz16}
+{Herenz} E.~C.,  et~al., 2016, \mn@doi [\aap] {10.1051/0004-6361/201527373},
+  \href {http://adsabs.harvard.edu/abs/2016A%26A...587A..78H} {587, A78}
+
+\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
+  {Storey}}{1987}]{Hummer1987}
+{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mn@doi [\mnras]
+  {10.1093/mnras/224.3.801}, \href
+  {http://adsabs.harvard.edu/abs/1987MNRAS.224..801H} {224, 801}
+
+\bibitem[\protect\citeauthoryear{{Hunter}}{{Hunter}}{2007}]{matplotlib}
+{Hunter} J.~D.,  2007, \mn@doi [Computing in Science and Engineering]
+  {10.1109/MCSE.2007.55}, \href
+  {http://adsabs.harvard.edu/abs/2007CSE.....9...90H} {9, 90}
+
+\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke}  \&
+  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
+{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,   {Thuan}
+  T.~X.,  2004, \mn@doi [\aap] {10.1051/0004-6361:20035847}, \href
+  {http://adsabs.harvard.edu/abs/2004A%26A...421..539I} {421, 539}
+
+\bibitem[\protect\citeauthoryear{James, Witten  \& Hastie}{James
+  et~al.}{2014}]{james2014introduction}
+James G.,  Witten D.,   Hastie T.,  2014, An Introduction to Statistical
+  Learning: With Applications in R.
+
+\bibitem[\protect\citeauthoryear{{Kennicutt}}{{Kennicutt}}{1998}]{Kennicutt98}
+{Kennicutt} Jr. R.~C.,  1998, \mn@doi [\araa] {10.1146/annurev.astro.36.1.189},
+  \href {http://adsabs.harvard.edu/abs/1998ARA%26A..36..189K} {36, 189}
+
+\bibitem[\protect\citeauthoryear{Kluyver et~al.,}{Kluyver
+  et~al.}{2016}]{jupyter}
+Kluyver T.,  et~al., 2016, in ELPUB. pp 87--90
+
+\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
+  {Malhotra}  \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
+{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,   {Wang}
+  J.,  2007, \mn@doi [\apj] {10.1086/520668}, \href
+  {http://adsabs.harvard.edu/abs/2007ApJ...668...15K} {668, 15}
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval}  \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013ApJ...766..124L}
+{Laursen} P.,  {Duval} F.,   {{\"O}stlin} G.,  2013, \mn@doi [\apj]
+  {10.1088/0004-637X/766/2/124}, \href
+  {http://adsabs.harvard.edu/abs/2013ApJ...766..124L} {766, 124}
+
+\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
+  {Rybicki}}{1999}]{LoebRybicki}
+{Loeb} A.,  {Rybicki} G.~B.,  1999, \mn@doi [\apj] {10.1086/307844}, \href
+  {http://adsabs.harvard.edu/abs/1999ApJ...524..527L} {524, 527}
+
+\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
+{Martin} C.~L.,  1998, \mn@doi [\apj] {10.1086/306219}, \href
+  {http://adsabs.harvard.edu/abs/1998ApJ...506..222M} {506, 222}
+
+\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
+  {Leitherer}, {Terlevich}  \& {Terlevich}}{{Mas-Hesse}
+  et~al.}{2003}]{mashesse03}
+{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
+  {Terlevich} R.~J.,   {Terlevich} E.,  2003, \mn@doi [\apj] {10.1086/379116},
+  \href {http://adsabs.harvard.edu/abs/2003ApJ...598..858M} {598, 858}
+
+\bibitem[\protect\citeauthoryear{{McCourt}, {Oh}, {O'Leary}  \&
+  {Madigan}}{{McCourt} et~al.}{2016}]{2016arXiv161001164M}
+{McCourt} M.,  {Oh} S.~P.,  {O'Leary} R.~M.,   {Madigan} A.-M.,  2016,
+  preprint, \href {http://esoads.eso.org/abs/2016arXiv161001164M} {}
+  (\mn@eprint {arXiv} {1610.01164})
+
+\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
+  {Ostriker}}{1977}]{1977ApJ...218..148M}
+{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \mn@doi [\apj] {10.1086/155667}, \href
+  {http://esoads.eso.org/abs/1977ApJ...218..148M} {218, 148}
+
+\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
+{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \mn@doi [\apj]
+  {10.3847/0004-637X/828/1/5}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...828....5M} {828, 5}
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
+{Neufeld} D.~A.,  1991, \mn@doi [\apjl] {10.1086/185983}, \href
+  {http://adsabs.harvard.edu/abs/1991ApJ...370L..85N} {370, L85}
+
+\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s}  \&
+  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
+{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,   {Fricke} K.~J.,  2003,
+  \mn@doi [\aap] {10.1051/0004-6361:20031147}, \href
+  {http://adsabs.harvard.edu/abs/2003A%26A...410..481N} {410, 481}
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh}  \& {Infante}}{{Orsi}
+  et~al.}{2008}]{2008MNRAS.391.1589O}
+{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,   {Infante} L.,  2008, \mn@doi
+  [\mnras] {10.1111/j.1365-2966.2008.14010.x}, \href
+  {http://adsabs.harvard.edu/abs/2008MNRAS.391.1589O} {391, 1589}
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}  \& {Baugh}}{{Orsi}
+  et~al.}{2012}]{Orsi12}
+{Orsi} A.,  {Lacey} C.~G.,   {Baugh} C.~M.,  2012, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2012.21396.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.425...87O} {425, 87}
+
+\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
+  et~al.}{2014}]{LARS}
+{{\"O}stlin} G.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/797/1/11},
+  \href {http://adsabs.harvard.edu/abs/2014ApJ...797...11O} {797, 11}
+
+\bibitem[\protect\citeauthoryear{{Ott}, {Walter}  \& {Brinks}}{{Ott}
+  et~al.}{2005}]{2005MNRAS.358.1453O}
+{Ott} J.,  {Walter} F.,   {Brinks} E.,  2005, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2005.08863.x}, \href
+  {http://adsabs.harvard.edu/abs/2005MNRAS.358.1453O} {358, 1453}
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
+  {Gonz{\'a}lez}, {Guaita}  \& {Infante}}{{Padilla}
+  et~al.}{2010}]{2010MNRAS.409..184P}
+{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
+  {Guaita} L.,   {Infante} L.,  2010, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2010.17317.x}, \href
+  {http://adsabs.harvard.edu/abs/2010MNRAS.409..184P} {409, 184}
+
+\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
+  {Peebles}}{1967}]{PartridgePeebles}
+{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \mn@doi [\apj] {10.1086/149079},
+  \href {http://adsabs.harvard.edu/abs/1967ApJ...147..868P} {147, 868}
+
+\bibitem[\protect\citeauthoryear{Pedregosa et~al.,}{Pedregosa
+  et~al.}{2011}]{scikit-learn}
+Pedregosa F.,  et~al., 2011, Journal of Machine Learning Research, 12, 2825
+
+\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
+  Granger}{2007}]{IPython}
+P\'erez F.,  Granger B.~E.,  2007, \mn@doi [Computing in Science and
+  Engineering] {10.1109/MCSE.2007.53}, 9, 21
+
+\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero}  \&
+  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
+{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,   {Mu{\~n}oz-Cuartas} J.~C.,
+  2016, \mn@doi [\apj] {10.3847/0004-637X/832/2/169}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...832..169P} {832, 169}
+
+\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
+  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
+{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
+  {Primack} J.,  2012, \mn@doi [\mnras] {10.1111/j.1365-2966.2012.21007.x},
+  \href {http://adsabs.harvard.edu/abs/2012MNRAS.423.3018P} {423, 3018}
+
+\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
+  {Martin}}{2007}]{pustilnikmartin07}
+{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \mn@doi [\aap]
+  {10.1051/0004-6361:20066137}, \href
+  {http://cdsads.u-strasbg.fr/abs/2007A%26A...464..859P} {464, 859}
+
+\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
+  et~al.}{2015}]{2015ApJ...805...14R}
+{Rivera-Thorsen} T.~E.,  et~al., 2015, \mn@doi [\apj]
+  {10.1088/0004-637X/805/1/14}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...805...14R} {805, 14}
+
+\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
+{Roth} M.~M.,  et~al., 2005, \mn@doi [\pasp] {10.1086/429877}, \href
+  {http://adsabs.harvard.edu/abs/2005PASP..117..620R} {117, 620}
+
+\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}  \& {Rakic}}{{Steidel}
+  et~al.}{2010}]{2010ApJ...717..289S}
+{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
+  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,   {Rakic} O.,  2010, \mn@doi [\apj]
+  {10.1088/0004-637X/717/1/289}, \href
+  {http://adsabs.harvard.edu/abs/2010ApJ...717..289S} {717, 289}
+
+\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada}  \& {van
+  der Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
+{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,   {van der Hulst} J.~M.,
+  2009, \mn@doi [\aap] {10.1051/0004-6361:200810516}, \href
+  {http://adsabs.harvard.edu/abs/2009A%26A...493..871S} {493, 871}
+
+\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
+{Tasitsiomi} A.,  2006, \mn@doi [\apj] {10.1086/504460}, \href
+  {http://adsabs.harvard.edu/abs/2006ApJ...645..792T} {645, 792}
+
+\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov}  \& {Gnedin}}{{Tassis}
+  et~al.}{2008}]{2008ApJ...672..888T}
+{Tassis} K.,  {Kravtsov} A.~V.,   {Gnedin} N.~Y.,  2008, \mn@doi [\apj]
+  {10.1086/523880}, \href {http://adsabs.harvard.edu/abs/2008ApJ...672..888T}
+  {672, 888}
+
+\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
+  {Izotov}}{1997}]{Thuan97}
+{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, \href
+  {http://adsabs.harvard.edu/abs/1997ApJ...489..623T} {489, 623}
+
+\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves}  \&
+  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
+{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,   {Wolf} J.,  2011,
+  \mn@doi [\apj] {10.1088/0004-637X/726/2/108}, \href
+  {http://adsabs.harvard.edu/abs/2011ApJ...726..108T} {726, 108}
+
+\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel}  \&
+  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
+{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,   {Rudie} G.~C.,  2016,
+  \mn@doi [\apj] {10.3847/0004-637X/832/2/171}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...832..171T} {832, 171}
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer}  \&
+  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
+{Verhamme} A.,  {Schaerer} D.,   {Maselli} A.,  2006, \mn@doi [\aap]
+  {10.1051/0004-6361:20065554}, \href
+  {http://adsabs.harvard.edu/abs/2006A%26A...460..397V} {460, 397}
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer}  \&
+  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
+{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,   {Hayes} M.,  2015, \mn@doi
+  [\aap] {10.1051/0004-6361/201423978}, \href
+  {http://adsabs.harvard.edu/abs/2015A%26A...578A...7V} {578, A7}
+
+\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
+  {Morimoto}  \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
+{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
+  {Umemura} M.,  2012, \mn@doi [\apj] {10.1088/0004-637X/751/1/29}, \href
+  {http://adsabs.harvard.edu/abs/2012ApJ...751...29Y} {751, 29}
+
+\makeatother
+\end{thebibliography}
 

### 2017-07-14 paper/paper.tex
coments removed

@@
 $v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
-\mg{These errors seem still pretty small to me. You obtained these via a Fisher matrix of a parabolic fit, right? How good was the fit? Are the off-diagonal elements included?}
-\jefr{The small uncertainty only says that the increase in
-  $\chi^2/dof$ is very steep as you vary a parameter. I don't think you can get larger errors
-  with the available data. Simple inspection of Figure 2 shows
-  that the errors will be small with the data we have. The
-  paremeter uncertainty roughly corresponds to the width of the parabola
-  when there is a difference of $\chi^2/dof\sim 1$ from the minimum. In the data we
-  have a huge jump of $\chi^2/dof$ of $\sim 5$ between the minimum
-  and the nearest data point. }
 
@@
 profile.
-
-\jefr{I find this paragraph confusing. Discussing an hypotetical case where
-all parameters are important undermines the explanation of our concrete case
-where only some parameters matter more. Probably we can remove it}.
-{\bf However, larger values of $f_{\rm cl}$ -- outside the here considered parameter range -- would re-introduce
-additional radiative transfer effects and thus increase the number of
-relevant parameters \citep[see ][for details]{2017arXiv170406278G}.   
-This means that even  
-if for clumply models the line profile is most sensitive to only
-a few parameters \citep{Gronke2016}, the rest of parameters
-affect the line profile at a level that cannot be neglected.}
-
-{\bf As a test we run a small set of $100$ additional radiative
-transfer simulations with random values for all parameters, except for
-$\sigma_{\rm cl}$, $P_{\rm cl}$ which are kept within the derived $3\sigma$
-constraints. We find that $30$ models show $\chi^2/d.o.f.<35$.
-That is, we have a $30\%$ chance to find good models, which is
-significanty higher than the lower $1\%$ success rate if the
-parameters were unconstrained.  }
-\mg{Is $1\sigma$ correct?}\jefr{I checked and only $\sigma_{cl}$ and
-  $P_{cl}$ were run within $3\sigma$. All the other parameters,
-  including $v_{\infty}$, were
-  unconstrained. Should we mention this test given that we didn't run
-  with a constrain on $v_{\infty}$?}
 
@@
 than \tol\ \citep{2015MNRAS.448.1767C}.
-\mg{I am confused -- are much lower rotational
-  velocities not exclude by the priors used?}\jefr{Yes, they are
-  discarded, but here we are talking about the most likely value of
-  350 km/s.}
 
@@
 $\chi^2/d.o.f.>35$, that is the limit that divides the best $1\%$ of
-the models from the rest. \mg{Why was $35$ chosen as a boundary?}\jefr{We
-  chose $35$ to match the cut that we used to make the  integrated
-  probability distributions. However the nuber itself is
-  arbitrary to have the $1\%$ of the initial number of models. 
-Ideally we should only chose models with $\chi^/dof$
-  higher by $2$ than the lowest $\chi^2/dof$, but we don't have any
-  models in that range.}
+the models from the rest. 
 The algorithm uses $500$ trees for the classification and a
@@
 $\chi^2/d.o.f.$.
-
-{\bf Furthermore, considering the sparse sampling of parameter space and the results
-from the random forest classifier, it is safer to consider that
-the best values for $\sigma_{\rm cl}$, $v_{\infty {\rm cl}}$, $P_{\rm
-  cl}$ are actually lower/upper/lower bounds, respectively.}
-\mg{This is interesting. Why do you think that? Could we use that to
-  increase the quoted errors? I am worried that the referee will
-  complain about the small errors.} \jefr{The referee didn't complain
-  about the small errors. And now that I see this with a bit more of
-  perspective, the tree classification always work with 'larger
-  than/less than' dualities. It would be unfair/unjustified to use that to justify
-our results as a lower bound. I suggest we remove this paragraph.}
 

### 2017-07-14 paper/paper.tex
new classification tree plot

@@
 We thank the referee for detailed comments and suggestions that
-improved this paper. 
+improved the paper. 
 We thank J. M. Mas-Hesse for providing us with \tol's observational
@@
 We are thankful to the community developing and maintining open source
-packages fundamental to our work: Jupyter notebook \citep{IPython,jupyter},
-matplotlib \citep{matplotlib}, astropy \citep{astropy} and
-scikit-learn \citep{scikit-learn}.
+packages fundamental to our work: numpy \& scipy \citep{numpy}, the
+Jupyter notebook \citep{IPython,jupyter}, matplotlib
+\citep{matplotlib}, astropy \citep{astropy},  scikit-learn
+\citep{scikit-learn}, pandas \citep{pandas} and daft
+(\url{http://daft-pgm.org/}).
 
@@
 
-\bibitem[\protect\citeauthoryear{{Gronke}, {Dijkstra}, {McCourt}  \&
-  {Oh}}{{Gronke} et~al.}{2017}]{2017arXiv170406278G}
-{Gronke} M.,  {Dijkstra} M.,  {McCourt} M.,   {Oh} S.~P.,  2017, preprint,
-  \href {http://esoads.eso.org/abs/2017arXiv170406278G} {} (\mn@eprint {arXiv}
-  {1704.06278})
-
 \bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
@@
   {http://esoads.eso.org/abs/1977ApJ...218..148M} {218, 148}
+
+\bibitem[\protect\citeauthoryear{McKinney et~al.}{McKinney
+  et~al.}{2010}]{pandas}
+McKinney W.,  et~al., 2010, in Proceedings of the 9th Python in Science
+  Conference. pp 51--56
 
@@
   {http://adsabs.harvard.edu/abs/2015A%26A...578A...7V} {578, A7}
+
+\bibitem[\protect\citeauthoryear{Walt, Colbert  \& Varoquaux}{Walt
+  et~al.}{2011}]{numpy}
+Walt S. v.~d.,  Colbert S.~C.,   Varoquaux G.,  2011, Computing in Science \&
+  Engineering, 13, 22
 
@@
 \begin{center}
-\includegraphics[width=0.95\textwidth]{tree_result.pdf}
+\includegraphics[width=0.95\textwidth]{classification_tree.pdf}
 \caption{Classification tree example. 

### 2017-07-17 paper/paper.tex
updated referee reply
explain random forest results

@@
 can estimate an escape fraction of $20$\% for \lya radiation.
+Figure \ref{fig:results} shows \tol's \lya\ profile reported by
+\cite{mashesse03}. This measurement as mede with the Space Telescope
+Imaging Spectrograph on board the Hubble Space Telescope, these
+observations have a spectral resolution of $\sim 37$\kms\ at the
+\lya\ wavelength.
 
@@
 
-Figure \ref{fig:tree} shows as an illustration the results for a
+Figure \ref{fig:tree} shows as an example the results for a
 single classification tree.
@@
 $\chi^2/d.o.f.$ classes, respectively. 
-We find that the best classification
+In this example the best classification
 yields $13$ and $44$ models in the low and high $\chi^2/d.o.f.$
@@
 $\sigma_{{\rm cl}}>55.6$ \kms and $P_{\rm cl}>0.683$.
-This means that these 3 parameters are the most useful parameters
-in finding models with low $\chi^2/d.o.f.$.
-
-The results of the random forest classifier yield that the clump outflow velocity
-$v_{\infty,\rm{cl}}$, the clump velocity dispersion $\sigma_{\rm cl}$ and the probability
-that the \lya emission comes from the clumps $P_{\rm cl}$, are the
-most influential parameters in finding a model with low
-$\chi^2/d.o.f.$.
+
+The results of the random forest classifier over $500$ trees yield
+that the clump outflow velocity $v_{\infty,\rm{cl}}$, the clump
+velocity dispersion $\sigma_{\rm cl}$ and the probability that the
+\lya emission comes from the clumps $P_{\rm cl}$, are the most
+influential parameters in finding a model with low $\chi^2/d.o.f.$.
 

### 2017-09-01 paper/paper.tex
updated abstract

@@
 bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
-We argue that the multiphase model has more chances to be correct.
+We argue that the results from the multiphase model are broadly
+consistent with observations of other CDGs. 
 The clump velocity dispersion implies a dynamical mass of $2\times
@@
 explained if \tol\ is hosted by a dark matter halo $6\times 10^{11}$
-M$_{\odot}$. If future kinematic maps of \tol\ confirm the velocities
-suggested by the multiphase model, it would provide additional support
-to expect this condition to be present  in primordial \lya emitting
-galaxies.   
+M$_{\odot}$. 
+If future kinematic maps of \tol\ confirm the velocities suggested by
+the multiphase model, it would provide additional support to expect
+such kinematic state in primordial \lya emitting galaxies.   
 \end{abstract}
@@
 models. 
+The hybrid case of a rotating multiphase configuration is also of
+interest, but cannot be simulated with in current models. 
+However, it is the subject of ongoing work  (Remolina-Gutierrez et
+al. in prep.).
 

### 2017-09-01 paper/paper.tex
new references updated disucssion

@@
 models.
-The hybrid case of a rotating multiphase configuration is also of
-interest, but cannot be simulated with in current models. 
-However, it is the subject of ongoing work  (Remolina-Gutierrez et
-al. in prep.).
 
@@
 
-Which model has more
-chances to be correct?  
+Which model could be closer to the actual kinematic conditions in \tol?  
+Recent Integral Field Unit (IFU) observation of other CDGs seem to
+favor the multiphse model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
+These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
+\citep{2003SPIE.4841.1670L}.
+The spatial smapling was $0.67$ arcseconds and covered about
+$30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
+They observed nine BCGs to produce two-dimensional maps of the
+continuum and promiment emission lines, this allowed them to produce 
+two-dimensional velocitity field maps using the H$\alpha$ emission
+line.
+They find velocity fields ranging from simple rotation patterns 
+(with amplitudes of $10-120\kms$) to highly irregular. 
+The velocity dispersion in most cases is typically less than $50$ \kms
+with the exception of one galaxy that shows a dispersion of $130$
+\kms.
+
+The hybrid case of a rotating multiphase configuration is also of
+interest, but cannot be simulated with in current models. 
+However, it is the subject of ongoing work  (Remolina-Gutierrez et
+al. in prep.).
+
 We argue that that the rotation model should be discarded by
@@
 \bibliographystyle{mnras}
-%\bibliography{references}
-\begin{thebibliography}{}
-\makeatletter
-\relax
-\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
-\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
-  {\mn@doi@[]}}
-\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
-  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
-  \endgroup}
-\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
-\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
-\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
-  {dblp:#1}}
-\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
-  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
-  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
-  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
-  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
-
-\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
-  Collaboration} et~al.}{2013}]{astropy}
-{Astropy Collaboration} et~al., 2013, \mn@doi [\aap]
-  {10.1051/0004-6361/201322068}, \href
-  {http://adsabs.harvard.edu/abs/2013A%26A...558A..33A} {558, A33}
-
-\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
-  et~al.}{2014}]{2014Msngr.157...13B}
-{Bacon} R.,  et~al., 2014, The Messenger, \href
-  {http://adsabs.harvard.edu/abs/2014Msngr.157...13B} {157, 13}
-
-\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur}  \&
-  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
-{Begum} A.,  {Chengalur} J.~N.,   {Karachentsev} I.~D.,  2005, \mn@doi [\aap]
-  {10.1051/0004-6361:200500026}, \href
-  {http://adsabs.harvard.edu/abs/2005A%26A...433L...1B} {433, L1}
-
-\bibitem[\protect\citeauthoryear{{Courtois}, {Zaritsky}, {Sorce}  \&
-  {Pomar{\`e}de}}{{Courtois} et~al.}{2015}]{2015MNRAS.448.1767C}
-{Courtois} H.~M.,  {Zaritsky} D.,  {Sorce} J.~G.,   {Pomar{\`e}de} D.,  2015,
-  \mn@doi [\mnras] {10.1093/mnras/stv071}, \href
-  {http://adsabs.harvard.edu/abs/2015MNRAS.448.1767C} {448, 1767}
-
-\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham}  \&
-  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
-{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,   {Chaffee} F.~H.,
-  1998, \mn@doi [\apjl] {10.1086/311331}, \href
-  {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}
-
-\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
-{Dijkstra} M.,  2014, \mn@doi [\pasa] {10.1017/pasa.2014.33}, \href
-  {http://adsabs.harvard.edu/abs/2014PASA...31...40D} {31, e040}
-
-\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
-  {Kramer}}{2012}]{2012MNRAS.424.1672D}
-{Dijkstra} M.,  {Kramer} R.,  2012, \mn@doi [\mnras]
-  {10.1111/j.1365-2966.2012.21131.x}, \href
-  {http://adsabs.harvard.edu/abs/2012MNRAS.424.1672D} {424, 1672}
-
-\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz}  \& {Wyithe}}{{Dijkstra}
-  et~al.}{2007}]{2007MNRAS.377.1175D}
-{Dijkstra} M.,  {Lidz} A.,   {Wyithe} J.~S.~B.,  2007, \mn@doi [\mnras]
-  {10.1111/j.1365-2966.2007.11666.x}, \href
-  {http://adsabs.harvard.edu/abs/2007MNRAS.377.1175D} {377, 1175}
-
-\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
-  {Werner}, {Moustakas}, {Willmer}  \& {Vanzi}}{{Engelbracht}
-  et~al.}{2008}]{2008ApJ...678..804E}
-{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
-  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,   {Vanzi} L.,  2008,
-  \mn@doi [\apj] {10.1086/529513}, \href
-  {http://adsabs.harvard.edu/abs/2008ApJ...678..804E} {678, 804}
-
-\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
-{Erb} D.~K.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/795/1/33}, \href
-  {http://adsabs.harvard.edu/abs/2014ApJ...795...33E} {795, 33}
-
-\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky}  \& {Meidt}}{{Eskew}
-  et~al.}{2012}]{2012AJ....143..139E}
-{Eskew} M.,  {Zaritsky} D.,   {Meidt} S.,  2012, \mn@doi [\aj]
-  {10.1088/0004-6256/143/6/139}, \href
-  {http://adsabs.harvard.edu/abs/2012AJ....143..139E} {143, 139}
-
-\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang}  \&
-  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
-{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,   {Goodman} J.,  2013, \mn@doi
-  [\pasp] {10.1086/670067}, \href
-  {http://adsabs.harvard.edu/abs/2013PASP..125..306F} {125, 306}
-
-\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
-  {Knollmann}, {Cuesta}  \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
-{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
-  {Cuesta} A.~J.,   {Prada} F.,  2011, \mn@doi [\mnras]
-  {10.1111/j.1365-2966.2011.18983.x}, \href
-  {http://adsabs.harvard.edu/abs/2011MNRAS.415.3666F} {415, 3666}
-
-\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva}  \&
-  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
-{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,   {Thuan}
-  T.~X.,  2001, \mn@doi [\aj] {10.1086/318016}, \href
-  {http://adsabs.harvard.edu/abs/2001AJ....121..169F} {121, 169}
-
-\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero}  \&
-  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
-{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,   {Dijkstra} M.,  2014,
-  \mn@doi [\apj] {10.1088/0004-637X/795/2/120}, \href
-  {http://adsabs.harvard.edu/abs/2014ApJ...795..120G} {795, 120}
-
-\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}}  \&
-  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
-{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,   {D{\'{\i}}az} {\'A}.~I.,
-  2013, \mn@doi [\mnras] {10.1093/mnras/stt1186}, \href
-  {http://adsabs.harvard.edu/abs/2013MNRAS.434.2491G} {434, 2491}
-
-\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
-  et~al.}{2007}]{2007ApJ...671..278G}
-{Gawiser} E.,  et~al., 2007, \mn@doi [\apj] {10.1086/522955}, \href
-  {http://adsabs.harvard.edu/abs/2007ApJ...671..278G} {671, 278}
-
-\bibitem[\protect\citeauthoryear{{Geha}, {Guhathakurta}  \& {van der
-  Marel}}{{Geha} et~al.}{2003}]{2003AJ....126.1794G}
-{Geha} M.,  {Guhathakurta} P.,   {van der Marel} R.~P.,  2003, \mn@doi [\aj]
-  {10.1086/377624}, \href {http://adsabs.harvard.edu/abs/2003AJ....126.1794G}
-  {126, 1794}
-
-\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
-  Weare}{2010}]{goodman2010ensemble}
-Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
-  computational science, 5, 65
-
-\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu}  \& {Wyithe}}{{Greig}
-  et~al.}{2013}]{2013MNRAS.431.1777G}
-{Greig} B.,  {Komatsu} E.,   {Wyithe} J.~S.~B.,  2013, \mn@doi [\mnras]
-  {10.1093/mnras/stt292}, \href
-  {http://adsabs.harvard.edu/abs/2013MNRAS.431.1777G} {431, 1777}
-
-\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
-  {Dijkstra}}{2016}]{Gronke2016}
-{Gronke} M.,  {Dijkstra} M.,  2016, \mn@doi [\apj]
-  {10.3847/0004-637X/826/1/14}, \href
-  {http://adsabs.harvard.edu/abs/2016ApJ...826...14G} {826, 14}
-
-\bibitem[\protect\citeauthoryear{{Gronke}, {Bull}  \& {Dijkstra}}{{Gronke}
-  et~al.}{2015}]{2015ApJ...812..123G}
-{Gronke} M.,  {Bull} P.,   {Dijkstra} M.,  2015, \mn@doi [\apj]
-  {10.1088/0004-637X/812/2/123}, \href
-  {http://adsabs.harvard.edu/abs/2015ApJ...812..123G} {812, 123}
-
-\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
-{Harrington} J.~P.,  1973, \mnras, \href
-  {http://adsabs.harvard.edu/abs/1973MNRAS.162...43H} {162, 43}
-
-\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
-  et~al.}{2004}]{2004AJ....128.2073H}
-{Hayashino} T.,  et~al., 2004, \mn@doi [\aj] {10.1086/424935}, \href
-  {http://adsabs.harvard.edu/abs/2004AJ....128.2073H} {128, 2073}
-
-\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
-{Hayes} M.,  2015, \mn@doi [\pasa] {10.1017/pasa.2015.25}, \href
-  {http://adsabs.harvard.edu/abs/2015PASA...32...27H} {32, e027}
-
-\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
-  et~al.}{2016}]{Herenz16}
-{Herenz} E.~C.,  et~al., 2016, \mn@doi [\aap] {10.1051/0004-6361/201527373},
-  \href {http://adsabs.harvard.edu/abs/2016A%26A...587A..78H} {587, A78}
-
-\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
-  {Storey}}{1987}]{Hummer1987}
-{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mn@doi [\mnras]
-  {10.1093/mnras/224.3.801}, \href
-  {http://adsabs.harvard.edu/abs/1987MNRAS.224..801H} {224, 801}
-
-\bibitem[\protect\citeauthoryear{{Hunter}}{{Hunter}}{2007}]{matplotlib}
-{Hunter} J.~D.,  2007, \mn@doi [Computing in Science and Engineering]
-  {10.1109/MCSE.2007.55}, \href
-  {http://adsabs.harvard.edu/abs/2007CSE.....9...90H} {9, 90}
-
-\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke}  \&
-  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
-{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,   {Thuan}
-  T.~X.,  2004, \mn@doi [\aap] {10.1051/0004-6361:20035847}, \href
-  {http://adsabs.harvard.edu/abs/2004A%26A...421..539I} {421, 539}
-
-\bibitem[\protect\citeauthoryear{James, Witten  \& Hastie}{James
-  et~al.}{2014}]{james2014introduction}
-James G.,  Witten D.,   Hastie T.,  2014, An Introduction to Statistical
-  Learning: With Applications in R.
-
-\bibitem[\protect\citeauthoryear{{Kennicutt}}{{Kennicutt}}{1998}]{Kennicutt98}
-{Kennicutt} Jr. R.~C.,  1998, \mn@doi [\araa] {10.1146/annurev.astro.36.1.189},
-  \href {http://adsabs.harvard.edu/abs/1998ARA%26A..36..189K} {36, 189}
-
-\bibitem[\protect\citeauthoryear{Kluyver et~al.,}{Kluyver
-  et~al.}{2016}]{jupyter}
-Kluyver T.,  et~al., 2016, in ELPUB. pp 87--90
-
-\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
-  {Malhotra}  \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
-{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,   {Wang}
-  J.,  2007, \mn@doi [\apj] {10.1086/520668}, \href
-  {http://adsabs.harvard.edu/abs/2007ApJ...668...15K} {668, 15}
-
-\bibitem[\protect\citeauthoryear{{Laursen}, {Duval}  \& {{\"O}stlin}}{{Laursen}
-  et~al.}{2013}]{Laursen2013ApJ...766..124L}
-{Laursen} P.,  {Duval} F.,   {{\"O}stlin} G.,  2013, \mn@doi [\apj]
-  {10.1088/0004-637X/766/2/124}, \href
-  {http://adsabs.harvard.edu/abs/2013ApJ...766..124L} {766, 124}
-
-\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
-  {Rybicki}}{1999}]{LoebRybicki}
-{Loeb} A.,  {Rybicki} G.~B.,  1999, \mn@doi [\apj] {10.1086/307844}, \href
-  {http://adsabs.harvard.edu/abs/1999ApJ...524..527L} {524, 527}
-
-\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
-{Martin} C.~L.,  1998, \mn@doi [\apj] {10.1086/306219}, \href
-  {http://adsabs.harvard.edu/abs/1998ApJ...506..222M} {506, 222}
-
-\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
-  {Leitherer}, {Terlevich}  \& {Terlevich}}{{Mas-Hesse}
-  et~al.}{2003}]{mashesse03}
-{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
-  {Terlevich} R.~J.,   {Terlevich} E.,  2003, \mn@doi [\apj] {10.1086/379116},
-  \href {http://adsabs.harvard.edu/abs/2003ApJ...598..858M} {598, 858}
-
-\bibitem[\protect\citeauthoryear{{McCourt}, {Oh}, {O'Leary}  \&
-  {Madigan}}{{McCourt} et~al.}{2016}]{2016arXiv161001164M}
-{McCourt} M.,  {Oh} S.~P.,  {O'Leary} R.~M.,   {Madigan} A.-M.,  2016,
-  preprint, \href {http://esoads.eso.org/abs/2016arXiv161001164M} {}
-  (\mn@eprint {arXiv} {1610.01164})
-
-\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
-  {Ostriker}}{1977}]{1977ApJ...218..148M}
-{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \mn@doi [\apj] {10.1086/155667}, \href
-  {http://esoads.eso.org/abs/1977ApJ...218..148M} {218, 148}
-
-\bibitem[\protect\citeauthoryear{McKinney et~al.}{McKinney
-  et~al.}{2010}]{pandas}
-McKinney W.,  et~al., 2010, in Proceedings of the 9th Python in Science
-  Conference. pp 51--56
-
-\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
-  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
-  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
-{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \mn@doi [\apj]
-  {10.3847/0004-637X/828/1/5}, \href
-  {http://adsabs.harvard.edu/abs/2016ApJ...828....5M} {828, 5}
-
-\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
-{Neufeld} D.~A.,  1991, \mn@doi [\apjl] {10.1086/185983}, \href
-  {http://adsabs.harvard.edu/abs/1991ApJ...370L..85N} {370, L85}
-
-\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s}  \&
-  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
-{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,   {Fricke} K.~J.,  2003,
-  \mn@doi [\aap] {10.1051/0004-6361:20031147}, \href
-  {http://adsabs.harvard.edu/abs/2003A%26A...410..481N} {410, 481}
-
-\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh}  \& {Infante}}{{Orsi}
-  et~al.}{2008}]{2008MNRAS.391.1589O}
-{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,   {Infante} L.,  2008, \mn@doi
-  [\mnras] {10.1111/j.1365-2966.2008.14010.x}, \href
-  {http://adsabs.harvard.edu/abs/2008MNRAS.391.1589O} {391, 1589}
-
-\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}  \& {Baugh}}{{Orsi}
-  et~al.}{2012}]{Orsi12}
-{Orsi} A.,  {Lacey} C.~G.,   {Baugh} C.~M.,  2012, \mn@doi [\mnras]
-  {10.1111/j.1365-2966.2012.21396.x}, \href
-  {http://adsabs.harvard.edu/abs/2012MNRAS.425...87O} {425, 87}
-
-\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
-  et~al.}{2014}]{LARS}
-{{\"O}stlin} G.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/797/1/11},
-  \href {http://adsabs.harvard.edu/abs/2014ApJ...797...11O} {797, 11}
-
-\bibitem[\protect\citeauthoryear{{Ott}, {Walter}  \& {Brinks}}{{Ott}
-  et~al.}{2005}]{2005MNRAS.358.1453O}
-{Ott} J.,  {Walter} F.,   {Brinks} E.,  2005, \mn@doi [\mnras]
-  {10.1111/j.1365-2966.2005.08863.x}, \href
-  {http://adsabs.harvard.edu/abs/2005MNRAS.358.1453O} {358, 1453}
-
-\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
-  {Gonz{\'a}lez}, {Guaita}  \& {Infante}}{{Padilla}
-  et~al.}{2010}]{2010MNRAS.409..184P}
-{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
-  {Guaita} L.,   {Infante} L.,  2010, \mn@doi [\mnras]
-  {10.1111/j.1365-2966.2010.17317.x}, \href
-  {http://adsabs.harvard.edu/abs/2010MNRAS.409..184P} {409, 184}
-
-\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
-  {Peebles}}{1967}]{PartridgePeebles}
-{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \mn@doi [\apj] {10.1086/149079},
-  \href {http://adsabs.harvard.edu/abs/1967ApJ...147..868P} {147, 868}
-
-\bibitem[\protect\citeauthoryear{Pedregosa et~al.,}{Pedregosa
-  et~al.}{2011}]{scikit-learn}
-Pedregosa F.,  et~al., 2011, Journal of Machine Learning Research, 12, 2825
-
-\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
-  Granger}{2007}]{IPython}
-P\'erez F.,  Granger B.~E.,  2007, \mn@doi [Computing in Science and
-  Engineering] {10.1109/MCSE.2007.53}, 9, 21
-
-\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero}  \&
-  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
-{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,   {Mu{\~n}oz-Cuartas} J.~C.,
-  2016, \mn@doi [\apj] {10.3847/0004-637X/832/2/169}, \href
-  {http://adsabs.harvard.edu/abs/2016ApJ...832..169P} {832, 169}
-
-\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
-  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
-{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
-  {Primack} J.,  2012, \mn@doi [\mnras] {10.1111/j.1365-2966.2012.21007.x},
-  \href {http://adsabs.harvard.edu/abs/2012MNRAS.423.3018P} {423, 3018}
-
-\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
-  {Martin}}{2007}]{pustilnikmartin07}
-{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \mn@doi [\aap]
-  {10.1051/0004-6361:20066137}, \href
-  {http://cdsads.u-strasbg.fr/abs/2007A%26A...464..859P} {464, 859}
-
-\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
-  et~al.}{2015}]{2015ApJ...805...14R}
-{Rivera-Thorsen} T.~E.,  et~al., 2015, \mn@doi [\apj]
-  {10.1088/0004-637X/805/1/14}, \href
-  {http://adsabs.harvard.edu/abs/2015ApJ...805...14R} {805, 14}
-
-\bibitem[\protect\citeauthoryear{{Roth} et~al.,}{{Roth} et~al.}{2005}]{PMAS}
-{Roth} M.~M.,  et~al., 2005, \mn@doi [\pasp] {10.1086/429877}, \href
-  {http://adsabs.harvard.edu/abs/2005PASP..117..620R} {117, 620}
-
-\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
-  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}  \& {Rakic}}{{Steidel}
-  et~al.}{2010}]{2010ApJ...717..289S}
-{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
-  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,   {Rakic} O.,  2010, \mn@doi [\apj]
-  {10.1088/0004-637X/717/1/289}, \href
-  {http://adsabs.harvard.edu/abs/2010ApJ...717..289S} {717, 289}
-
-\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada}  \& {van
-  der Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
-{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,   {van der Hulst} J.~M.,
-  2009, \mn@doi [\aap] {10.1051/0004-6361:200810516}, \href
-  {http://adsabs.harvard.edu/abs/2009A%26A...493..871S} {493, 871}
-
-\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
-{Tasitsiomi} A.,  2006, \mn@doi [\apj] {10.1086/504460}, \href
-  {http://adsabs.harvard.edu/abs/2006ApJ...645..792T} {645, 792}
-
-\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov}  \& {Gnedin}}{{Tassis}
-  et~al.}{2008}]{2008ApJ...672..888T}
-{Tassis} K.,  {Kravtsov} A.~V.,   {Gnedin} N.~Y.,  2008, \mn@doi [\apj]
-  {10.1086/523880}, \href {http://adsabs.harvard.edu/abs/2008ApJ...672..888T}
-  {672, 888}
-
-\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
-  {Izotov}}{1997}]{Thuan97}
-{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, \href
-  {http://adsabs.harvard.edu/abs/1997ApJ...489..623T} {489, 623}
-
-\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves}  \&
-  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
-{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,   {Wolf} J.,  2011,
-  \mn@doi [\apj] {10.1088/0004-637X/726/2/108}, \href
-  {http://adsabs.harvard.edu/abs/2011ApJ...726..108T} {726, 108}
-
-\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel}  \&
-  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
-{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,   {Rudie} G.~C.,  2016,
-  \mn@doi [\apj] {10.3847/0004-637X/832/2/171}, \href
-  {http://adsabs.harvard.edu/abs/2016ApJ...832..171T} {832, 171}
-
-\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer}  \&
-  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
-{Verhamme} A.,  {Schaerer} D.,   {Maselli} A.,  2006, \mn@doi [\aap]
-  {10.1051/0004-6361:20065554}, \href
-  {http://adsabs.harvard.edu/abs/2006A%26A...460..397V} {460, 397}
-
-\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer}  \&
-  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
-{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,   {Hayes} M.,  2015, \mn@doi
-  [\aap] {10.1051/0004-6361/201423978}, \href
-  {http://adsabs.harvard.edu/abs/2015A%26A...578A...7V} {578, A7}
-
-\bibitem[\protect\citeauthoryear{Walt, Colbert  \& Varoquaux}{Walt
-  et~al.}{2011}]{numpy}
-Walt S. v.~d.,  Colbert S.~C.,   Varoquaux G.,  2011, Computing in Science \&
-  Engineering, 13, 22
-
-\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
-  {Morimoto}  \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
-{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
-  {Umemura} M.,  2012, \mn@doi [\apj] {10.1088/0004-637X/751/1/29}, \href
-  {http://adsabs.harvard.edu/abs/2012ApJ...751...29Y} {751, 29}
-
-\makeatother
-\end{thebibliography}
+\bibliography{references}
 

### 2017-09-01 paper/paper.tex
new discussion + new references

@@
 consistent with observations of other CDGs. 
-The clump velocity dispersion implies a dynamical mass of $2\times
-10^{9}$ M$_{\odot}$, ten times its baryonic mass, which can be
-explained if \tol\ is hosted by a dark matter halo $6\times 10^{11}$
-M$_{\odot}$. 
+If \tol\ is dispersion dominated, the clump velocity dispersion
+implies a dynamical mass of $2\times 10^{9}$ M$_{\odot}$, ten times
+its baryonic mass, which can be explained if \tol\ is hosted by a dark
+matter halo $6\times 10^{11}$ M$_{\odot}$. 
 If future kinematic maps of \tol\ confirm the velocities suggested by
@@
 
+Observations of other Compact Dwarf Galaxies (CDGs) also show 
+that the kinematics can renge from pure rotation and low velocity
+dispersion to high velocity dispersion without rotaion.
+\citep{2015A&A...577A..21C,2017A&A...600A.125C}.
+
 The models we use correspond to simplified geometrical configurations.
@@
 models. 
+The hybrid case of a rotating multiphase configuration
+(as observed in some of the galaxies in \cite{2015A&A...577A..21C}) is
+the subject of ongoing research (Remolina-Gutierrez et al. in prep.).  as
+it cannot be simulated with existing models.
 
@@
 Which model could be closer to the actual kinematic conditions in \tol?  
-Recent Integral Field Unit (IFU) observation of other CDGs seem to
-favor the multiphse model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
+Recent Integral Field Unit (IFU) observations of other CDGs seem to
+favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
 These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
 \citep{2003SPIE.4841.1670L}.
-The spatial smapling was $0.67$ arcseconds and covered about
+The spatial smapling was $0.67^{\prime\prime}$ and covered about
 $30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
@@
 They find velocity fields ranging from simple rotation patterns 
-(with amplitudes of $10-120\kms$) to highly irregular. 
-The velocity dispersion in most cases is typically less than $50$ \kms
+(with amplitudes of $10-120$ \kms) to highly irregular. 
+The typical velocity dispersion values are in the range $10-50$ \kms
 with the exception of one galaxy that shows a dispersion of $130$
@@
 
-The hybrid case of a rotating multiphase configuration is also of
-interest, but cannot be simulated with in current models. 
-However, it is the subject of ongoing work  (Remolina-Gutierrez et
-al. in prep.).
+These results disfavor the high rotational velocity of $V_{m}\sim350$
+\kms\  that we find in the pure rotation model. 
+On the other hand the results from the multiphase model yield a
+velocity dispersion $\sigma=$\sigmaclump, quite close to observed
+values in other CDG, favoring the multiphase model.
 
-We argue that that the rotation model should be discarded by
-considering that the prefered rotational velocity of $V_{m}\sim350$
-\kms\ is of the same order as the largest rotational velocity of giant
-disc galaxies that have two orders of magnitude more baryonic mass
-than \tol\ \citep{2015MNRAS.448.1767C}.
-
-Furthermore, \tol's structural properties seem to be similar to known dwarf
-elliptical (dE) galaxies. 
-The sample of 7 dE galaxies observed by
-\cite{2003AJ....126.1794G} shows similar properties as \tol. 
-For instance, the dE galaxies IC 3344 and IC 794 have similar absolute $M_V$
-magnitudes (-17.10 and -17.19) and sizes (0.90 kpc and 0.82 kpc) as
-\tol. 
-These dE galaxies have velocity dispersions of $31.1$ \kms and
-$44.6$ \kms, respectively,  and their rotational velocities are lower
-than $1$ \kms.  
-This leads us to prefer the multiphase model as it provides 
-a broad consistency with kinematic properties of dE galaxies.
-
-Following the results of \cite{2011ApJ...726..108T}, who made a
-detailed analysis for all kind of elliptical galaxies including dE galaxies, we
-estimate a value for the dynamical mass using the constraints for
-the velocity dispersion, $\sigma$,  in a spherical system localized in a
-region of size $r$
+In this case we can  estimate a value for the dynamical
+mass using the constraints for the velocity dispersion, $\sigma$,  in
+a spherical system localized in a region of size $r$
 
@@
 for the HI region, in the multiphase model the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump thus corresponds to a dynamical mass of
+$\sigma_{\rm{cl}}=$\sigmaclump\  corresponds to a dynamical mass of
 $M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
 times the estimated baryonic mass in \tol.
+This would mean that \tol\ is dark matter dominated.
 
-Figure \ref{fig:mass} illustrates  how such dynamical
-mass can be explained if \tol\ is hosted by a dark matter halo of at
-$\sim 6\times 10^{11}$ M$_{\odot}$ in virial mass. 
+Following the methodology of \citet{2011ApJ...726..108T} we estimate 
+that a dark matter halo of at $\sim 6\times 10^{11}$ M$_{\odot}$ in
+virial mass can explain this dynamical mass.
 This estimate is based on computing the integrated mass profile of a
@@
 \citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
+Figure \ref{fig:mass} shows the enclosed mass as a function of radius
+for different dark matter halos and the estimates for \tol.
 
-These results would imply that \tol\ is part of the dE
-class. 
-However, this hypothesis opens up two puzzles.
-First, dE galaxies are found either in clusters or groups of
-galaxies; while \tol\ does not belong either to a group or a cluster
-\citep{2001AJ....121..169F}. 
-The second issue is that, unlike a dE, \tol\ hosts a bright and compact
-starburst; imaging and spectroscopy studies suggest that the
-starburst started less than 4 Myr ago, while the low surface
-brightness regins are consistent with an age below one Gyr
-\citep{2001AJ....121..169F}.
-
-We suggest that new observational tests are needed to clarify the
-kinematic nature of \tol.
-Integral field unit measurements resolving its spatial extent are up
-to the task.  
-\tol\ spans a region of $4$ arcseconds,
-an instrument such as the Multi Unit Spectroscopic Explorer (MUSE)
-\citep{2014Msngr.157...13B} with its nominal $0.2$ arcseconds spatial
-sampling over a $1.0$ arcminute field in wide-field mode could provide
-a coarse mapping of different ionization lines to infer a kinematic
-map in the H$\alpha$ line, following the kind of work presented by
-\citet{Herenz16} done with the Potsdam Multi-Aperture Spectrometer
-(PMAS) \citep{PMAS} on nearby \lya emitting galaxies.
-
-Another observational hint to clarify \tol's state could be
-the measurement of the \lya ionizing continuum escape fraction. 
-The multiphase model predicts that averaging over all sightlines
-it should be around $0.5^{+1.0}_{-0.4}$\%, with the possibility of strong
-variations depending on viewing angle, i.e. some sightlines can have
-an escape fraction close to $100\%$ \citep{Gronke2016}.
+New IFU observations are needed to completeley confirm \tol's.
+This could be done with the Multi Unit Spectroscopic Explorer (MUSE) 
+\citep{2014Msngr.157...13B}, the Gemini Multi-Object Spectrographs (GMOS) 
+\citep{2004PASP..116..425H} or the Fibre Large Array Multi Element
+Spectrograph (\citep{2002Msngr.110....1P})
 
@@
 In this particular case, we prefer the multiphase model because it has kinematic
-conditions similar to those in dwarf ellipticals, while the
+conditions similar to those in similar compact dwarf galaxies observed
+with integral field unit spectroscopy, while the
 rotational model produces rotational velocities too high for a dwarf
 galaxy.  
-
-However, \tol's environment and star forming activity are radically
-different from those of dwarf ellipticals.
-We suggest that additional integral field unit observations are the
-only way to be certain about the detailed kinematic structure in \tol.
+New IFU observations are the only way to be certain about the detailed
+kinematic structure in \tol.
 

### 2017-09-01 paper/paper.tex
update body + abstract

@@
 the multiphase model, it would provide additional support to expect
-such kinematic state in primordial \lya emitting galaxies.   
+such kinematic state in primordial \lya emitting galaxies which in
+turn can help to constrain star formation and feedback in the first
+generation of galaxies.
 \end{abstract}
@@
 
-Observations of other Compact Dwarf Galaxies (CDGs) also show 
-that the kinematics can renge from pure rotation and low velocity
-dispersion to high velocity dispersion without rotaion.
+Furthermore, observations of other Compact Dwarf Galaxies (CDGs) also show 
+that the kinematics range from pure rotation and low velocity
+dispersion to high velocity dispersion without rotaion
 \citep{2015A&A...577A..21C,2017A&A...600A.125C}.
@@
 (as observed in some of the galaxies in \cite{2015A&A...577A..21C}) is
-the subject of ongoing research (Remolina-Gutierrez et al. in prep.).  as
+the subject of ongoing research (Remolina-Gutierrez et al. in prep.)  as
 it cannot be simulated with existing models.
@@
 values in other CDG, favoring the multiphase model.
-
 In this case we can  estimate a value for the dynamical
@@
 Figure \ref{fig:mass} shows the enclosed mass as a function of radius
-for different dark matter halos and the estimates for \tol.
+for different dark matter halos together with the \tol's dynamical
+mass estimate.
 
@@
 \citep{2004PASP..116..425H} or the Fibre Large Array Multi Element
-Spectrograph (\citep{2002Msngr.110....1P})
+Spectrograph (\citep{2002Msngr.110....1P}) as they have the spatial
+resolution and field of view required to perform the kind of study
+presented by \citep{2015A&A...577A..21C} on CDGs or \citep{Herenz16}
+in nearby \lya\ emitting galaxies.
 

### 2017-09-01 paper/paper.tex
updating referee reply and text

--- 2017-09-01 paper/paper.tex
@@
 bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
-We argue that the results from the multiphase model are broadly
-consistent with observations of other CDGs. 
-If \tol\ is dispersion dominated, the clump velocity dispersion
-implies a dynamical mass of $2\times 10^{9}$ M$_{\odot}$, ten times
-its baryonic mass, which can be explained if \tol\ is hosted by a dark
-matter halo $6\times 10^{11}$ M$_{\odot}$. 
+{\bf We argue that the results from the multiphase model 
+provides a correct interpretation of the data.
+In that case the clump velocity dispersion implies a dynamical mass of
+$2\times 10^{9}$ M$_{\odot}$,  ten times its baryonic mass.}
 If future kinematic maps of \tol\ confirm the velocities suggested by
 the multiphase model, it would provide additional support to expect
-such kinematic state in primordial \lya emitting galaxies.   
+such kinematic state in primordial \lya emitting galaxies {\bf which in
+turn can help to constrain star formation and feedback in the first
+generation of galaxies.}
 \end{abstract}
@@
 in a range of astrophysical systems
-\citep[][]{1977ApJ...218..148M,2016arXiv161001164M}.
-
-The motivation for the rotation without outflows as presented in
-\citep[as presented in]{GaravitoCamargo2014} is that dwarf galaxies show coherent
+\citep[][]{1977ApJ...218..148M}.
+
+The motivation for the rotation without outflows 
+\citep[as presented in][]{GaravitoCamargo2014} is that dwarf galaxies show coherent
 rotation features  \citep{2009A&A...493..871S} and it is expected that
@@
 
-Observations of other Compact Dwarf Galaxies (CDGs) also show 
-that the kinematics can renge from pure rotation and low velocity
-dispersion to high velocity dispersion without rotaion.
-\citep{2015A&A...577A..21C,2017A&A...600A.125C}.
+{\bf Furthermore, observations of other Compact Dwarf Galaxies (CDGs) also show 
+that the kinematics range from pure rotation and low velocity
+dispersion to high velocity dispersion without rotaion
+\citep{2015A&A...577A..21C,2017A&A...600A.125C}. }
 
@@
 models. 
-The hybrid case of a rotating multiphase configuration
-(as observed in some of the galaxies in \cite{2015A&A...577A..21C}) is
-the subject of ongoing research (Remolina-Gutierrez et al. in prep.).  as
-it cannot be simulated with existing models.
+{\bf The hybrid case of a rotating multiphase configuration
+is the subject of ongoing research (Remolina-Gutierrez et al. in
+prep.)  as it cannot be simulated with existing models.  }
 
@@
 Figure \ref{fig:results} shows \tol's \lya\ profile reported by
-\cite{mashesse03}. This measurement as mede with the Space Telescope
+\cite{mashesse03}. This measurement was made with the Space Telescope
 Imaging Spectrograph on board the Hubble Space Telescope, these
@@
 
-Which model could be closer to the actual kinematic conditions in \tol?  
+{\bf Which model could be closer to the actual kinematic conditions in \tol?  
 Recent Integral Field Unit (IFU) observations of other CDGs seem to
@@
 with the exception of one galaxy that shows a dispersion of $130$
-\kms.
-
-These results disfavor the high rotational velocity of $V_{m}\sim350$
+\kms. }
+
+{\bf These results disfavor the high rotational velocity of $V_{m}\sim350$
 \kms\  that we find in the pure rotation model. 
@@
 velocity dispersion $\sigma=$\sigmaclump, quite close to observed
-values in other CDG, favoring the multiphase model.
-
+values in other CDG, favoring the multiphase model.}
 In this case we can  estimate a value for the dynamical
@@
 Following the methodology of \citet{2011ApJ...726..108T} we estimate
-that a dark matter halo of at $\sim 6\times 10^{11}$ M$_{\odot}$ in
-virial mass can explain this dynamical mass.
+that a dark matter halo of $\sim 6\times 10^{11}$ M$_{\odot}$ in
+virial mass {\bf and virial radius $220$ kpc } could explain this dynamical mass.
 This estimate is based on computing the integrated mass profile of a
@@
 \citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
+{\bf This estimate should be considered an upper bound, lower values
+  could be achieved if one considers instead a cored profile.}
 Figure \ref{fig:mass} shows the enclosed mass as a function of radius
-for different dark matter halos and the estimates for \tol.
-
-New IFU observations are needed to completeley confirm \tol's.
+for different dark matter halos together with the \tol's dynamical
+mass estimate. 
+{\bf This estimate and the validity of its assumptions can only be
+  verified by detailed mass modelling once \tol's full rotation curve
+  becomes available.}
+
+{\bf New IFU observations are needed to confirm \tol's kinematics.
 This could be done with the Multi Unit Spectroscopic Explorer (MUSE) 
@@
 \citep{2004PASP..116..425H} or the Fibre Large Array Multi Element
-Spectrograph (\citep{2002Msngr.110....1P})
+Spectrograph (FLAMES) \citep{2002Msngr.110....1P} as they have the spatial
+resolution and field of view required to perform the kind of study
+presented by \citet{2015A&A...577A..21C} on CDGs or \citet{Herenz16}
+onnearby \lya\ emitting galaxies.}
 
@@
 \caption{Enclosed mass in a spherical system as a function of radius.
-  Lines correspond to the expectation for dark matter halos with
+  Lines correspond to the expectation for dark matter halos following
+  an NFW profile with
   different viral masses as shown in the legend, the arrow corresponds
@@
   $\sim 6\times10^{11}$ M$_{\odot}$ in mass.
+  {\bf Lower mass estimates could be possible if one considers instead a
+  cored profile. }
     \label{fig:mass}} 
@@
 \bibliographystyle{mnras}
-\bibliography{references}
+%\bibliography{references}
+\begin{thebibliography}{}
+\makeatletter
+\relax
+\def\mn@urlcharsother{\let\do\@makeother \do\$\do\&\do\#\do\^\do\_\do\%\do\~}
+\def\mn@doi{\begingroup\mn@urlcharsother \@ifnextchar [ {\mn@doi@}
+  {\mn@doi@[]}}
+\def\mn@doi@[#1]#2{\def\@tempa{#1}\ifx\@tempa\@empty \href
+  {http://dx.doi.org/#2} {doi:#2}\else \href {http://dx.doi.org/#2} {#1}\fi
+  \endgroup}
+\def\mn@eprint#1#2{\mn@eprint@#1:#2::\@nil}
+\def\mn@eprint@arXiv#1{\href {http://arxiv.org/abs/#1} {{\tt arXiv:#1}}}
+\def\mn@eprint@dblp#1{\href {http://dblp.uni-trier.de/rec/bibtex/#1.xml}
+  {dblp:#1}}
+\def\mn@eprint@#1:#2:#3:#4\@nil{\def\@tempa {#1}\def\@tempb {#2}\def\@tempc
+  {#3}\ifx \@tempc \@empty \let \@tempc \@tempb \let \@tempb \@tempa \fi \ifx
+  \@tempb \@empty \def\@tempb {arXiv}\fi \@ifundefined
+  {mn@eprint@\@tempb}{\@tempb:\@tempc}{\expandafter \expandafter \csname
+  mn@eprint@\@tempb\endcsname \expandafter{\@tempc}}}
+
+\bibitem[\protect\citeauthoryear{{Astropy Collaboration} et~al.,}{{Astropy
+  Collaboration} et~al.}{2013}]{astropy}
+{Astropy Collaboration} et~al., 2013, \mn@doi [\aap]
+  {10.1051/0004-6361/201322068}, \href
+  {http://adsabs.harvard.edu/abs/2013A%26A...558A..33A} {558, A33}
+
+\bibitem[\protect\citeauthoryear{{Bacon} et~al.,}{{Bacon}
+  et~al.}{2014}]{2014Msngr.157...13B}
+{Bacon} R.,  et~al., 2014, The Messenger, \href
+  {http://adsabs.harvard.edu/abs/2014Msngr.157...13B} {157, 13}
+
+\bibitem[\protect\citeauthoryear{{Begum}, {Chengalur}  \&
+  {Karachentsev}}{{Begum} et~al.}{2005}]{2005A&A...433L...1B}
+{Begum} A.,  {Chengalur} J.~N.,   {Karachentsev} I.~D.,  2005, \mn@doi [\aap]
+  {10.1051/0004-6361:200500026}, \href
+  {http://adsabs.harvard.edu/abs/2005A%26A...433L...1B} {433, L1}
+
+\bibitem[\protect\citeauthoryear{{Cair{\'o}s} \&
+  {Gonz{\'a}lez-P{\'e}rez}}{{Cair{\'o}s} \&
+  {Gonz{\'a}lez-P{\'e}rez}}{2017}]{2017A&A...600A.125C}
+{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017, \mn@doi [\aap]
+  {10.1051/0004-6361/201629681}, \href
+  {http://adsabs.harvard.edu/abs/2017A%26A...600A.125C} {600, A125}
+
+\bibitem[\protect\citeauthoryear{{Cair{\'o}s}, {Caon}  \&
+  {Weilbacher}}{{Cair{\'o}s} et~al.}{2015}]{2015A&A...577A..21C}
+{Cair{\'o}s} L.~M.,  {Caon} N.,   {Weilbacher} P.~M.,  2015, \mn@doi [\aap]
+  {10.1051/0004-6361/201322518}, \href
+  {http://adsabs.harvard.edu/abs/2015A%26A...577A..21C} {577, A21}
+
+\bibitem[\protect\citeauthoryear{{Dey}, {Spinrad}, {Stern}, {Graham}  \&
+  {Chaffee}}{{Dey} et~al.}{1998}]{1998ApJ...498L..93D}
+{Dey} A.,  {Spinrad} H.,  {Stern} D.,  {Graham} J.~R.,   {Chaffee} F.~H.,
+  1998, \mn@doi [\apjl] {10.1086/311331}, \href
+  {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}}{{Dijkstra}}{2014}]{2014PASA...31...40D}
+{Dijkstra} M.,  2014, \mn@doi [\pasa] {10.1017/pasa.2014.33}, \href
+  {http://adsabs.harvard.edu/abs/2014PASA...31...40D} {31, e040}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra} \& {Kramer}}{{Dijkstra} \&
+  {Kramer}}{2012}]{2012MNRAS.424.1672D}
+{Dijkstra} M.,  {Kramer} R.,  2012, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2012.21131.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.424.1672D} {424, 1672}
+
+\bibitem[\protect\citeauthoryear{{Dijkstra}, {Lidz}  \& {Wyithe}}{{Dijkstra}
+  et~al.}{2007}]{2007MNRAS.377.1175D}
+{Dijkstra} M.,  {Lidz} A.,   {Wyithe} J.~S.~B.,  2007, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2007.11666.x}, \href
+  {http://adsabs.harvard.edu/abs/2007MNRAS.377.1175D} {377, 1175}
+
+\bibitem[\protect\citeauthoryear{{Engelbracht}, {Rieke}, {Gordon}, {Smith},
+  {Werner}, {Moustakas}, {Willmer}  \& {Vanzi}}{{Engelbracht}
+  et~al.}{2008}]{2008ApJ...678..804E}
+{Engelbracht} C.~W.,  {Rieke} G.~H.,  {Gordon} K.~D.,  {Smith} J.-D.~T.,
+  {Werner} M.~W.,  {Moustakas} J.,  {Willmer} C.~N.~A.,   {Vanzi} L.,  2008,
+  \mn@doi [\apj] {10.1086/529513}, \href
+  {http://adsabs.harvard.edu/abs/2008ApJ...678..804E} {678, 804}
+
+\bibitem[\protect\citeauthoryear{{Erb} et~al.,}{{Erb} et~al.}{2014}]{Erb14}
+{Erb} D.~K.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/795/1/33}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...795...33E} {795, 33}
+
+\bibitem[\protect\citeauthoryear{{Eskew}, {Zaritsky}  \& {Meidt}}{{Eskew}
+  et~al.}{2012}]{2012AJ....143..139E}
+{Eskew} M.,  {Zaritsky} D.,   {Meidt} S.,  2012, \mn@doi [\aj]
+  {10.1088/0004-6256/143/6/139}, \href
+  {http://adsabs.harvard.edu/abs/2012AJ....143..139E} {143, 139}
+
+\bibitem[\protect\citeauthoryear{{Foreman-Mackey}, {Hogg}, {Lang}  \&
+  {Goodman}}{{Foreman-Mackey} et~al.}{2013}]{2013PASP..125..306F}
+{Foreman-Mackey} D.,  {Hogg} D.~W.,  {Lang} D.,   {Goodman} J.,  2013, \mn@doi
+  [\pasp] {10.1086/670067}, \href
+  {http://adsabs.harvard.edu/abs/2013PASP..125..306F} {125, 306}
+
+\bibitem[\protect\citeauthoryear{{Forero-Romero}, {Yepes}, {Gottl{\"o}ber},
+  {Knollmann}, {Cuesta}  \& {Prada}}{{Forero-Romero} et~al.}{2011}]{CLARA}
+{Forero-Romero} J.~E.,  {Yepes} G.,  {Gottl{\"o}ber} S.,  {Knollmann} S.~R.,
+  {Cuesta} A.~J.,   {Prada} F.,  2011, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2011.18983.x}, \href
+  {http://adsabs.harvard.edu/abs/2011MNRAS.415.3666F} {415, 3666}
+
+\bibitem[\protect\citeauthoryear{{Fricke}, {Izotov}, {Papaderos}, {Guseva}  \&
+  {Thuan}}{{Fricke} et~al.}{2001}]{2001AJ....121..169F}
+{Fricke} K.~J.,  {Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,   {Thuan}
+  T.~X.,  2001, \mn@doi [\aj] {10.1086/318016}, \href
+  {http://adsabs.harvard.edu/abs/2001AJ....121..169F} {121, 169}
+
+\bibitem[\protect\citeauthoryear{{Garavito-Camargo}, {Forero-Romero}  \&
+  {Dijkstra}}{{Garavito-Camargo} et~al.}{2014}]{GaravitoCamargo2014}
+{Garavito-Camargo} J.~N.,  {Forero-Romero} J.~E.,   {Dijkstra} M.,  2014,
+  \mn@doi [\apj] {10.1088/0004-637X/795/2/120}, \href
+  {http://adsabs.harvard.edu/abs/2014ApJ...795..120G} {795, 120}
+
+\bibitem[\protect\citeauthoryear{{Gavil{\'a}n}, {Ascasibar}, {Moll{\'a}}  \&
+  {D{\'{\i}}az}}{{Gavil{\'a}n} et~al.}{2013}]{2013MNRAS.434.2491G}
+{Gavil{\'a}n} M.,  {Ascasibar} Y.,  {Moll{\'a}} M.,   {D{\'{\i}}az} {\'A}.~I.,
+  2013, \mn@doi [\mnras] {10.1093/mnras/stt1186}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.434.2491G} {434, 2491}
+
+\bibitem[\protect\citeauthoryear{{Gawiser} et~al.,}{{Gawiser}
+  et~al.}{2007}]{2007ApJ...671..278G}
+{Gawiser} E.,  et~al., 2007, \mn@doi [\apj] {10.1086/522955}, \href
+  {http://adsabs.harvard.edu/abs/2007ApJ...671..278G} {671, 278}
+
+\bibitem[\protect\citeauthoryear{Goodman \& Weare}{Goodman \&
+  Weare}{2010}]{goodman2010ensemble}
+Goodman J.,  Weare J.,  2010, Communications in applied mathematics and
+  computational science, 5, 65
+
+\bibitem[\protect\citeauthoryear{{Greig}, {Komatsu}  \& {Wyithe}}{{Greig}
+  et~al.}{2013}]{2013MNRAS.431.1777G}
+{Greig} B.,  {Komatsu} E.,   {Wyithe} J.~S.~B.,  2013, \mn@doi [\mnras]
+  {10.1093/mnras/stt292}, \href
+  {http://adsabs.harvard.edu/abs/2013MNRAS.431.1777G} {431, 1777}
+
+\bibitem[\protect\citeauthoryear{{Gronke} \& {Dijkstra}}{{Gronke} \&
+  {Dijkstra}}{2016}]{Gronke2016}
+{Gronke} M.,  {Dijkstra} M.,  2016, \mn@doi [\apj]
+  {10.3847/0004-637X/826/1/14}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...826...14G} {826, 14}
+
+\bibitem[\protect\citeauthoryear{{Gronke}, {Bull}  \& {Dijkstra}}{{Gronke}
+  et~al.}{2015}]{2015ApJ...812..123G}
+{Gronke} M.,  {Bull} P.,   {Dijkstra} M.,  2015, \mn@doi [\apj]
+  {10.1088/0004-637X/812/2/123}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...812..123G} {812, 123}
+
+\bibitem[\protect\citeauthoryear{{Harrington}}{{Harrington}}{1973}]{Harrington73}
+{Harrington} J.~P.,  1973, \mnras, \href
+  {http://adsabs.harvard.edu/abs/1973MNRAS.162...43H} {162, 43}
+
+\bibitem[\protect\citeauthoryear{{Hayashino} et~al.,}{{Hayashino}
+  et~al.}{2004}]{2004AJ....128.2073H}
+{Hayashino} T.,  et~al., 2004, \mn@doi [\aj] {10.1086/424935}, \href
+  {http://adsabs.harvard.edu/abs/2004AJ....128.2073H} {128, 2073}
+
+\bibitem[\protect\citeauthoryear{{Hayes}}{{Hayes}}{2015}]{Hayes15}
+{Hayes} M.,  2015, \mn@doi [\pasa] {10.1017/pasa.2015.25}, \href
+  {http://adsabs.harvard.edu/abs/2015PASA...32...27H} {32, e027}
+
+\bibitem[\protect\citeauthoryear{{Herenz} et~al.,}{{Herenz}
+  et~al.}{2016}]{Herenz16}
+{Herenz} E.~C.,  et~al., 2016, \mn@doi [\aap] {10.1051/0004-6361/201527373},
+  \href {http://adsabs.harvard.edu/abs/2016A%26A...587A..78H} {587, A78}
+
+\bibitem[\protect\citeauthoryear{{Hook}, {J{\o}rgensen}, {Allington-Smith},
+  {Davies}, {Metcalfe}, {Murowinski}  \& {Crampton}}{{Hook}
+  et~al.}{2004}]{2004PASP..116..425H}
+{Hook} I.~M.,  {J{\o}rgensen} I.,  {Allington-Smith} J.~R.,  {Davies} R.~L.,
+  {Metcalfe} N.,  {Murowinski} R.~G.,   {Crampton} D.,  2004, \mn@doi [\pasp]
+  {10.1086/383624}, \href {http://adsabs.harvard.edu/abs/2004PASP..116..425H}
+  {116, 425}
+
+\bibitem[\protect\citeauthoryear{{Hummer} \& {Storey}}{{Hummer} \&
+  {Storey}}{1987}]{Hummer1987}
+{Hummer} D.~G.,  {Storey} P.~J.,  1987, \mn@doi [\mnras]
+  {10.1093/mnras/224.3.801}, \href
+  {http://adsabs.harvard.edu/abs/1987MNRAS.224..801H} {224, 801}
+
+\bibitem[\protect\citeauthoryear{{Hunter}}{{Hunter}}{2007}]{matplotlib}
+{Hunter} J.~D.,  2007, \mn@doi [Computing in Science and Engineering]
+  {10.1109/MCSE.2007.55}, \href
+  {http://adsabs.harvard.edu/abs/2007CSE.....9...90H} {9, 90}
+
+\bibitem[\protect\citeauthoryear{{Izotov}, {Papaderos}, {Guseva}, {Fricke}  \&
+  {Thuan}}{{Izotov} et~al.}{2004}]{Izotov04}
+{Izotov} Y.~I.,  {Papaderos} P.,  {Guseva} N.~G.,  {Fricke} K.~J.,   {Thuan}
+  T.~X.,  2004, \mn@doi [\aap] {10.1051/0004-6361:20035847}, \href
+  {http://adsabs.harvard.edu/abs/2004A%26A...421..539I} {421, 539}
+
+\bibitem[\protect\citeauthoryear{James, Witten  \& Hastie}{James
+  et~al.}{2014}]{james2014introduction}
+James G.,  Witten D.,   Hastie T.,  2014, An Introduction to Statistical
+  Learning: With Applications in R.
+
+\bibitem[\protect\citeauthoryear{{Kennicutt}}{{Kennicutt}}{1998}]{Kennicutt98}
+{Kennicutt} Jr. R.~C.,  1998, \mn@doi [\araa] {10.1146/annurev.astro.36.1.189},
+  \href {http://adsabs.harvard.edu/abs/1998ARA%26A..36..189K} {36, 189}
+
+\bibitem[\protect\citeauthoryear{Kluyver et~al.,}{Kluyver
+  et~al.}{2016}]{jupyter}
+Kluyver T.,  et~al., 2016, in ELPUB. pp 87--90
+
+\bibitem[\protect\citeauthoryear{{Kova{\v c}}, {Somerville}, {Rhoads},
+  {Malhotra}  \& {Wang}}{{Kova{\v c}} et~al.}{2007}]{2007ApJ...668...15K}
+{Kova{\v c}} K.,  {Somerville} R.~S.,  {Rhoads} J.~E.,  {Malhotra} S.,   {Wang}
+  J.,  2007, \mn@doi [\apj] {10.1086/520668}, \href
+  {http://adsabs.harvard.edu/abs/2007ApJ...668...15K} {668, 15}
+
+\bibitem[\protect\citeauthoryear{{Laursen}, {Duval}  \& {{\"O}stlin}}{{Laursen}
+  et~al.}{2013}]{Laursen2013ApJ...766..124L}
+{Laursen} P.,  {Duval} F.,   {{\"O}stlin} G.,  2013, \mn@doi [\apj]
+  {10.1088/0004-637X/766/2/124}, \href
+  {http://adsabs.harvard.edu/abs/2013ApJ...766..124L} {766, 124}
+
+\bibitem[\protect\citeauthoryear{{Le F{\`e}vre} et~al.,}{{Le F{\`e}vre}
+  et~al.}{2003}]{2003SPIE.4841.1670L}
+{Le F{\`e}vre} O.,  et~al., 2003, in {Iye} M.,  {Moorwood} A.~F.~M.,  eds,
+  \procspie Vol. 4841, Instrument Design and Performance for Optical/Infrared
+  Ground-based Telescopes. pp 1670--1681, \mn@doi{10.1117/12.460959}
+
+\bibitem[\protect\citeauthoryear{{Loeb} \& {Rybicki}}{{Loeb} \&
+  {Rybicki}}{1999}]{LoebRybicki}
+{Loeb} A.,  {Rybicki} G.~B.,  1999, \mn@doi [\apj] {10.1086/307844}, \href
+  {http://adsabs.harvard.edu/abs/1999ApJ...524..527L} {524, 527}
+
+\bibitem[\protect\citeauthoryear{{Martin}}{{Martin}}{1998}]{1998ApJ...506..222M}
+{Martin} C.~L.,  1998, \mn@doi [\apj] {10.1086/306219}, \href
+  {http://adsabs.harvard.edu/abs/1998ApJ...506..222M} {506, 222}
+
+\bibitem[\protect\citeauthoryear{{Mas-Hesse}, {Kunth}, {Tenorio-Tagle},
+  {Leitherer}, {Terlevich}  \& {Terlevich}}{{Mas-Hesse}
+  et~al.}{2003}]{mashesse03}
+{Mas-Hesse} J.~M.,  {Kunth} D.,  {Tenorio-Tagle} G.,  {Leitherer} C.,
+  {Terlevich} R.~J.,   {Terlevich} E.,  2003, \mn@doi [\apj] {10.1086/379116},
+  \href {http://adsabs.harvard.edu/abs/2003ApJ...598..858M} {598, 858}
+
+\bibitem[\protect\citeauthoryear{{McKee} \& {Ostriker}}{{McKee} \&
+  {Ostriker}}{1977}]{1977ApJ...218..148M}
+{McKee} C.~F.,  {Ostriker} J.~P.,  1977, \mn@doi [\apj] {10.1086/155667}, \href
+  {http://esoads.eso.org/abs/1977ApJ...218..148M} {218, 148}
+
+\bibitem[\protect\citeauthoryear{McKinney et~al.}{McKinney
+  et~al.}{2010}]{pandas}
+McKinney W.,  et~al., 2010, in Proceedings of the 9th Python in Science
+  Conference. pp 51--56
+
+\bibitem[\protect\citeauthoryear{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{{Mej{\'{\i}}a-Restrepo} \&
+  {Forero-Romero}}{2016}]{2016ApJ...828....5M}
+{Mej{\'{\i}}a-Restrepo} J.~E.,  {Forero-Romero} J.~E.,  2016, \mn@doi [\apj]
+  {10.3847/0004-637X/828/1/5}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...828....5M} {828, 5}
+
+\bibitem[\protect\citeauthoryear{{Neufeld}}{{Neufeld}}{1991}]{1991ApJ...370L..85N}
+{Neufeld} D.~A.,  1991, \mn@doi [\apjl] {10.1086/185983}, \href
+  {http://adsabs.harvard.edu/abs/1991ApJ...370L..85N} {370, L85}
+
+\bibitem[\protect\citeauthoryear{{Noeske}, {Papaderos}, {Cair{\'o}s}  \&
+  {Fricke}}{{Noeske} et~al.}{2003}]{2003A&A...410..481N}
+{Noeske} K.~G.,  {Papaderos} P.,  {Cair{\'o}s} L.~M.,   {Fricke} K.~J.,  2003,
+  \mn@doi [\aap] {10.1051/0004-6361:20031147}, \href
+  {http://adsabs.harvard.edu/abs/2003A%26A...410..481N} {410, 481}
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}, {Baugh}  \& {Infante}}{{Orsi}
+  et~al.}{2008}]{2008MNRAS.391.1589O}
+{Orsi} A.,  {Lacey} C.~G.,  {Baugh} C.~M.,   {Infante} L.,  2008, \mn@doi
+  [\mnras] {10.1111/j.1365-2966.2008.14010.x}, \href
+  {http://adsabs.harvard.edu/abs/2008MNRAS.391.1589O} {391, 1589}
+
+\bibitem[\protect\citeauthoryear{{Orsi}, {Lacey}  \& {Baugh}}{{Orsi}
+  et~al.}{2012}]{Orsi12}
+{Orsi} A.,  {Lacey} C.~G.,   {Baugh} C.~M.,  2012, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2012.21396.x}, \href
+  {http://adsabs.harvard.edu/abs/2012MNRAS.425...87O} {425, 87}
+
+\bibitem[\protect\citeauthoryear{{{\"O}stlin} et~al.,}{{{\"O}stlin}
+  et~al.}{2014}]{LARS}
+{{\"O}stlin} G.,  et~al., 2014, \mn@doi [\apj] {10.1088/0004-637X/797/1/11},
+  \href {http://adsabs.harvard.edu/abs/2014ApJ...797...11O} {797, 11}
+
+\bibitem[\protect\citeauthoryear{{Ott}, {Walter}  \& {Brinks}}{{Ott}
+  et~al.}{2005}]{2005MNRAS.358.1453O}
+{Ott} J.,  {Walter} F.,   {Brinks} E.,  2005, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2005.08863.x}, \href
+  {http://adsabs.harvard.edu/abs/2005MNRAS.358.1453O} {358, 1453}
+
+\bibitem[\protect\citeauthoryear{{Padilla}, {Christlein}, {Gawiser},
+  {Gonz{\'a}lez}, {Guaita}  \& {Infante}}{{Padilla}
+  et~al.}{2010}]{2010MNRAS.409..184P}
+{Padilla} N.~D.,  {Christlein} D.,  {Gawiser} E.,  {Gonz{\'a}lez} R.~E.,
+  {Guaita} L.,   {Infante} L.,  2010, \mn@doi [\mnras]
+  {10.1111/j.1365-2966.2010.17317.x}, \href
+  {http://adsabs.harvard.edu/abs/2010MNRAS.409..184P} {409, 184}
+
+\bibitem[\protect\citeauthoryear{{Partridge} \& {Peebles}}{{Partridge} \&
+  {Peebles}}{1967}]{PartridgePeebles}
+{Partridge} R.~B.,  {Peebles} P.~J.~E.,  1967, \mn@doi [\apj] {10.1086/149079},
+  \href {http://adsabs.harvard.edu/abs/1967ApJ...147..868P} {147, 868}
+
+\bibitem[\protect\citeauthoryear{{Pasquini} et~al.,}{{Pasquini}
+  et~al.}{2002}]{2002Msngr.110....1P}
+{Pasquini} L.,  et~al., 2002, The Messenger, \href
+  {http://esoads.eso.org/abs/2002Msngr.110....1P} {110, 1}
+
+\bibitem[\protect\citeauthoryear{Pedregosa et~al.,}{Pedregosa
+  et~al.}{2011}]{scikit-learn}
+Pedregosa F.,  et~al., 2011, Journal of Machine Learning Research, 12, 2825
+
+\bibitem[\protect\citeauthoryear{P\'erez \& Granger}{P\'erez \&
+  Granger}{2007}]{IPython}
+P\'erez F.,  Granger B.~E.,  2007, \mn@doi [Computing in Science and
+  Engineering] {10.1109/MCSE.2007.53}, 9, 21
+
+\bibitem[\protect\citeauthoryear{{Poveda-Ruiz}, {Forero-Romero}  \&
+  {Mu{\~n}oz-Cuartas}}{{Poveda-Ruiz} et~al.}{2016}]{2016ApJ...832..169P}
+{Poveda-Ruiz} C.~N.,  {Forero-Romero} J.~E.,   {Mu{\~n}oz-Cuartas} J.~C.,
+  2016, \mn@doi [\apj] {10.3847/0004-637X/832/2/169}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...832..169P} {832, 169}
+
+\bibitem[\protect\citeauthoryear{{Prada}, {Klypin}, {Cuesta}, {Betancort-Rijo}
+  \& {Primack}}{{Prada} et~al.}{2012}]{2012MNRAS.423.3018P}
+{Prada} F.,  {Klypin} A.~A.,  {Cuesta} A.~J.,  {Betancort-Rijo} J.~E.,
+  {Primack} J.,  2012, \mn@doi [\mnras] {10.1111/j.1365-2966.2012.21007.x},
+  \href {http://adsabs.harvard.edu/abs/2012MNRAS.423.3018P} {423, 3018}
+
+\bibitem[\protect\citeauthoryear{{Pustilnik} \& {Martin}}{{Pustilnik} \&
+  {Martin}}{2007}]{pustilnikmartin07}
+{Pustilnik} S.~A.,  {Martin} J.-M.,  2007, \mn@doi [\aap]
+  {10.1051/0004-6361:20066137}, \href
+  {http://cdsads.u-strasbg.fr/abs/2007A%26A...464..859P} {464, 859}
+
+\bibitem[\protect\citeauthoryear{{Rivera-Thorsen} et~al.,}{{Rivera-Thorsen}
+  et~al.}{2015}]{2015ApJ...805...14R}
+{Rivera-Thorsen} T.~E.,  et~al., 2015, \mn@doi [\apj]
+  {10.1088/0004-637X/805/1/14}, \href
+  {http://adsabs.harvard.edu/abs/2015ApJ...805...14R} {805, 14}
+
+\bibitem[\protect\citeauthoryear{{Steidel}, {Erb}, {Shapley}, {Pettini},
+  {Reddy}, {Bogosavljevi{\'c}}, {Rudie}  \& {Rakic}}{{Steidel}
+  et~al.}{2010}]{2010ApJ...717..289S}
+{Steidel} C.~C.,  {Erb} D.~K.,  {Shapley} A.~E.,  {Pettini} M.,  {Reddy} N.,
+  {Bogosavljevi{\'c}} M.,  {Rudie} G.~C.,   {Rakic} O.,  2010, \mn@doi [\apj]
+  {10.1088/0004-637X/717/1/289}, \href
+  {http://adsabs.harvard.edu/abs/2010ApJ...717..289S} {717, 289}
+
+\bibitem[\protect\citeauthoryear{{Swaters}, {Sancisi}, {van Albada}  \& {van
+  der Hulst}}{{Swaters} et~al.}{2009}]{2009A&A...493..871S}
+{Swaters} R.~A.,  {Sancisi} R.,  {van Albada} T.~S.,   {van der Hulst} J.~M.,
+  2009, \mn@doi [\aap] {10.1051/0004-6361:200810516}, \href
+  {http://adsabs.harvard.edu/abs/2009A%26A...493..871S} {493, 871}
+
+\bibitem[\protect\citeauthoryear{{Tasitsiomi}}{{Tasitsiomi}}{2006}]{2006ApJ...645..792T}
+{Tasitsiomi} A.,  2006, \mn@doi [\apj] {10.1086/504460}, \href
+  {http://adsabs.harvard.edu/abs/2006ApJ...645..792T} {645, 792}
+
+\bibitem[\protect\citeauthoryear{{Tassis}, {Kravtsov}  \& {Gnedin}}{{Tassis}
+  et~al.}{2008}]{2008ApJ...672..888T}
+{Tassis} K.,  {Kravtsov} A.~V.,   {Gnedin} N.~Y.,  2008, \mn@doi [\apj]
+  {10.1086/523880}, \href {http://adsabs.harvard.edu/abs/2008ApJ...672..888T}
+  {672, 888}
+
+\bibitem[\protect\citeauthoryear{{Thuan} \& {Izotov}}{{Thuan} \&
+  {Izotov}}{1997}]{Thuan97}
+{Thuan} T.~X.,  {Izotov} Y.~I.,  1997, \apj, \href
+  {http://adsabs.harvard.edu/abs/1997ApJ...489..623T} {489, 623}
+
+\bibitem[\protect\citeauthoryear{{Tollerud}, {Bullock}, {Graves}  \&
+  {Wolf}}{{Tollerud} et~al.}{2011}]{2011ApJ...726..108T}
+{Tollerud} E.~J.,  {Bullock} J.~S.,  {Graves} G.~J.,   {Wolf} J.,  2011,
+  \mn@doi [\apj] {10.1088/0004-637X/726/2/108}, \href
+  {http://adsabs.harvard.edu/abs/2011ApJ...726..108T} {726, 108}
+
+\bibitem[\protect\citeauthoryear{{Trainor}, {Strom}, {Steidel}  \&
+  {Rudie}}{{Trainor} et~al.}{2016}]{Trainor16}
+{Trainor} R.~F.,  {Strom} A.~L.,  {Steidel} C.~C.,   {Rudie} G.~C.,  2016,
+  \mn@doi [\apj] {10.3847/0004-637X/832/2/171}, \href
+  {http://adsabs.harvard.edu/abs/2016ApJ...832..171T} {832, 171}
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Schaerer}  \&
+  {Maselli}}{{Verhamme} et~al.}{2006}]{2006A&A...460..397V}
+{Verhamme} A.,  {Schaerer} D.,   {Maselli} A.,  2006, \mn@doi [\aap]
+  {10.1051/0004-6361:20065554}, \href
+  {http://adsabs.harvard.edu/abs/2006A%26A...460..397V} {460, 397}
+
+\bibitem[\protect\citeauthoryear{{Verhamme}, {Orlitov{\'a}}, {Schaerer}  \&
+  {Hayes}}{{Verhamme} et~al.}{2015}]{2015A&A...578A...7V}
+{Verhamme} A.,  {Orlitov{\'a}} I.,  {Schaerer} D.,   {Hayes} M.,  2015, \mn@doi
+  [\aap] {10.1051/0004-6361/201423978}, \href
+  {http://adsabs.harvard.edu/abs/2015A%26A...578A...7V} {578, A7}
+
+\bibitem[\protect\citeauthoryear{Walt, Colbert  \& Varoquaux}{Walt
+  et~al.}{2011}]{numpy}
+Walt S. v.~d.,  Colbert S.~C.,   Varoquaux G.,  2011, Computing in Science \&
+  Engineering, 13, 22
+
+\bibitem[\protect\citeauthoryear{{Yamada}, {Matsuda}, {Kousai}, {Hayashino},
+  {Morimoto}  \& {Umemura}}{{Yamada} et~al.}{2012}]{2012ApJ...751...29Y}
+{Yamada} T.,  {Matsuda} Y.,  {Kousai} K.,  {Hayashino} T.,  {Morimoto} N.,
+  {Umemura} M.,  2012, \mn@doi [\apj] {10.1088/0004-637X/751/1/29}, \href
+  {http://adsabs.harvard.edu/abs/2012ApJ...751...29Y} {751, 29}
+
+\makeatother
+\end{thebibliography}
 

### 2017-09-01 paper/paper.tex
mas updates

@@
   M$_V$ & -17.6\\ 
-Redshift & $0.026\pm0.001$ \\\hline
+Redshift & $0.026\pm0.001$ \\
+2D half-light radius  & $1.5\pm 0.1$ kpc\\\hline
 \end{tabular}
@@
 \caption{Basic observational characteristics of \tol\ 
-  \citep{Thuan97}\label{obstable}} 
+  \citep{Thuan97}.
+The 2D half-light radius is
+computed from the results reported by \citet{2001AJ....121..169F}.
+\label{obstable}}
 \end{table}

### 2017-09-01 paper/paper.tex
complete new version updated referee reply

@@
 {\bf We argue that the results from the multiphase model 
-provides a correct interpretation of the data.
+provide a correct interpretation of the data.
 In that case the clump velocity dispersion implies a dynamical mass of
@@
 the multiphase model, it would provide additional support to expect
-such kinematic state in primordial \lya emitting galaxies {\bf which in
-turn can help to constrain star formation and feedback in the first
-generation of galaxies.}
+such kinematic state in primordial \lya emitting galaxies, opening
+{\bf the opportunity to constrain models of star formation and
+  feedback in the first generation of galaxies.}
 \end{abstract}
@@
 that the kinematics range from pure rotation and low velocity
-dispersion to high velocity dispersion without rotaion
+dispersion to high velocity dispersion without rotation
 \citep{2015A&A...577A..21C,2017A&A...600A.125C}. }
@@
 \cite{mashesse03}. This measurement was made with the Space Telescope
-Imaging Spectrograph on board the Hubble Space Telescope, these
-observations have a spectral resolution of $\sim 37$\kms\ at the
-\lya\ wavelength.
+Imaging Spectrograph on board the Hubble Space Telescope, with a
+spectral resolution of $\sim 37$\kms\ at the  \lya\ wavelength.
 
@@
 In order to map out this large parameter space, we randomly drew
-$2500$ sets of parameters within a observationally realistic range,
+$2500$ sets of parameters within an observationally realistic range,
 based on the considerations of \citet{Laursen2013ApJ...766..124L}, 
@@
 details on the explicit form of this approximation.
-To fully explore the
-parameter space using a Markov Chain Monte Carlo (MCMC) calculation with the
-\texttt{emcee} Python library \citep{2013PASP..125..306F}. \texttt{emcee} 
-is an open source optimized implementation of the affine-invariant 
-MCMC sampler \citep{goodman2010ensemble}. 
+To fully explore the parameter space we perform Markov Chain Monte
+Carlo (MCMC) calculations with the \texttt{emcee} Python library
+\citep{2013PASP..125..306F}. \texttt{emcee}  is an open source
+optimized implementation of the affine-invariant  MCMC sampler
+\citep{goodman2010ensemble}.  
 The algorithm creates a number of walkers that,
@@
 Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
-$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump.
+$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, {\bf
+  with the minimum $\chi^2/d.o.f.=11.7$.}
 
@@
 is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
-$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$.
+$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, {\bf where $\beta_{\rm cl}$ is
+the exponent defining the steepness of the radial velocity profile. }
 Furthermore, the relatively low mean number of clumps per line of
-sight, $f_{\mathrm{cl}}$, combined with the high velocity dispersion
+sight, $0.8<f_{\mathrm{cl}}<8$, combined with the high velocity dispersion
 of the clumps implies existence of low-density inter-clump 
@@
 Following the methodology of \citet{2011ApJ...726..108T} we estimate
-that a dark matter halo of $\sim 6\times 10^{11}$ M$_{\odot}$ in
-virial mass {\bf and virial radius $220$ kpc } could explain this dynamical mass.
+that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
+M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
 This estimate is based on computing the integrated mass profile of a
@@
 presented by \citet{2015A&A...577A..21C} on CDGs or \citet{Herenz16}
-onnearby \lya\ emitting galaxies.}
+on nearby \lya\ emitting galaxies.}
 
@@
   an NFW profile with
-  different viral masses as shown in the legend, the arrow corresponds
-  to the dynamical mass lower bounds for \tol.  
-  The dynamical mass estimates for \tol\ are consistent with the
+  different virial masses as shown in the legend. The circle corresponds
+  to the dynamical mass estimates for \tol.  
+  Under this conditions the dynamical mass estimates for \tol\ are consistent with the
   galaxy being hosted by a dark matter halo of
   $\sim 6\times10^{11}$ M$_{\odot}$ in mass.
-  {\bf Lower mass estimates could be possible if one considers instead a
-  cored profile. }
     \label{fig:mass}} 

### 2017-09-02 paper/paper.tex
latest

@@
 {\bf The hybrid case of a rotating multiphase configuration
+cannot be simulated with existing numerical implementations and 
 is the subject of ongoing research (Remolina-Gutierrez et al. in
-prep.)  as it cannot be simulated with existing models.  }
+prep.) }
 
@@
 
-\tol\ presents one of the most atypical \lya spectra observed so far.
+\tol\ presents an atypical \lya spectrum. 
 Its flux at the line's center is high compared to other LAEs at low
@@
 They observed nine BCGs to produce two-dimensional maps of the
-continuum and promiment emission lines, this allowed them to produce 
-two-dimensional velocitity field maps using the H$\alpha$ emission
-line.
+continuum and promiment emission lines to finally compute velocitity
+field maps using the H$\alpha$ emission line. 
 They find velocity fields ranging from simple rotation patterns 
@@
 \citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
-{\bf This estimate should be considered an upper bound, lower values
+{\bf This estimate should be considered an upper bound as lower values
   could be achieved if one considers instead a cored profile.}
@@
 In this particular case, we prefer the multiphase model because it has kinematic
-conditions similar to those in similar compact dwarf galaxies observed
+conditions similar to other compact dwarf galaxies observed
 with integral field unit spectroscopy, while the

### 2017-09-02 paper/paper.tex
latest paper

@@
 the multiphase model, it would provide additional support to expect
-such kinematic state in primordial \lya emitting galaxies, opening
-{\bf the opportunity to constrain models of star formation and
-  feedback in the first generation of galaxies.}
+such kinematic state in primordial galaxies, opening
+{\bf the opportunity to use the models and methods presented in this
+  paper to constrain the physics of star formation and feedback in the
+  early generation of \lya emitting galaxies.} 
 \end{abstract}
@@
 
-\tol\ is a compact star forming dwarf galaxy that presents a
+\tol\ is a compact dwarf galaxy (CDG) that presents a
 strong \lya emission with puzzling 
@@
 so far \citep{mashesse03,2015A&A...578A...7V}.
-This justifies a new study using two new physically motivated
-situations: a multiphase outflowing interstellar medium and bulk rotation for a
-galaxy without outflows.
-
-The main motivation for the outflowing multiphase model \citep[as presented
+
+{\bf Motivated by observations of other CDGs
+  that show gas kinematics ranging from pure rotation and low velocity
+dispersion to high velocity dispersion without rotation
+\citep{2015A&A...577A..21C,2017A&A...600A.125C} we perform here a new
+study to explain \tol's \lya emission features under two physical
+conditions for the interstellar medium: multiphase outflows and pure rotation.}
+
+Additional motivation for the outflowing multiphase model \citep[as presented
 in][]{Gronke2016} is that some dwarf galaxies are expected to
@@
 
-The motivation for the rotation without outflows 
+Further  motivation for the model of pure rotation without outflows 
 \citep[as presented in][]{GaravitoCamargo2014} is that dwarf galaxies show coherent
@@
 \citep{2005A&A...433L...1B,2008ApJ...672..888T,2013MNRAS.434.2491G}.
-
-{\bf Furthermore, observations of other Compact Dwarf Galaxies (CDGs) also show 
-that the kinematics range from pure rotation and low velocity
-dispersion to high velocity dispersion without rotation
-\citep{2015A&A...577A..21C,2017A&A...600A.125C}. }
 
@@
 models.
-{\bf The hybrid case of a rotating multiphase configuration
-cannot be simulated with existing numerical implementations and 
-is the subject of ongoing research (Remolina-Gutierrez et al. in
-prep.) }
 
@@
 over the rotation model.
-We close by discussing the additional observational information needed
-to clarify the kinematic nature of \tol.
 
@@
   \citep{Thuan97}.
-The 2D half-light radius is
-computed from the results reported by \citet{2001AJ....121..169F}.
+The 2D half-light radius is computed from the results reported by
+\citet{2003A&A...410..481N}.  
 \label{obstable}}
@@
 Due to the large fraction of \lya photons being emitted within the
-moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile follows 
-the clump kinematics. In other words, the width of the intrinsic line
+moving clumps ($P_{\rm cl}\sim 1$) the `intrinsic' profile closely follows 
+the clump kinematics. 
+In other words, the width of the intrinsic line
 is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
-$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, {\bf where $\beta_{\rm cl}$ is
-the exponent defining the steepness of the radial velocity profile. }
+$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, {\bf the exponent defining
+  the steepness of the radial velocity profile. } 
 Furthermore, the relatively low mean number of clumps per line of
@@
 future with, e.g., a higher sampling of the parameter space once new 
-observations  clarify the kinematic nature of \tol. 
-In Section \S \ref{sec:conclusions} we describe  in more detail what
-kind of observations could be performed in the near future to improve
-our understanding of \tol's kinematics.
+observations  yield more details on \tol's kinematic structure.
 
@@
 
-\tol\ presents an atypical \lya spectrum. 
+{\bf \tol\ presents a \lya emission line with puzzling fetures.}
 Its flux at the line's center is high compared to other LAEs at low
@@
 {\bf Which model could be closer to the actual kinematic conditions in \tol?  
-Recent Integral Field Unit (IFU) observations of other CDGs seem to
+Integral Field Unit (IFU) observations of other CDGs seem to
 favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
@@
 On the other hand the results from the multiphase model yield a
-velocity dispersion $\sigma=$\sigmaclump, quite close to observed
+velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with observed
 values in other CDG, favoring the multiphase model.}
@@
 we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
-for the HI region, in the multiphase model the clump velocity dispersion
-$\sigma_{\rm{cl}}=$\sigmaclump\  corresponds to a dynamical mass of
-$M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
-times the estimated baryonic mass in \tol.
-This would mean that \tol\ is dark matter dominated.
-
+for the HI region and that  $\sigma=\sigma_{\rm{cl}}=$\sigmaclump, we
+obtain a dynamical mass of  $M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$
+$M_{\odot}$, which is ten times the estimated baryonic mass in
+\tol.
+
+A larger dynamical mass estimate over its baryonic mass is a hint that
+\tol\ is dark matter dominated.  
 Following the methodology of \citet{2011ApJ...726..108T} we estimate
@@
 \citep{2012MNRAS.423.3018P,2016ApJ...832..169P}.  
-{\bf This estimate should be considered an upper bound as lower values
-  could be achieved if one considers instead a cored profile.}
 Figure \ref{fig:mass} shows the enclosed mass as a function of radius
@@
 mass estimate. 
-{\bf This estimate and the validity of its assumptions can only be
-  verified by detailed mass modelling once \tol's full rotation curve
-  becomes available.}
+{\bf This value should be considered an upper bound as lower values
+  could be achieved if one considers instead a cored profile.}
+{\bf More realistic mass estimates can only achieved by detailed mass
+  modelling once \tol's full rotation curve   becomes available.}
 
@@
 Spectrograph (FLAMES) \citep{2002Msngr.110....1P} as they have the spatial
-resolution and field of view required to perform the kind of study
-presented by \citet{2015A&A...577A..21C} on CDGs or \citet{Herenz16}
-on nearby \lya\ emitting galaxies.}
+resolution, spectral coverage and field of view required to produce
+H$\alpha$ velocity maps to perform the kind of study presented by
+\citet{2015A&A...577A..21C} on CDGs or \citet{Herenz16} on nearby
+\lya\ emitting galaxies.}
 
@@
 A confirmation of our results by new observations would support the multiphase model
-as an element to be included in the study of primordial \lya emitting
-galaxies.
+as an element to be included in the study of \lya emitting
+galaxies, {\bf consolidating the possibility to use the \lya line to
+  constrain different models of star formation and feedback in the
+  first generation of galaxies. }
 

### 2017-09-02 paper/paper.tex
latest paper

@@
 mass estimate. 
-{\bf This value should be considered an upper bound as lower values
+{\bf This should be considered an an upper bound as lower values
   could be achieved if one considers instead a cored profile.}
-{\bf More realistic mass estimates can only achieved by detailed mass
+{\bf Realistic mass estimates could only be achieved by detailed mass
   modelling once \tol's full rotation curve   becomes available.}

### 2017-09-02 paper/paper.tex
latest referee reply

@@
 
-{\bf \tol\ presents a \lya emission line with puzzling fetures.}
+{\bf \tol\ presents a \lya emission line with puzzling features.}
 Its flux at the line's center is high compared to other LAEs at low

### 2017-09-04 paper/paper.tex
minor typos

@@
 favored by \tol's observations. 
-A large proability of having \lya\ photons emitted in the clumps
+A large probability of having \lya\ photons emitted in the clumps
 makes radiative transfer effects, and therefore other parameters such
@@
 \citep{2003SPIE.4841.1670L}.
-The spatial smapling was $0.67^{\prime\prime}$ and covered about
+The spatial sampling was $0.67^{\prime\prime}$ and covered about
 $30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
 They observed nine BCGs to produce two-dimensional maps of the
-continuum and promiment emission lines to finally compute velocitity
+continuum and prominent emission lines to finally compute velocity
 field maps using the H$\alpha$ emission line. 

### 2017-09-05 paper/paper.tex
minor changes

@@
   that show gas kinematics ranging from pure rotation and low velocity
-dispersion to high velocity dispersion without rotation
+dispersion to high velocity dispersion without a clear rotation pattern
 \citep{2015A&A...577A..21C,2017A&A...600A.125C} we perform here a new
@@
 We use the results to interpret them in terms of the galaxy's
-dynamical mass and argue why the multiphase model should be preferred
-over the rotation model.
+dynamical mass and argue why in this case the multiphase model should
+be preferred over the rotation model.
 
@@
 $v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, {\bf
-  with the minimum $\chi^2/d.o.f.=11.7$.}
+  with the inimum $\chi^2/d.o.f.=11.7$.}
 
@@
 velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with observed
-values in other CDG, favoring the multiphase model.}
+values in other CDGs, favoring the multiphase model.}
 In this case we can  estimate a value for the dynamical
@@
 {\bf This should be considered an an upper bound as lower values
-  could be achieved if one considers instead a cored profile.}
+  could be achieved if one considers instead a cored DM profile.}
 {\bf Realistic mass estimates could only be achieved by detailed mass
-  modelling once \tol's full rotation curve   becomes available.}
+  modelling once \tol's detailed kinematic information becomes
+  available.}
 
@@
 Spectrograph (FLAMES) \citep{2002Msngr.110....1P} as they have the spatial
-resolution, spectral coverage and field of view required to produce
-H$\alpha$ velocity maps to perform the kind of study presented by
-\citet{2015A&A...577A..21C} on CDGs or \citet{Herenz16} on nearby
-\lya\ emitting galaxies.}
+resolution ($\sim0.5^{\prime\prime}$), spectral coverage and field
+of view required to produce H$\alpha$ velocity maps to perform the
+kind of study presented by \citet{2015A&A...577A..21C} on CDGs or by
+\citet{Herenz16} on nearby \lya\ emitting galaxies.}
 

### 2017-09-13 paper/paper.tex
minor changes

@@
 \title[An atypical \lya dwarf galaxy]{
-Modelling the gas kinematics of an atypical Lyman alpha emitting compact dwarf galaxy}
+Modelling the gas kinematics of an atypical Lyman-alpha emitting compact dwarf galaxy}
 \author[J.E. Forero-Romero et al.]
@@
 distant, relatively young, not primordial, galaxies \citep{1998ApJ...498L..93D}.
-Currently Lyman Alpha Emitting (LAE) galaxies are commonly targeted
+Currently Lyman Alpha Emitting galaxies (LAEs) are commonly targeted
 in surveys. 
@@
 emerging \lya line
-\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...645..792T}. 
+\citep{Harrington73,1991ApJ...370L..85N,LoebRybicki,2006ApJ...649...14D,2006ApJ...645..792T}. 
 They are applicable only in highly idealized conditions that
@@
 This can be explained as the results of multiple \lya photon
-scatterings through an outflowing shell of neutral Hydrogen
+scatterings through a homogeneous medium such as an (outflowing) shell of neutral Hydrogen
 \citep{2006A&A...460..397V,Orsi12,2012ApJ...751...29Y,2015ApJ...812..123G}.
@@
 luminosity and star formation rate of $9.1\times 10^{-43}$
-$L_{Ly\alpha}$ M$_{\odot}$ yr$^{-1}$ 
+$L_{\rm Ly\alpha} / (\mathrm{erg}\,\mathrm{s}^{-1})$ M$_{\odot}$ yr$^{-1}$ 
 without any
@@
 $v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, {\bf
-  with the inimum $\chi^2/d.o.f.=11.7$.}
+  with the minimum $\chi^2/d.o.f.=11.7$.}
 
@@
   {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}
+
+\bibitem[Dijkstra et al.(2006)]{2006ApJ...649...14D} Dijkstra, M., Haiman, Z., \& Spaans, M.\ 2006, \apj, 649, 14
 

### 2017-09-13 paper/paper.tex
additional boldface

@@
   the steepness of the radial velocity profile. } 
-Furthermore, the relatively low mean number of clumps per line of
-sight, $0.8<f_{\mathrm{cl}}<8$, combined with the high velocity dispersion
+{\bf Furthermore, the relatively low mean number of clumps per line of
+sight, $0.8<f_{\mathrm{cl}}<8$,} combined with the high velocity dispersion
 of the clumps implies existence of low-density inter-clump 

### 2017-09-13 paper/paper.tex
add SLAE

@@
 \citep{Thuan97}.
-This kind of profile also raises the question whether some high
+{\bf The existence of this Symmetric Lyman Alpha Emitter (SLAE)} raises the question whether some high
 redshift LAEs have asymmetric lines because the blue half was
@@
 simplicity of our models, this is the first time that the main
-\tol\ features can be reproduced: a broad, highly symmetric,
+\tol\ features of {\bf this SLAE} can be reproduced: a broad, highly symmetric,
 single-peaked \lya line.
@@
 Its flux at the line's center is high compared to other LAEs at low
-redshift and the broad, highly symmetrical peak is virtually absent from other
-LAEs at low and high redshift
+redshift and the broad, highly symmetrical peak.
+{\bf SLAEs are} virtually absent from other LAE surveys at low and high redshift
 \citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
@@
 
-All in all, the mere existence of a strong LAE galaxy with a broad,
-highly symmetric line is interesting. 
+All in all, the mere existence of {\bf a broad SLAE} is interesting.  
 \tol's line shape is different to others and seems to reveal an

### 2017-09-14 paper/paper.tex
minor changes

@@
 simplicity of our models, this is the first time that the main
-\tol\ features of {\bf this SLAE} can be reproduced: a broad, highly symmetric,
+features of {\bf this SLAE} can be reproduced: a broad, highly symmetric,
 single-peaked \lya line.

### 2017-09-15 paper/paper.tex
minor edtis

@@
 For the same reason, higher rotation velocities could produce a single
-peak but the line would be broader than it is observed.
+/eak but the line would be broader than it is observed.
 The fact that the velocity and optical depth priors were wide enough,
@@
 $30^{\prime\prime}\times 30^{\prime\prime}$ on the sky. 
-They observed nine BCGs to produce two-dimensional maps of the
+They observed nine Blue Compact Galaxies (BCGs) to produce two-dimensional maps of the
 continuum and prominent emission lines to finally compute velocity
@@
 mass estimate. 
-{\bf This should be considered an an upper bound as lower values
+{\bf This should be considered an upper bound as lower values
   could be achieved if one considers instead a cored DM profile.}
@@
 writing stages of this paper.
-We are thankful to the community developing and maintining open source
+We are thankful to the community developing and maintaining open source
 packages fundamental to our work: numpy \& scipy \citep{numpy}, the

### 2017-09-15 paper/paper.tex
peak!
as an

@@
 For the same reason, higher rotation velocities could produce a single
-/eak but the line would be broader than it is observed.
+peak but the line would be broader than it is observed.
 The fact that the velocity and optical depth priors were wide enough,
@@
 mass estimate. 
-{\bf This should be considered an upper bound as lower values
+{\bf This should be considered as an upper bound as lower values
   could be achieved if one considers instead a cored DM profile.}

### 2017-10-04 paper/paper.tex
all models are wrong but some are useful

@@
 evaded theoretical interpretation so far.  
-In this paper we explain these features by two different physically
-motivated kinematic models: 
+{\bf In this paper we reproduce for the first time these line features with two
+different physically motivated kinematic models: 
 an interstellar medium composed by outflowing clumps with 
 random motions and an homogeneous gaseous sphere undergoing solid body
-rotation.
-It is the first time that an observed \lya spectrum can be explained
-assuming either of these kinematic conditions.
+rotation.}
 The multiphase model requires a clump velocity dispersion of
@@
 bulk rotation velocity is constrained to be $348^{+75}_{-48}$ \kms.
-{\bf We argue that the results from the multiphase model 
+We argue that the results from the multiphase model 
 provide a correct interpretation of the data.
 In that case the clump velocity dispersion implies a dynamical mass of
-$2\times 10^{9}$ M$_{\odot}$,  ten times its baryonic mass.}
+$2\times 10^{9}$ M$_{\odot}$,  ten times its baryonic mass.
 If future kinematic maps of \tol\ confirm the velocities suggested by
@@
 such kinematic state in primordial galaxies, opening
-{\bf the opportunity to use the models and methods presented in this
+the opportunity to use the models and methods presented in this
   paper to constrain the physics of star formation and feedback in the
-  early generation of \lya emitting galaxies.} 
+  early generation of \lya emitting galaxies.
 \end{abstract}
@@
 \citep{Thuan97}.
-{\bf The existence of this Symmetric Lyman Alpha Emitter (SLAE)} raises the question whether some high
+The existence of this Symmetric Lyman Alpha Emitter (SLAE) raises the question whether some high
 redshift LAEs have asymmetric lines because the blue half was
@@
 
-{\bf Motivated by observations of other CDGs
+Motivated by observations of other CDGs
   that show gas kinematics ranging from pure rotation and low velocity
@@
 study to explain \tol's \lya emission features under two physical
-conditions for the interstellar medium: multiphase outflows and pure rotation.}
+conditions for the interstellar medium: multiphase outflows and pure rotation.
 
@@
 simplicity of our models, this is the first time that the main
-features of {\bf this SLAE} can be reproduced: a broad, highly symmetric,
+features of this SLAE can be reproduced: a broad, highly symmetric,
 single-peaked \lya line.
@@
 Under these conditions we find $\sigma_{\rm cl}=$\sigmaclump,
-$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, {\bf
-  with the minimum $\chi^2/d.o.f.=11.7$.}
+$v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, 
+  with the minimum $\chi^2/d.o.f.=11.7$. {\bf This relatively high value
+    could be interpreted as low statistical significance.
+However, we stress once more that this is the first time that the main
+features of \tol\ can be reproduced, making this model an useful tool
+to guide the interpretation of complex observational data.}
 
@@
 is set by $\sigma_{\mathrm{cl}}$ and its median offset mainly by
-$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, {\bf the exponent defining
-  the steepness of the radial velocity profile. } 
-{\bf Furthermore, the relatively low mean number of clumps per line of
-sight, $0.8<f_{\mathrm{cl}}<8$,} combined with the high velocity dispersion
+$v_{\infty,{\rm cl}}$ and $\beta_{\rm cl}$, the exponent defining
+  the steepness of the radial velocity profile. 
+Furthermore, the relatively low mean number of clumps per line of
+sight, $0.8<f_{\mathrm{cl}}<8$, combined with the high velocity dispersion
 of the clumps implies existence of low-density inter-clump 
@@
 
-{\bf \tol\ presents a \lya emission line with puzzling features.}
+\tol\ presents a \lya emission line with puzzling features.
 Its flux at the line's center is high compared to other LAEs at low
 redshift and the broad, highly symmetrical peak.
-{\bf SLAEs are} virtually absent from other LAE surveys at low and high redshift
+SLAEs are virtually absent from other LAE surveys at low and high redshift
 \citep{2012ApJ...751...29Y,LARS,Erb14,Trainor16}. 
@@
 
-{\bf Which model could be closer to the actual kinematic conditions in \tol?  
+Which model could be closer to the actual kinematic conditions in \tol?  
 Integral Field Unit (IFU) observations of other CDGs seem to
@@
 with the exception of one galaxy that shows a dispersion of $130$
-\kms. }
-
-{\bf These results disfavor the high rotational velocity of $V_{m}\sim350$
+\kms.
+
+These results disfavor the high rotational velocity of $V_{m}\sim350$
 \kms\  that we find in the pure rotation model. 
@@
 velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with observed
-values in other CDGs, favoring the multiphase model.}
+values in other CDGs, favoring the multiphase model.
 In this case we can  estimate a value for the dynamical
@@
 that a dark matter halo with a virial mass $\sim 6\times 10^{11}$
-M$_{\odot}$ {\bf and a virial radius $220$ kpc } could explain this dynamical mass.
+M$_{\odot}$ and a virial radius $220$ kpc could explain this dynamical mass.
 This estimate is based on computing the integrated mass profile of a
@@
 mass estimate. 
-{\bf This should be considered as an upper bound as lower values
-  could be achieved if one considers instead a cored DM profile.}
-{\bf Realistic mass estimates could only be achieved by detailed mass
+This should be considered as an upper bound as lower values
+  could be achieved if one considers instead a cored DM profile.
+Realistic mass estimates could only be achieved by detailed mass
   modelling once \tol's detailed kinematic information becomes
-  available.}
-
-{\bf New IFU observations are needed to confirm \tol's kinematics.
+  available.
+
+New IFU observations are needed to confirm \tol's kinematics.
 This could be done with the Multi Unit Spectroscopic Explorer (MUSE) 
@@
 kind of study presented by \citet{2015A&A...577A..21C} on CDGs or by
-\citet{Herenz16} on nearby \lya\ emitting galaxies.}
+\citet{Herenz16} on nearby \lya\ emitting galaxies.
 
@@
 
-All in all, the mere existence of {\bf a broad SLAE} is interesting.  
+All in all, the mere existence of a broad SLAE is interesting.  
 \tol's line shape is different to others and seems to reveal an
@@
 as an element to be included in the study of \lya emitting
-galaxies, {\bf consolidating the possibility to use the \lya line to
+galaxies, consolidating the possibility to use the \lya line to
   constrain different models of star formation and feedback in the
-  first generation of galaxies. }
+  first generation of galaxies.
 

### 2017-10-04 paper/paper.tex
latest

@@
 dispersion to high velocity dispersion without a clear rotation pattern
-\citep{2015A&A...577A..21C,2017A&A...600A.125C} we perform here a new
-study to explain \tol's \lya emission features under two physical
+\citep{2015A&A...577A..21C,2017arXiv170809407C,2017A&A...600A.125C}
+we perform here a new study to explain \tol's \lya emission features under two physical
 conditions for the interstellar medium: multiphase outflows and pure rotation.
@@
   with the minimum $\chi^2/d.o.f.=11.7$. {\bf This relatively high value
-    could be interpreted as low statistical significance.
-However, we stress once more that this is the first time that the main
+    for the reduced $\chi^2$ could be interpreted as low statistical
+    significance. 
+However, we stress once more that the is the first time that the main
 features of \tol\ can be reproduced, making this model an useful tool
-to guide the interpretation of complex observational data.}
+to guide the interpretation of complex observational data. 
+These results certainly open up the path to future searches to
+construct new models.}
 
@@
 Integral Field Unit (IFU) observations of other CDGs seem to
-favor the multiphase model \citep{2015A&A...577A..21C,2017A&A...600A.125C}. 
+favor the multiphase model \citep{2015A&A...577A..21C,2017arXiv170809407C,2017A&A...600A.125C}.
 These observations  were performed with the Visible Multi-Object Spectrograph (VIMOS)
@@
 the other on gas bulk solid body rotation. 
-It is the first time that an observed \lya profile can be fully
+It is the first time that an observed \lya profile can be 
 reproduced by either of these two kinematic conditions.
@@
 \bibliographystyle{mnras}
-%\bibliography{references}
 \begin{thebibliography}{}
@@
   {Gonz{\'a}lez-P{\'e}rez}}{{Cair{\'o}s} \&
-  {Gonz{\'a}lez-P{\'e}rez}}{2017}]{2017A&A...600A.125C}
-{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017, \mn@doi [\aap]
+  {Gonz{\'a}lez-P{\'e}rez}}{2017a}]{2017arXiv170809407C}
+{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017a, preprint, \href
+  {http://adsabs.harvard.edu/abs/2017arXiv170809407C} {} (\mn@eprint {arXiv}
+  {1708.09407})
+
+\bibitem[\protect\citeauthoryear{{Cair{\'o}s} \&
+  {Gonz{\'a}lez-P{\'e}rez}}{{Cair{\'o}s} \&
+  {Gonz{\'a}lez-P{\'e}rez}}{2017b}]{2017A&A...600A.125C}
+{Cair{\'o}s} L.~M.,  {Gonz{\'a}lez-P{\'e}rez} J.~N.,  2017b, \mn@doi [\aap]
   {10.1051/0004-6361/201629681}, \href
@@
   {http://adsabs.harvard.edu/abs/1998ApJ...498L..93D} {498, L93}
-
-\bibitem[Dijkstra et al.(2006)]{2006ApJ...649...14D} Dijkstra, M., Haiman, Z., \& Spaans, M.\ 2006, \apj, 649, 14
 
@@
 \end{thebibliography}
+
+%\bibliography{references}
 

### 2017-10-05 paper/paper.tex
submitted

@@
 
-Qualitatively this result can be understood as follows.
+The results from this model can be qualitatively explained as follows.
 Due to the large fraction of \lya photons being emitted within the
@@
 regions where \lya photons can freely propagate.
-This gives result to an emergent spectrum close to the intrinsic one, explaining the high
-flux at the line's center.
+This gives result to an emergent spectrum close to the intrinsic one,
+explaining the high flux at the line's center.
 
@@
 On the other hand the results from the multiphase model yield a
-velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with observed
-values in other CDGs, favoring the multiphase model.
-In this case we can  estimate a value for the dynamical
-mass using the constraints for the velocity dispersion, $\sigma$,  in
-a spherical system localized in a region of size $r$
+velocity dispersion $\sigma_{\rm cl}=$\sigmaclump, consistent with
+other observations.
+We can now estimate a value for the dynamical mass using the
+constraints for the velocity dispersion, $\sigma$,  in a spherical
+system localized in a region of size $r$
 
@@
 we use the 3D half-light radius $r_s=2.25$ kpc as the typical size
-for the HI region and that  $\sigma=\sigma_{\rm{cl}}=$\sigmaclump, we
-obtain a dynamical mass of  $M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$
-$M_{\odot}$, which is ten times the estimated baryonic mass in
-\tol.
-
-A larger dynamical mass estimate over its baryonic mass is a hint that
+for the HI region. 
+With $\sigma=\sigma_{\rm{cl}}=$\sigmaclump we obtain a dynamical mass
+of  $M_{\rm dyn}=2.31\pm0.04 \times 10^{9}$ $M_{\odot}$, which is ten
+times the estimated baryonic mass in \tol.
+
+A larger dynamical mass estimate over its baryonic mass hints that
 \tol\ is dark matter dominated.  

### 2017-10-10 paper/paper.tex
remove boldface

@@
 evaded theoretical interpretation so far.  
-{\bf In this paper we reproduce for the first time these line features with two
+In this paper we reproduce for the first time these line features with two
 different physically motivated kinematic models: 
@@
 random motions and an homogeneous gaseous sphere undergoing solid body
-rotation.}
+rotation.
 The multiphase model requires a clump velocity dispersion of
@@
 $v_{\infty {\rm, cl}}=$\inftyclump\ and $P_{\rm cl}=$\probaclump, 
-  with the minimum $\chi^2/d.o.f.=11.7$. {\bf This relatively high value
+  with the minimum $\chi^2/d.o.f.=11.7$. This relatively high value
     for the reduced $\chi^2$ could be interpreted as low statistical
@@
 These results certainly open up the path to future searches to
-construct new models.}
+construct new models.
 
